### 2017-06-14 Tex/Paper.tex
Initial template

%%
%%  Beam Loading Paper '17'
%% ***************************
%%  Veronica K. Berglyd Olsen
%%

\documentclass[aps,prstab,reprint,groupedaddress]{revtex4-1}

% ************************************************************************************************ %
\begin{document}
% ************************************************************************************************ %

\title{Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield}

\author{Veronica K. Berglyd Olsen}
\email[]{v.k.b.olsen@cern.ch}

\author{Erik Adli}
\affiliation{University of Oslo, Oslo, Norway}

\author{Patric Muggli}
\affiliation{Max Planck Institute for Physics, Munich, Germany}
\affiliation{CERN, Geneva, Switzerland}

\date{\today}

\begin{abstract}
We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear plasma wakefield driven by a short proton beam. The structure of the wakefield is similar to that of a long, modulated proton beam. By selecting transverse and longitudinal electron beam parameters in order to  appropriately load of the wake, we show that the bulk of the electron beam can be accelerated without significant emittance growth.
\end{abstract}

\maketitle

\section[\label{S:I}]{Introduction}

- interested from SMI/AWAKE \\
- requirements for AWAKE Run 2 \\

\section[\label{S:M}]{Method}

- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
- simulation setup PIC/quickpic OS \\

\section[\label{S:BL}]{Beam loading}

- discussion of the main physics and results; beam loading, bubble creation, emittance preservation \\

\section[\label{S:D}]{Discussion}
\section[\label{S:C}]{Conclusion}

- discussion of optimal electron beam parameters \\
- implications for AWAKE Run 2 \\

\bibliography{Bibliography}

% ************************************************************************************************ %
\end{document}
% ************************************************************************************************ %

### 2017-06-18 Tex/Paper.tex
Fixed compiling issues and added some text

@@
 \section[\label{S:M}]{Method}
+%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
+%- simulation setup PIC/quickpic OS \\
 
-- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
-- simulation setup PIC/quickpic OS \\
+Initial beam loading studies were done using the full PIC code Osiris \cite{fonseca_osiris:_2002}.
+these simulations were done using a short, pre.dodulated prton drive bunch.
+That is, we applied a clipped cosine function to the longitudinal density profile of the proton beam, with a period matching the wavelength, $\lambda_p$, of the plasma.
+
+\subsection[\label{S:M:Setup}]{Simulationn Setup}
 

### 2017-06-21 Tex/Paper.tex
Added more text

--- 2017-06-14 Tex/Paper.tex
@@
 - requirements for AWAKE Run 2 \\
+The preliminary design of AWAKE Run 2 will split the plasma cell into two sections.
+The first section of 4m is the SMI stage.
+The electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur.
+As the $e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible \cite{adli_towards_2016}.
 
 \section[\label{S:M}]{Method}
+%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
+%- simulation setup PIC/quickpic OS \\
 
-- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
-- simulation setup PIC/quickpic OS \\
+The main focus of this study has been on the beam loading of the electron beam.
+In order to eliminate other factors that may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies [citations].
+
+Our first approach was to use a premodulated, short proton beam with the same structure as a section of the full AWAKE proton drive beam.
+These studies were done using the full PIC code Osiris \cite{fonseca_osiris:_2002} using 2D cylindrical-symetric simulations.
+The proton beam was pre-modulated by a clipped cosine function to the longitudinal density profile, with a period matching the wavelength, $\lambda_p$, of the plasma.
+The length was limited to $26\cdot\lambda_p$, and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen_loading_2015}.
+We performed several parameter scans with this setup, testing for optimal charge as well as beam length \cite{adli_towards_2016, berglyd_olsen_loading_2016}.
+
+[Add something about the optimal results]
+
+In order to evaluate the quality of the beam, we also needed to study its emittance.
+Full PIC codes like Osiris are voulnerable to numerical growth of emittance caused by what is usually referred to as the ``ǹumerical Cherenkov effect'' \cite{godfrey_numerical_1974}.
+The effect is caused by the EMF solver which will cause the phase velocity of electromagnetic fields to be lowet than $c$, while the beam moves very close to $c$.
+The effect can be mitigated somewhat by a the Lehe solver \cite{lehe_numerical_2013}, but the effect is still prominent in the the high density regions of the electron beam.
+
+\subsection[\label{S:M:Setup}]{Simulationn Setup}
 

### 2017-06-22 Tex/Paper.tex
Modified bibliography format and added some text

--- 2017-06-14 Tex/Paper.tex
@@
 %%
-%%  Beam Loading Paper '17'
+%%  Beam Loading Paper '17
 %% ***************************
@@
 
-\documentclass[aps,prstab,reprint,groupedaddress]{revtex4-1}
+\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
+\bibliographystyle{apsrev}
 
@@
 
-- interested from SMI/AWAKE \\
-- requirements for AWAKE Run 2 \\
+% interested from SMI/AWAKE
+% requirements for AWAKE Run 2
+
+The preliminary design of AWAKE Run 2 will split the plasma cell into two sections.
+The first section of 4m is the SMI stage.
+The electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur.
+As the $e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible \cite{adli:2016}.
 
 \section[\label{S:M}]{Method}
+%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers
+%- simulation setup PIC/quickpic OS
 
-- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers \\
-- simulation setup PIC/quickpic OS \\
+The main focus of this study has been on the beam loading of the electron beam.
+In order to eliminate other factors that may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies [citations].
+
+Our first approach was to use a premodulated, short proton beam with the same structure as a section of the full AWAKE proton drive beam.
+These studies were done using the full PIC code Osiris \cite{fonseca:2002} using 2D cylindrical-symetric simulations.
+The proton beam was pre-modulated by a clipped cosine function to the longitudinal density profile, with a period matching the wavelength, $\lambda_p$, of the plasma.
+The length was limited to $26\cdot\lambda_p$, and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}.
+We performed several parameter scans with this setup, testing for optimal charge as well as beam length \cite{adli:2016, berglyd_olsen:2016}.
+
+[Add something about the optimal results]
+
+In order to evaluate the quality of the beam, we also needed to study its emittance.
+Full PIC codes like Osiris are voulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
+This is a know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$, while the beam moves very close to $c$.
+The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but the effect is still prominent in the the high density regions of the electron beam.
+
+In order to study the emittance evolution of the beam we used QuickPIC, a fully relativistic 3D PIC code \cite{huang:2006, an:2013}.
+
+\subsection[\label{S:M:Setup}]{Simulationn Setup}
 
@@
 
-- discussion of the main physics and results; beam loading, bubble creation, emittance preservation \\
+% discussion of the main physics and results; beam loading, bubble creation, emittance preservation
 
@@
 
-- discussion of optimal electron beam parameters \\
-- implications for AWAKE Run 2 \\
+% discussion of optimal electron beam parameters
+% implications for AWAKE Run 2
 

### 2017-07-05 Tex/Paper.tex
Updates
Added line endings

@@
 
-% ************************************************************************************************ %
+% ******************************************************************************************************************** %
 \begin{document}
-% ************************************************************************************************ %
+% ******************************************************************************************************************** %
 
@@
 \begin{abstract}
-We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear plasma wakefield driven by a short proton beam.
-The structure of the wakefield is similar to that of a long, modulated proton beam.
-By selecting transverse and longitudinal electron beam parameters in order to  appropriately load of the wake, we show that the bulk of the electron beam can be accelerated without significant emittance growth.
+We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear
+plasma wakefield driven by a short proton beam. The structure of the wakefield is similar to that of a long, modulated
+proton beam. By selecting transverse and longitudinal electron beam parameters in order to  appropriately load of the
+wake, we show that the bulk of the electron beam can be accelerated without significant emittance growth.
 \end{abstract}
@@
 
-The preliminary design of AWAKE Run 2 will split the plasma cell into two sections.
-The first section of 4m is the SMI stage.
-The electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur.
-As the $e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible \cite{adli:2016}.
+The preliminary design of AWAKE Run 2 proposes to use two plasma sections. The first section of 4m is the SMI stage. The
+electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
+$e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible
+\cite{adli:2016}.
 
@@
 
-The main focus of this study has been on the beam loading of the electron beam.
-In order to eliminate other factors that may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies [citations].
+The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors that
+may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies
+[citations].
 
-Our first approach was to use a premodulated, short proton beam with the same structure as a section of the full AWAKE proton drive beam.
-These studies were done using the full PIC code Osiris \cite{fonseca:2002} using 2D cylindrical-symetric simulations.
-The proton beam was pre-modulated by a clipped cosine function to the longitudinal density profile, with a period matching the wavelength, $\lambda_p$, of the plasma.
-The length was limited to $26\cdot\lambda_p$, and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}.
-We performed several parameter scans with this setup, testing for optimal charge as well as beam length \cite{adli:2016, berglyd_olsen:2016}.
+Our first approach was to use a premodulated, short proton beam with the same structure as a section of the full AWAKE
+proton drive beam. These studies were done using the full PIC code Osiris \cite{fonseca:2002} using 2D
+cylindrical-symetric simulations. The proton beam was pre-modulated by a clipped cosine function to the longitudinal
+density profile, with a period matching the wavelength, $\lambda_p$, of the plasma. The length was limited to
+$26\cdot\lambda_p$, and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed
+several parameter scans with this setup, testing for optimal charge as well as beam length
+\cite{adli:2016, berglyd_olsen:2016}.
 
@@
 
-In order to evaluate the quality of the beam, we also needed to study its emittance.
-Full PIC codes like Osiris are voulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
-This is a know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$, while the beam moves very close to $c$.
-The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but the effect is still prominent in the the high density regions of the electron beam.
+In order to evaluate the quality of the beam, we also needed to study its emittance. Full PIC codes like Osiris are
+voulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
+know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$,
+while the beam moves very close to $c$. The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but
+the effect is still prominent in the the high density regions of the electron beam.
 
-In order to study the emittance evolution of the beam we used QuickPIC, a fully relativistic 3D PIC code \cite{huang:2006, an:2013}.
+In order to study the emittance evolution of the beam we used QuickPIC, a fully relativistic 3D PIC code
+\cite{huang:2006, an:2013}.
 
@@
 
-% ************************************************************************************************ %
+% ******************************************************************************************************************** %
 \end{document}
-% ************************************************************************************************ %
+% ******************************************************************************************************************** %

### 2017-07-06 Tex/Paper.tex
Added comments from Patric and Erik

@@
 % ******************************************************************************************************************** %
+
+%~ Eric's Comments
+%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
+%~   unloaded wake)
+%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
+%~   flatten and energy spread reduced [well known result, Tzoufras] 
+%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
+%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
+%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
+%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
+%~   electron densities etc. )
+%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
+%~   longitudinal phase spaces, space long simulation)
+%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
+%~   show: transverse and longitudinal phase spaces, long offset simulation)
+%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
+%~ beam, and preferably some scalings]
+%~ - how to select electron beam parameters:
+%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
+%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
+%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
+%~ (- plasma density?)
+
+%~ Patric's Comments
+%~ - Self-modulation as a driver
+%~ - SM does not reach blow out
+%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
+%~   not desirable
+%~ - Beam loading for narrow energy spread
+%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
+%~   (Tzoufras) well know
+%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
+%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
+%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
+%~   bunch and the SM
+%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
+%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
+%~ As for N+2, I am a firm supporter of on-axis injection ... and most of the issue with that has to do with the plasma
+%~ ramp, otherwise it would be a non-issue (assuming of course that one can split the plasma in two sections). It is in
+%~ itself a topic of research, so I think we can only state a few things ...
 
@@
 plasma wakefield driven by a short proton beam. The structure of the wakefield is similar to that of a long, modulated
-proton beam. By selecting transverse and longitudinal electron beam parameters in order to  appropriately load of the
-wake, we show that the bulk of the electron beam can be accelerated without significant emittance growth.
+proton beam. By selecting transverse and longitudinal electron beam parameters in order to appropriately load the wake,
+we show that the bulk of the electron beam can be accelerated without significant emittance growth.
 \end{abstract}
@@
 
-\section[\label{S:BL}]{Beam loading}
+\section[\label{S:BL}]{Beam Loading}
 
-% discussion of the main physics and results; beam loading, bubble creation, emittance preservation
+%~ Eric's Comments
+%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+
+%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
+%~   unloaded wake)
+The structure of the single drive beam set-up behaves similarly to the self-modulated case. However, since the drive
+beam is prevented from significant evolution in this simulation set-up, we are presented with an idealised case where
+the electron witness beam sees consistent fields.
+
+%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
+%~   flatten and energy spread reduced [well known result, Tzoufras]
+
+%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
+%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
+%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
+%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
+%~   electron densities etc. )
+%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
+%~   longitudinal phase spaces, space long simulation)
+%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
+%~   show: transverse and longitudinal phase spaces, long offset simulation)
+
+\section[\label{S:PO}]{Parameter Optimisation}
+
+%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
+%~ beam, and preferably some scalings]
+%~ - how to select electron beam parameters:
+%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
+%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
+%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
+%~ (- plasma density?)
 

### 2017-07-06 Tex/Paper.tex
Added text and made some layout updates

@@
 \documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
-\bibliographystyle{apsrev}
+\bibliographystyle{apsrev4-1}
+\usepackage{hyperref}
+\hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}
 
@@
 In order to evaluate the quality of the beam, we also needed to study its emittance. Full PIC codes like Osiris are
-voulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
+vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
 know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$,
@@
 
-\subsection[\label{S:M:Setup}]{Simulationn Setup}
+\subsection[\label{S:M:Setup}]{Simulation Setup}
+
+In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
+see from the self-modulated SPS beam. This was done both to reduce simulation time, as we run 3D simulations, and to
+create a stable environment for the witness beam.
 
@@
 %~   electron densities etc. )
+
 %~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
 %~   longitudinal phase spaces, space long simulation)
+
 %~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to

### 2017-07-07 Tex/Paper.tex
Daily commit

@@
 \hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}
+
+% Custom Commands
+%*****************
+
+% Text
+%~ \newcommand{\eq}[1]{Eq. \ref{#1}}
+%~ \newcommand{\fig}[1]{Fig. \ref{#1}}
+%~ \newcommand{\tbl}[1]{Table \ref{#1}}
+
+% Math
+\newcommand{\unit}[1]{\,\mathrm{#1}}
+\newcommand{\funit}[2]{\,\mathrm{#1}/\mathrm{#2}}
+\newcommand{\mexp}[1]{\mathrm{e}^{#1}}
+\newcommand{\nexp}[1]{\times 10^{#1}}
 
@@
 
-\subsection[\label{S:M:Setup}]{Simulation Setup}
+\subsection[\label{S:M:Setup}]{Drive Beam Parameters}
 
 In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
-see from the self-modulated SPS beam. This was done both to reduce simulation time, as we run 3D simulations, and to
-create a stable environment for the witness beam.
+see from the self-modulated SPS beam in AWAKE. The baseline AWAKE drive beam contains $3\nexp{11}$ protons
+\cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded in the
+middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during self-modulation. The
+needed gap between the two plasma cells also contributes to a decreased density of protons near the axis, and some of
+the field is drained by other protons seeing an accelerating face within the drive beam. In total, the expected peak
+$E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in the second cell
+\cite{awake_collaboration:2016}. A single proton beam of $1.46\nexp{10}$, or $2.34\unit{nC}$ and $7\unit{kA}$, is needed
+to drive an $E_{z}$ field of a comparable magnitude.
+
+The single bunch approach was chosen to reduce simulation time for the 3D simulations, and to create a stable
+environment for the witness beam. We are not considering the evolution of the proton beam in this test setup, so to
+prevent the proton beam from evolving radially, we increased its mass.
+
+The basline AWAKE drive beam current is insufficient to produce a plasma bubble. The plasma electrons are depleted to
+around $65\%$ of nominal plasma density at the injection point of the electron beam. This condition is replicated in out
+single bunch case. The single bunch setup also uses the baseline proton energy $W_{pb} = 400\unit{GeV}$.
+
+\subsection[\label{S:M:Setup}]{Witness Beam Parameters}
+
+The witness beam in our simulation differs from AWAKE baseline parameters on several key points. Initial beam energy is
+set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This is to eliminate the problem of initial de-phasing of the witness
+beam. AWAKE baseline witness beam energy for Run 1 is $W_{eb} = 10-20\unit{MeV}$ \cite{gschwendtner:2016}. Beam loading
+of a short witness beam is sensitive to initial position. AWAKE Run 2 will likely require a higher initial energy, but a
+$W_{eb} = 30--50\unit{MeV}$ is sufficient to minimise de-phasing \cite{berglyd_olsen:2015}. For this case we have
+eliminated it entirely in order to reduce the number of variables in our parameter scans.
+
+Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ causes the beam radius to rapidly shrink as the
+beam enters the plasma \cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma
+density. The relation is given by
+\begin{align}
+    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+\end{align}
+where $\lambda_{p}$ is the plasma wavelength.
 
@@
 %~   unloaded wake)
-The structure of the single drive beam set-up behaves similarly to the self-modulated case. However, since the drive
-beam is prevented from significant evolution in this simulation set-up, we are presented with an idealised case where
+The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
+beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
 the electron witness beam sees consistent fields.

### 2017-07-11 Tex/Paper.tex
Added some figures, and addes SVG support in makefile

@@
 \bibliographystyle{apsrev4-1}
+
 \usepackage{hyperref}
 \hypersetup{colorlinks=true, citecolor=blue, urlcolor=blue, linkcolor=blue}
+
+\usepackage{graphicx}
 
@@
 \end{align}
-where $\lambda_{p}$ is the plasma wavelength.
+where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
+$2$ and $6\unit{\mu m}$.
 
@@
 %~   unloaded wake)
+
 The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
@@
 
+\begin{figure}
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
+    \label{Fig:BeamLoading}
+    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
+        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
+        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of plasma density
+        $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
+\end{figure}
+
 %~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
 %~   flatten and energy spread reduced [well known result, Tzoufras]
+
+\begin{figure}
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
+    \label{Fig:PlasmaDenTWake}
+    \caption{}
+\end{figure}
 

### 2017-07-12 Tex/Paper.tex
Updated plots
Some cleanup and plot fix

@@
 
+% ******************************************************************************************************************** %
 \section[\label{S:I}]{Introduction}
-
 % interested from SMI/AWAKE
 % requirements for AWAKE Run 2
+% ******************************************************************************************************************** %
 
@@
 
+% ******************************************************************************************************************** %
 \section[\label{S:M}]{Method}
@@
 %- simulation setup PIC/quickpic OS
+% ******************************************************************************************************************** %
 
@@
 
+% ******************************************************************************************************************** %
 \subsection[\label{S:M:Setup}]{Drive Beam Parameters}
+% ******************************************************************************************************************** %
 
@@
 
+% ******************************************************************************************************************** %
 \subsection[\label{S:M:Setup}]{Witness Beam Parameters}
+% ******************************************************************************************************************** %
 
@@
 
+% ******************************************************************************************************************** %
 \section[\label{S:BL}]{Beam Loading}
-
 %~ Eric's Comments
 %~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+% ******************************************************************************************************************** %
+
+\begin{figure}[hbt]
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
+    \label{Fig:BeamLoading}
+    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
+        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
+        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of initial plasma
+        density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$. The bottom plot shows the plasma density for the loaded and
+        unloaded case. The plasma depletion region behind the proton bunch has a minimum of $67.4\%$ of $n_{0}$. }
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
+    \label{Fig:PlasmaDenTWake}
+    \caption{The plasma density in grey with the proton beam (blue) and the electron beam (red) superimposed. The line
+        plot indicates the transverse wakefield $W_{x}(\xi,x) = E_{\xi}(z,x) - B_{y}(\xi,x)$ evaluated at
+        $+1\sigma_{eb}$ from the axis.}
+\end{figure}
 
@@
 
-\begin{figure}
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
-    \label{Fig:BeamLoading}
-    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
-        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
-        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of plasma density
-        $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
-\end{figure}
-
 %~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
 %~   flatten and energy spread reduced [well known result, Tzoufras]
-
-\begin{figure}
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
-    \label{Fig:PlasmaDenTWake}
-    \caption{}
-\end{figure}
 
@@
 
+% ******************************************************************************************************************** %
 \section[\label{S:PO}]{Parameter Optimisation}
-
 %~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
@@
 %~ (- plasma density?)
+% ******************************************************************************************************************** %
 
+% ******************************************************************************************************************** %
 \section[\label{S:D}]{Discussion}
+% ******************************************************************************************************************** %
+
+% ******************************************************************************************************************** %
 \section[\label{S:C}]{Conclusion}
-
 % discussion of optimal electron beam parameters
 % implications for AWAKE Run 2
-
-\bibliography{Bibliography}
+% ******************************************************************************************************************** %
 
 % ******************************************************************************************************************** %
+\bibliography{Bibliography}
 \end{document}

### 2017-07-12 Tex/Paper.tex
Additions

@@
 electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
-$e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible
+$e_z$ field will decrease due to the gap between the two cells, it is desirable to keep this as short as possible
 \cite{adli:2016}.
+
+% ******************************************************************************************************************** %
+\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
+%~ Patric's Comments
+%~ - Self-modulation as a driver
+%~ - SM does not reach blow out
+%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
+%~   not desirable
+% ******************************************************************************************************************** %
+
+A train of electron drive bunches with a separation $\lambda_{p}$ and a length $l_{b} \ll \lambda_{p}$, where
+$\lambda_{p} = 2\pi c/\omega_{p}$ and $\omega_{p} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$, will drive an
+increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak accelerating
+phase of this field will quickly gain energy from the wakefield. However, electron drive bunches will quickly lose
+energy to the plasma, and the accelerating witness beam will eventually catch up with the drive beam and the
+acceleration stop.
+
+The de-phasing problem can be minimised by instead using a proton drive bunch \cite{caldwell:2009}. Proton beams, like
+the LHC and SPS beams at CERN, are ideal candidates for such an accelerator; however, they are orders of magnitude
+longer than the plasma wavelengths needed for such applications. This issue is resolved by letting the proton beam
+undergo self-modulation, an instability caused by the transverse fields generated by the beam acts upon itself causing
+regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma,
+leaving a train of proton bunches along the beam axis.
+
+The AWAKE experiment currently in its first stages of operation at CERN, uses the SPS beam as its driver. The experiment
+is set up with a $10\unit{m}$ rubidium plasma cell, with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$.
 
@@
 \subsection[\label{S:M:Setup}]{Drive Beam Parameters}
+%~ Patric's Comments
+%~ - Self-modulation as a driver
+%~ - SM does not reach blow out
+%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
+%~   not desirable
 % ******************************************************************************************************************** %
@@
 %~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+%~
+%~ Patric's Comments
+%~ - Beam loading for narrow energy spread
+%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
+%~   (Tzoufras) well know
+%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
+%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
+%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
+%~   bunch and the SM
+%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
+%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
 % ******************************************************************************************************************** %
@@
 
-The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
-beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
-the electron witness beam sees consistent fields.
+The single drive beam setup is designed to behave similarly to the self-modulated case. However, since the drive beam is
+prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
+sees consistent fields. The
 

### 2017-07-13 Tex/Paper.tex
End of day commit

--- 2017-07-11 Tex/Paper.tex
@@
 
+% ******************************************************************************************************************** %
 \section[\label{S:I}]{Introduction}
-
 % interested from SMI/AWAKE
 % requirements for AWAKE Run 2
+% ******************************************************************************************************************** %
 
-The preliminary design of AWAKE Run 2 proposes to use two plasma sections. The first section of 4m is the SMI stage. The
-electron beam will be injected into the modulated proton beam before stage two, where acceleration will occur. As the
-$e_z$ field will decrease due to the gap between the two cells, it is desireable to keep this as short as possible
-\cite{adli:2016}.
+Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
+gradients, and has been of interest for several decades \cite{chen:1985}. A relativist beam travelling through a plasma
+will excite a strong longitudinal e-field that can be loaded by a trailing witness beam, which can achieve a high
+acceleration gradient. Acceleration of an electron beam by an electron drive bunch has been demonstrated experimentally
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. The AWAKE experiment at CERN is a proof of concept
+proton driven plasma wakefield accelerator \cite{awake_collaboration:2014}.
 
+A major challenge with plasma wakefield accelerators is, however, to produce an accelerated beam with a minimal increase
+in energy spread and emittance. In the well described linear case where the beam density $n_{b}$ is much smaller than
+the plasma density $n_{0}$ the plasma causes emittance growth in the beam. A finite length beam will also see a varying
+transverse wakefield causing increasing energy spread \cite{katsouleas:1987}. In the non-linear regime, where
+$n_{b} > n_{0}$, the drive beam sees an unvarying transverse field due to a bubble forming in the plasma behind the
+drive beam. The bubble is formed by the transverse oscillations of the plasma electrons which move near uniformly as a
+function of distance from the drive beam forming a sheet around an evacuated area. Since the much heavier plasma ions
+have no significant movement within the relevant time frame, these remaining ion channel creates a focusing force that
+scales linearly with the radius within this bubble producing a angularly symmetric focusing force
+\cite{lu:2006-1, lu:2006}. This effect also avoid the issue of increasing energy spread due to transverse beam loading.
+Increase in energy spread is still dependent on beam loading of the longitudinal e-field, $E_{z}$. This effect can be
+negated by specially shaped beams \cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not
+a topic explored in this paper.
+
+% ******************************************************************************************************************** %
+\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
+%~ Patric's Comments
+%~ - Self-modulation as a driver
+%~ - SM does not reach blow out
+%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
+%~   not desirable
+% ******************************************************************************************************************** %
+
+A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where
+$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$, will drive an
+increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak accelerating
+phase of this field will quickly gain energy from the wakefield. Acceleration of an electron witness beam driven by two
+electron drive beams was demonstrated at Brookhaven National Laboratory \cite{muggli:2011}. However, electron drive
+bunches will quickly lose energy to the plasma, and the accelerating witness beam will eventually catch up with the
+drive beam and the acceleration stop.
+
+This de-phasing problem can be minimised by instead using a proton drive bunch \cite{caldwell:2009}. Proton beams, like
+for instance the LHC and SPS beams at CERN, are ideal candidates for such an accelerator; however, they are orders of
+magnitude longer than the plasma wavelengths needed for such applications. This issue is resolved by letting the proton
+beam undergo self-modulation before injecting the witness beam into one of the buckets in the modulated structure. This
+self-modulation instability is caused by the transverse fields generated by the beam acting upon the beam itself,
+causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the
+plasma, leaving a train of proton bunches along the beam axis.
+
+% ******************************************************************************************************************** %
+\subsection[\label{S:I:AWAKE}]{The AWAKE Experiment}
+% ******************************************************************************************************************** %
+
+The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam as its driver. The first run
+of the experiment is set up with a $10\unit{m}$ rubidium plasma cell, with a nominal plasma density of
+$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. The corresponding plasma wavelength is $1.26\unit{mm}$. The plasma
+density is matched to the SPS proton beam such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = \lambda_{pe}/2\pi$ is the
+plasma wave number. The aim of the first run is to demonstrate self-modulation of the proton beam, and in 2018 to
+sample the wake field with a long electron bunch. The study presented here is for run two, which aims to demonstrate
+acceleration of a short electron bunch producing at high energy and low emittance and low energy spread.
+
+\begin{figure}[hbt]
+    \includegraphics[width=0.99\linewidth,trim={1mm 2mm 1mm 2mm},clip]{figures/figAWAKE}
+    \caption{\label{Fig:AWAKER2} A simplified illustration of the experimental setup for AWAKE Run 2. The SPS proton
+        beam undergoes self-modulation in the first $4\unit{m}$ plasma cell. The electron witness beam is injected in
+        one of the buckets, and undergoes acceleration in the second plasma cell \cite{berglyd_olsen:2015, adli:2016}.}
+\end{figure}
+
+The preliminary design of the second run proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}.
+The first section of $4\unit{m}$ is the self-modulation stage. The electron beam will be injected into the modulated
+proton beam before stage two, where acceleration will occur. As the $e_z$ field will decrease due to the gap between the
+two cells, it is desirable to keep this as short as possible \cite{adli:2016}.
+
+% ******************************************************************************************************************** %
 \section[\label{S:M}]{Method}
@@
 %- simulation setup PIC/quickpic OS
+% ******************************************************************************************************************** %
 
 The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors that
-may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies
-[citations].
+may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies.
 
-Our first approach was to use a premodulated, short proton beam with the same structure as a section of the full AWAKE
-proton drive beam. These studies were done using the full PIC code Osiris \cite{fonseca:2002} using 2D
-cylindrical-symetric simulations. The proton beam was pre-modulated by a clipped cosine function to the longitudinal
-density profile, with a period matching the wavelength, $\lambda_p$, of the plasma. The length was limited to
-$26\cdot\lambda_p$, and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed
-several parameter scans with this setup, testing for optimal charge as well as beam length
-\cite{adli:2016, berglyd_olsen:2016}.
+Our first approach was to use a pre-modulated, short proton beam with similar structure to the one produced by the
+self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
+using 2D cylindrical-symmetric simulations. The proton beam was pre-modulated by a clipped cosine function to the
+longitudinal density profile, with a period matching $\lambda_{pe}$. Its transverse profile was kept as a Gaussian with
+$\sigma_{r} = k_{pe} = 200\unit{\mu m}$. The length of the simulation beam was limited to $26\cdot\lambda_{pe}$, and the
+electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed several parameter scans with
+this setup, testing for the the maximum beam charge that could be accelerated with a high energy gain and low energy
+spread \cite{adli:2016, berglyd_olsen:2016}.
 
-[Add something about the optimal results]
+In order to evaluate the quality of the beam, we also needed to study emittance evolution. However, full PIC codes like
+Osiris are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
+This is a know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lower than
+$c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing the Yee solver with a
+solver designed by Lehe \cite{lehe:2013}. These simulations showed that this numerical effect is still prominent in the
+high density regions of the electron beam, making it difficult to distinguish the physics from the numerical error.
 
-In order to evaluate the quality of the beam, we also needed to study its emittance. Full PIC codes like Osiris are
-vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}. This is a
-know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lowet than $c$,
-while the beam moves very close to $c$. The effect can be mitigated somewhat by a the Lehe solver \cite{lehe:2013}, but
-the effect is still prominent in the the high density regions of the electron beam.
+Quasi-static PIC codes do not suffer this problem, so in order to study the emittance evolution of the beam we instead
+turned to the recently released open source version QuickPIC developed by UCLA. QuickPIC a fully relativistic 3D PIC
+code \cite{huang:2006, an:2013}.
 
-In order to study the emittance evolution of the beam we used QuickPIC, a fully relativistic 3D PIC code
-\cite{huang:2006, an:2013}.
-
+% ******************************************************************************************************************** %
 \subsection[\label{S:M:Setup}]{Drive Beam Parameters}
+%~ Patric's Comments
+%~ - Self-modulation as a driver
+%~ - SM does not reach blow out
+%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
+%~   not desirable
+% ******************************************************************************************************************** %
 
@@
 needed gap between the two plasma cells also contributes to a decreased density of protons near the axis, and some of
-the field is drained by other protons seeing an accelerating face within the drive beam. In total, the expected peak
+the field is drained by other protons seeing an accelerating phase within the drive beam. In total, the expected peak
 $E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in the second cell
@@
 environment for the witness beam. We are not considering the evolution of the proton beam in this test setup, so to
-prevent the proton beam from evolving radially, we increased its mass.
+prevent the proton beam from evolving radially, we also increased its mass.
 
-The basline AWAKE drive beam current is insufficient to produce a plasma bubble. The plasma electrons are depleted to
-around $65\%$ of nominal plasma density at the injection point of the electron beam. This condition is replicated in out
-single bunch case. The single bunch setup also uses the baseline proton energy $W_{pb} = 400\unit{GeV}$.
+The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. The
+plasma electrons are depleted to around $65\%$ of nominal plasma density at the injection point of the electron beam.
+This condition is replicated in out single bunch case as the peak density of the drive beam is $0.83\cdot n_{0}$. The
+single bunch setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size
+$\sigma_{r} = k_{pe}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
 
+% ******************************************************************************************************************** %
 \subsection[\label{S:M:Setup}]{Witness Beam Parameters}
+% ******************************************************************************************************************** %
 
 The witness beam in our simulation differs from AWAKE baseline parameters on several key points. Initial beam energy is
-set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This is to eliminate the problem of initial de-phasing of the witness
-beam. AWAKE baseline witness beam energy for Run 1 is $W_{eb} = 10-20\unit{MeV}$ \cite{gschwendtner:2016}. Beam loading
-of a short witness beam is sensitive to initial position. AWAKE Run 2 will likely require a higher initial energy, but a
-$W_{eb} = 30--50\unit{MeV}$ is sufficient to minimise de-phasing \cite{berglyd_olsen:2015}. For this case we have
-eliminated it entirely in order to reduce the number of variables in our parameter scans.
+set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This was done to eliminate the problem of initial de-phasing of the
+witness beam. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
+\cite{gschwendtner:2016}. Beam loading of a short witness beam is sensitive to initial position. AWAKE Run 2 will likely
+require a higher initial energy, but a $W_{eb} = 30-50\unit{MeV}$ is sufficient to minimise de-phasing as the drift
+$\Delta\xi \propto \gamma^{-2}$ \cite{berglyd_olsen:2015}. For this case we have eliminated it entirely in order to
+reduce the number of variables in our parameter scans.
 
-Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ causes the beam radius to rapidly shrink as the
-beam enters the plasma \cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma
-density. The relation is given by
+Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ caused the beam radius to undergo rapid transverse
+evolution as the beam enters the plasma, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
+\cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma density. This relation is
+given by
 \begin{align}
@@
 where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
-$2$ and $6\unit{\mu m}$.
+$2$ and $6\unit{\mu m}$, corresponding to $\sigma_{r}$ ranging from $5.25\unit{\mu m}$ to $9.09\unit{\mu m}$.
 
+% ******************************************************************************************************************** %
 \section[\label{S:BL}]{Beam Loading}
-
 %~ Eric's Comments
 %~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+%~
+%~ Patric's Comments
+%~ - Beam loading for narrow energy spread
+%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
+%~   (Tzoufras) well know
+%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
+%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
+%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
+%~   bunch and the SM
+%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
+%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
+% ******************************************************************************************************************** %
+
+\begin{figure}[hbt]
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
+    \caption{\label{Fig:BeamLoading} Comparison between the unloaded longitudinal e-field (no witness beam) and the
+        loaded e-field along the axis. The magnitude of the beam density along the axis is shown for reference. The
+        beams travel towards the left. $\xi = z - tc$ is the position in the simulation box. The beam density is in
+        units of initial plasma density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$. The bottom plot shows the plasma density
+        for the loaded and unloaded case. The plasma depletion region behind the proton bunch has a minimum of $67.4\%${}
+        of $n_{0}$. }
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
+    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the proton beam (blue) and the electron beam
+        (red) superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
+        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
+\end{figure}
 
@@
 
-The structure of the single drive beam setup behaves similarly to the self-modulated case. However, since the drive
-beam is prevented from significant evolution in this simulation setup, we are presented with an idealised case where
-the electron witness beam sees consistent fields.
-
-\begin{figure}
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
-    \label{Fig:BeamLoading}
-    \caption{Comparison between the unloaded longitudinal e-field (no witness beam) and the loaded e-field along the
-        axis. The magnitude of the beam density along the axis is shown for reference. The beams travel towards the
-        left. $\xi = z - tc$ is the position in the simulation box. The beam density is in units of plasma density
-        $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
-\end{figure}
+The single drive beam setup is designed to behave similarly to the self-modulated case. However, since the drive beam is
+prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
+sees consistent fields. The field generated by the proton drive bunch is seen as the dotted lint in figure
+\ref{Fig:BeamLoading}. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near
+non-linear \cite{rosenzweig:2010}. There is some depletion of plasma electrons, but not enough to form a bubble. The
+dotted green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density has a
+depletion of $67\%$.
 
@@
 %~   flatten and energy spread reduced [well known result, Tzoufras]
-
-\begin{figure}
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
-    \label{Fig:PlasmaDenTWake}
-    \caption{}
-\end{figure}
 

### 2017-07-28 Tex/Paper.tex
Daily commit
Added more text and figures

@@
 single bunch setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size
-$\sigma_{r} = k_{pe}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
+$\sigma_{r} = k_{pe} = 200\unit{\mu m}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
 
@@
 witness beam. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
-\cite{gschwendtner:2016}. Beam loading of a short witness beam is sensitive to initial position. AWAKE Run 2 will likely
-require a higher initial energy, but a $W_{eb} = 30-50\unit{MeV}$ is sufficient to minimise de-phasing as the drift
-$\Delta\xi \propto \gamma^{-2}$ \cite{berglyd_olsen:2015}. For this case we have eliminated it entirely in order to
-reduce the number of variables in our parameter scans.
+\cite{gschwendtner:2016}. Beam loading of a short witness beam is sensitive to its position relative to the field
+\cite{tzoufras:2009}. AWAKE Run 2 will likely require a higher initial energy, but a $W_{eb} = 30-50\unit{MeV}$ is
+sufficient to minimise de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$ \cite{berglyd_olsen:2015}. For this case
+we have eliminated it entirely in order to reduce the number of variables in our parameter scans.
 
@@
 \begin{figure}[hbt]
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} Comparison between the unloaded longitudinal e-field (no witness beam) and the
-        loaded e-field along the axis. The magnitude of the beam density along the axis is shown for reference. The
-        beams travel towards the left. $\xi = z - tc$ is the position in the simulation box. The beam density is in
-        units of initial plasma density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$. The bottom plot shows the plasma density
-        for the loaded and unloaded case. The plasma depletion region behind the proton bunch has a minimum of $67.4\%${}
-        of $n_{0}$. }
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
+    \caption{\label{Fig:BeamLoading} The top plot compares the unloaded longitudinal e-field (no witness beam, blue.
+        dashed  line) and the loaded e-field (blue line) along the beam axis. The magnitude of the beam density along
+        the axis is shown (red line) for reference. The bottom plot compares the plasma density along the beam axis for
+        a drive beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line),
+        and both witness and drive beam present (continuous green line). $\xi = z - tc$ is the position in the
+        simulation box and both beams travel towards the left. The beam and plasma densities arein units of initial
+        plasma density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
 \end{figure}
@@
 \begin{figure}[hbt]
-    \includegraphics[width=0.99\linewidth,trim={4mm 0mm 4mm 0mm},clip]{figures/plasmaDenTWake}
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
     \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the proton beam (blue) and the electron beam
@@
 prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
-sees consistent fields. The field generated by the proton drive bunch is seen as the dotted lint in figure
-\ref{Fig:BeamLoading}. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near
-non-linear \cite{rosenzweig:2010}. There is some depletion of plasma electrons, but not enough to form a bubble. The
-dotted green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density has a
-depletion of $67\%$.
+sees consistent fields throughout the plasma stage. The field generated by the proton drive bunch is seen as the dotted
+line in figure \ref{Fig:BeamLoading}. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear
+regime but near non-linear \cite{rosenzweig:2010}. There is some depletion of plasma electrons, but not enough to form a
+bubble. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density
+has a depletion of $67\%$.
 
@@
 %~   flatten and energy spread reduced [well known result, Tzoufras]
+
+The witness bunch generates its own wakefield, which in the accelerating phase cancels out the $E_{z}$ field generated
+by the drive bunch. For a finite length bunch this causes the particles in the tail of the witness bunch to be
+accelerated less than those at the front resulting in high energy spread in exchange for high energy transfer
+\cite{van_der_meer:1985}. Since $E_{z} \propto \rho_{b}$, a beam profile $\rho_{b}(\xi)$ that perfectly flattens the
+accelerating field within the witness beam, reduces energy spread to zero. The ideal shape is triangular or trapezoidal
+with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
 
@@
 %~   electron densities etc. )
+
+For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
+density. In our case, with a matched beam to the plasma density \ref{EQ:Matched}, we are limited on how much total
+charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and \ref{Fig:PlasmaDenTWake} has a total
+charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial normalised emittance
+$\epsilon_{0} = 2\unit{\mu m}$.
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
+    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
+        after $4\unit{m}$ of plasma. Mean momentum is $1.67\unit{GeV/c}$ with an RMS spread of $87\unit{MeV/c}$
+        ($5.2\%$) for the full beam.}
+\end{figure}
+
+As illustrated in figure \ref{Fig:BeamPS}, our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam indeed
+shows a difference in energy transfer to the tail of the beam. Also the front of the beam has a large tail in momentum
+space. The positioning of the witness beam is chosen to put the bulk of the charge as close to the peak accelerating
+field as possible, as can be seen in figure \ref{Fig:BeamLoading}.
+
+Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
+non-linear regime with $n_{eb} \approx 35\times n_{0}$. The plasma region reaches full depletion close to the peak of
+the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam axis
+(see figure \ref{Fig:PlasmaDenTWake}).
 
@@
 
+\section[\label{Ack}]{Acknowledgements}
+% ******************************************************************************************************************** %
+
+The simulations forming the basis for this study have been made possible using the open source version of QuickPIC
+released in early 2017 and owned by UCLA.
+
+These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway
+maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the University
+of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code: nn9303k.
+
+The authors would also like to acknowledge the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS
+was used extensively for simulations leading up to the work presented in this paper.
+
 % ******************************************************************************************************************** %

### 2017-08-01 Tex/Paper.tex
Added emittance figures

@@
 \begin{align}
-    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_p}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
 \end{align}
@@
 
-For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
-density. In our case, with a matched beam to the plasma density \ref{EQ:Matched}, we are limited on how much total
-charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and \ref{Fig:PlasmaDenTWake} has a total
-charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial normalised emittance
-$\epsilon_{0} = 2\unit{\mu m}$.
-
 \begin{figure}[hbt]
@@
 \end{figure}
+
+For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
+density. In our case, with a matched beam to the plasma density defined by equation \ref{EQ:Matched}, we are limited on
+how much total charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and
+\ref{Fig:PlasmaDenTWake} has a total charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial
+normalised emittance $\epsilon_{0} = 2\unit{\mu m}$.
 
@@
 %~   longitudinal phase spaces, space long simulation)
+
+\begin{figure*}[hbt]
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
+    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
+        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
+        $\sigma_{x}$ in the x plane. The moving window for emittance calculation is longitudinal slices of
+        $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than $100$ macro
+        particles have been included, which accounts for the abrupt edge as well as the noise at either end of the beam
+        due to low statistics. The blue lines show the peak electron beam density profile. For reference, the plasma 
+        density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid lines are at
+        the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after $40\unit{m}$, and
+        the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the witness beam, these
+        simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which causes the
+        structure to brake down after about $50\unit{m}$.}
+\end{figure*}
+
+The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
+For the majority of the cases we studied that maintained a stable accelerating structure, about $70\%$ of the beam
+retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
+case extended to a $100\unit{m}$ plasma case and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to
+prevent dephasing, which for the SPS beam case starts to become significant after about $50\unit{m}$.
+
+The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
+beam radius follows the matched beam equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$.
 
@@
 \section[\label{S:D}]{Discussion}
+% discussion of optimal electron beam parameters
+% implications for AWAKE Run 2
 % ******************************************************************************************************************** %
@@
 \section[\label{S:C}]{Conclusion}
-% discussion of optimal electron beam parameters
-% implications for AWAKE Run 2
 % ******************************************************************************************************************** %
@@
 
-The simulations forming the basis for this study have been made possible using the open source version of QuickPIC
-released in early 2017 and owned by UCLA.
+The simulations for this study have been run using the open source version of QuickPIC released in early 2017 and owned
+by UCLA.
 
-These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway
-maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the University
-of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code: nn9303k.
+These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway. Abel
+is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
+University of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code for
+this work is nn9303k.
 

### 2017-08-10 Tex/Paper.tex
Updated plots
Added transverse phasespace plots

@@
         an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
-        $\sigma_{x}$ in the x plane. The moving window for emittance calculation is longitudinal slices of
-        $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than $100$ macro
-        particles have been included, which accounts for the abrupt edge as well as the noise at either end of the beam
-        due to low statistics. The blue lines show the peak electron beam density profile. For reference, the plasma 
-        density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid lines are at
-        the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after $40\unit{m}$, and
-        the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the witness beam, these
-        simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which causes the
-        structure to brake down after about $50\unit{m}$.}
+        $\sigma_{x} = 5.24\unit{\mu m}$ in the x plane. The moving window for emittance calculation is longitudinal
+        slices of $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
+        $100$ macro particles have been included, which accounts for the abrupt edge as well as the noise at either end
+        of the beam due to low statistics. The blue lines show the peak electron beam density profile. For reference,
+        the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid
+        lines are at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after
+        $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
+        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which
+        causes the structure to brake down after about $50\unit{m}$.}
 \end{figure*}
@@
 The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
-For the majority of the cases we studied that maintained a stable accelerating structure, about $70\%$ of the beam
+For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the beam
 retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
-case extended to a $100\unit{m}$ plasma case and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to
-prevent dephasing, which for the SPS beam case starts to become significant after about $50\unit{m}$.
+case extended to a $100\unit{m}$ plasma and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent
+dephasing. Dephasing for the SPS beam case starts to become significant after about $50\unit{m}$.
 
 The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
-beam radius follows the matched beam equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$.
+beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
+of the beam where normalised emittance is preserved.
 
@@
 %~   show: transverse and longitudinal phase spaces, long offset simulation)
+
+\begin{figure*}[hbt]
+    \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
+    \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
+    \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
+    \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
+    \\
+    \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
+    \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
+    \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
+    \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
+    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
+        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
+        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
+        represent particles with position $1.55 < \xi < 1.57$.}
+\end{figure*}
+
+Our configuration shows robustness to electron beam transverse offset as the bubble generated by the witness beam
+wakefield follows the beam. The head of the beam does not benefit from this, and we see some defocusing in this region.
+However, since this the proton wakefield creates a quasi linear condition, we still see the head of the beam
+stabilising. The off-axis case has a larger initial emittance growth, but the growth levels off after the first few
+metres and stays constant for the remainder of the plasma accelerator section.
 

### 2017-08-10 Tex/Paper.tex
Compined transverse phasespace plots to one figure

@@
 
+\begin{figure*}[hbt]
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
+    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
+        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
+        $\sigma_{x} = 5.24\unit{\mu m}$ in the x plane. The moving window for emittance calculation is longitudinal
+        slices of $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
+        $100$ macro particles have been included, which accounts for the abrupt edge as well as the noise at either end
+        of the beam due to low statistics. The blue lines show the peak electron beam density profile. For reference,
+        the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid
+        lines are at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after
+        $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
+        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which
+        causes the structure to brake down after about $50\unit{m}$.}
+\end{figure*}
+
+\begin{figure*}[hbt]
+    \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
+    %~ \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
+    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
+    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
+    %~ \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
+    %~ \\
+    %~ \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
+    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
+    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
+    %~ \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
+    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
+        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
+        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
+        represent particles with position $1.55 < \xi < 1.57$.}
+\end{figure*}
+
 For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
@@
 
-\begin{figure*}[hbt]
-    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
-    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
-    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
-        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
-        $\sigma_{x} = 5.24\unit{\mu m}$ in the x plane. The moving window for emittance calculation is longitudinal
-        slices of $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
-        $100$ macro particles have been included, which accounts for the abrupt edge as well as the noise at either end
-        of the beam due to low statistics. The blue lines show the peak electron beam density profile. For reference,
-        the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid
-        lines are at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after
-        $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
-        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which
-        causes the structure to brake down after about $50\unit{m}$.}
-\end{figure*}
-
 The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
@@
 %~   show: transverse and longitudinal phase spaces, long offset simulation)
-
-\begin{figure*}[hbt]
-    \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
-    \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
-    \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
-    \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
-    \\
-    \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
-    \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
-    \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
-    \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
-    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
-        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
-        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
-        represent particles with position $1.55 < \xi < 1.57$.}
-\end{figure*}
 

### 2017-08-10 Tex/Paper.tex
Some edits and additions

@@
         $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
-        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid dephasing which
-        causes the structure to brake down after about $50\unit{m}$.}
+        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid de-phasing
+        which causes the structure to break down after about $50\unit{m}$.}
 \end{figure*}
@@
         plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
-        particles and lines represent particles with position $1.40 < \xi < 1.42$. The red particles and lines
-        represent particles with position $1.55 < \xi < 1.57$.}
+        particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
+        particles and lines represent particles with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
 \end{figure*}
@@
 
-As illustrated in figure \ref{Fig:BeamPS}, our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam indeed
-shows a difference in energy transfer to the tail of the beam. Also the front of the beam has a large tail in momentum
-space. The positioning of the witness beam is chosen to put the bulk of the charge as close to the peak accelerating
-field as possible, as can be seen in figure \ref{Fig:BeamLoading}.
+As illustrated in figure \ref{Fig:BeamPS}, our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam, as
+expected, shows a difference in energy transfer to the tail of the beam compared to the centre where the $E_{z}$-field
+is nearly flat. Also the front of the beam has a large tail in momentum space corresponding to a smaller acceleration
+gradient. The positioning of the witness beam is chosen to put the bulk of the charge as close to the peak accelerating
+field as possible, but prioritising the tail end over the front as the front is in any case in the quasi-linear regime.
 
 Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
-non-linear regime with $n_{eb} \approx 35\times n_{0}$. The plasma region reaches full depletion close to the peak of
-the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam axis
-(see figure \ref{Fig:PlasmaDenTWake}).
+non-linear regime with $n_{eb} \approx 35\times n_{0}$. The wakefield is driven by the beam's own front. The space
+charge rapidly becomes high enough to start expel plasma electrons from the beam axis, and form the characteristic
+electrons sheet that defines the blowout regime. As a result the plasma region reaches full depletion close to the peak
+of the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam
+axis (see figure \ref{Fig:PlasmaDenTWake}).
 
@@
 
-The witness beam's self-generated bubble prevents the tailing end of the beam to see any measurable emittance growth.
+The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
 For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the beam
@@
 case extended to a $100\unit{m}$ plasma and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent
-dephasing. Dephasing for the SPS beam case starts to become significant after about $50\unit{m}$.
+de-phasing. De-phasing for the SPS beam case starts to become significant after about $50\unit{m}$.
 
@@
 
-Our configuration shows robustness to electron beam transverse offset as the bubble generated by the witness beam
-wakefield follows the beam. The head of the beam does not benefit from this, and we see some defocusing in this region.
-However, since this the proton wakefield creates a quasi linear condition, we still see the head of the beam
-stabilising. The off-axis case has a larger initial emittance growth, but the growth levels off after the first few
-metres and stays constant for the remainder of the plasma accelerator section.
+Our configuration also shows some robustness to electron beam transverse offset as the bubble generated by the witness
+beam wakefield follows the beam. The head of the beam does not benefit from this effect, and we see some defocusing in
+this region (see bottom, right plot of figure \ref{Fig:BeamFilament}). However, since the proton wakefield creates a
+quasi linear condition, we still see the head of the beam stabilising (see top, right plot of figure
+\ref{Fig:BeamFilament}). The off-axis case has a larger initial emittance growth (left side plot of figure
+\ref{Fig:BeamFilament}), but the growth levels off after the first few metres and stays constant for the remainder of
+the plasma accelerator section (figure \ref{Fig:BeamEmitt}).
 
@@
 % ******************************************************************************************************************** %
+
+For accelerator applications in general, and also for Run II of the AWAKE experiment, it is desirable to maximise the
+charge that can be successfully accelerated in the witness bunch. However, since longitudinally constant accelerating
+fields depend on both the position and the charge density of the witness beam \cite{katsouleas:1987, tzoufras:2009}.
+
+The large number of parameters involved makes the problem difficult to solve in simulations, and difficult to measure in
+experiments. For this study we limited ourselves to look at a range of initial emittances, which allows for a range of
+transverse beam sizes when with a fixed $\beta$-function matched to the plasma density; and a range of beam lengths with
+a maximum at the same point on the wakefield as for our reference case covered above.
 

### 2017-08-16 Tex/Paper.tex
Added beam quality figure
Updated beamQuality figure and added one with absolute values. Also added relevant text

@@
 A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where
-$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$, will drive an
-increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak accelerating
-phase of this field will quickly gain energy from the wakefield. Acceleration of an electron witness beam driven by two
-electron drive beams was demonstrated at Brookhaven National Laboratory \cite{muggli:2011}. However, electron drive
-bunches will quickly lose energy to the plasma, and the accelerating witness beam will eventually catch up with the
-drive beam and the acceleration stop.
+\begin{align}
+    \lambda_{p} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
+\end{align}
+and
+\begin{align}
+    \omega_{pe} = \sqrt{\frac{n_{0} e^{2}}{m_{e} \epsilon_{0}}}, \label{EQ:OmegaP}
+\end{align}
+%$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
+will drive an increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak
+accelerating phase of this field will quickly gain energy from the wakefield. Acceleration of an electron witness beam
+driven by two electron drive beams was demonstrated at Brookhaven National Laboratory \cite{muggli:2011}. However,
+electron drive bunches will quickly lose energy to the plasma, and the accelerating witness beam will eventually catch
+up with the drive beam and the acceleration stop.
 
@@
 $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. The corresponding plasma wavelength is $1.26\unit{mm}$. The plasma
-density is matched to the SPS proton beam such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = \lambda_{pe}/2\pi$ is the
+density is matched to the SPS proton beam such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the
 plasma wave number. The aim of the first run is to demonstrate self-modulation of the proton beam, and in 2018 to
@@
 longitudinal density profile, with a period matching $\lambda_{pe}$. Its transverse profile was kept as a Gaussian with
-$\sigma_{r} = k_{pe} = 200\unit{\mu m}$. The length of the simulation beam was limited to $26\cdot\lambda_{pe}$, and the
-electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed several parameter scans with
-this setup, testing for the the maximum beam charge that could be accelerated with a high energy gain and low energy
-spread \cite{adli:2016, berglyd_olsen:2016}.
+$\sigma_{r} = k_{pe}^{-1} = 200\unit{\mu m}$. The length of the simulation beam was limited to $26\cdot\lambda_{pe}$,
+and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed several parameter
+scans with this setup, testing for the the maximum beam charge that could be accelerated with a high energy gain and low
+energy spread \cite{adli:2016, berglyd_olsen:2016}.
 
@@
 single bunch setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size
-$\sigma_{r} = k_{pe} = 200\unit{\mu m}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
+$\sigma_{r} = 200\unit{\mu m}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
 
@@
 
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
+    \caption{\label{Fig:BeamQ} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
+        function of initial beam charge (blue), and relative energy spread (red), after $4\unit{m}$ of plasma and with
+        an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from
+        $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam loading section corrspond to the
+        square marked lines at $100\unit{pC}$.}
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
+    \caption{\label{Fig:BeamQAbs} Total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a function of
+        initial beam charge (blue), and final momentum (red), after $4\unit{m}$ of plasma and with an initial emittance
+        $\epsilon_{N,0}=2\unit{\mu m}$.}
+\end{figure}
+
 For accelerator applications in general, and also for Run II of the AWAKE experiment, it is desirable to maximise the
@@
 The large number of parameters involved makes the problem difficult to solve in simulations, and difficult to measure in
-experiments. For this study we limited ourselves to look at a range of initial emittances, which allows for a range of
-transverse beam sizes when with a fixed $\beta$-function matched to the plasma density; and a range of beam lengths with
-a maximum at the same point on the wakefield as for our reference case covered above.
+experiments. Presented in figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} is a parameter scan for a matched beam with
+initial normalised emittance $\epsilon_{N,0}=2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the
+scan with beam charge from $10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to
+$100\unit{\mu m}$. We see from figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a
+well defined minimum energy spread with a beam charge $\geq 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower
+beam charges tend to underload the field, while higher beam charges tend to overload. It is also clear that long beams
+with respect to the accelerating flank of the $E_{z}$-field, $\approx\lambda_{pe}/4$, will not optimally load the field
+along its length thus experiencing a larger spread in energy.
+
+A higher charge beam will generate a non-linear wakefield sooner, which in turns ensures that a smaller portion of the
+beam experiences the quasi-linear region with emittance growth. As figure \ref{Fig:BeamQAbs} illustrates, a higher
+charge also results in a lower energy gain.
 
@@
 is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
-University of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code for
-this work is nn9303k.
+University of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code:
+nn9303k. Some of the simulations were also run on the student-maintained computing cluster ``Smaug'' at the University
+of Oslo, Department of Physics.
 

### 2017-08-24 Tex/Paper.tex
Fixed typo
Text cleanup

@@
 gradients, and has been of interest for several decades \cite{chen:1985}. A relativist beam travelling through a plasma
-will excite a strong longitudinal e-field that can be loaded by a trailing witness beam, which can achieve a high
-acceleration gradient. Acceleration of an electron beam by an electron drive bunch has been demonstrated experimentally
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. The AWAKE experiment at CERN is a proof of concept
-proton driven plasma wakefield accelerator \cite{awake_collaboration:2014}.
+will excite a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading, the
+witness beam can have a high acceleration gradient. Acceleration of an electron beam by an electron drive bunch has been
+demonstrated experimentally \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. The AWAKE experiment at
+CERN is a proof of concept proton driven plasma wakefield accelerator \cite{awake_collaboration:2014}.
 
@@
 drive beam. The bubble is formed by the transverse oscillations of the plasma electrons which move near uniformly as a
-function of distance from the drive beam forming a sheet around an evacuated area. Since the much heavier plasma ions
-have no significant movement within the relevant time frame, these remaining ion channel creates a focusing force that
-scales linearly with the radius within this bubble producing a angularly symmetric focusing force
-\cite{lu:2006-1, lu:2006}. This effect also avoid the issue of increasing energy spread due to transverse beam loading.
-Increase in energy spread is still dependent on beam loading of the longitudinal e-field, $E_{z}$. This effect can be
-negated by specially shaped beams \cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not
-a topic explored in this paper.
+function of distance from the drive beam, forming a sheet around an evacuated area. The much heavier plasma ions have no
+significant movement within the relevant time frame, and form an ion channel creating a focusing force that scales
+linearly with the radius. This produces an angularly symmetric focusing force \cite{lu:2006-1, lu:2006}. This effect
+also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread is still
+dependent on beam loading of the longitudinal e-field, $E_{z}$. Non-uniform beam loading can be negated by specially
+shaped beams that optimally flattens the field \cite{katsouleas:1987, tzoufras:2009}, but this is difficult
+experimentally and is not a topic explored in this paper.
 
@@
 This de-phasing problem can be minimised by instead using a proton drive bunch \cite{caldwell:2009}. Proton beams, like
-for instance the LHC and SPS beams at CERN, are ideal candidates for such an accelerator; however, they are orders of
+for instance the LHC and SPS beams at CERN, are ideal candidates for such an accelerator. However, they are orders of
 magnitude longer than the plasma wavelengths needed for such applications. This issue is resolved by letting the proton
@@
 causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the
-plasma, leaving a train of proton bunches along the beam axis.
+plasma, and leaves a train of proton bunches along the beam axis with a surrounding halo.
 
@@
 The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam as its driver. The first run
-of the experiment is set up with a $10\unit{m}$ rubidium plasma cell, with a nominal plasma density of
-$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. The corresponding plasma wavelength is $1.26\unit{mm}$. The plasma
-density is matched to the SPS proton beam such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the
-plasma wave number. The aim of the first run is to demonstrate self-modulation of the proton beam, and in 2018 to
-sample the wake field with a long electron bunch. The study presented here is for run two, which aims to demonstrate
-acceleration of a short electron bunch producing at high energy and low emittance and low energy spread.
+of the experiment is set up with a $10\unit{m}$ rubidium vapour cell. The rubidium vapour is ionised by a
+$780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$. The nominal plasma density of
+the AWAKE experiment is $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to a plasma
+wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam such that
+$k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first phase of Run 1
+of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the wake field with a long
+electron bunch. The study presented here is for Run 2, which aims to demonstrate acceleration of a short electron bunch
+to high energy with a minimal increase in emittance and energy spread.
 
@@
 The preliminary design of the second run proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}.
-The first section of $4\unit{m}$ is the self-modulation stage. The electron beam will be injected into the modulated
-proton beam before stage two, where acceleration will occur. As the $e_z$ field will decrease due to the gap between the
-two cells, it is desirable to keep this as short as possible \cite{adli:2016}.
+The first section of $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without
+the electron beam present. The electron witness beam will be injected into the modulated proton beam before stage two,
+where acceleration will occur. As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
+keep this as short as possible \cite{adli:2016}.
 
@@
 The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors that
-may affect this, we have tried several approaches to create a stable drive beam structure based on previous SMI studies.
+may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
+modulation studies.
 
@@
 self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
-using 2D cylindrical-symmetric simulations. The proton beam was pre-modulated by a clipped cosine function to the
+using 2D cylindrical-symmetric simulations. The proton beam was pre-modulated by a clipped cosine function to its
 longitudinal density profile, with a period matching $\lambda_{pe}$. Its transverse profile was kept as a Gaussian with
@@
 Osiris are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
-This is a know issue with the Yee EMF solver, which causes the phase velocity of electromagnetic fields to be lower than
+This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic fields to be lower than
 $c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing the Yee solver with a
-solver designed by Lehe \cite{lehe:2013}. These simulations showed that this numerical effect is still prominent in the
-high density regions of the electron beam, making it difficult to distinguish the physics from the numerical error.
+solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is still prominent in the
+high density regions of the electron beam, making it difficult to distinguish emittance growth from the physics from
+that originating from numerical error.
 
 Quasi-static PIC codes do not suffer this problem, so in order to study the emittance evolution of the beam we instead
-turned to the recently released open source version QuickPIC developed by UCLA. QuickPIC a fully relativistic 3D PIC
+turned to the recently released open source version QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D PIC
 code \cite{huang:2006, an:2013}.
@@
 
-In these simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we expect to
-see from the self-modulated SPS beam in AWAKE. The baseline AWAKE drive beam contains $3\nexp{11}$ protons
-\cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded in the
-middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during self-modulation. The
-needed gap between the two plasma cells also contributes to a decreased density of protons near the axis, and some of
-the field is drained by other protons seeing an accelerating phase within the drive beam. In total, the expected peak
-$E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in the second cell
-\cite{awake_collaboration:2016}. A single proton beam of $1.46\nexp{10}$, or $2.34\unit{nC}$ and $7\unit{kA}$, is needed
-to drive an $E_{z}$ field of a comparable magnitude.
+In the QuickPIC simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we
+expect to see from the self-modulated SPS beam in AWAKE Run 2. The baseline AWAKE drive beam contains $3\nexp{11}$
+protons \cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded
+in the middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during
+self-modulation. The needed gap between the two plasma cells also contributes to a decreased density of protons near the
+axis, and some of the field is drained by other protons seeing an accelerating phase within the drive beam itself. In
+total, the expected peak $E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in
+the second cell \cite{awake_collaboration:2016}. A single proton bunch of $1.46\nexp{10}$, or $2.34\unit{nC}$ and
+$7\unit{kA}$ was able to drive an $E_{z}$ field of a comparable magnitude in our single drive bunch setup.
 
-The single bunch approach was chosen to reduce simulation time for the 3D simulations, and to create a stable
-environment for the witness beam. We are not considering the evolution of the proton beam in this test setup, so to
-prevent the proton beam from evolving radially, we also increased its mass.
+The single bunch approach also has the benefit of reducing simulation time for the 3D simulations. Our aim was to create
+a stable environment for the witness beam. We are not considering the evolution of the proton beam in this test setup,
+so to prevent the proton beam from evolving radially, we increased the drive beam particle mass by a factor of
+$1\mexp{6}$.
 
 The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. The
-plasma electrons are depleted to around $65\%$ of nominal plasma density at the injection point of the electron beam.
-This condition is replicated in out single bunch case as the peak density of the drive beam is $0.83\cdot n_{0}$. The
-single bunch setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size
-$\sigma_{r} = 200\unit{\mu m}$. The length of the bunch $\sigma_{z} = 40\unit{\mu m}$.
+plasma electrons are depleted to around $65\%$ of nominal plasma density at the injection point of the electron beam in
+reference simulations \cite{awake_collaboration:2016}. This condition is replicated in out single bunch case. The peak
+density of the drive beam is $0.83\cdot n_{0}$ producing a quasi-linear condition behind it. The single bunch setup uses
+the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size $\sigma_{r} = 200\unit{\mu m}$
+throughout the plasma cell. The length of the drive bunch $\sigma_{z} = 40\unit{\mu m}$.
 
@@
 set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This was done to eliminate the problem of initial de-phasing of the
-witness beam. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
-\cite{gschwendtner:2016}. Beam loading of a short witness beam is sensitive to its position relative to the field
-\cite{tzoufras:2009}. AWAKE Run 2 will likely require a higher initial energy, but a $W_{eb} = 30-50\unit{MeV}$ is
-sufficient to minimise de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$ \cite{berglyd_olsen:2015}. For this case
-we have eliminated it entirely in order to reduce the number of variables in our parameter scans.
+witness beam. Beam loading of a short witness beam is sensitive to its position relative to the field
+\cite{tzoufras:2009}. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
+\cite{gschwendtner:2016}. In Run 2 the experiment will likely require a higher initial energy, but a
+$W_{eb} \approx 50\unit{MeV}$ is sufficient to minimise de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$
+\cite{berglyd_olsen:2015}. For this case we have eliminated this source of de-phasing entirely in order to reduce the
+number of variables.
 
-Earlier simulations with witness beam $\sigma_{r} = 100\unit{\mu m}$ caused the beam radius to undergo rapid transverse
-evolution as the beam enters the plasma, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
-\cite{berglyd_olsen:2016}. This is due to a mismatch between beam emittance and the plasma density. This relation is
-given by
+Earlier simulations with witness beam radius $\sigma_{r} = 100\unit{\mu m}$ caused the beam to undergo rapid transverse
+evolution as the beam entered the plasma region, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
+\cite{berglyd_olsen:2016}. This was primarily due to a mismatch between beam emittance and the plasma density. This
+relation is given by
 \begin{align}
@@
 \end{align}
-where $\lambda_{p}$ is the plasma wavelength. In these simulations we have used matched beams for emittances between
-$2$ and $6\unit{\mu m}$, corresponding to $\sigma_{r}$ ranging from $5.25\unit{\mu m}$ to $9.09\unit{\mu m}$.
+where $\lambda_{p}$ is the plasma wavelength.
+
+In these simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
+$\sigma_{r}$ of $5.25\unit{\mu m}$. The relatively small size of the witness beam compared to the proton beam put some
+restrictions on the transverse resolution of the witness beam. The transverse grid cell resolution was set to
+$1.17\unit{\mu m}$.
 
@@
 prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
-sees consistent fields throughout the plasma stage. The field generated by the proton drive bunch is seen as the dotted
-line in figure \ref{Fig:BeamLoading}. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear
-regime but near non-linear \cite{rosenzweig:2010}. There is some depletion of plasma electrons, but not enough to form a
-bubble. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density
-has a depletion of $67\%$.
+sees consistent wakefields throughout the plasma stage. The $E_{z}$-field generated by the proton drive bunch is seen as
+the blue line in figure \ref{Fig:BeamLoading}, shown with and without the electron beam present. With a proton beam
+density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near non-linear \cite{rosenzweig:2010}. There is
+some depletion of plasma electrons, but not enough to form a bubble. The dashed green line in the lower part of figure
+\ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of $67\%$, close to what we see in full
+scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
 
@@
 
-The witness bunch generates its own wakefield, which in the accelerating phase cancels out the $E_{z}$ field generated
-by the drive bunch. For a finite length bunch this causes the particles in the tail of the witness bunch to be
-accelerated less than those at the front resulting in high energy spread in exchange for high energy transfer
+The witness bunch generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
+generated by the drive bunch. For a finite length bunch this causes the particles in the tail of the witness bunch to be
+accelerated less than those at the front resulting in higher energy spread in exchange for higher energy transfer
 \cite{van_der_meer:1985}. Since $E_{z} \propto \rho_{b}$, a beam profile $\rho_{b}(\xi)$ that perfectly flattens the
-accelerating field within the witness beam, reduces energy spread to zero. The ideal shape is triangular or trapezoidal
-with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
+accelerating field within the witness beam will reduces energy spread to zero. The ideal shape is triangular or
+trapezoidal with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
 
@@
     \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
-        plasma position. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
+        plasma positions. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
         particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
@@
 
-For Gaussian beams a reasonable flat field and consequently low energy spread can be achieved by controlling the charge
-density. In our case, with a matched beam to the plasma density defined by equation \ref{EQ:Matched}, we are limited on
-how much total charge we can accelerate. The test case shown in figures \ref{Fig:BeamLoading} and
+For Gaussian beams a reasonable flat field, and consequently low energy spread, can be achieved by controlling the
+charge density to achieve a similar effect. This, however, puts the front of the witness bunch outside of the ideal
+region while the middle bulk of the beam has a trapezoidal-like shape. In our case, with a matched beam to the plasma
+density defined by equation \ref{EQ:Matched}, we are limited on how much total charge we can accelerate without reaching
+charge densities that will overload the field. The test case shown in figures \ref{Fig:BeamLoading} and
 \ref{Fig:PlasmaDenTWake} has a total charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial
@@
 
-As illustrated in figure \ref{Fig:BeamPS}, our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam, as
+As illustrated in figure \ref{Fig:BeamPS} our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam, as
 expected, shows a difference in energy transfer to the tail of the beam compared to the centre where the $E_{z}$-field
-is nearly flat. Also the front of the beam has a large tail in momentum space corresponding to a smaller acceleration
-gradient. The positioning of the witness beam is chosen to put the bulk of the charge as close to the peak accelerating
-field as possible, but prioritising the tail end over the front as the front is in any case in the quasi-linear regime.
+is nearly flat. Also the front of the beam has a large tail in momentum space as this regions sees a consistently
+smaller accelerating field. The positioning of the witness beam is chosen to put the bulk of the charge as close to the
+peak accelerating field as possible.
 
 Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
-non-linear regime with $n_{eb} \approx 35\times n_{0}$. The wakefield is driven by the beam's own front. The space
-charge rapidly becomes high enough to start expel plasma electrons from the beam axis, and form the characteristic
+non-linear regime with $n_{eb} \approx 35\times n_{0}$. This second wakefield is driven by the beam's own front. The
+space charge rapidly becomes high enough to start expel plasma electrons from the beam axis, and form the characteristic
 electrons sheet that defines the blowout regime. As a result the plasma region reaches full depletion close to the peak
@@
 beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
-of the beam where normalised emittance is preserved.
+of the beam where normalised emittance is preserved. This has the potential to cause overloading of the field. However,
+our $100\unit{pC}$ case is slightly under loaded, and this does not seem to be a significant effect in this instance.
 
@@
 
-Our configuration also shows some robustness to electron beam transverse offset as the bubble generated by the witness
-beam wakefield follows the beam. The head of the beam does not benefit from this effect, and we see some defocusing in
-this region (see bottom, right plot of figure \ref{Fig:BeamFilament}). However, since the proton wakefield creates a
-quasi linear condition, we still see the head of the beam stabilising (see top, right plot of figure
-\ref{Fig:BeamFilament}). The off-axis case has a larger initial emittance growth (left side plot of figure
-\ref{Fig:BeamFilament}), but the growth levels off after the first few metres and stays constant for the remainder of
-the plasma accelerator section (figure \ref{Fig:BeamEmitt}).
+Our configuration also shows some robustness to small electron bunch transverse offsets as the bubble generated by the
+witness bunch wakefield follows the bunch itself. The head of the bunch does not benefit from this effect, and we see
+some defocusing in this region. This effect is likely to be greater for larger offsets as the bunch oscillates around
+the axis of the drive bunch wakefield (see right hand plots of figure \ref{Fig:BeamFilament}). However, since the proton
+wakefield creates a quasi linear condition, we still see the head of the beam stabilising after some time. The off-axis
+case has a larger initial emittance growth (see left hand plots of figure \ref{Fig:BeamFilament}), but the growth levels
+off after the first few metres and stays constant for the remainder of the plasma accelerator section (figure
+\ref{Fig:BeamEmitt}).
 
@@
 
-For accelerator applications in general, and also for Run II of the AWAKE experiment, it is desirable to maximise the
-charge that can be successfully accelerated in the witness bunch. However, since longitudinally constant accelerating
-fields depend on both the position and the charge density of the witness beam \cite{katsouleas:1987, tzoufras:2009}.
+For accelerator applications in general, and also for Run 2 of the AWAKE experiment, it is desirable to maximise the
+charge that can be successfully accelerated in the witness bunch. However, a longitudinally constant accelerating
+field depends on both the position and the charge density of the witness beam \cite{katsouleas:1987, tzoufras:2009}.
 
@@
 
-A higher charge beam will generate a non-linear wakefield sooner, which in turns ensures that a smaller portion of the
-beam experiences the quasi-linear region with emittance growth. As figure \ref{Fig:BeamQAbs} illustrates, a higher
-charge also results in a lower energy gain.
+A higher charge beam will generate a non-linear wakefield closer to the head of the bunch, which in turns ensures that a
+smaller portion of the beam experiences the quasi-linear region with emittance growth. As figure \ref{Fig:BeamQAbs}
+illustrates, a higher charge also results in a lower energy gain.
 

### 2017-08-30 Tex/Paper.tex
Applied some corrections and changes from Patric

@@
 Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
-gradients, and has been of interest for several decades \cite{chen:1985}. A relativist beam travelling through a plasma
-will excite a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading, the
-witness beam can have a high acceleration gradient. Acceleration of an electron beam by an electron drive bunch has been
-demonstrated experimentally \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. The AWAKE experiment at
-CERN is a proof of concept proton driven plasma wakefield accelerator \cite{awake_collaboration:2014}.
+gradients, and have been of interest for several decades \cite{chen:1985}. A relativist beam travelling through a plasma
+excites a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading, increase
+in energy spread can be kept to a minimum. Acceleration of an electron bunch by an electron drive bunch has been
+demonstrated experimentally \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. AWAKE at CERN is a proof
+of concept proton driven plasma wakefield accelerator experiment \cite{awake_collaboration:2014}.
 
-A major challenge with plasma wakefield accelerators is, however, to produce an accelerated beam with a minimal increase
-in energy spread and emittance. In the well described linear case where the beam density $n_{b}$ is much smaller than
-the plasma density $n_{0}$ the plasma causes emittance growth in the beam. A finite length beam will also see a varying
-transverse wakefield causing increasing energy spread \cite{katsouleas:1987}. In the non-linear regime, where
-$n_{b} > n_{0}$, the drive beam sees an unvarying transverse field due to a bubble forming in the plasma behind the
-drive beam. The bubble is formed by the transverse oscillations of the plasma electrons which move near uniformly as a
-function of distance from the drive beam, forming a sheet around an evacuated area. The much heavier plasma ions have no
-significant movement within the relevant time frame, and form an ion channel creating a focusing force that scales
-linearly with the radius. This produces an angularly symmetric focusing force \cite{lu:2006-1, lu:2006}. This effect
-also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread is still
-dependent on beam loading of the longitudinal e-field, $E_{z}$. Non-uniform beam loading can be negated by specially
-shaped beams that optimally flattens the field \cite{katsouleas:1987, tzoufras:2009}, but this is difficult
-experimentally and is not a topic explored in this paper.
+A major challenge with plasma wakefield accelerators is, however, to produce an accelerated beam while keeping growth in
+energy spread and emittance as low as possible. In the well described linear case where the beam density $n_{b}$ is much
+smaller than the plasma density $n_{0}$ the transverse wakefields cause emittance growth of the accelerated bunch. A
+finite length bunch will also see a transversely varying accelerating field causing increasing energy spread
+\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, the drive beam sees a constant transverse field
+due to a bubble forming in the plasma behind the drive beam. The bubble is formed by the transverse oscillations of the
+plasma electrons in the wake of the drive bunch, forming a sheet around an evacuated area. The much heavier plasma ions
+have no significant transverse movement within the time frame of the plasma electron oscillation as these are
+proportional to $sqrt{m}$. The ions form an ion channel creating a focusing force that varies linearly with radius. This
+produces an angularly symmetric focusing force \cite{lu:2006-1, lu:2006}. This effect also avoids the issue of
+increasing energy spread due to transverse beam loading. Increase in energy spread is still dependent on beam loading
+$E_{z}$. Ideal beam loading can be achieved by specially shaped beams that optimally flattens the field
+\cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not a topic explored in this paper.
 
@@
 A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where
-\begin{align}
-    \lambda_{p} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
-\end{align}
-and
-\begin{align}
-    \omega_{pe} = \sqrt{\frac{n_{0} e^{2}}{m_{e} \epsilon_{0}}}, \label{EQ:OmegaP}
-\end{align}
-%$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
-will drive an increasingly strong field $E_{z}$ for each bunch \cite{chen:1985}. A tailing witness beam loading the peak
-accelerating phase of this field will quickly gain energy from the wakefield. Acceleration of an electron witness beam
-driven by two electron drive beams was demonstrated at Brookhaven National Laboratory \cite{muggli:2011}. However,
-electron drive bunches will quickly lose energy to the plasma, and the accelerating witness beam will eventually catch
-up with the drive beam and the acceleration stop.
+%~ \begin{align}
+    %~ \lambda_{p} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
+%~ \end{align}
+%~ and
+%~ \begin{align}
+    %~ \omega_{pe} = \sqrt{\frac{n_{0} e^{2}}{m_{e} \epsilon_{0}}}, \label{EQ:OmegaP}
+%~ \end{align}
+$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
+will produce a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness beam loading the
+peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches. Acceleration of
+an electron witness beam driven by two electron drive beams was demonstrated at Brookhaven National Laboratory
+\cite{muggli:2011}.
 
-This de-phasing problem can be minimised by instead using a proton drive bunch \cite{caldwell:2009}. Proton beams, like
-for instance the LHC and SPS beams at CERN, are ideal candidates for such an accelerator. However, they are orders of
-magnitude longer than the plasma wavelengths needed for such applications. This issue is resolved by letting the proton
-beam undergo self-modulation before injecting the witness beam into one of the buckets in the modulated structure. This
-self-modulation instability is caused by the transverse fields generated by the beam acting upon the beam itself,
-causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the
-plasma, and leaves a train of proton bunches along the beam axis with a surrounding halo.
+The energy carried by electron drive bunches used in previous experiments is typically small, on the order of
+$100\unit{J}$, and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. De-phasing of the
+witness bunch relative to the drive bunch, caused by loss of energy in the drive bunch and gain of energy in the witness
+bunch, limits the effective length of a plasma accelerator stage. Proton drive beams available at CERN carry
+significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator
+stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications.
+This issue is resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of
+the buckets in the modulated structure. This self-modulation instability is caused by the transverse fields generated by
+the beam acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation
+frequency is close to that of the plasma, and leaves a train of proton bunches along the beam axis with a surrounding
+halo.
 
@@
 
-The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam as its driver. The first run
-of the experiment is set up with a $10\unit{m}$ rubidium vapour cell. The rubidium vapour is ionised by a
-$780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$. The nominal plasma density of
-the AWAKE experiment is $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to a plasma
-wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam such that
-$k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first phase of Run 1
-of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the wake field with a long
-electron bunch. The study presented here is for Run 2, which aims to demonstrate acceleration of a short electron bunch
-to high energy with a minimal increase in emittance and energy spread.
+The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam at $400\unit{GeV}$ as its
+driver. The first run of the experiment is set up with a $10\unit{m}$ rubidium vapour cell. The rubidium vapour is
+ionised by a $780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$. The nominal
+plasma density of the AWAKE experiment is $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
+corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam
+such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
+phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the
+wakefield with a long electron bunch. The study presented here is for Run 2, which aims to demonstrate acceleration of a
+short electron bunch to high energy with a minimal increase in emittance and energy spread.
 
@@
 keep this as short as possible \cite{adli:2016}.
+
+\vspace{1em}
+\noindent\textbf{From Patric, expand and add this:}\\
+Then I would propose to state that the SM does not create a focusing force increasing linearly with radius because not
+all e- are evacuated. The state that because the structure is small, a  bunch with significant charge and reasonable
+current is not much shorter than the structure size and thus large energy spread is expected.
 

### 2017-08-30 Tex/Paper.tex
More text tinkering

@@
 
-\vspace{1em}
-\noindent\textbf{From Patric, expand and add this:}\\
-Then I would propose to state that the SM does not create a focusing force increasing linearly with radius because not
-all e- are evacuated. The state that because the structure is small, a  bunch with significant charge and reasonable
-current is not much shorter than the structure size and thus large energy spread is expected.
+With this experimental design the self-modulated proton beam does not produce a non-linear wakefield, and not all plasma
+electrons are therefore evacuated. The result is that the focusing force will not increase linearly with radius. The
+small size of the accelerating structure produced by the self-modulated beam also put constraints on the size of the
+electron witness bunch, and thus its charge and current, if we wish to prevent large energy spread. By matching the
+transverse size to a practical emittance and the plasma density, we prevent large amplitude oscillations which may cause
+additional growth in energy spread as well as in emittance.
+
+This beam matching relation is given by
+\begin{align}
+    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+\end{align}
+where $\lambda_{p}$ is the plasma wavelength. For a reasonable initial emittance of $2\unit{\mu m}$, this corresponds to
+a $\sigma_{r}$ of $5.25\unit{\mu m}$ -- a very narrow bunch compared to the drive beam initial
+$\sigma_{r} = 200\unit{\mu m}$. This charge density of this compact witness bunch reaches that of the plasma density at
+only a few $\unit{pC}$. It only and reaches optimal beam loading at around $1-200\unit{pC}$, the implication being that
+the witness bunch produces its own non-linear wakefield already at the head of the bunch. The majority of the electrons
+within it will therefore see a linear focusing force preventing the bulk of the beam from undergoing emittance growth.
 
@@
 
-The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors that
-may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
+The main focus of this study has been on the beam loading of the electron bunch. In order to eliminate other factors
+that may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
 modulation studies.
@@
 
-In order to evaluate the quality of the beam, we also needed to study emittance evolution. However, full PIC codes like
-Osiris are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
-This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic fields to be lower than
-$c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing the Yee solver with a
-solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is still prominent in the
-high density regions of the electron beam, making it difficult to distinguish emittance growth from the physics from
-that originating from numerical error.
+In order to evaluate the quality of the accelerated bunch it was also necessary to study emittance evolution. However,
+full PIC codes like Osiris are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect''
+\cite{godfrey:1974}. This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic
+fields to be lower than $c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing
+the Yee solver with a solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is
+still prominent in the high density regions of our very compact electron bunch, making it difficult to distinguish
+emittance growth from the physics from that originating from numerical error, and for long simulations drowning it
+entirely.
 
-Quasi-static PIC codes do not suffer this problem, so in order to study the emittance evolution of the beam we instead
-turned to the recently released open source version QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D PIC
-code \cite{huang:2006, an:2013}.
+In order to study the witness bunch emittance evolution we turned to the recently released open source version of
+QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}. The
+numerical Cherenkov effect does not apply to such quasi-static codes.
 
@@
 
-In the QuickPIC simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we
+In these QuickPIC simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we
 expect to see from the self-modulated SPS beam in AWAKE Run 2. The baseline AWAKE drive beam contains $3\nexp{11}$
 protons \cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded
-in the middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during
-self-modulation. The needed gap between the two plasma cells also contributes to a decreased density of protons near the
-axis, and some of the field is drained by other protons seeing an accelerating phase within the drive beam itself. In
-total, the expected peak $E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in
-the second cell \cite{awake_collaboration:2016}. A single proton bunch of $1.46\nexp{10}$, or $2.34\unit{nC}$ and
-$7\unit{kA}$ was able to drive an $E_{z}$ field of a comparable magnitude in our single drive bunch setup.
+in the middle of the unmodulated bunch. In addition, a significant portion of the protons are lost from the near axis
+region during self-modulation. The needed gap between the two plasma cells also contributes to a decreased density of
+protons near the axis, and some of the field is drained by other protons seeing an accelerating phase within the drive
+beam itself. In total, the expected peak $E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to
+$500-600\funit{MV}{m}$ in the second cell \cite{awake_collaboration:2016}. A single proton bunch of $1.46\nexp{10}$,
+or $2.34\unit{nC}$ and $7\unit{kA}$ was able to drive an $E_{z}$ field of a comparable magnitude in our single drive
+bunch setup.
 
-The single bunch approach also has the benefit of reducing simulation time for the 3D simulations. Our aim was to create
-a stable environment for the witness beam. We are not considering the evolution of the proton beam in this test setup,
-so to prevent the proton beam from evolving radially, we increased the drive beam particle mass by a factor of
-$1\mexp{6}$.
-
-The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. The
-plasma electrons are depleted to around $65\%$ of nominal plasma density at the injection point of the electron beam in
-reference simulations \cite{awake_collaboration:2016}. This condition is replicated in out single bunch case. The peak
-density of the drive beam is $0.83\cdot n_{0}$ producing a quasi-linear condition behind it. The single bunch setup uses
+As the baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble, the
+plasma electrons are only depleted to around $65\%$ of nominal plasma density at the point where we inject the electron
+bunch in reference simulations \cite{awake_collaboration:2016}. This condition is replicated in out single bunch case.
+The peak density of the drive beam is $0.83\cdot n_{0}$, producing a quasi-linear wakefield. The single bunch setup uses
 the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size $\sigma_{r} = 200\unit{\mu m}$
-throughout the plasma cell. The length of the drive bunch $\sigma_{z} = 40\unit{\mu m}$.
+throughout the plasma cell. The length of the drive bunch in these simulations is $\sigma_{z} = 40\unit{\mu m}$.
+In order to create a stable environment to study the evolution of the witness bunch we prevented the proton beam from
+evolving radially by increasing the particle mass by a factor of $1\mexp{6}$. We are not considering the evolution of
+the proton beam in this study.
 
@@
 witness beam. Beam loading of a short witness beam is sensitive to its position relative to the field
-\cite{tzoufras:2009}. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
-\cite{gschwendtner:2016}. In Run 2 the experiment will likely require a higher initial energy, but a
-$W_{eb} \approx 50\unit{MeV}$ is sufficient to minimise de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$
-\cite{berglyd_olsen:2015}. For this case we have eliminated this source of de-phasing entirely in order to reduce the
-number of variables.
+\cite{tzoufras:2009}, and the number of inter-dependent parameters is already large for these simulations. AWAKE
+baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$ \cite{gschwendtner:2016}, but in Run 2
+the experiment will likely require a higher initial energy A $W_{eb} \approx 50\unit{MeV}$ is sufficient to minimise
+de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$ \cite{berglyd_olsen:2015}.
 
-Earlier simulations with witness beam radius $\sigma_{r} = 100\unit{\mu m}$ caused the beam to undergo rapid transverse
-evolution as the beam entered the plasma region, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
-\cite{berglyd_olsen:2016}. This was primarily due to a mismatch between beam emittance and the plasma density. This
-relation is given by
-\begin{align}
-    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
-\end{align}
-where $\lambda_{p}$ is the plasma wavelength.
+Earlier simulations were done using Run 1 witness bunch parameters, with radius $\sigma_{r} = 100\unit{\mu m}$. This
+caused the bunch to undergo rapid transverse evolution as the it entered the plasma region, reducing its $\sigma_{r}$
+from $100\unit{\mu m}$ to $< 10\unit{\mu m}$ \cite{berglyd_olsen:2016}. This transverse evolution was primarily due to a
+mismatch between beam emittance and the plasma density, but was difficult to avoid as narrow on-axis bunches were
+numerically difficult to resolve sufficiently in cylindrical geometry.
 
-In these simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
+In these 3D simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
 $\sigma_{r}$ of $5.25\unit{\mu m}$. The relatively small size of the witness beam compared to the proton beam put some
-restrictions on the transverse resolution of the witness beam. The transverse grid cell resolution was set to
-$1.17\unit{\mu m}$.
+restrictions on the transverse resolution of the witness beam also in these simulations. The transverse grid cell
+resolution was set to $1.17\unit{\mu m}$, and the witness bunch was simulated with $16.8+unit{M}$ non-weighted
+particles.
 

### 2017-08-31 Tex/Paper.tex
Edits after meeting with Erik

--- 2017-08-30 Tex/Paper.tex
@@
 
-\title{Emittance preservation of an electron bunch in a loaded quasi-linear plasma wakefield}
+\title{Emittance preservation of an electron beam in a loaded quasi-linear plasma wakefield}
 
@@
 plasma wakefield driven by a short proton beam. The structure of the wakefield is similar to that of a long, modulated
-proton beam. By selecting transverse and longitudinal electron beam parameters in order to appropriately load the wake,
-we show that the bulk of the electron beam can be accelerated without significant emittance growth.
+proton beam, such as the one being studied by AWAKE.  We show that by exploiting two well known effects, full blow out
+of plasma electrons by the accelerated beam, and beam loading of the wake field, the electron beam can be accelerated
+without significant emittance growth.
 \end{abstract}
@@
 excites a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading, increase
-in energy spread can be kept to a minimum. Acceleration of an electron bunch by an electron drive bunch has been
+in energy spread can be kept to a minimum. Acceleration of an electron withness beam by an electron drive beam has been
 demonstrated experimentally \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. AWAKE at CERN is a proof
@@
 energy spread and emittance as low as possible. In the well described linear case where the beam density $n_{b}$ is much
-smaller than the plasma density $n_{0}$ the transverse wakefields cause emittance growth of the accelerated bunch. A
-finite length bunch will also see a transversely varying accelerating field causing increasing energy spread
+smaller than the plasma density $n_{0}$, the non-linear transverse wakefields cause emittance growth of the accelerated
+beam. A finite length beam will also see a transversely varying accelerating field causing increasing energy spread
 \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, the drive beam sees a constant transverse field
 due to a bubble forming in the plasma behind the drive beam. The bubble is formed by the transverse oscillations of the
-plasma electrons in the wake of the drive bunch, forming a sheet around an evacuated area. The much heavier plasma ions
-have no significant transverse movement within the time frame of the plasma electron oscillation as these are
-proportional to $sqrt{m}$. The ions form an ion channel creating a focusing force that varies linearly with radius. This
-produces an angularly symmetric focusing force \cite{lu:2006-1, lu:2006}. This effect also avoids the issue of
-increasing energy spread due to transverse beam loading. Increase in energy spread is still dependent on beam loading
-$E_{z}$. Ideal beam loading can be achieved by specially shaped beams that optimally flattens the field
-\cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not a topic explored in this paper.
+plasma electrons in the wake of the drive beam, forming a sheet around an evacuated area. The ions, assumed stationary,
+form an ion channel creating a focusing force that varies linearly with radius. This
+produces an axially symmetric focusing force \cite{lu:2006-1, lu:2006}.
+%~ This effect also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread
+%~ is still dependent on beam loading $E_{z}$.
+%~ Ideal beam loading can be achieved by specially shaped beams that optimally flattens the field
+%~ \cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not a topic explored in this paper.
 
@@
 
-The energy carried by electron drive bunches used in previous experiments is typically small, on the order of
+The energy carried by electron drive bunches used in previous experiments were typically small, on the order of
 $100\unit{J}$, and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. De-phasing of the
-witness bunch relative to the drive bunch, caused by loss of energy in the drive bunch and gain of energy in the witness
-bunch, limits the effective length of a plasma accelerator stage. Proton drive beams available at CERN carry
+witness beam relative to the drive beam, caused by loss of energy in the drive beam and gain of energy in the witness
+beam, limits the effective length of a plasma accelerator stage. Proton drive beams available at CERN carry
 significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator
@@
 % ******************************************************************************************************************** %
-\subsection[\label{S:I:AWAKE}]{The AWAKE Experiment}
+\subsection[\label{S:I:AWAKE}]{AWAKE Run 2}
 % ******************************************************************************************************************** %
 
+%~ The first run of the experiment is set up with a $10\unit{m}$ rubidium vapour cell.
+%~ The rubidium vapour is
+%~ ionised by a $780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$.
 The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam at $400\unit{GeV}$ as its
-driver. The first run of the experiment is set up with a $10\unit{m}$ rubidium vapour cell. The rubidium vapour is
-ionised by a $780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$. The nominal
-plasma density of the AWAKE experiment is $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
+driver, and a nominal plasma density $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
 corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam
@@
 phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the
-wakefield with a long electron bunch. The study presented here is for Run 2, which aims to demonstrate acceleration of a
-short electron bunch to high energy with a minimal increase in emittance and energy spread.
+wakefield with a long electron beam. The study presented here is for Run 2 \cite{adli:2016}, which aims to demonstrate
+acceleration of a short electron beam to high energy with a minimal increase in emittance and energy spread.
 
@@
 the electron beam present. The electron witness beam will be injected into the modulated proton beam before stage two,
-where acceleration will occur. As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
-keep this as short as possible \cite{adli:2016}.
+where acceleration will occur.
+%~ As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
+%~ keep this as short as possible.
 
-\vspace{1em}
-\noindent\textbf{From Patric, expand and add this:}\\
-Then I would propose to state that the SM does not create a focusing force increasing linearly with radius because not
-all e- are evacuated. The state that because the structure is small, a  bunch with significant charge and reasonable
-current is not much shorter than the structure size and thus large energy spread is expected.
+With this experimental design the self-modulated proton beam does not produce a non-linear wakefield, and not all plasma
+electrons are therefore evacuated. The result is that the focusing force will not increase linearly with radius. The
+small size of the accelerating structure produced by the self-modulated beam also put constraints on the size of the
+electron witness beam, and thus its charge and current, if we wish to prevent large energy spread. By matching the
+transverse size to a practical emittance and the plasma density, we prevent large amplitude oscillations which may cause
+additional growth in energy spread as well as in emittance.
+
+The key idea in this paper is that while the proton beam wake is not fully blown-out leading to non-linear focusing
+forces, the electron beam, if intense enough, may load the field and at the same time create its own ion bubble. As will
+be shown, exploiting these two well known effect, the electron beam can be accelerated, for long distances, without
+significant emittance growth.
+
+%~ The beam matching relation is given by
+%~ \begin{align}
+    %~ \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+%~ \end{align}
+%~ where $\lambda_{p}$ is the plasma wavelength. For a reasonable initial emittance of $2\unit{\mu m}$, this corresponds to
+%~ a $\sigma_{r}$ of $5.25\unit{\mu m}$ -- a very narrow bunch compared to the drive beam $\sigma_{r} = 200\unit{\mu m}$.
+%~ The charge density of this compact witness bunch reaches that of the plasma density at only a few $\unit{pC}$, but
+%~ reaches optimal beam loading at around $1-200\unit{pC}$. The implication here being that the witness bunch produces its
+%~ own non-linear wakefield already at the head of the bunch. The majority of the electrons within it will therefore see a
+%~ linear focusing force preventing the bulk of the beam from undergoing emittance growth.
 
@@
 
-The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors that
-may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
+The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors
+that may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
 modulation studies.
@@
 self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
-using 2D cylindrical-symmetric simulations. The proton beam was pre-modulated by a clipped cosine function to its
-longitudinal density profile, with a period matching $\lambda_{pe}$. Its transverse profile was kept as a Gaussian with
-$\sigma_{r} = k_{pe}^{-1} = 200\unit{\mu m}$. The length of the simulation beam was limited to $26\cdot\lambda_{pe}$,
-and the electron beam injected after the 20th micro-bunch \cite{berglyd_olsen:2015}. We performed several parameter
-scans with this setup, testing for the the maximum beam charge that could be accelerated with a high energy gain and low
-energy spread \cite{adli:2016, berglyd_olsen:2016}.
+using 2D cylindrical-symmetric simulations \cite{berglyd_olsen:2015, berglyd_olsen:2016}.
 
-In order to evaluate the quality of the beam, we also needed to study emittance evolution. However, full PIC codes like
-Osiris are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect'' \cite{godfrey:1974}.
-This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic fields to be lower than
-$c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing the Yee solver with a
-solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is still prominent in the
-high density regions of the electron beam, making it difficult to distinguish emittance growth from the physics from
-that originating from numerical error.
+%~ In order to evaluate the quality of the accelerated bunch it was also necessary to study emittance evolution. However,
+%~ full PIC codes are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect''
+%~ \cite{godfrey:1974}. This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic
+%~ fields to be lower than $c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing
+%~ the Yee solver with a solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is
+%~ still prominent in the high density regions of our very compact electron bunch, making it difficult to distinguish
+%~ emittance growth from the physics from that originating from numerical error.
 
-Quasi-static PIC codes do not suffer this problem, so in order to study the emittance evolution of the beam we instead
-turned to the recently released open source version QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D PIC
-code \cite{huang:2006, an:2013}.
+In order to study the witness beam emittance evolution we turned to the recently released open source version of
+QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}.
+Since QuickPIC is a quasi-static code, it does not suffer from the numerical Cherenkov effect that full PIC codes do
+\cite{godfrey:1974,lehe:2013}, it is well suited to study emittance preservation.
 
@@
 
-In the QuickPIC simulations we use a single proton drive bunch that sets up a wakefield comparable to that which we
-expect to see from the self-modulated SPS beam in AWAKE Run 2. The baseline AWAKE drive beam contains $3\nexp{11}$
-protons \cite{gschwendtner:2016}. Only half of these are driving the wakefield, presuming the self-modulation is seeded
-in the middle of the unmodulated bunch. In addition. a significant portion of the protons are lost during
-self-modulation. The needed gap between the two plasma cells also contributes to a decreased density of protons near the
-axis, and some of the field is drained by other protons seeing an accelerating phase within the drive beam itself. In
-total, the expected peak $E_{z}$ field of $~2\funit{GV}{m}$ in the first plasma cell drops to $500-600\funit{MV}{m}$ in
-the second cell \cite{awake_collaboration:2016}. A single proton bunch of $1.46\nexp{10}$, or $2.34\unit{nC}$ and
-$7\unit{kA}$ was able to drive an $E_{z}$ field of a comparable magnitude in our single drive bunch setup.
+In these simulations we use a single proton drive beam that sets up a wakefield comparable to that which we expect to
+see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}). When the
+initial SPS beam containing $3\nexp{11}$ protons \cite{gschwendtner:2016} enters the second plasma cell the peak $E_{z}$
+field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to reach the
+non-linear regime and produce a plasma bubble, the plasma electrons are only depleted to around $65\%$ of nominal plasma
+density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions are replicated
+in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and $7\unit{kA}$.
 
-The single bunch approach also has the benefit of reducing simulation time for the 3D simulations. Our aim was to create
-a stable environment for the witness beam. We are not considering the evolution of the proton beam in this test setup,
-so to prevent the proton beam from evolving radially, we increased the drive beam particle mass by a factor of
-$1\mexp{6}$.
-
-The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. The
-plasma electrons are depleted to around $65\%$ of nominal plasma density at the injection point of the electron beam in
-reference simulations \cite{awake_collaboration:2016}. This condition is replicated in out single bunch case. The peak
-density of the drive beam is $0.83\cdot n_{0}$ producing a quasi-linear condition behind it. The single bunch setup uses
-the baseline proton energy $W_{pb} = 400\unit{GeV}$, and retains the transverse size $\sigma_{r} = 200\unit{\mu m}$
-throughout the plasma cell. The length of the drive bunch $\sigma_{z} = 40\unit{\mu m}$.
+The peak density of the simulation drive beam is $0.83\cdot n_{0}$, producing a quasi-linear wakefield. The single bunch
+setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{r} = 200\unit{\mu m}$. We
+set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. In order to create a stable environment to study the
+evolution of the witness beam we prevented the proton beam from evolving radially by increasing the particle mass by a
+factor of $1\mexp{6}$. We are not considering the evolution of the proton beam itself in this study.
 
@@
 witness beam. Beam loading of a short witness beam is sensitive to its position relative to the field
-\cite{tzoufras:2009}. AWAKE baseline energy for the long witness beam for Run 1 is $W_{eb} = 10-20\unit{MeV}$
-\cite{gschwendtner:2016}. In Run 2 the experiment will likely require a higher initial energy, but a
-$W_{eb} \approx 50\unit{MeV}$ is sufficient to minimise de-phasing as the drift $\Delta\xi \propto \gamma^{-2}$
-\cite{berglyd_olsen:2015}. For this case we have eliminated this source of de-phasing entirely in order to reduce the
-number of variables.
+\cite{tzoufras:2009}. The relative drift causing the de-phasing $\Delta\xi \propto \gamma^{-2}$. By simply matching the
+initial $\gamma$ values we eliminate this effect entirely, but a lower initial value is likely to be sufficient
+\cite{berglyd_olsen:2015}.
 
-Earlier simulations with witness beam radius $\sigma_{r} = 100\unit{\mu m}$ caused the beam to undergo rapid transverse
-evolution as the beam entered the plasma region, reducing its $\sigma_{r}$ from $100\unit{\mu m}$ to $< 10\unit{\mu m}$
-\cite{berglyd_olsen:2016}. This was primarily due to a mismatch between beam emittance and the plasma density. This
-relation is given by
+In these 3D simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
+$\sigma_{r}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
 \begin{align}
@@
 \end{align}
-where $\lambda_{p}$ is the plasma wavelength.
+where $\lambda_{p}$ is the plasma wavelength. This is a very narrow beam compared to the drive beam
+$\sigma_{r} = 200\unit{\mu m}$. The charge density of this compact witness beam reaches that of the plasma density at
+only a few $\unit{pC}$, but reaches optimal beam loading at around $1-200\unit{pC}$. The implication here being that the
+witness beam produces its own non-linear wakefield already at the head of the beam. The majority of the electrons
+within it will therefore see a linear focusing force preventing the bulk of the beam from undergoing emittance growth.
 
-In these simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
-$\sigma_{r}$ of $5.25\unit{\mu m}$. The relatively small size of the witness beam compared to the proton beam put some
-restrictions on the transverse resolution of the witness beam. The transverse grid cell resolution was set to
-$1.17\unit{\mu m}$.
+The relatively small size of the witness beam compared to the proton beam put some restrictions on the transverse
+resolution of the witness beam. We used a transverse grid cell size of $1.17\unit{\mu m}$, and $2.34\unit{\mu m}$ for
+the longitudinal grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles.
 
@@
 prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
-sees consistent wakefields throughout the plasma stage. The $E_{z}$-field generated by the proton drive bunch is seen as
+sees consistent wakefields throughout the plasma stage. The $E_{z}$-field generated by the proton drive beam is seen as
 the blue line in figure \ref{Fig:BeamLoading}, shown with and without the electron beam present. With a proton beam
@@
 
-The witness bunch generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
-generated by the drive bunch. For a finite length bunch this causes the particles in the tail of the witness bunch to be
+The witness beam generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
+generated by the drive beam. For a finite length beam this causes the particles in the tail of the witness beam to be
 accelerated less than those at the front resulting in higher energy spread in exchange for higher energy transfer
@@
 For Gaussian beams a reasonable flat field, and consequently low energy spread, can be achieved by controlling the
-charge density to achieve a similar effect. This, however, puts the front of the witness bunch outside of the ideal
+charge density to achieve a similar effect. This, however, puts the front of the witness beam outside of the ideal
 region while the middle bulk of the beam has a trapezoidal-like shape. In our case, with a matched beam to the plasma
@@
 
-Our configuration also shows some robustness to small electron bunch transverse offsets as the bubble generated by the
-witness bunch wakefield follows the bunch itself. The head of the bunch does not benefit from this effect, and we see
-some defocusing in this region. This effect is likely to be greater for larger offsets as the bunch oscillates around
-the axis of the drive bunch wakefield (see right hand plots of figure \ref{Fig:BeamFilament}). However, since the proton
+Our configuration also shows some robustness to small electron beam transverse offsets as the bubble generated by the
+witness beam wakefield follows the beam itself. The head of the beam does not benefit from this effect, and we see
+some defocusing in this region. This effect is likely to be greater for larger offsets as the beam oscillates around
+the axis of the drive beam wakefield (see right hand plots of figure \ref{Fig:BeamFilament}). However, since the proton
 wakefield creates a quasi linear condition, we still see the head of the beam stabilising after some time. The off-axis
@@
 For accelerator applications in general, and also for Run 2 of the AWAKE experiment, it is desirable to maximise the
-charge that can be successfully accelerated in the witness bunch. However, a longitudinally constant accelerating
+charge that can be successfully accelerated in the witness beam. However, a longitudinally constant accelerating
 field depends on both the position and the charge density of the witness beam \cite{katsouleas:1987, tzoufras:2009}.
@@
 
-A higher charge beam will generate a non-linear wakefield closer to the head of the bunch, which in turns ensures that a
+A higher charge beam will generate a non-linear wakefield closer to the head of the beam, which in turns ensures that a
 smaller portion of the beam experiences the quasi-linear region with emittance growth. As figure \ref{Fig:BeamQAbs}

### 2017-09-01 Tex/Paper.tex
Edits after meeting with Erik for section III

@@
 corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam
-such that $k_{pe}\sigma_{r} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
+such that $k_{pe}\sigma_{x} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
 phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the
@@
 %~ where $\lambda_{p}$ is the plasma wavelength. For a reasonable initial emittance of $2\unit{\mu m}$, this corresponds to
-%~ a $\sigma_{r}$ of $5.25\unit{\mu m}$ -- a very narrow bunch compared to the drive beam $\sigma_{r} = 200\unit{\mu m}$.
+%~ a $\sigma_{x}$ of $5.25\unit{\mu m}$ -- a very narrow bunch compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$.
 %~ The charge density of this compact witness bunch reaches that of the plasma density at only a few $\unit{pC}$, but
@@
 The peak density of the simulation drive beam is $0.83\cdot n_{0}$, producing a quasi-linear wakefield. The single bunch
-setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{r} = 200\unit{\mu m}$. We
+setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
 set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. In order to create a stable environment to study the
@@
 In these 3D simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
-$\sigma_{r}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
+$\sigma_{x}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
 \begin{align}
@@
 where $\lambda_{p}$ is the plasma wavelength. This is a very narrow beam compared to the drive beam
-$\sigma_{r} = 200\unit{\mu m}$. The charge density of this compact witness beam reaches that of the plasma density at
+$\sigma_{x} = 200\unit{\mu m}$. The charge density of this compact witness beam reaches that of the plasma density at
 only a few $\unit{pC}$, but reaches optimal beam loading at around $1-200\unit{pC}$. The implication here being that the
@@
 the longitudinal grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles.
+
+In the following section we study a witness beam with a total charge of $100\unit{pC}$, a $\sigma_{z}=60\unit{\mu m}$,
+and with a $\sigma_{x}=5.23\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We
+refer to this parameter set as our base case.
 
@@
 the blue line in figure \ref{Fig:BeamLoading}, shown with and without the electron beam present. With a proton beam
-density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near non-linear \cite{rosenzweig:2010}. There is
-some depletion of plasma electrons, but not enough to form a bubble. The dashed green line in the lower part of figure
-\ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of $67\%$, close to what we see in full
-scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
+density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near non-linear \cite{rosenzweig:2010}. The dashed
+green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of
+$67\%$, close to what we see in full scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
 
@@
 
-The witness beam generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
-generated by the drive beam. For a finite length beam this causes the particles in the tail of the witness beam to be
-accelerated less than those at the front resulting in higher energy spread in exchange for higher energy transfer
-\cite{van_der_meer:1985}. Since $E_{z} \propto \rho_{b}$, a beam profile $\rho_{b}(\xi)$ that perfectly flattens the
-accelerating field within the witness beam will reduces energy spread to zero. The ideal shape is triangular or
-trapezoidal with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
+%~ The witness beam generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
+%~ generated by the drive beam. For a finite length beam this causes the particles in the tail of the witness beam to be
+%~ accelerated less than those at the front resulting in higher energy spread in exchange for higher energy transfer
+%~ \cite{van_der_meer:1985}. A beam profile $\rho_{b}(\xi)$ that perfectly flattens the
+%~ accelerating field within the witness beam will reduces energy spread to zero. The ideal shape is triangular or
+%~ trapezoidal with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
+
+The witness beam generates its own wakefield which partially cancels out the $E_{z}$ field generated by the drive beam.
+With an ideally shaped electron beam charge profile it is possible to optimally load the field, such that the
+accelerating $E_{z}$ is constant along the bunch \cite{katsouleas:1987, tzoufras:2009}.
 
@@
 
-For Gaussian beams a reasonable flat field, and consequently low energy spread, can be achieved by controlling the
-charge density to achieve a similar effect. This, however, puts the front of the witness beam outside of the ideal
-region while the middle bulk of the beam has a trapezoidal-like shape. In our case, with a matched beam to the plasma
-density defined by equation \ref{EQ:Matched}, we are limited on how much total charge we can accelerate without reaching
-charge densities that will overload the field. The test case shown in figures \ref{Fig:BeamLoading} and
-\ref{Fig:PlasmaDenTWake} has a total charge of $100\unit{pC}$ with a $\sigma_{r}=5.23\unit{\mu m}$ matching an initial
-normalised emittance $\epsilon_{0} = 2\unit{\mu m}$.
+While the ideal shape is trapezodial, for Gaussians beams a reasonable flat field, and consequently low energy spread,
+can be achieved by controlling the charge density to achieve a similar effect. This, however, puts the front of the
+witness beam outside of the ideal region while the middle bulk of the beam has a trapezoidal-like shape. In our case,
+with a matched beam to the plasma density defined by equation \ref{EQ:Matched}, we are limited on how much total charge
+we can accelerate without reaching charge densities that will overload the field.
 
-As illustrated in figure \ref{Fig:BeamPS} our base case of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam, as
-expected, shows a difference in energy transfer to the tail of the beam compared to the centre where the $E_{z}$-field
-is nearly flat. Also the front of the beam has a large tail in momentum space as this regions sees a consistently
-smaller accelerating field. The positioning of the witness beam is chosen to put the bulk of the charge as close to the
-peak accelerating field as possible.
+As illustrated in figure \ref{Fig:BeamPS} our base case shows a difference in energy transfer to the tail of the beam
+compared to the centre where the $E_{z}$-field is nearly flat. Also the front of the beam has a large tail in momentum
+space as this regions sees a smaller accelerating field. The positioning of the witness beam is chosen to put the bulk
+of the charge as close to the peak accelerating field as possible.
 
-Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
-non-linear regime with $n_{eb} \approx 35\times n_{0}$. This second wakefield is driven by the beam's own front. The
-space charge rapidly becomes high enough to start expel plasma electrons from the beam axis, and form the characteristic
-electrons sheet that defines the blowout regime. As a result the plasma region reaches full depletion close to the peak
-of the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam
-axis (see figure \ref{Fig:PlasmaDenTWake}).
+The charge density required to optimally load the $E_{z}$ field is $n_{eb} \approx 35\times n_{0}$. This means that the
+witness beam's own wakefield is in the fully non-linear regime, where the space charge force is sufficient to blow-out
+all plasma electrons resulting in an ion column. This ion column, as is well known \cite{rosenzweig:1991}, provides a
+linear focusing force on the part the electron beam within the ion column, and therefore prevents emittance growth for
+this region. This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
+gradient of $20\unit{kT/m}$ near the beam axis.
+
+%~ Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
+%~ non-linear regime with $n_{eb} \approx 35\times n_{0}$. This second wakefield is driven by the beam's own front. The
+%~ space charge rapidly becomes high enough to start expel plasma electrons from the beam axis and form the characteristic
+%~ electrons sheet that defines the blowout regime. As a result the plasma region reaches full depletion close to the peak
+%~ of the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam
+%~ axis (see figure \ref{Fig:PlasmaDenTWake}).
 
@@
 
-The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
+%~ The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
 For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the beam
-retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows the $100\unit{pC}$ and $\sigma_{z} = 60\unit{\mu m}$
-case extended to a $100\unit{m}$ plasma and the drive beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent
-de-phasing. De-phasing for the SPS beam case starts to become significant after about $50\unit{m}$.
+retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance growth for the base case as a function of
+propagation length. No significant emittance growth was observed for propagation lengths up to $100\unit{m}$. The drive
+beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing. De-phasing for the SPS beam case starts to
+become significant after about $50\unit{m}$.
 
@@
 beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
-of the beam where normalised emittance is preserved. This has the potential to cause overloading of the field. However,
-our $100\unit{pC}$ case is slightly under loaded, and this does not seem to be a significant effect in this instance.
+of the beam where normalised emittance is preserved as shown in figure \ref{Fig:BeamFilament}. This has the potential to
+cause overloading of the field. However, for our base case this effect is not significant.
 
@@
 
-Our configuration also shows some robustness to small electron beam transverse offsets as the bubble generated by the
-witness beam wakefield follows the beam itself. The head of the beam does not benefit from this effect, and we see
-some defocusing in this region. This effect is likely to be greater for larger offsets as the beam oscillates around
-the axis of the drive beam wakefield (see right hand plots of figure \ref{Fig:BeamFilament}). However, since the proton
-wakefield creates a quasi linear condition, we still see the head of the beam stabilising after some time. The off-axis
-case has a larger initial emittance growth (see left hand plots of figure \ref{Fig:BeamFilament}), but the growth levels
-off after the first few metres and stays constant for the remainder of the plasma accelerator section (figure
-\ref{Fig:BeamEmitt}).
+%~ Our configuration also shows some robustness to small electron beam transverse offsets as the bubble generated by the
+%~ witness beam wakefield follows the beam itself.
+
+Since the accelerated electron beam creates its own focusing bubble, the emittance of the part of the beam inside the
+bubble is not affected by small beam offsets with respect to the proton beam axis. This is an added benefit of this new
+accelerating regime, and may ease the transverse injection tolerances. The head of the beam does not benefit from this
+effect, but since the proton beam creates a quasi linear wake, the head of the beam still stabilises after some time.
+This is illustrated on figure \ref{Fig:BeamEmitt} for an electron beam offset of $1\sigma_{x}$. In this case there is a
+larger initial emittance growth (see left hand plots of figure \ref{Fig:BeamFilament}), but the emittance growth stop
+after the first few metres (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the
+beam oscillates around the axis of the drive beam wakefield (see right hand plots of figure \ref{Fig:BeamFilament}).
 

### 2017-09-03 Tex/Paper.tex
Added Erik's suggestions for parameter section and conclusion

@@
 \begin{align}
-    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
 \end{align}
@@
 
-For accelerator applications in general, and also for Run 2 of the AWAKE experiment, it is desirable to maximise the
-charge that can be successfully accelerated in the witness beam. However, a longitudinally constant accelerating
-field depends on both the position and the charge density of the witness beam \cite{katsouleas:1987, tzoufras:2009}.
+The beam loading and blow out properties of the electron beam depends on a large number of parameters: the longitudinal
+profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
 
-The large number of parameters involved makes the problem difficult to solve in simulations, and difficult to measure in
-experiments. Presented in figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} is a parameter scan for a matched beam with
-initial normalised emittance $\epsilon_{N,0}=2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the
-scan with beam charge from $10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to
-$100\unit{\mu m}$. We see from figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a
-well defined minimum energy spread with a beam charge $\geq 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower
-beam charges tend to underload the field, while higher beam charges tend to overload. It is also clear that long beams
-with respect to the accelerating flank of the $E_{z}$-field, $\approx\lambda_{pe}/4$, will not optimally load the field
-along its length thus experiencing a larger spread in energy.
+We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
+For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated
+and minimize the emittance growth. In addition, the bunch length should be such that it is possible to generate and
+transport by a compact electron injector [IPAC]. These are contradictory constraints. We  investigate the
+interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial emittance. We
+quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will depend
+on the application.
 
-A higher charge beam will generate a non-linear wakefield closer to the head of the beam, which in turns ensures that a
-smaller portion of the beam experiences the quasi-linear region with emittance growth. As figure \ref{Fig:BeamQAbs}
-illustrates, a higher charge also results in a lower energy gain.
+Figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} show the dependence on bunch length and bunch charge for an initial beam
+emittance of $2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the scan with beam charges from
+$10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. We see from
+figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy
+spread with a beam charge $\geq 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to
+underload the $E_{z}$-field, while higher beam charges tend to overload it. It is also clear that long beams with
+respect to the accelerating flank of the $E_{z}$-field, $\approx\lambda_{pe}/4$, will not optimally load the field along
+its length thus experiencing a larger spread in energy.
+
+[Discussion of new emittance scan figure(s) to be added.]
 
@@
 % ******************************************************************************************************************** %
+
+We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a quasi-
+linear proton driven wake. When optimally loaded, the electron beam creates its own ion bubble, yielding emittance
+preservation for a large parts of the electron beam.
+
+These result indicates that emittance preservation for an on-axis injected electron beam, properly optimized, is
+feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might be accelerated, for bunches of length
+$40-60\unit{\mu m}$. Such an electron bunch may be generated by a standard S-band RF gun.
+
+As this study assumes a wake driven by a single, short proton beam, the studies for interesting cases for AWAKE should
+be repeated by a full simulation of a self-modulated proton beam.
 

### 2017-09-04 Tex/Paper.tex
Added beam emittance scan figure

@@
 and minimize the emittance growth. In addition, the bunch length should be such that it is possible to generate and
-transport by a compact electron injector [IPAC]. These are contradictory constraints. We  investigate the
+transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We  investigate the
 interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial emittance. We
@@
 
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
+    \caption{\label{Fig:BeamQEmit} }
+\end{figure}
+
 [Discussion of new emittance scan figure(s) to be added.]
-
-% ******************************************************************************************************************** %
-\section[\label{S:D}]{Discussion}
-% discussion of optimal electron beam parameters
-% implications for AWAKE Run 2
-% ******************************************************************************************************************** %
 

### 2017-09-05 Tex/Paper.tex
Last additions after last meeting w/Erik

@@
 beam. A finite length beam will also see a transversely varying accelerating field causing increasing energy spread
-\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, the drive beam sees a constant transverse field
-due to a bubble forming in the plasma behind the drive beam. The bubble is formed by the transverse oscillations of the
-plasma electrons in the wake of the drive beam, forming a sheet around an evacuated area. The ions, assumed stationary,
-form an ion channel creating a focusing force that varies linearly with radius. This
-produces an axially symmetric focusing force \cite{lu:2006-1, lu:2006}.
+\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the transverse
+oscillations of the plasma electrons forming a sheet around an evacuated area leaving only ions. The ions, assumed
+stationary, form an ion channel creating a focusing force that varies linearly with radius. This produces an axially
+symmetric focusing force \cite{lu:2006-1, lu:2006}.
 %~ This effect also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread
@@
 The energy carried by electron drive bunches used in previous experiments were typically small, on the order of
-$100\unit{J}$, and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. De-phasing of the
-witness beam relative to the drive beam, caused by loss of energy in the drive beam and gain of energy in the witness
-beam, limits the effective length of a plasma accelerator stage. Proton drive beams available at CERN carry
+$100\unit{J}$, and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. The energy of a
+high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam in the international linear collider with
+$1\mexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers as drivers a large number of plasma stages
+is required. How to efficiently stage plasma accelerators is challenging without reducing the effective gradient and
+spoiling the beam quality \cite{steinke:2016,lindstrom:2016}. Proton drive beams available at CERN carry
 significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator
@@
 halo.
+%~ De-phasing of the
+%~ witness beam relative to the drive beam, caused by loss of energy in the drive beam and gain of energy in the witness
+%~ beam, limits the effective length of a plasma accelerator stage.
 
@@
     \caption{\label{Fig:BeamQ} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial beam charge (blue), and relative energy spread (red), after $4\unit{m}$ of plasma and with
-        an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from
-        $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam loading section corrspond to the
-        square marked lines at $100\unit{pC}$.}
+        function of initial beam charge (blue), and relative energy spread of the accepted charge (red), after
+        $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These are shown for four
+        different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam
+        loading section corrspond to the square marked lines at $100\unit{pC}$.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} }
+    \caption{\label{Fig:BeamQEmit} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
+        function of initial emittance (blue), and relative energy spread of the accepted charge (red), after $4\unit{m}$
+        of plasma.}
 \end{figure}
 
-[Discussion of new emittance scan figure(s) to be added.]
+Figure \ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
+emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
+to growth for high emittance beams; the transverse beam size may increase beyond the size of the bubble, or the beam
+density may be reduced so much that the plasma electrons are no longer fully evacuated from the ion column. Emittance
+values higher than a few micrometers lead to a significant increase in both emittance and energy spread. In these
+simulations the focusing of the beam to the plasma remains matched for each emittance value.
 

### 2017-09-12 Tex/Paper.tex
Cleanup

@@
 \newcommand{\funit}[2]{\,\mathrm{#1}/\mathrm{#2}}
-\newcommand{\mexp}[1]{\mathrm{e}^{#1}}
+\newcommand{\mexp}[1]{\mathrm{e}{#1}}
 \newcommand{\nexp}[1]{\times 10^{#1}}
@@
 Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
-gradients, and have been of interest for several decades \cite{chen:1985}. A relativist beam travelling through a plasma
-excites a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading, increase
-in energy spread can be kept to a minimum. Acceleration of an electron withness beam by an electron drive beam has been
-demonstrated experimentally \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} in the past. AWAKE at CERN is a proof
-of concept proton driven plasma wakefield accelerator experiment \cite{awake_collaboration:2014}.
+gradients, and have been of interest for several decades \cite{chen:1985}. A relativistic beam travelling through a
+plasma excites a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading,
+an increase in energy spread can be kept to a minimum. Acceleration of an electron withness beam by an electron drive
+beam has been demonstrated experimentally in the past \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at
+CERN is a proof of concept proton driven plasma wakefield accelerator experiment \cite{awake_collaboration:2014}.
 
@@
 smaller than the plasma density $n_{0}$, the non-linear transverse wakefields cause emittance growth of the accelerated
-beam. A finite length beam will also see a transversely varying accelerating field causing increasing energy spread
+beam. The beam will also see a transversely varying accelerating field causing increasing energy spread
 \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the transverse
@@
 peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches. Acceleration of
-an electron witness beam driven by two electron drive beams was demonstrated at Brookhaven National Laboratory
+an electron witness beam driven by two electron drive beams has been demonstrated at Brookhaven National Laboratory
 \cite{muggli:2011}.
 
-The energy carried by electron drive bunches used in previous experiments were typically small, on the order of
-$100\unit{J}$, and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. The energy of a
+The energy carried by electron drive bunches used in previous experiments were typically small -- on the order of
+$100\unit{J}$ -- and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. The energy of a
 high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam in the international linear collider with
-$1\mexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers as drivers a large number of plasma stages
+$1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers as drivers, a large number of plasma stages
 is required. How to efficiently stage plasma accelerators is challenging without reducing the effective gradient and
-spoiling the beam quality \cite{steinke:2016,lindstrom:2016}. Proton drive beams available at CERN carry
-significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator
-stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications.
-This issue is resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of
-the buckets in the modulated structure. This self-modulation instability is caused by the transverse fields generated by
-the beam acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation
-frequency is close to that of the plasma, and leaves a train of proton bunches along the beam axis with a surrounding
-halo.
+spoiling the beam quality \cite{steinke:2016,lindstrom:2016}. Proton drive beams available at CERN carry significantly
+more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator stages. However,
+the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications. This issue is
+resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of the buckets in
+the modulated structure. This self-modulation instability is caused by the transverse fields generated by the beam
+acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency
+is close to that of the plasma, and leaves a train of proton bunches along the beam axis with a surrounding halo.
 %~ De-phasing of the
@@
 corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam
-such that $k_{pe}\sigma_{x} = 1$ where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
+such that $k_{pe}\sigma_{x} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
 phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the
@@
 
-The preliminary design of the second run proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}.
+The preliminary design of Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}.
 The first section of $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without
-the electron beam present. The electron witness beam will be injected into the modulated proton beam before stage two,
-where acceleration will occur.
+the electron beam present. The electron witness beam will then be injected into the modulated proton beam before stage
+two, where it undergoes acceleration.
 %~ As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
@@
 
-With this experimental design the self-modulated proton beam does not produce a non-linear wakefield, and not all plasma
-electrons are therefore evacuated. The result is that the focusing force will not increase linearly with radius. The
-small size of the accelerating structure produced by the self-modulated beam also put constraints on the size of the
-electron witness beam, and thus its charge and current, if we wish to prevent large energy spread. By matching the
-transverse size to a practical emittance and the plasma density, we prevent large amplitude oscillations which may cause
-additional growth in energy spread as well as in emittance.
+With this experimental design the self-modulated proton beam does not produce a full non-linear wakefield, and not all
+plasma electrons are therefore evacuated. The result is that the focusing force will not increase linearly with radius.
+The small size of the accelerating structure produced by the self-modulated beam also puts constraints on the size of
+the electron witness beam, and thus its charge and current -- if we at the same time wish to prevent large energy
+spread. By matching the transverse size of the beam at a given emittance to the plasma density, we prevent large
+amplitude oscillations which may cause additional growth in energy spread as well as in emittance.
 
@@
 The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors
-that may affect this, we have tried several approaches to create a stable drive beam structure based on previous self-
-modulation studies.
+that may affect this (add examples?), we have tried several approaches to create a stable drive beam structure based on
+previous self-modulation studies.
 
@@
 Since QuickPIC is a quasi-static code, it does not suffer from the numerical Cherenkov effect that full PIC codes do
-\cite{godfrey:1974,lehe:2013}, it is well suited to study emittance preservation.
+\cite{godfrey:1974,lehe:2013}, making it a well suited code to study emittance preservation.
 
@@
 see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}). When the
-initial SPS beam containing $3\nexp{11}$ protons \cite{gschwendtner:2016} enters the second plasma cell the peak $E_{z}$
-field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to reach the
-non-linear regime and produce a plasma bubble, the plasma electrons are only depleted to around $65\%$ of nominal plasma
-density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions are replicated
-in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and $7\unit{kA}$.
+initial SPS beam containing $3\nexp{11}$ protons \cite{gschwendtner:2016} enters the second plasma cell, the peak
+$E_{z}$ field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to
+reach the non-linear regime and produce a plasma bubble, the plasma electrons are only depleted to around $65\%$ of
+nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions
+are replicated in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
+$7\unit{kA}$.
 
@@
 setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
-set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. In order to create a stable environment to study the
-evolution of the witness beam we prevented the proton beam from evolving radially by increasing the particle mass by a
-factor of $1\mexp{6}$. We are not considering the evolution of the proton beam itself in this study.
+also set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. In order to create a stable environment to study
+the evolution of the witness beam we in addition prevented the proton beam from evolving radially by increasing the
+particle mass by a factor of $1\mexp{6}$. We are not considering the evolution of the proton beam itself in this study.
 
@@
 
-The witness beam in our simulation differs from AWAKE baseline parameters on several key points. Initial beam energy is
+The witness beam in our simulations differs from AWAKE baseline parameters on several key points. Initial beam energy is
 set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This was done to eliminate the problem of initial de-phasing of the
 witness beam. Beam loading of a short witness beam is sensitive to its position relative to the field
-\cite{tzoufras:2009}. The relative drift causing the de-phasing $\Delta\xi \propto \gamma^{-2}$. By simply matching the
+\cite{tzoufras:2009}. The relative drift causing the de-phasing is proportional to $\gamma^{-2}$. By simply matching the
 initial $\gamma$ values we eliminate this effect entirely, but a lower initial value is likely to be sufficient
@@
 \begin{align}
-    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
+    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma}, \label{EQ:Matched}
 \end{align}
-where $\lambda_{p}$ is the plasma wavelength. This is a very narrow beam compared to the drive beam
-$\sigma_{x} = 200\unit{\mu m}$. The charge density of this compact witness beam reaches that of the plasma density at
-only a few $\unit{pC}$, but reaches optimal beam loading at around $1-200\unit{pC}$. The implication here being that the
-witness beam produces its own non-linear wakefield already at the head of the beam. The majority of the electrons
-within it will therefore see a linear focusing force preventing the bulk of the beam from undergoing emittance growth.
+where $\lambda_{pe}$ is the plasma wavelength and $\gamma$ is the beam relativistic factor. This relation requires a
+very narrow beam compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$. The charge density of this compact witness
+beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal beam loading at around
+$1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear wakefield already at the
+head of the beam. The majority of the electrons within it will therefore see a linear focusing force preventing the bulk
+of the beam from undergoing emittance growth.
 
@@
 resolution of the witness beam. We used a transverse grid cell size of $1.17\unit{\mu m}$, and $2.34\unit{\mu m}$ for
-the longitudinal grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles.
+the longitudinal grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles. For the largest
+parameter scans, shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell size of $2.34\unit{\mu m}$.
 
@@
         and both witness and drive beam present (continuous green line). $\xi = z - tc$ is the position in the
-        simulation box and both beams travel towards the left. The beam and plasma densities arein units of initial
+        simulation box, and both beams travel towards the left. The beam and plasma densities are in units of initial
         plasma density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
@@
     \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the proton beam (blue) and the electron beam
-        (red) superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
+        (red) superimposed. The super-imposed line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
         $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
@@
 The witness beam generates its own wakefield which partially cancels out the $E_{z}$ field generated by the drive beam.
-With an ideally shaped electron beam charge profile it is possible to optimally load the field, such that the
+With an ideally shaped electron beam charge profile it is possible to optimally load the field in such a way that the
 accelerating $E_{z}$ is constant along the bunch \cite{katsouleas:1987, tzoufras:2009}.
@@
     \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
-        an on-axis beam with respect to the drive beam axis (left) and an offset beam (right) with an offset of one
-        $\sigma_{x} = 5.24\unit{\mu m}$ in the x plane. The moving window for emittance calculation is longitudinal
-        slices of $l = 4\times\Delta\xi = 18.75\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
-        $100$ macro particles have been included, which accounts for the abrupt edge as well as the noise at either end
-        of the beam due to low statistics. The blue lines show the peak electron beam density profile. For reference,
-        the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible. The solid
-        lines are at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the dash-dotted after
-        $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating field for the
-        witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid de-phasing
-        which causes the structure to break down after about $50\unit{m}$.}
+        an on-axis beam with respect to the drive beam axis (left), and an offset beam (right) with an offset of one
+        $\sigma_{x} = 5.24\unit{\mu m}$ in the x-plane. The moving window for emittance calculation is longitudinal
+        slices of $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
+        $100$ macro particles have been included. The blue lines show the on-axis electron beam density profile. For
+        reference, the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible.
+        The solid lines are taken at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the
+        dash-dotted after $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating
+        field for the witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid
+        de-phasing which otherwise causes the structure to break down after about $50\unit{m}$ of plasma.}
 \end{figure*}
@@
 
-While the ideal shape is trapezodial, for Gaussians beams a reasonable flat field, and consequently low energy spread,
+While the ideal shape is trapezoidal, for Gaussian beams a reasonable flat field, and consequently low energy spread,
 can be achieved by controlling the charge density to achieve a similar effect. This, however, puts the front of the
@@
 As illustrated in figure \ref{Fig:BeamPS} our base case shows a difference in energy transfer to the tail of the beam
-compared to the centre where the $E_{z}$-field is nearly flat. Also the front of the beam has a large tail in momentum
-space as this regions sees a smaller accelerating field. The positioning of the witness beam is chosen to put the bulk
-of the charge as close to the peak accelerating field as possible.
+compared to the centre where the $E_{z}$-field is nearly flat. In addition, the front of the beam has a large tail in
+momentum space as this regions sees a smaller accelerating field. The positioning of the witness beam is chosen to put
+the bulk of the charge as close to the peak accelerating field as possible.
 
@@
 all plasma electrons resulting in an ion column. This ion column, as is well known \cite{rosenzweig:1991}, provides a
-linear focusing force on the part the electron beam within the ion column, and therefore prevents emittance growth for
-this region. This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
+linear focusing force on the part the electron beam within the column, and therefore prevents emittance growth for this
+region of the beam. This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
 gradient of $20\unit{kT/m}$ near the beam axis.
@@
 propagation length. No significant emittance growth was observed for propagation lengths up to $100\unit{m}$. The drive
-beam energy increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing. De-phasing for the SPS beam case starts to
-become significant after about $50\unit{m}$.
+beam energy was here increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as de-phasing starts to become a
+significant effect for the SPS beam after about $50\unit{m}$.
 
@@
 beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
-of the beam where normalised emittance is preserved as shown in figure \ref{Fig:BeamFilament}. This has the potential to
-cause overloading of the field. However, for our base case this effect is not significant.
+of the beam where normalised emittance is preserved -- as shown in figure \ref{Fig:BeamFilament}. This has the potential
+to cause overloading of the field. However, for our base case this effect was not significant.
 
@@
 after the first few metres (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the
-beam oscillates around the axis of the drive beam wakefield (see right hand plots of figure \ref{Fig:BeamFilament}).
+beam oscillates around the axis of the drive beam wakefield, as can bee seen from the right hand plots of figure
+\ref{Fig:BeamFilament}.
 
@@
 respect to the accelerating flank of the $E_{z}$-field, $\approx\lambda_{pe}/4$, will not optimally load the field along
-its length thus experiencing a larger spread in energy.
+its length, thus producing a larger spread in energy.
 
@@
 density may be reduced so much that the plasma electrons are no longer fully evacuated from the ion column. Emittance
-values higher than a few micrometers lead to a significant increase in both emittance and energy spread. In these
+values higher than a few micrometres lead to a significant increase in both emittance and energy spread. In these
 simulations the focusing of the beam to the plasma remains matched for each emittance value.

### 2017-09-20 Tex/Paper.tex
Implemented many of Patric's comments

@@
 Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
-gradients, and have been of interest for several decades \cite{chen:1985}. A relativistic beam travelling through a
-plasma excites a strong longitudinal e-field that can be loaded by a trailing witness beam. With optimal beam loading,
-an increase in energy spread can be kept to a minimum. Acceleration of an electron withness beam by an electron drive
-beam has been demonstrated experimentally in the past \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at
-CERN is a proof of concept proton driven plasma wakefield accelerator experiment \cite{awake_collaboration:2014}.
+gradients, and have been of interest for several decades \cite{chen:1985}. A relativistic charged particle beam
+travelling through a plasma excites a strong longitudinal electric field that can be loaded by a trailing witness beam.
+With optimal beam loading, an increase in energy spread can be kept to a minimum. Acceleration of an electron withness
+beam by an electron drive beam has been demonstrated experimentally in the past
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at CERN is a proof of concept proton driven plasma wakefield
+accelerator experiment \cite{awake_collaboration:2014}.
 
@@
 energy spread and emittance as low as possible. In the well described linear case where the beam density $n_{b}$ is much
-smaller than the plasma density $n_{0}$, the non-linear transverse wakefields cause emittance growth of the accelerated
-beam. The beam will also see a transversely varying accelerating field causing increasing energy spread
-\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the transverse
-oscillations of the plasma electrons forming a sheet around an evacuated area leaving only ions. The ions, assumed
-stationary, form an ion channel creating a focusing force that varies linearly with radius. This produces an axially
-symmetric focusing force \cite{lu:2006-1, lu:2006}.
+smaller than the plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the
+accelerated beam. The beam will also see a transversely and longitudinally varying accelerating field causing an
+increase in energy spread \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
+the transverse oscillations of the plasma electrons forming a sheet around an evacuated area filled with only ions. The
+ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
+radius. This produces an axially symmetric focusing force which preserves emittance \cite{lu:2006-1, lu:2006}.
 %~ This effect also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread
@@
 %~ \begin{align}
-    %~ \lambda_{p} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
+    %~ \lambda_{pe} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
 %~ \end{align}
@@
 %~ \end{align}
-$\lambda_{p} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
-will produce a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness beam loading the
-peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches. Acceleration of
-an electron witness beam driven by two electron drive beams has been demonstrated at Brookhaven National Laboratory
-\cite{muggli:2011}.
+$\lambda_{pe} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
+produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness beam loading the
+peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches when they are
+properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two electron drive
+beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
 
@@
 high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam in the international linear collider with
-$1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers as drivers, a large number of plasma stages
-is required. How to efficiently stage plasma accelerators is challenging without reducing the effective gradient and
-spoiling the beam quality \cite{steinke:2016,lindstrom:2016}. Proton drive beams available at CERN carry significantly
-more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for longer accelerator stages. However,
-the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications. This issue is
-resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of the buckets in
-the modulated structure. This self-modulation instability is caused by the transverse fields generated by the beam
-acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency
-is close to that of the plasma, and leaves a train of proton bunches along the beam axis with a surrounding halo.
+$1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses as drivers, a large number of plasma
+stages is required. Staging plasma accelerators without reducing the effective gradient and spoiling the beam quality is
+challenging \cite{steinke:2016,lindstrom:2016}. Proton beams available at CERN carry significantly more energy,
+$19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for driving longer plasma wakefield accelerator
+stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications.
+This issue is resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of
+the buckets in the modulated structure. This self-modulation process is caused by the transverse fields generated by the
+beam acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation
+frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis with a
+surrounding halo of defocused particles. The train resonantly produces wakefields to larger amplitudes.
 %~ De-phasing of the
@@
 The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam at $400\unit{GeV}$ as its
-driver, and a nominal plasma density $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
-corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the SPS proton beam
-such that $k_{pe}\sigma_{x} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number. The aim of the first
-phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam, and in 2018 to sample the
-wakefield with a long electron beam. The study presented here is for Run 2 \cite{adli:2016}, which aims to demonstrate
-acceleration of a short electron beam to high energy with a minimal increase in emittance and energy spread.
+driver and a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
+corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the transverse size
+of the SPS proton beam such that $k_{pe}\sigma_{x} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number.
+The aim of the first phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam. The aim of
+the second phase in 2018 is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented
+here is for Run 2 \cite{adli:2016}, which aims to demonstrate acceleration of a short electron beam, $\ll\lambda_{pe}$,
+to high energy with a minimal increase in emittance and energy spread.
 
@@
 
-The preliminary design of Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}.
-The first section of $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without
-the electron beam present. The electron witness beam will then be injected into the modulated proton beam before stage
-two, where it undergoes acceleration.
+The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}. The first
+section of $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the electron
+beam present. The electron witness beam is then  injected into the modulated proton beam before stage two, where it
+undergoes acceleration.
 %~ As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
@@
 
-With this experimental design the self-modulated proton beam does not produce a full non-linear wakefield, and not all
-plasma electrons are therefore evacuated. The result is that the focusing force will not increase linearly with radius.
-The small size of the accelerating structure produced by the self-modulated beam also puts constraints on the size of
-the electron witness beam, and thus its charge and current -- if we at the same time wish to prevent large energy
-spread. By matching the transverse size of the beam at a given emittance to the plasma density, we prevent large
-amplitude oscillations which may cause additional growth in energy spread as well as in emittance.
+Using the SPS proton beam as driver, the self-modulated proton beam does not produce a full non-linear wakefield, and
+not all plasma electrons are therefore evacuated from the plasma bubble. The result is that the focusing force does not
+increase linearly with radius. The small size of the accelerating structure produced by the self-modulated beam also
+puts constraints on the size of the electron witness beam, and thus its charge and current -- if at the same time we
+wish to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma
+density, we prevent large amplitude oscillations which may cause additional growth in energy spread as well as in
+emittance.
 
-The key idea in this paper is that while the proton beam wake is not fully blown-out leading to non-linear focusing
-forces, the electron beam, if intense enough, may load the field and at the same time create its own ion bubble. As will
-be shown, exploiting these two well known effect, the electron beam can be accelerated, for long distances, without
-significant emittance growth.
+The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
+focusing forces, the electron beam, if intense enough, may load the field and at the same time create its own ion
+bubble. As will be shown, exploiting these two well known effects, the electron beam can be accelerated for long
+distances without significant emittance growth.
 
@@
 
-The main focus of this study has been on the beam loading of the electron beam. In order to eliminate other factors
-that may affect this (add examples?), we have tried several approaches to create a stable drive beam structure based on
-previous self-modulation studies.
+The main focus of this study is on the loading of the wakefields driven by the proton beam. In order to eliminate other
+factors that may affect this (add examples?), we tried several approaches to create a stable drive beam structure based
+on previous self-modulation studies.
 
@@
 In order to study the witness beam emittance evolution we turned to the recently released open source version of
-QuickPIC developed by UCLA. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}.
-Since QuickPIC is a quasi-static code, it does not suffer from the numerical Cherenkov effect that full PIC codes do
-\cite{godfrey:1974,lehe:2013}, making it a well suited code to study emittance preservation.
+QuickPIC. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}. It does not suffer from
+the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
+study emittance preservation.
 
@@
 setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
-also set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. In order to create a stable environment to study
-the evolution of the witness beam we in addition prevented the proton beam from evolving radially by increasing the
-particle mass by a factor of $1\mexp{6}$. We are not considering the evolution of the proton beam itself in this study.
+also set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. We are not considering the evolution of the
+proton beam itself in this study, so in order to create a stable environment to study the evolution of the witness beam
+we prevent the proton beam from evolving radially by increasing the particle mass 6 orders of magnitude.
 
@@
 
-The witness beam in our simulations differs from AWAKE baseline parameters on several key points. Initial beam energy is
-set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. This was done to eliminate the problem of initial de-phasing of the
-witness beam. Beam loading of a short witness beam is sensitive to its position relative to the field
-\cite{tzoufras:2009}. The relative drift causing the de-phasing is proportional to $\gamma^{-2}$. By simply matching the
-initial $\gamma$ values we eliminate this effect entirely, but a lower initial value is likely to be sufficient
-\cite{berglyd_olsen:2015}.
+Beam loading of a short witness beam is sensitive to its position relative to the field \cite{tzoufras:2009}. To
+eliminate the problem of initial de-phasing of the witness beam with respect to the proton wakefield, initial beam
+energy was set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. The relative drift causing the de-phasing is proportional
+to $\gamma^{-2}$. By simply matching the initial $\gamma$ values we eliminate this effect entirely. However, a lower
+initial value is likely to be sufficient \cite{berglyd_olsen:2015}.
 
-In these 3D simulations we have used a matched beam for an initial emittance of $2\unit{\mu m}$, corresponding to a
-$\sigma_{x}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
+In these 3D simulations we have used a matched beam for an initial normalised emittance of $\epsilon = 2\unit{\mu m}$,
+corresponding to a $\sigma_{x}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
 \begin{align}
-    \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma}, \label{EQ:Matched}
+    \beta = \frac{\sigma_r^2\gamma}{\epsilon} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma}, \label{EQ:Matched}
 \end{align}
-where $\lambda_{pe}$ is the plasma wavelength and $\gamma$ is the beam relativistic factor. This relation requires a
-very narrow beam compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$. The charge density of this compact witness
-beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal beam loading at around
-$1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear wakefield already at the
-head of the beam. The majority of the electrons within it will therefore see a linear focusing force preventing the bulk
-of the beam from undergoing emittance growth.
+This relation requires a very narrow beam compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$. The charge density
+of this compact witness beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal beam
+loading at around $1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
+wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
+force preventing the bulk of the beam from undergoing emittance growth.
 
 The relatively small size of the witness beam compared to the proton beam put some restrictions on the transverse
-resolution of the witness beam. We used a transverse grid cell size of $1.17\unit{\mu m}$, and $2.34\unit{\mu m}$ for
-the longitudinal grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles. For the largest
-parameter scans, shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell size of $2.34\unit{\mu m}$.
+resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the
+narrower one. We used a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal
+grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles. For the largest parameter scans,
+shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell size of $2.34\unit{\mu m}$.
 
 In the following section we study a witness beam with a total charge of $100\unit{pC}$, a $\sigma_{z}=60\unit{\mu m}$,
-and with a $\sigma_{x}=5.23\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We
+and with a $\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We
 refer to this parameter set as our base case.
@@
 
-The single drive beam setup is designed to behave similarly to the self-modulated case. However, since the drive beam is
-prevented from significant transverse evolution, we are presented with an idealised case where the electron witness beam
-sees consistent wakefields throughout the plasma stage. The $E_{z}$-field generated by the proton drive beam is seen as
-the blue line in figure \ref{Fig:BeamLoading}, shown with and without the electron beam present. With a proton beam
-density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime but near non-linear \cite{rosenzweig:2010}. The dashed
-green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of
-$67\%$, close to what we see in full scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
+The single drive beam setup is designed to produce similar initial conditions for the witness beam as the self-modulated
+case. However, since the drive beam is prevented from significant transverse evolution, we are presented with an
+idealised case where the electron witness beam sees consistent wakefields throughout the plasma stage. The $E_{z}$-field
+generated by the proton drive beam is seen as the blue line in figure \ref{Fig:BeamLoading}, shown with and without the
+electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime
+\cite{rosenzweig:2010}. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis
+plasma density has a depletion of $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
+\cite{awake_collaboration:2016}.
 
@@
     \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
-        plasma positions. The Right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
+        plasma positions. The right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
         particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
@@
 witness beam's own wakefield is in the fully non-linear regime, where the space charge force is sufficient to blow-out
-all plasma electrons resulting in an ion column. This ion column, as is well known \cite{rosenzweig:1991}, provides a
-linear focusing force on the part the electron beam within the column, and therefore prevents emittance growth for this
-region of the beam. This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
-gradient of $20\unit{kT/m}$ near the beam axis.
+all plasma electrons resulting in the formation of an ion column. This ion column, as is well known
+\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore
+prevents emittance growth for this region of the beam. This effect is shown for our base case in figure
+\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis.
 
@@
 %~ The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
-For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the beam
-retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance growth for the base case as a function of
-propagation length. No significant emittance growth was observed for propagation lengths up to $100\unit{m}$. The drive
-beam energy was here increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as de-phasing starts to become a
-significant effect for the SPS beam after about $50\unit{m}$.
+For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the
+electron beam retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance growth for the base case as a
+function of propagation length. No significant emittance growth was observed for propagation lengths up to
+$100\unit{m}$. The drive beam energy was here increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
+de-phasing starts to become a significant effect for the SPS beam of $400+unit{GeV}$ after about $50\unit{m}$.
 
 The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
-beam radius follows the evolution given by equation \ref{EQ:Matched} with $\lambda_{pe} = \lambda_{0}$ for the section
-of the beam where normalised emittance is preserved -- as shown in figure \ref{Fig:BeamFilament}. This has the potential
-to cause overloading of the field. However, for our base case this effect was not significant.
+beam radius within the bubble, where normalised emittance is preserved, follows the evolution given by equation
+\ref{EQ:Matched} -- as shown in figure \ref{Fig:BeamFilament}. This has the potential to cause overloading of the field.
+However, for our base case this effect was not significant.
 
@@
 
-The authors would also like to acknowledge the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS
-was used extensively for simulations leading up to the work presented in this paper.
+The authors would also like to thank the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS was used
+extensively for simulations leading to the work presented in this paper.
 

### 2017-09-21 Tex/Paper.tex
Changes after discussion with Patric

@@
 % ******************************************************************************************************************** %
-\section[\label{S:I}]{Introduction}
+\section{Introduction}\label{S:I}
 % interested from SMI/AWAKE
@@
 travelling through a plasma excites a strong longitudinal electric field that can be loaded by a trailing witness beam.
-With optimal beam loading, an increase in energy spread can be kept to a minimum. Acceleration of an electron withness
-beam by an electron drive beam has been demonstrated experimentally in the past
+With optimal beam loading, an increase in absolute energy spread can be kept to a minimum. Acceleration of an electron
+withness beam by an electron drive beam has been demonstrated experimentally in the past
 \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at CERN is a proof of concept proton driven plasma wakefield
@@
 ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
-radius. This produces an axially symmetric focusing force which preserves emittance \cite{lu:2006-1, lu:2006}.
+radius. This produces a focusing force that preserves emittance \cite{lu:2006-1, lu:2006}.
 %~ This effect also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread
@@
 $100\unit{J}$ -- and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. The energy of a
-high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam in the international linear collider with
-$1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses as drivers, a large number of plasma
-stages is required. Staging plasma accelerators without reducing the effective gradient and spoiling the beam quality is
-challenging \cite{steinke:2016,lindstrom:2016}. Proton beams available at CERN carry significantly more energy,
-$19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for driving longer plasma wakefield accelerator
-stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications.
-This issue is resolved by letting the proton beam undergo self-modulation before injecting the witness beam into one of
-the buckets in the modulated structure. This self-modulation process is caused by the transverse fields generated by the
-beam acting upon the beam itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation
-frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis with a
-surrounding halo of defocused particles. The train resonantly produces wakefields to larger amplitudes.
+high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam that could be produced by the international
+linear collider with $1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses as drivers, a
+large number of plasma stages is required. Staging plasma accelerators without reducing the effective gradient and
+spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}. Proton beams available at CERN carry
+significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for driving longer plasma
+wakefield accelerator stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for
+such applications. This issue is resolved by letting the proton beam undergo self-modulation before injecting the
+witness beam into one of the buckets in the modulated structure. This self-modulation process is caused by the
+transverse fields generated by the beam acting upon the beam itself, causing regions of the beam to rapidly defocus
+\cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton bunches
+along the beam axis with a surrounding halo of defocused particles. The train resonantly produces wakefields to larger
+amplitudes.
 %~ De-phasing of the
@@
 % ******************************************************************************************************************** %
-\subsection[\label{S:I:AWAKE}]{AWAKE Run 2}
+\subsection{AWAKE Run 2}\label{S:I:AWAKE}
 % ******************************************************************************************************************** %
@@
 corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the transverse size
-of the SPS proton beam such that $k_{pe}\sigma_{x} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number.
+of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number.
 The aim of the first phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam. The aim of
@@
 
+[Replace]
+
 The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
@@
 
-Our first approach was to use a pre-modulated, short proton beam with similar structure to the one produced by the
+Our previous approach was to use a pre-modulated, short proton beam with similar structure to the one produced by the
 self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
@@
 % ******************************************************************************************************************** %
-\subsection[\label{S:M:Setup}]{Drive Beam Parameters}
+\subsection{Drive Beam Parameters}\label{S:M:Setup}
 %~ Patric's Comments
@@
 initial SPS beam containing $3\nexp{11}$ protons \cite{gschwendtner:2016} enters the second plasma cell, the peak
-$E_{z}$ field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to
+electric
+
+field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to
 reach the non-linear regime and produce a plasma bubble, the plasma electrons are only depleted to around $65\%$ of
@@
 % ******************************************************************************************************************** %
-\subsection[\label{S:M:Setup}]{Witness Beam Parameters}
+\subsection{Witness Beam Parameters}\label{S:M:Setup}
 % ******************************************************************************************************************** %
 
-Beam loading of a short witness beam is sensitive to its position relative to the field \cite{tzoufras:2009}. To
-eliminate the problem of initial de-phasing of the witness beam with respect to the proton wakefield, initial beam
+Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}.
+To eliminate the problem of initial de-phasing of the witness beam with respect to the proton wakefield, initial beam
 energy was set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. The relative drift causing the de-phasing is proportional
-to $\gamma^{-2}$. By simply matching the initial $\gamma$ values we eliminate this effect entirely. However, a lower
-initial value is likely to be sufficient \cite{berglyd_olsen:2015}.
+to $\gamma^{-2}$. By matching the initial $\gamma$ values in these simulations we eliminate this effect entirely.
+However, a lower initial value is likely to be sufficient \cite{berglyd_olsen:2015}.
 
-In these 3D simulations we have used a matched beam for an initial normalised emittance of $\epsilon = 2\unit{\mu m}$,
-corresponding to a $\sigma_{x}$ of $5.25\unit{\mu m}$. The beam matching relation is given by
-\begin{align}
-    \beta = \frac{\sigma_r^2\gamma}{\epsilon} = \frac{\lambda_{pe}}{2\pi}\sqrt{2\gamma}, \label{EQ:Matched}
-\end{align}
-This relation requires a very narrow beam compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$. The charge density
-of this compact witness beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal beam
-loading at around $1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
+In these simulations we have used a matched beam for an initial normalised emittance of $\epsilon_{N} = 2\unit{\mu m}$.
+The beam matching relation is given by
+\begin{equation}
+    \beta = \frac{\sigma_{x,y}^{2}\gamma}{\epsilon_{N}}
+          = \frac{c}{\omega_{pe}}\sqrt{2\gamma}, \label{EQ:MatchedB}
+    % = c\sqrt{\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}}2\gamma}
+\end{equation}
+where $\beta$ is the Twiss parameter. It then follows that the transverse profile of the beam must satisfy
+\begin{equation}
+    \sigma_{x,y}^{2} = c\epsilon_{N}\sqrt{2\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}} \label{EQ:MatchedR}
+\end{equation}
+in order to be matched to a given plasma density, initial emittance and energy. This relation requires a very narrow
+beam with a $\sigma_{x,y}$ of $5.25\unit{\mu m}$ compared to the drive beam $\sigma_{x,y} = 200\unit{\mu m}$. The charge
+density of this compact witness beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal
+beam loading at around $1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
 wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
@@
 narrower one. We used a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal
-grid cells. The witness beam was simulated with $16.8\unit{M}$ non-weighted particles. For the largest parameter scans,
-shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell size of $2.34\unit{\mu m}$.
+grid cells  for the simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\unit{M}$
+non-weighted particles. For the largest parameter scans, shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell
+size of $2.34\unit{\mu m}$.
 
@@
 % ******************************************************************************************************************** %
-\section[\label{S:BL}]{Beam Loading}
+\section{Beam Loading}\label{S:BL}
 %~ Eric's Comments
@@
 witness beam outside of the ideal region while the middle bulk of the beam has a trapezoidal-like shape. In our case,
-with a matched beam to the plasma density defined by equation \ref{EQ:Matched}, we are limited on how much total charge
+with a matched beam to the plasma density defined by equation \ref{EQ:MatchedB}, we are limited on how much total charge
 we can accelerate without reaching charge densities that will overload the field.
@@
 The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
-beam radius within the bubble, where normalised emittance is preserved, follows the evolution given by equation
-\ref{EQ:Matched} -- as shown in figure \ref{Fig:BeamFilament}. This has the potential to cause overloading of the field.
-However, for our base case this effect was not significant.
+transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by equation
+\ref{EQ:MatchedR} where the plasma density is given by the ion density -- as shown in figure \ref{Fig:BeamFilament}.
+This has the potential to cause overloading of the field. However, for our base case this effect was not significant.
 
@@
 % ******************************************************************************************************************** %
-\section[\label{S:C}]{Conclusion}
+\section{Conclusion}\label{S:C}
 % ******************************************************************************************************************** %
@@
 
-\section[\label{Ack}]{Acknowledgements}
+\section{Acknowledgements}\label{Ack}
 % ******************************************************************************************************************** %

### 2017-09-25 Tex/Paper.tex
Added the rest of Patric's suggestions ... more or less

@@
 here is for Run 2 \cite{adli:2016}, which aims to demonstrate acceleration of a short electron beam, $\ll\lambda_{pe}$,
-to high energy with a minimal increase in emittance and energy spread.
+to high energy with a minimal increase in emittance and absolute energy spread.
 
@@
     \caption{\label{Fig:AWAKER2} A simplified illustration of the experimental setup for AWAKE Run 2. The SPS proton
-        beam undergoes self-modulation in the first $4\unit{m}$ plasma cell. The electron witness beam is injected in
-        one of the buckets, and undergoes acceleration in the second plasma cell \cite{berglyd_olsen:2015, adli:2016}.}
+        beam undergoes self-modulation in the first $4\unit{m}$ plasma section. The electron witness beam is injected
+        into the accelerating structure, and undergoes acceleration in the second plasma stage
+        \cite{berglyd_olsen:2015, adli:2016}.}
 \end{figure}
@@
 
-[Replace]
-
-The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
-focusing forces, the electron beam, if intense enough, may load the field and at the same time create its own ion
-bubble. As will be shown, exploiting these two well known effects, the electron beam can be accelerated for long
-distances without significant emittance growth.
+The key idea is to have enough charge in the witness bunch to at the same time load the wakefield to produce low
+relative energy spread $\Delta E/E$ and blow out the electrons left in the accelerating structure to reach conditions
+that preserves emittance.
+%~ The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
+%~ focusing forces, the electron beam, if intense enough, may load the field and at the same time create its own ion
+%~ bubble. As will be shown, exploiting these two well known effects, the electron beam can be accelerated for long
+%~ distances without significant emittance growth.
 
@@
 
-In these simulations we use a single proton drive beam that sets up a wakefield comparable to that which we expect to
-see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}). When the
-initial SPS beam containing $3\nexp{11}$ protons \cite{gschwendtner:2016} enters the second plasma cell, the peak
-electric
+%~ In these simulations we use a single proton drive beam that sets up a wakefield comparable to that which we expect to
+%~ see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}).
 
-field is expected to be $500-600\funit{MV}{m}$. As the baseline AWAKE drive beam current is insufficient to
-reach the non-linear regime and produce a plasma bubble, the plasma electrons are only depleted to around $65\%$ of
-nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions
-are replicated in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
+The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. When
+the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma cell, the peak electric
+field is expected to be $500-600\funit{MV}{m}$. The plasma electrons are only depleted to around $65\%$ of nominal
+plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions are
+replicated in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
 $7\unit{kA}$.
@@
 grid cells for the simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\unit{M}$
-non-weighted particles. For the largest parameter scans, shown in figure \ref{Fig:BeamQ}, we used a transverse grid cell
-size of $2.34\unit{\mu m}$.
+non-weighted particles. The witness beam has a total charge of $100\unit{pC}$, a $\sigma_{z}=60\unit{\mu m}$, and a
+$\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We refer to this
+parameter set as our base case.
 
-In the following section we study a witness beam with a total charge of $100\unit{pC}$, a $\sigma_{z}=60\unit{\mu m}$,
-and with a $\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We
-refer to this parameter set as our base case.
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
+    \caption{\label{Fig:BeamLoading} The top plot shows the unloaded longitudinal electric field with no witness beam
+        (dashed blue line) and the loaded field (whole blue line) along the beam axis. The beam density along the axis
+        for both beams is shown in red line. The bottom plot compares the plasma density along the beam axis for a drive
+        beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line), and
+        both beams present (whole green line). $\xi = z - tc$ is the position in the simulation box, travelling towards
+        the left. the plots are normalised to $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
+    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the drive beam (blue) and the witness beam (red)
+        superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
+        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
+    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
+        after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS of $87\unit{MeV/c}$ ($5.2\%$){}
+        for the full beam.}
+\end{figure}
+
+\begin{figure*}[hbt]
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
+    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
+    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
+        an on-axis beam with respect to the drive beam axis (left), and an offset beam (right) with an offset of one
+        $\sigma_{x} = 5.24\unit{\mu m}$ in the x-plane. The moving window for emittance calculation is longitudinal
+        slices of $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
+        $100$ macro particles have been included. The blue lines show the on-axis electron beam density profile. For
+        reference, the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible.
+        The solid lines are taken at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the
+        dash-dotted after $40\unit{m}$, and the dotted after $100\unit{m}$. These simulations were run with an LHC
+        energy drive beam of $7\unit{TeV}$}
+\end{figure*}
+
+\begin{figure*}[hbt]
+    \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
+    %~ \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
+    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
+    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
+    %~ \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
+    %~ \\
+    %~ \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
+    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
+    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
+    %~ \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
+    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
+        plasma positions. The right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
+        particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
+        particles and lines represent particles with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
+\end{figure*}
 
@@
 % ******************************************************************************************************************** %
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} The top plot compares the unloaded longitudinal e-field (no witness beam, blue.
-        dashed line) and the loaded e-field (blue line) along the beam axis. The magnitude of the beam density along
-        the axis is shown (red line) for reference. The bottom plot compares the plasma density along the beam axis for
-        a drive beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line),
-        and both witness and drive beam present (continuous green line). $\xi = z - tc$ is the position in the
-        simulation box, and both beams travel towards the left. The beam and plasma densities are in units of initial
-        plasma density $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
-\end{figure}
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the proton beam (blue) and the electron beam
-        (red) superimposed. The super-imposed line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
-        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
-\end{figure}
 
@@
 
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
-        after $4\unit{m}$ of plasma. Mean momentum is $1.67\unit{GeV/c}$ with an RMS spread of $87\unit{MeV/c}$
-        ($5.2\%$) for the full beam.}
-\end{figure}
+A Gaussian beams cannot completely flatten the electric field and thus accelerate the beam with no spread in energy.
+However, with an adequate charge, the middle and the tail of the beam can produce a reasonably flat field -- keeping
+energy spread to a minimum. As illustrated in figure \ref{Fig:BeamPS} our base case shows a difference in energy
+transfer to the tail of the beam compared to the centre where the electric field is nearly flat. In addition, the front
+of the beam has a large tail in momentum space as this regions sees a smaller accelerating field.
 
-\begin{figure*}[hbt]
-    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittance}
-    \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
-    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
-        an on-axis beam with respect to the drive beam axis (left), and an offset beam (right) with an offset of one
-        $\sigma_{x} = 5.24\unit{\mu m}$ in the x-plane. The moving window for emittance calculation is longitudinal
-        slices of $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
-        $100$ macro particles have been included. The blue lines show the on-axis electron beam density profile. For
-        reference, the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible.
-        The solid lines are taken at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the
-        dash-dotted after $40\unit{m}$, and the dotted after $100\unit{m}$. In order to sustain a stable accelerating
-        field for the witness beam, these simulations were run with an LHC energy drive beam of $7\unit{TeV}$ to avoid
-        de-phasing which otherwise causes the structure to break down after about $50\unit{m}$ of plasma.}
-\end{figure*}
-
-\begin{figure*}[hbt]
-    \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
-    %~ \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
-    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
-    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
-    %~ \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
-    %~ \\
-    %~ \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
-    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
-    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
-    %~ \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
-    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
-        plasma positions. The right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
-        particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
-        particles and lines represent particles with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
-\end{figure*}
-
-While the ideal shape is trapezoidal, for Gaussian beams a reasonable flat field, and consequently low energy spread,
-can be achieved by controlling the charge density to achieve a similar effect. This, however, puts the front of the
-witness beam outside of the ideal region while the middle bulk of the beam has a trapezoidal-like shape. In our case,
-with a matched beam to the plasma density defined by equation \ref{EQ:MatchedB}, we are limited on how much total charge
-we can accelerate without reaching charge densities that will overload the field.
-
-As illustrated in figure \ref{Fig:BeamPS} our base case shows a difference in energy transfer to the tail of the beam
-compared to the centre where the $E_{z}$-field is nearly flat. In addition, the front of the beam has a large tail in
-momentum space as this regions sees a smaller accelerating field. The positioning of the witness beam is chosen to put
-the bulk of the charge as close to the peak accelerating field as possible.
-
-The charge density required to optimally load the $E_{z}$ field is $n_{eb} \approx 35\times n_{0}$. This means that the
+The charge density required to optimally load the electric field is $n_{eb} \approx 35\times n_{0}$. This means that the
 witness beam's own wakefield is in the fully non-linear regime, where the space charge force is sufficient to blow-out
@@
 prevents emittance growth for this region of the beam. This effect is shown for our base case in figure
-\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis.
+\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis. However, with a
+matched beam to the plasma density defined by equation \ref{EQ:MatchedB}, we are limited on how much total charge we can
+accelerate without reaching charge densities that will overload the field.
 
@@
 $100\unit{m}$. The drive beam energy was here increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
-de-phasing starts to become a significant effect for the SPS beam of $400+unit{GeV}$ after about $50\unit{m}$.
+de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
 
@@
 
-Since the accelerated electron beam creates its own focusing bubble, the emittance of the part of the beam inside the
+Since the accelerated electron beam creates its own plasma bubble, the emittance of the part of the beam inside the
 bubble is not affected by small beam offsets with respect to the proton beam axis. This is an added benefit of this new
@@
 \ref{Fig:BeamFilament}.
-
-% ******************************************************************************************************************** %
-\section[\label{S:PO}]{Parameter Optimisation}
-%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
-%~ beam, and preferably some scalings]
-%~ - how to select electron beam parameters:
-%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
-%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
-%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
-%~ (- plasma density?)
-% ******************************************************************************************************************** %
 
@@
 
-The beam loading and blow out properties of the electron beam depends on a large number of parameters: the longitudinal
-profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
-
-We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
-For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated
-and minimize the emittance growth. In addition, the bunch length should be such that it is possible to generate and
-transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We investigate the
-interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial emittance. We
-quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will depend
-on the application.
-
-Figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} show the dependence on bunch length and bunch charge for an initial beam
-emittance of $2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the scan with beam charges from
-$10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. We see from
-figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy
-spread with a beam charge $\geq 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to
-underload the $E_{z}$-field, while higher beam charges tend to overload it. It is also clear that long beams with
-respect to the accelerating flank of the $E_{z}$-field, $\approx\lambda_{pe}/4$, will not optimally load the field along
-its length, thus producing a larger spread in energy.
-
 \begin{figure}[hbt]
@@
 \end{figure}
+
+% ******************************************************************************************************************** %
+\section{Parameter Optimisation}\label{S:PO}
+%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
+%~ beam, and preferably some scalings]
+%~ - how to select electron beam parameters:
+%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
+%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
+%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
+%~ (- plasma density?)
+% ******************************************************************************************************************** %
+
+The beam loading and blow out properties of the electron beam depends on a large number of parameters: the longitudinal
+profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
+
+%~ We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
+For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be
+accelerated, and minimize the emittance growth. In addition, the bunch length should be such that it is possible to
+generate and transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We
+investigate the interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial
+emittance. We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection
+parameters will depend on the application. For the parameter scans in this section we used a transverse grid cell size
+of $2.34\unit{\mu m}$.
+
+Figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} show the dependence on bunch length and bunch charge for an initial beam
+emittance of $2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the scan with beam charges from
+$10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. We see from
+figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy
+spread with a beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to
+underload the electric field, while higher beam charges tend to overload it. It is also clear that longer beams with
+respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, will not optimally load the,
+thus producing a larger spread in energy.
 

### 2017-09-29 Tex/Paper.tex
Edits before sending to Erik and Patric

@@
 Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
-gradients, and have been of interest for several decades \cite{chen:1985}. A relativistic charged particle beam
-travelling through a plasma excites a strong longitudinal electric field that can be loaded by a trailing witness beam.
-With optimal beam loading, an increase in absolute energy spread can be kept to a minimum. Acceleration of an electron
-withness beam by an electron drive beam has been demonstrated experimentally in the past
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at CERN is a proof of concept proton driven plasma wakefield
-accelerator experiment \cite{awake_collaboration:2014}.
+gradients, and have been of interest for several decades \cite{chen:1985}. With a relativistic charged particle drive
+beam travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
+witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept to a minimum. The concept
+has been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at CERN is a proof of concept beam driven plasma wakefield
+accelerator experiment using a proton drive beam delivered by the SPS accelerator \cite{awake_collaboration:2014}.
 
-A major challenge with plasma wakefield accelerators is, however, to produce an accelerated beam while keeping growth in
-energy spread and emittance as low as possible. In the well described linear case where the beam density $n_{b}$ is much
-smaller than the plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the
-accelerated beam. The beam will also see a transversely and longitudinally varying accelerating field causing an
-increase in energy spread \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
-the transverse oscillations of the plasma electrons forming a sheet around an evacuated area filled with only ions. The
+A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping energy spread and
+emittance growth to a minimum. In the well described linear case where the beam density $n_{b}$ is much smaller than the
+plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. the beam
+will also see a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has
+been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the
+transverse oscillations of the plasma electrons, forming a sheet around an evacuated area filled with only ions. The
 ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
 radius. This produces a focusing force that preserves emittance \cite{lu:2006-1, lu:2006}.
-%~ This effect also avoids the issue of increasing energy spread due to transverse beam loading. Increase in energy spread
-%~ is still dependent on beam loading $E_{z}$.
-%~ Ideal beam loading can be achieved by specially shaped beams that optimally flattens the field
-%~ \cite{katsouleas:1987, tzoufras:2009}, but this is difficult experimentally and is not a topic explored in this paper.
+
+In this paper we present simulation results showing how we can use the non-linear wakefields driven by the head of a
+high charge density witness beam to reduce energy spread and emittance growth in the rest of the beam, while being
+accelerated by a proton drive beam producing quasi-linear wakefields.
 
@@
 
-A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where
-%~ \begin{align}
-    %~ \lambda_{pe} = 2\pi\frac{c}{\omega_{pe}} \label{EQ:LambdaP}
-%~ \end{align}
-%~ and
-%~ \begin{align}
-    %~ \omega_{pe} = \sqrt{\frac{n_{0} e^{2}}{m_{e} \epsilon_{0}}}, \label{EQ:OmegaP}
-%~ \end{align}
-$\lambda_{pe} = 2\pi c/\omega_{pe}$ and $\omega_{pe} = (n_{0} e^{2} / m_{e} \epsilon_{0})^{1/2}$,
-produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness beam loading the
-peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches when they are
-properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two electron drive
-beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
+A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where the
+plasma wavelength $\lambda_{pe} = 2\pi c/\omega_{pe}$ and the plasma frequency $\omega_{pe} = (n_{0} e^{2} / m_{e}
+\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness
+beam loading the peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches
+when they are properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two
+electron drive beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
 
 The energy carried by electron drive bunches used in previous experiments were typically small -- on the order of
-$100\unit{J}$ -- and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. The energy of a
-high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam that could be produced by the international
-linear collider with $1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses as drivers, a
-large number of plasma stages is required. Staging plasma accelerators without reducing the effective gradient and
-spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}. Proton beams available at CERN carry
-significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016}, allowing for driving longer plasma
-wakefield accelerator stages. However, the SPS beam is orders of magnitude longer than the plasma wavelengths needed for
-such applications. This issue is resolved by letting the proton beam undergo self-modulation before injecting the
-witness beam into one of the buckets in the modulated structure. This self-modulation process is caused by the
-transverse fields generated by the beam acting upon the beam itself, causing regions of the beam to rapidly defocus
-\cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton bunches
-along the beam axis with a surrounding halo of defocused particles. The train resonantly produces wakefields to larger
-amplitudes.
-%~ De-phasing of the
-%~ witness beam relative to the drive beam, caused by loss of energy in the drive beam and gain of energy in the witness
-%~ beam, limits the effective length of a plasma accelerator stage.
+$100\unit{J}$ -- and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. Higher energy
+electron beam can be improve the propagation length and thus the energy of the accelerated beam. For instance, the
+energy of a high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam that could be produced by the
+international linear collider with $1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses
+as drivers, a large number of plasma stages is required. However, staging plasma accelerators without reducing the
+effective gradient and spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}.
+
+Proton beams available at CERN carry significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016},
+allowing for much longer plasma wakefield accelerator stages. The SPS beam is, unfortunately, orders of magnitude longer
+than the plasma wavelengths needed for such applications. This can be resolved by letting the proton beam undergo
+self-modulation before injecting the witness beam into accelerating structure. The self-modulation of the beam is
+produced by the transverse fields generated by the beam acting upon itself, causing regions of the beam to rapidly
+defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton
+bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly produces
+wakefields to larger amplitudes.
 
@@
 
-%~ The first run of the experiment is set up with a $10\unit{m}$ rubidium vapour cell.
-%~ The rubidium vapour is
-%~ ionised by a $780\unit{nm}$, $4.5\unit{TW}$ peak power laser with a pulse length of $100−120\unit{fs}$.
-The AWAKE experiment, currently in its first stages of operation at CERN, uses the SPS beam at $400\unit{GeV}$ as its
-driver and a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density
-corresponds to a plasma wavelength $\lambda_{pe} = 1.26\unit{mm}$. The plasma density is matched to the transverse size
-of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number.
+The AWAKE experiment, currently in its first stages of operation at CERN, uses a $400\unit{GeV}$ beam delivered by the
+SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$
+\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$ -- matched to the transverse
+size of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave
+number.
+
 The aim of the first phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam. The aim of
@@
     \caption{\label{Fig:AWAKER2} A simplified illustration of the experimental setup for AWAKE Run 2. The SPS proton
-        beam undergoes self-modulation in the first $4\unit{m}$ plasma section. The electron witness beam is injected
-        into the accelerating structure, and undergoes acceleration in the second plasma stage
+        beam undergoes self-modulation in the first plasma section. The electron witness beam is injected into the
+        accelerating structure, and undergoes acceleration in the second plasma stage
         \cite{berglyd_olsen:2015, adli:2016}.}
@@
 undergoes acceleration.
-%~ As the $E_z$-field will decrease due to the gap between the two cells, it is desirable to
-%~ keep this as short as possible.
 
@@
 increase linearly with radius. The small size of the accelerating structure produced by the self-modulated beam also
-puts constraints on the size of the electron witness beam, and thus its charge and current -- if at the same time we
-wish to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma
-density, we prevent large amplitude oscillations which may cause additional growth in energy spread as well as in
-emittance.
+puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
+to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma density,
+we prevent large amplitude oscillations which may cause additional energy spread as well as emittance growth.
 
-The key idea is to have enough charge in the witness bunch to at the same time load the wakefield to produce low
-relative energy spread $\Delta E/E$ and blow out the electrons left in the accelerating structure to reach conditions
-that preserves emittance.
+%~ Eric's version:
 %~ The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
@@
 
-%~ The beam matching relation is given by
-%~ \begin{align}
-    %~ \beta = \frac{\sigma_r^2}{\epsilon_g} = \frac{\lambda_pe}{2\pi}\sqrt{2\gamma_{rel}}, \label{EQ:Matched}
-%~ \end{align}
-%~ where $\lambda_{p}$ is the plasma wavelength. For a reasonable initial emittance of $2\unit{\mu m}$, this corresponds to
-%~ a $\sigma_{x}$ of $5.25\unit{\mu m}$ -- a very narrow bunch compared to the drive beam $\sigma_{x} = 200\unit{\mu m}$.
-%~ The charge density of this compact witness bunch reaches that of the plasma density at only a few $\unit{pC}$, but
-%~ reaches optimal beam loading at around $1-200\unit{pC}$. The implication here being that the witness bunch produces its
-%~ own non-linear wakefield already at the head of the bunch. The majority of the electrons within it will therefore see a
-%~ linear focusing force preventing the bulk of the beam from undergoing emittance growth.
+%~ Patric's version:
+The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low
+relative energy spread $\Delta E/E$, and blow out the electrons left in the accelerating structure to reach conditions
+that preserves emittance.
 
@@
 
-The main focus of this study is on the loading of the wakefields driven by the proton beam. In order to eliminate other
-factors that may affect this (add examples?), we tried several approaches to create a stable drive beam structure based
-on previous self-modulation studies.
+A main focus of this study is on the loading of the wakefields driven by the proton beam. In order to eliminate other
+factors that may affect this, like decay and defocusing of the proton beam, we tried several approaches to create a
+stable drive beam structure based in previous self-modulation studies.
 
-Our previous approach was to use a pre-modulated, short proton beam with similar structure to the one produced by the
+In these studies we used a short, pre-modulated proton beam with similar structure to the beam produced by the
 self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
-using 2D cylindrical-symmetric simulations \cite{berglyd_olsen:2015, berglyd_olsen:2016}.
+using 2D cylindrical-symmetric simulations and primarily looked at beam loading, energy gain and energy spread
+\cite{berglyd_olsen:2015, berglyd_olsen:2016}.
+
+In order to study the witness beam emittance evolution we turned to the recently released open source version of
+QuickPIC. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}. It does not suffer from
+the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
+study emittance preservation.
 
@@
 
-In order to study the witness beam emittance evolution we turned to the recently released open source version of
-QuickPIC. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}. It does not suffer from
-the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
-study emittance preservation.
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
+    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the drive beam (blue) and the witness beam (red)
+        superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
+        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
+\end{figure}
 
@@
 The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. When
-the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma cell, the peak electric
-field is expected to be $500-600\funit{MV}{m}$. The plasma electrons are only depleted to around $65\%$ of nominal
-plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. These conditions are
-replicated in our simulations using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
+the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma stage, the peak
+electric field is expected to be $500-600\funit{MV}{m}$. The plasma electrons are only depleted to around $65\%$ of
+nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. In our simulation
+these conditions are replicated using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
 $7\unit{kA}$.
@@
 The peak density of the simulation drive beam is $0.83\cdot n_{0}$, producing a quasi-linear wakefield. The single bunch
-setup uses the baseline proton energy $W_{pb} = 400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
+setup uses the baseline proton beam energy of $400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
 also set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. We are not considering the evolution of the
 proton beam itself in this study, so in order to create a stable environment to study the evolution of the witness beam
-we prevent the proton beam from evolving radially by increasing the particle mass 6 orders of magnitude.
+we prevent the proton beam from evolving radially by increasing the particle mass by 6 orders of magnitude.
 
@@
 Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}.
-To eliminate the problem of initial de-phasing of the witness beam with respect to the proton wakefield, initial beam
-energy was set such that $\gamma_{eb} = \gamma_{pb} = 426.3$. The relative drift causing the de-phasing is proportional
-to $\gamma^{-2}$. By matching the initial $\gamma$ values in these simulations we eliminate this effect entirely.
-However, a lower initial value is likely to be sufficient \cite{berglyd_olsen:2015}.
+A low gamma witness beam can easily drift out of phase with the drive beam wakefield. The drift of the beams is
+proportional to $\gamma^{-2}$, so to eliminate initial de-phasing of the witness beam, initial beam energy was set such
+that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$. A lower initial value is likely to be
+sufficient \cite{berglyd_olsen:2015}.
 
@@
 density of this compact witness beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal
-beam loading at around $1-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
+beam loading at around $100-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
 wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
@@
 resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the
-narrower one. We used a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal
-grid cells for the simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\unit{M}$
-non-weighted particles. The witness beam has a total charge of $100\unit{pC}$, a $\sigma_{z}=60\unit{\mu m}$, and a
-$\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance $\epsilon_{0} = 2\unit{\mu m}$. We refer to this
-parameter set as our base case.
+narrower one (see figure \ref{Fig:PlasmaDenTWake}). We used a transverse grid cell size of $1.17\unit{\mu m}$, and of
+$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
+was simulated with $16.8\nexp{6}$ non-weighted particles. The witness beam has a total charge of $100\unit{pC}$, a
+$\sigma_{z}=60\unit{\mu m}$, and a $\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance
+$\epsilon_{0} = 2\unit{\mu m}$. We refer to this parameter set as our base case.
 
@@
         (dashed blue line) and the loaded field (whole blue line) along the beam axis. The beam density along the axis
-        for both beams is shown in red line. The bottom plot compares the plasma density along the beam axis for a drive
+        for both beams are shown in red. The bottom plot compares the plasma densities along the beam axis for a drive
         beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line), and
-        both beams present (whole green line). $\xi = z - tc$ is the position in the simulation box, travelling towards
-        the left. the plots are normalised to $n_{0} = 7\nexp{-14}\unit{cm}^{-3}$.}
-\end{figure}
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the drive beam (blue) and the witness beam (red)
-        superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
-        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
+        both beams present (whole green line). $\xi = z - tc$ is the position in the simulation box, moving towards the
+        left.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
-        after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS of $87\unit{MeV/c}$ ($5.2\%$){}
-        for the full beam.}
+    \caption{\label{Fig:BeamPS} The phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness
+        beam after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of
+        $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
 \end{figure}
@@
     \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
-    \caption{\label{Fig:BeamEmitt} The red lines show a moving window calculation of transverse normalised emittance for
-        an on-axis beam with respect to the drive beam axis (left), and an offset beam (right) with an offset of one
-        $\sigma_{x} = 5.24\unit{\mu m}$ in the x-plane. The moving window for emittance calculation is longitudinal
-        slices of $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a $\Delta\xi$ resolution. Only slices with more than
-        $100$ macro particles have been included. The blue lines show the on-axis electron beam density profile. For
-        reference, the plasma density profile is included in green, but scaled up by a factor of $100$ to be visible.
-        The solid lines are taken at the plasma entry point, the dashed lines after $4\unit{m}$ of plasma, the
-        dash-dotted after $40\unit{m}$, and the dotted after $100\unit{m}$. These simulations were run with an LHC
-        energy drive beam of $7\unit{TeV}$}
+    \caption{\label{Fig:BeamEmitt} Beam density in blue along the beam axis for an on-axis beam with respect to the
+        drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x} = 5.24\unit{\mu m}$ in the
+        x-plane. At four different positions $z$ in the plasma stage. The red lines show a moving window calculation of
+        transverse normalised emittance. The moving window calculation uses longitudinal slices of
+        $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
+        particles have been included. The plasma density profile is included in green, and scaled up by a factor of
+        $100$ to be visible. These simulations were run with an LHC energy drive beam of $7\unit{TeV}$}
 \end{figure*}
@@
     \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
-    %~ \includegraphics[height=22.2mm,trim={ 0mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation01}
-    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  6mm 0mm},clip]{figures/beamFilamentation02}
-    %~ \includegraphics[height=22.2mm,trim={16mm 9.5mm  0mm 0mm},clip]{figures/beamFilamentation03}
-    %~ \includegraphics[height=22.2mm,trim={10mm 9.5mm 15mm 0mm},clip]{figures/beamOffsetMean}
-    %~ \\
-    %~ \includegraphics[height=26.0mm,trim={ 0mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation04}
-    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  6mm 2mm},clip]{figures/beamFilamentation05}
-    %~ \includegraphics[height=26.0mm,trim={16mm 0.1mm  0mm 2mm},clip]{figures/beamFilamentation06}
-    %~ \includegraphics[height=26.0mm,trim={10mm 0.1mm 15mm 2mm},clip]{figures/beamOffsetRMS}
-    \caption{\label{Fig:BeamFilament} The left plots show the transverse phase space of the electron beam at different
-        plasma positions. The right side shows the macro particle mean position (top) and RMS spread (bottom). The blue
-        particles and lines represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. The red
-        particles and lines represent particles with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
+    \caption{\label{Fig:BeamFilament} Plots \textbf{a} to \textbf{f} show the transverse phase space of the offset
+        electron beam at different plasma positions. Plot \textbf{g} shows the macro particle mean position, and plot
+        \textbf{h} their RMS spread. Plots \textbf{a}, \textbf{b} and \textbf{c}, as well as the blue lines in plots
+        \textbf{g} and \textbf{h} represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots
+        \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent particles
+        with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
 \end{figure*}
@@
 %~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
+%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
+%~   unloaded wake)
+%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
+%~   flatten and energy spread reduced [well known result, Tzoufras]
+%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
+%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
+%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
+%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
+%~   electron densities etc. )
+%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
+%~   longitudinal phase spaces, space long simulation)
+%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
+%~   show: transverse and longitudinal phase spaces, long offset simulation)
 %~
@@
 
-%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
-%~   unloaded wake)
-
 The single drive beam setup is designed to produce similar initial conditions for the witness beam as the self-modulated
@@
 \cite{awake_collaboration:2016}.
-
-%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
-%~   flatten and energy spread reduced [well known result, Tzoufras]
 
@@
 With an ideally shaped electron beam charge profile it is possible to optimally load the field in such a way that the
-accelerating $E_{z}$ is constant along the bunch \cite{katsouleas:1987, tzoufras:2009}.
-
-%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
-%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
-%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
-%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
-%~   electron densities etc. )
-
-A Gaussian beams cannot completely flatten the electric field and thus accelerate the beam with no spread in energy.
-However, with an adequate charge, the middle and the tail of the beam can produce a reasonably flat field -- keeping
-energy spread to a minimum. As illustrated in figure \ref{Fig:BeamPS} our base case shows a difference in energy
-transfer to the tail of the beam compared to the centre where the electric field is nearly flat. In addition, the front
-of the beam has a large tail in momentum space as this regions sees a smaller accelerating field.
-
-The charge density required to optimally load the electric field is $n_{eb} \approx 35\times n_{0}$. This means that the
-witness beam's own wakefield is in the fully non-linear regime, where the space charge force is sufficient to blow-out
-all plasma electrons resulting in the formation of an ion column. This ion column, as is well known
-\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore
-prevents emittance growth for this region of the beam. This effect is shown for our base case in figure
-\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis. However, with a
-matched beam to the plasma density defined by equation \ref{EQ:MatchedB}, we are limited on how much total charge we can
-accelerate without reaching charge densities that will overload the field.
+accelerating field is constant along the beam \cite{katsouleas:1987, tzoufras:2009}. However, a Gaussian beam cannot
+completely flatten the electric field and thus accelerate the beam with no spread in energy. Our base case beam has a
+tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}, but the bulk of
+the sees a relatively flat field when $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield
+is in the fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting
+in the formation of an ion column. This ion column, as is well known \cite{rosenzweig:1991}, provides a linear focusing
+force on the part the electron beam within the column, and therefore prevents emittance growth for this region of the
+beam. This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of
+$20\unit{kT/m}$ near the beam axis. However, with such a narrow beem wehn matched beam to the plasma density (equation
+\ref{EQ:MatchedB}), we are limited on how much total charge we can accelerate without reaching charge densities that
+will overload the field.
 
@@
 
-%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
-%~   longitudinal phase spaces, space long simulation)
-
 %~ The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
-For the majority of the cases we studied that maintained a stable accelerating structure, about $70-80\%$ of the
-electron beam retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance growth for the base case as a
-function of propagation length. No significant emittance growth was observed for propagation lengths up to
-$100\unit{m}$. The drive beam energy was here increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
-de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
-
-The on-axis density of the electron beam increases as its gamma factor increases and its transverse size decreases. The
-transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by equation
-\ref{EQ:MatchedR} where the plasma density is given by the ion density -- as shown in figure \ref{Fig:BeamFilament}.
-This has the potential to cause overloading of the field. However, for our base case this effect was not significant.
-
-%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
-%~   show: transverse and longitudinal phase spaces, long offset simulation)
+For the majority of the cases we studied, that maintained a stable accelerating structure, about $70-80\%$ of the
+electron beam retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance along the beam for the base
+case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma. Emittance growth mainly occurs in
+first few meteres, and no significant emittance growth was observed after this for propagation lengths up to
+$100\unit{m}$. For this simulation, drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing,
+as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
 
@@
 accelerating regime, and may ease the transverse injection tolerances. The head of the beam does not benefit from this
-effect, but since the proton beam creates a quasi linear wake, the head of the beam still stabilises after some time.
-This is illustrated on figure \ref{Fig:BeamEmitt} for an electron beam offset of $1\sigma_{x}$. In this case there is a
-larger initial emittance growth (see left hand plots of figure \ref{Fig:BeamFilament}), but the emittance growth stop
-after the first few metres (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the
-beam oscillates around the axis of the drive beam wakefield, as can bee seen from the right hand plots of figure
-\ref{Fig:BeamFilament}.
+effect, but since the proton beam creates a quasi-linear wake, the head of the beam still stabilises after some time.
+This is illustrated in figure \ref{Fig:BeamEmitt} for an electron beam offset of $1\sigma_{x}$. In this case there is a
+larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f), but the emittance growth stops after the first
+few metres (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the beam oscillates
+around the axis of the drive beam wakefield, as can bee seen from in figure \ref{Fig:BeamFilament}g-h.
+
+The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
+equation \ref{EQ:MatchedR} where the plasma density is given by the ion density. The on-axis density of the electron
+beam, as a result, increases as its gamma factor increases and its transverse size decreases. The effect can be seen in
+figure \ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for our base case
+this effect was not significant.
 
@@
 
-The beam loading and blow out properties of the electron beam depends on a large number of parameters: the longitudinal
-profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
+The beam loading and blow out properties of the electron beam depends on a large number of parameters, including the
+longitudinal profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
 
@@
 generate and transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We
-investigate the interdependence of these parameters by simulation. We vary the electron bunch length, charge and initial
-emittance. We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection
-parameters will depend on the application. For the parameter scans in this section we used a transverse grid cell size
-of $2.34\unit{\mu m}$.
+investigate the interdependence of these parameters in our simulation by varying the electron bunch length, its charge,
+and initial emittance. The results were quantified in terms of how much of the initial charge retained its initial
+emittance within a $5\%$ margin. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$,
+and let the beams proagate through $4\unit{m}$ of plasma.
+%~ We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will
+%~ depend on the application.
 
 Figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} show the dependence on bunch length and bunch charge for an initial beam
-emittance of $2\unit{\mu m}$ after propagating through $4\unit{m}$ of plasma. We ran the scan with beam charges from
-$10\unit{pC}$ to $300\unit{pC}$ and with length $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. We see from
-figure \ref{Fig:BeamQ} that both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy
-spread with a beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to
-underload the electric field, while higher beam charges tend to overload it. It is also clear that longer beams with
-respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, will not optimally load the,
-thus producing a larger spread in energy.
+emittance of $2\unit{\mu m}$. We ran the scan with beam charges from $10\unit{pC}$ to $300\unit{pC}$ and with length
+$\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ}, both the
+$40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy spread with a beam charge
+$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to underload the electric field,
+while higher beam charges tend to overload it. It is also clear that longer beams with respect to the accelerating phase
+of the field, $\approx\lambda_{pe}/4$, will not optimally load the, thus producing a larger spread in energy.
 

### 2017-10-05 Tex/Paper.tex
Changes from Erik and Patric

@@
 
-\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
+\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress,onecolumn]{revtex4-1}
 \bibliographystyle{apsrev4-1}
@@
 % ******************************************************************************************************************** %
+
+%Patric general comments
+%energy labels not consistent between figs 7, 9 and 8
+%labels for the fractional charge is too complicated on Figs 7,8,9.
+it needs to be explained in the caption and/or in the text.
+"On the left axis we plot the fraction of that charge whose emittance remains ....
+"
+%Add scale for grey color on Fig. 2
+%Fig. 3 has a "v=c" and an arrow that are only on that figure ...
+%It is not clear to me what the conclusions/outcome of the last section are ....
 
@@
 We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear
-plasma wakefield driven by a short proton beam. The structure of the wakefield is similar to that of a long, modulated
-proton beam, such as the one being studied by AWAKE.  We show that by exploiting two well known effects, full blow out
-of plasma electrons by the accelerated beam, and beam loading of the wake field, the electron beam can be accelerated
-without significant emittance growth.
+plasma wakefield driven by a short proton beam. The structure of the studied wakefields are similar to those of a long, modulated
+proton beam, such as the AWAKE proton driver.  We show that by %
+properly choosing the electron beam parameters and exploiting two well known effects, beam loading of the wake field and full blow out
+of plasma electrons by the accelerated beam, the electron beam can %PM be accelerated - EA ok
+gain large amounts of energy with a narrow final energy spread (\%-level) and without significant emittance growth.
 \end{abstract}
@@
 
-Beam driven plasma wakefield accelerators have the potential to offer compact linear accelerators with high energy
-gradients, and have been of interest for several decades \cite{chen:1985}. With a relativistic charged particle drive
+Beam driven plasma wakefield accelerators \cite{chen:1985} have the potential to offer compact linear accelerators with high energy
+gradients, and have been of interest for several decades. With a relativistic charged particle drive
 beam travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
-witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept to a minimum. The concept
+witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. %to a minimum. %PM - EA ok
+The concept
 has been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008}. AWAKE at CERN is a proof of concept beam driven plasma wakefield
-accelerator experiment using a proton drive beam delivered by the SPS accelerator \cite{awake_collaboration:2014}.
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} [EA: M. Litos et al., Nature 515, 92?95 (2014)].
 
-A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping energy spread and
-emittance growth to a minimum. In the well described linear case where the beam density $n_{b}$ is much smaller than the
-plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. the beam
-will also see a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has
+A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread and
+emittance growth small. %growth to a minimum. PM - EA ok
+In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the
+plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. The beam
+%will %PM - EA ok
+also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has
 been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the
-transverse oscillations of the plasma electrons, forming a sheet around an evacuated area filled with only ions. The
+transverse oscillations of the plasma electrons, %forming PM - EA ok
+gathering in a sheet around an evacuated area filled with only ions. The
 ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
-radius. This produces a focusing force that preserves emittance \cite{lu:2006-1, lu:2006}.
+radius. This %produces a  PM - EA ok
+focusing force %that PM - EA ok
+preserves emittance \cite{rosenzweig:1991}.
+% EA: I put Rosenzweig original blow out paper as citation here instead of, \cite{lu:2006-1, lu:2006}.
 
-In this paper we present simulation results showing how we can use the non-linear wakefields driven by the head of a
-high charge density witness beam to reduce energy spread and emittance growth in the rest of the beam, while being
-accelerated by a proton drive beam producing quasi-linear wakefields.
+In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can be ensured, when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}.
+By quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
+%~ Patric's version is implemented:
+The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low
+relative energy spread%$\Delta E/E$, 
+, and completely blow out the electrons left in the bubble after the beam to reach conditions that preserves emittance.
+The results have importance for the preparation of AWAKE Run 2 and possibly other applications in the quasi-linear regime.
 
 % ******************************************************************************************************************** %
-\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
+%\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
 %~ Patric's Comments
@@
 
-A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where the
-plasma wavelength $\lambda_{pe} = 2\pi c/\omega_{pe}$ and the plasma frequency $\omega_{pe} = (n_{0} e^{2} / m_{e}
-\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness
-beam loading the peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches
-when they are properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two
-electron drive beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
-
-The energy carried by electron drive bunches used in previous experiments were typically small -- on the order of
-$100\unit{J}$ -- and the propagation length typically $<1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. Higher energy
-electron beam can be improve the propagation length and thus the energy of the accelerated beam. For instance, the
-energy of a high-charge electron beam accelerated to $1\unit{TeV}$, similar to the beam that could be produced by the
-international linear collider with $1\nexp{10}$ electrons, is $1.6\unit{kJ}$. By using electron beams or lasers pulses
-as drivers, a large number of plasma stages is required. However, staging plasma accelerators without reducing the
-effective gradient and spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}.
-
-Proton beams available at CERN carry significantly more energy, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016},
-allowing for much longer plasma wakefield accelerator stages. The SPS beam is, unfortunately, orders of magnitude longer
-than the plasma wavelengths needed for such applications. This can be resolved by letting the proton beam undergo
-self-modulation before injecting the witness beam into accelerating structure. The self-modulation of the beam is
-produced by the transverse fields generated by the beam acting upon itself, causing regions of the beam to rapidly
-defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton
-bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly produces
-wakefields to larger amplitudes.
+% 	EA comment: is this part relevant?  Feels out of place.  We repeat this physics below when discussing proton beam SMI.  
+%A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where the
+%plasma wavelength $\lambda_{pe} = 2\pi c/\omega_{pe}$ and the plasma frequency $\omega_{pe} = (n_{0} e^{2} / m_{e}
+%\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness
+%beam loading the peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches
+%when they are properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two
+%electron drive beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
 
@@
 
-The AWAKE experiment, currently in its first stages of operation at CERN, uses a $400\unit{GeV}$ beam delivered by the
+The energy carried by electron drive bunches used in previous plasma wakefield experiments have been no more than
+$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}.
+For high-energy physics application a higher total beam energy is often desired, for instance, the energy of a high-charge electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be produced by the
+international linear collider, is $1.6\unit{kJ}$.  Using electron beams 
+as drivers a large number of plasma stages is required to reach %PM - EA ok
+an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma accelerators without reducing the
+effective gradient and spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}.
+
+Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016},
+allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of magnitude longer
+than the plasma wavelengths needed for such applications, and the beam %will PM - EA ok
+does not drive a strong wake \cite{gschwendtner:2016}.  By letting the proton beam undergo
+self-modulation before injecting the witness beam into accelerating structure, %most PM - EA ok
+stronger wakefields are %formed PM - EA ok
+excited. The self-modulation of the beam is
+produced by the transverse fields generated by the beam acting upon itself, causing regions of the beam to rapidly
+defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton
+bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly %produces - EA ok
+drives
+wakefields to large %r PM - EA ok 
+amplitudes.
+
+AWAKE at CERN is a proof of concept proton beam driven plasma wakefield
+accelerator experiment \cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton beam delivered by the
 SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$
@@
 size of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave
-number.
+number, %PM. - EA ok
+$\lambda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency. %
 
-The aim of the first phase of Run 1 of the experiment is to demonstrate self-modulation of the proton beam. The aim of
-the second phase in 2018 is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented
-here is for Run 2 \cite{adli:2016}, which aims to demonstrate acceleration of a short electron beam, $\ll\lambda_{pe}$,
-to high energy with a minimal increase in emittance and absolute energy spread.
+The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of
+the second phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented
+here has relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate acceleration of a short electron beam, $\ll\lambda_{pe}$,
+to high energy and with a minimal increase in emittance and absolute energy spread.
 
@@
         beam undergoes self-modulation in the first plasma section. The electron witness beam is injected into the
-        accelerating structure, and undergoes acceleration in the second plasma stage
+        accelerating structure, and undergoes acceleration in the second plasma section
         \cite{berglyd_olsen:2015, adli:2016}.}
@@
 The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}. The first
-section of $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the electron
-beam present. The electron witness beam is then injected into the modulated proton beam before stage two, where it
-undergoes acceleration.
+section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the electron
+beam present. The electron witness beam is then injected into the modulated proton beam before section two, where it
+undergoes acceleration. The self-modulated proton beam does not produce a fully non-linear wakefield, and
+ therefore not all plasma electrons are evacuated from the plasma bubble. The result is that the focusing force does not
+increase linearly with radius %PM
+and the accelerated beam emittance is not preserved.
 
-Using the SPS proton beam as driver, the self-modulated proton beam does not produce a full non-linear wakefield, and
-not all plasma electrons are therefore evacuated from the plasma bubble. The result is that the focusing force does not
-increase linearly with radius. The small size of the accelerating structure produced by the self-modulated beam also
-puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
-to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma density,
-we prevent large amplitude oscillations which may cause additional energy spread as well as emittance growth.
+%   EA: Moved to "witness beam"
+%The small size of the accelerating structure produced by the self-modulated beam also
+%puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
+%to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma density,
+%we prevent large amplitude oscillations which may cause additional energy spread as well as emittance growth.
 
+%    EA: I kept Patric's version, but moved it to the end of the introduction
 %~ Eric's version:
@@
 %~ distances without significant emittance growth.
-
-%~ Patric's version:
-The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low
-relative energy spread $\Delta E/E$, and blow out the electrons left in the accelerating structure to reach conditions
-that preserves emittance.
 
@@
 
-A main focus of this study is on the loading of the wakefields driven by the proton beam. In order to eliminate other
-factors that may affect this, like decay and defocusing of the proton beam, we tried several approaches to create a
-stable drive beam structure based in previous self-modulation studies.
+The focus in this study is the beam loading of the wakefields driven by the proton beam.
+Studies of self-modulated proton bunches show that the proton bunch evolve as it propagates through a uniform plasma [EA: K.
+V.
+Lotov, Phys.
+Plas.
+18, 024501 (2011], but that small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances [EA: K.
+V.
+Lotov, Phys.
+Plas.
+18, 024501 (2011), K.
+V.
+Lotov, Phys.
+Plas.
+22, 103110 (2015), A.
+Caldwell and K.
+Lotov, Phys.
+Plas.
+5, 103101 (2011)].
+To study the witness beam evolution in a stable wake, independent of the dynamics of the self-modulation, %PMwe define here - EA ok
+here we use a single, non-evolving proton bunch as driver.
+The proton bunch parameters are chosen so that key features of the wake - the plasma electron density in the wake and the longitudinal electric field - are the same as %PM - EA ok
+in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}.  Both the proton beam and the witness have Gaussian %PM - EA ok
+longitudinal charge distribution and bi-Gaussian transverse charge distributions.
 
-In these studies we used a short, pre-modulated proton beam with similar structure to the beam produced by the
-self-modulation of the SPS beam in AWAKE. These studies were done using the full PIC code Osiris \cite{fonseca:2002}
-using 2D cylindrical-symmetric simulations and primarily looked at beam loading, energy gain and energy spread
-\cite{berglyd_olsen:2015, berglyd_olsen:2016}.
-
-In order to study the witness beam emittance evolution we turned to the recently released open source version of
-QuickPIC. QuickPIC is a fully relativistic 3D quasi-static PIC code \cite{huang:2006, an:2013}. It does not suffer from
+We have previously studied the beam loading in a proton beam wake using the full PIC code Osiris \cite{fonseca:2002}
+%using PM - EA ok
+and with 2D cylindrical-symmetric simulations.
+The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to create a stable drive beam structure based on previous self-modulation studies.
+In order to study the witness beam emittance evolution we adopt the recently released open source version of QuickPIC \cite{huang:2006, an:2013}.
+QuickPIC is a fully relativistic 3D quasi-static PIC code.
+It does not suffer from
 the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
-study emittance preservation.
+study emittance preservation.  All simulation results in this paper are %PMcalculated - EA ok
+obtained using QuickPIC open source.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} The plasma density in grey with the drive beam (blue) and the witness beam (red)
+    \caption{\label{Fig:PlasmaDenTWake} %PMThe p
+    Plasma density in grey with the drive beam (blue) and the witness beam (red)
         superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
-        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.}
+        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.
+        %PM
+        Beams move to the left.}
 \end{figure}
@@
 
-The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. When
-the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma stage, the peak
-electric field is expected to be $500-600\funit{MV}{m}$. The plasma electrons are only depleted to around $65\%$ of
-nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}. In our simulation
-these conditions are replicated using a single proton beam of $1.46\nexp{10}$ protons, or $2.34\unit{nC}$ and
-$7\unit{kA}$.
-
-The peak density of the simulation drive beam is $0.83\cdot n_{0}$, producing a quasi-linear wakefield. The single bunch
-setup uses the baseline proton beam energy of $400\unit{GeV}$ and transverse size $\sigma_{x} = 200\unit{\mu m}$. We
-also set the length of the drive beam to $\sigma_{z} = 40\unit{\mu m}$. We are not considering the evolution of the
-proton beam itself in this study, so in order to create a stable environment to study the evolution of the witness beam
-we prevent the proton beam from evolving radially by increasing the particle mass by 6 orders of magnitude.
+%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. - EA ok
+The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void of plasma electrons. When
+the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma stage (figure \ref{Fig:AWAKER2}), the peak
+electric field is expected to be about $500\funit{MV}{m}$. The plasma electron density are only depleted to around $65\%$ of
+nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}.
+The plasma electron density depletion and the peak field is replicated using a single %PM proton
+bunch with $1.46\nexp{10}$ protons (or $2.34\unit{nC}$), a %PM bunch
+length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$), and a transverse size $\sigma_{x,y,proton} = 200\unit{\mu m}$.
+The peak density is $0.83\cdot n_{0}$ results in a quasi-linear wake.
+%PM The beam energy is $400\unit{GeV}$.
+To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam [EA: K.
+V.
+Lotov, Phys.
+Plas.
+18, 024501 (2011), K.
+V.
+Lotov, Phys.
+Plas.
+22, 103110 (2015), A.
+Caldwell and K.
+Lotov, Phys.
+Plas.
+5, 103101 (2011)] we freeze the transverse evolution of the equivalent proton bunch by increasing the particles mass by six orders of magnitude.
 
@@
 
-Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}.
-A low gamma witness beam can easily drift out of phase with the drive beam wakefield. The drift of the beams is
-proportional to $\gamma^{-2}$, so to eliminate initial de-phasing of the witness beam, initial beam energy was set such
-that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$. A lower initial value is likely to be
-sufficient \cite{berglyd_olsen:2015}.
+%The small size of the accelerating structure produced by the self-modulated beam also
+%puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
+%to prevent large energy spread.  
+%PM not sure what the point of the above sentence is ... - EA ok
+In order to prevent large amplitude oscillations %PM
+of the witness beam particles, which may cause additional energy spread as well as emittance growth, we %PMstudy
+consider a witness beam matched to the plasma density.  
+%The beam matching relation is given by
+%\begin{equation}
+%    \beta = \frac{\sigma_{x,y}^{2}\gamma}{\epsilon_{N}}
+%          = \frac{c}{\omega_{pe}}\sqrt{2\gamma}, \label{EQ:MatchedB}
+%    % = c\sqrt{\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}}2\gamma}
+%\end{equation}
+%where $\beta$ is the Twiss parameter. It then follows that the transverse profile of the beam must satisfy
+%PM Not sure what the point of the above lines is ....
+The matched beam transverse size is:
+\begin{equation}
+%    \sigma_{x,y}^{2} = c\epsilon_{N}\sqrt{2\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}} \label{EQ:MatchedR}
+%    \sigma_{x,y} =\left(c^2\epsilon_{N}^2m_{e}\varepsilon_{0}n_{pe}e^{2}\gamma \right)^{1/4} \label{EQ:MatchedR} - % PM - EA: not correct
+	\sigma_{x,y}=\left(\frac{2c^{2}\varepsilon_{\mathrm{\mathrm{N}}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}  \label{EQ:MatchedR}  % EA 
+\end{equation}
 
-In these simulations we have used a matched beam for an initial normalised emittance of $\epsilon_{N} = 2\unit{\mu m}$.
-The beam matching relation is given by
-\begin{equation}
-    \beta = \frac{\sigma_{x,y}^{2}\gamma}{\epsilon_{N}}
-          = \frac{c}{\omega_{pe}}\sqrt{2\gamma}, \label{EQ:MatchedB}
-    % = c\sqrt{\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}}2\gamma}
-\end{equation}
-where $\beta$ is the Twiss parameter. It then follows that the transverse profile of the beam must satisfy
-\begin{equation}
-    \sigma_{x,y}^{2} = c\epsilon_{N}\sqrt{2\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}} \label{EQ:MatchedR}
-\end{equation}
-in order to be matched to a given plasma density, initial emittance and energy. This relation requires a very narrow
-beam with a $\sigma_{x,y}$ of $5.25\unit{\mu m}$ compared to the drive beam $\sigma_{x,y} = 200\unit{\mu m}$. The charge
-density of this compact witness beam reaches that of the plasma density at only a few $\unit{pC}$, but reaches optimal
-beam loading at around $100-200\unit{pC}$. The implication here being that the witness beam produces its own non-linear
-wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
-force preventing the bulk of the beam from undergoing emittance growth.
+We %furthermore PM - EA ok
+assume an initial normalized emittance of $\epsilon_{N} = 2\unit{\mu m}$.
+This emittance is possible to produce with a standard RF-injector, while at the same time yielding a sufficient narrow beam.
+% EA: comment, perhaps put a ref here [***ref].
 
-The relatively small size of the witness beam compared to the proton beam put some restrictions on the transverse
-resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the
-narrower one (see figure \ref{Fig:PlasmaDenTWake}). We used a transverse grid cell size of $1.17\unit{\mu m}$, and of
+Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009} %PM
+as well as to its dephasing with respect to the wakefields when at low energy.
+%PM A low gamma witness beam can easily drift out of phase with the drive beam wakefield. The drift of the beams is proportional to $\gamma^{-2}$,  
+To eliminate %initial 
+de-phasing of the witness beam, % PM
+the initial beam energy %PMwas
+is set such
+that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.  A lower initial energy is likely to be
+sufficient for AWAKE Run 2 injection. 
+% EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement, no details in \cite{berglyd_olsen:2015}.
+
+Eq.
+(\ref{EQ:MatchedR}) yields a transverse size of $\sigma_{x,y}$ of $5.25\unit{\mu m}$, narrow compared to the drive beam $\sigma_{x,y,proton} = 200\unit{\mu m}$.
+The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier %PM
+beam loading studies \cite{berglyd_olsen:2016}.  The charge %PM was
+is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the \emph{base case}.  
+% EA: the key figure, figure 2, was not discussed in the text until very far down!  I therefore added (text could possibly be improved)
+Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base case parameters; the proton bunch in blue, the trailing electron beam in red and the plasma electron density in grey.
+
+%   EA: the discussing of charge could better be discussed in the "beam loading chapter" - the information has been moved to there
+% the charge required to load the field is 
+% density of the electron beam reaches that of the plasma density for a bunch charge of a few $\unit{pC}$.   
+% but reaches optimal beam loading at around $100-200\unit{pC}$. 
+%The implication here being that the witness beam produces its own non-linear
+%wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
+%force preventing the bulk of the beam from undergoing emittance growth.
+
+% ******************************************************************************************************************** %
+\subsection{Simulation parameters}\label{SIM}
+% ******************************************************************************************************************** %
+
+The relatively small size of the witness beam %PM compared to the proton beam put some restrictions on the transverse resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the narrower one (see figure \ref{Fig:PlasmaDenTWake}).
+puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron beam and large number of to resolve the large proton beam and the wakefields. %
+We use %PMd  - EA ok
+a transverse grid cell size of $1.17\unit{\mu m}$, and of
 $2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
-was simulated with $16.8\nexp{6}$ non-weighted particles. The witness beam has a total charge of $100\unit{pC}$, a
-$\sigma_{z}=60\unit{\mu m}$, and a $\sigma_{x}=5.25\unit{\mu m}$ matching an initial normalised emittance
-$\epsilon_{0} = 2\unit{\mu m}$. We refer to this parameter set as our base case.
+was simulated with $16.8\nexp{6}$ non-weighted particles.  ***NN*** plasma particles were simulated per grid cell.
+%   EA: Veronica to fill in NN above
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} The top plot shows the unloaded longitudinal electric field with no witness beam
-        (dashed blue line) and the loaded field (whole blue line) along the beam axis. The beam density along the axis
-        for both beams are shown in red. The bottom plot compares the plasma densities along the beam axis for a drive
+    \caption{\label{Fig:BeamLoading} Top plot%PM plot shows the - EA ok
+: unloaded longitudinal electric field with no witness beam
+        (dashed blue line) and %PMthe 
+        loaded field (whole blue line) along the beam axis. The beam density along the axis
+        for both beams are shown in red. %PM The bottom plot compares the 
+        Bottom plot: plasma densities along the beam axis for a drive
         beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line), and
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} The phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness
+    \caption{\label{Fig:BeamPS} %PMThe p
+    Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness
         beam after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of
@@
         \textbf{h} their RMS spread. Plots \textbf{a}, \textbf{b} and \textbf{c}, as well as the blue lines in plots
-        \textbf{g} and \textbf{h} represent particles with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots
-        \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent particles
+        \textbf{g} and \textbf{h} represent particles %PM
+        not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots
+        \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent particles %PM
+        in the ion column 
         with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
@@
 
-The single drive beam setup is designed to produce similar initial conditions for the witness beam as the self-modulated
-case. However, since the drive beam is prevented from significant transverse evolution, we are presented with an
-idealised case where the electron witness beam sees consistent wakefields throughout the plasma stage. The $E_{z}$-field
-generated by the proton drive beam is seen as the blue line in figure \ref{Fig:BeamLoading}, shown with and without the
-electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, we are in the quasi-linear regime
+%  EA: the below has already been clearly spelled out in methods
+%The single drive beam setup is designed to produce similar initial conditions for the witness beam as the self-modulated
+%case. However, since the drive beam is prevented from significant transverse evolution, we are presented with an
+%idealised case where the electron witness beam sees consistent wakefields throughout the plasma stage.
+
+Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step, for the base case parameters. The $E_{z}$-field
+generated by the proton drive beam is seen as the blue line, shown with and without the
+electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, %PMwe 
+the wakefields are in the quasi-linear regime
 \cite{rosenzweig:2010}. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis
@@
 
-The witness beam generates its own wakefield which partially cancels out the $E_{z}$ field generated by the drive beam.
+The witness beam generates its own wakefield which %PM partially cancels out 
+loads the $E_{z}$ field generated by the drive beam.
 With an ideally shaped electron beam charge profile it is possible to optimally load the field in such a way that the
-accelerating field is constant along the beam \cite{katsouleas:1987, tzoufras:2009}. However, a Gaussian beam cannot
-completely flatten the electric field and thus accelerate the beam with no spread in energy. Our base case beam has a
-tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}, but the bulk of
-the sees a relatively flat field when $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield
+accelerating field is constant along the beam \cite{katsouleas:1987, tzoufras:2009}.  Gaussian beams, as assumed in these studies, cannot
+completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
+tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}.  The bulk of
+the beam, however, sees a relatively flat field.  
+% EA: I rewrote this to the sentence after the comments
+%we can acceleratoreHowever, with such a narrow beam when matched beam to the plasma density (equation
+%\ref{EQ:MatchedB}), we are limited on how much total charge we can accelerate without reaching charge densities that
+%will overload the field.
+%  EA: shall we say the below?  The sentence asks for more detailed studies of the dependence of the loading of the transverse fields.
+%The amounts of charge required to load the field depends both on the witness bunch length as well as the transverse size.
+
+The %PM corresponding 
+electron beam density is $n_{eb} \approx 35\times n_{0}$.  This means that the witness beam's own wakefield
 is in the fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting
-in the formation of an ion column. This ion column, as is well known \cite{rosenzweig:1991}, provides a linear focusing
-force on the part the electron beam within the column, and therefore prevents emittance growth for this region of the
+in the formation of an ion column %PM 
+(Fig.~\ref{Fig:BeamLoading} bottom). This ion column, as is well known \cite{rosenzweig:1991}, provides a linear focusing
+force on the part the electron beam within the column, and therefore prevents emittance growth for this %PMregion
+part of the
 beam.  This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}.  The focusing field has a gradient of
-$20\unit{kT/m}$ near the beam axis. However, with such a narrow beem wehn matched beam to the plasma density (equation
-\ref{EQ:MatchedB}), we are limited on how much total charge we can accelerate without reaching charge densities that
-will overload the field.
+$20\unit{kT/m}$ near the beam axis, corresponding to the matched field gradient.
 
@@
 %~ The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
-For the majority of the cases we studied, that maintained a stable accelerating structure, about $70-80\%$ of the
-electron beam retained its initial emittance. Figure \ref{Fig:BeamEmitt} shows emittance along the beam for the base
-case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma. Emittance growth mainly occurs in
-first few meteres, and no significant emittance growth was observed after this for propagation lengths up to
-$100\unit{m}$. For this simulation, drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing,
+% EA: I cut the line below, we are still discussing the base case
+%For the majority of the cases we studied, that maintained a stable accelerating structure, 
+ %PMDue to the ion column focusing, 
+ Simulation results show that about $70-80\%$ of the electron beam longitudinal slices retain their initial emittance after the propagation in the plasma.
+Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma.
+Emittance growth mainly occurs in first few meters, and no significant emittance growth %PMwas
+is observed after this for propagation lengths up to
+$100\unit{m}$.
+The head of the beam does not benefit from the full ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still stabilizes after some time.
+For the 100 meter simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing,
 as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
@@
 %~ witness beam wakefield follows the beam itself.
+%PM
+So far we have considered a witness beam injected on the axis of the proton bunch. %
+We now briefly examine the case of injection of a witness beam with an offset with respect to the proton bunch axis. %
+Since the witness beam creates its own plasma bubble, the emittance of the part of the beam inside the
+bubble is not affected by small transverse offsets of the witness beam with respect to the proton beam axis.
+This is illustrated in figure \ref{Fig:BeamEmitt}, right, for an electron beam offset of $1\sigma_{xe}$.
+Emittance preservation for small offsets is an added benefit of this
+accelerating regime, and may ease transverse injection tolerances. 
+The head of the beam experiences a 
+%larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f),
+%PM
+%THERE IS NO EMITTANCE SHOWN OR NOTHING TO COMPARE TO ... WHAT TO DO????
+% EA: one way out, can compare emittance growth using fig 5 instead, as follows (alternatively, a new set of figures must be created)
+larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to \ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
+Figure \ref{Fig:BeamFilament} a-c show the phase space of the head of the electron beam after 0, 1.0 and 2.5 m, while figure \ref{Fig:BeamFilament} d-f show the phase space of the trailing part of the beam.
+The centroid oscillations of the head and the trailing part are shown in figure \ref{Fig:BeamFilament} g.
+This effect of a transverse offset is likely to be greater for larger offsets as the beam oscillates
+around the axis of the drive beam wakefield.% EA: would be good to include a statement of how large the offsets can be before when the electron beam starts to break up / not preserve emittance.
 
-Since the accelerated electron beam creates its own plasma bubble, the emittance of the part of the beam inside the
-bubble is not affected by small beam offsets with respect to the proton beam axis. This is an added benefit of this new
-accelerating regime, and may ease the transverse injection tolerances. The head of the beam does not benefit from this
-effect, but since the proton beam creates a quasi-linear wake, the head of the beam still stabilises after some time.
-This is illustrated in figure \ref{Fig:BeamEmitt} for an electron beam offset of $1\sigma_{x}$. In this case there is a
-larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f), but the emittance growth stops after the first
-few metres (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the beam oscillates
-around the axis of the drive beam wakefield, as can bee seen from in figure \ref{Fig:BeamFilament}g-h.
-
-The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
-equation \ref{EQ:MatchedR} where the plasma density is given by the ion density. The on-axis density of the electron
+The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
+equation \ref{EQ:MatchedR} %PM where the plasma density is given by the ion density - EA ok
+,i .e., evolves to stay matched. The on-axis density of the electron
 beam, as a result, increases as its gamma factor increases and its transverse size decreases. The effect can be seen in
-figure \ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for our base case
-this effect was not significant.
+figure \ref{Fig:BeamFilament} h. This has the potential to cause overloading of the field. However, for the base case
+no significant overloading %PMwas
+is observed.
 
@@
     \caption{\label{Fig:BeamQ} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial beam charge (blue), and relative energy spread of the accepted charge (red), after
+        function of initial beam charge (blue %PM
+        symbols, lines), and relative energy spread of the accepted charge (red %PM
+        symbols, lines), after
         $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These are shown for four
         different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam
-        loading section corrspond to the square marked lines at $100\unit{pC}$.}
+        loading section correspond to the square marked lines at $100\unit{pC}$.}
 \end{figure}
@@
     \caption{\label{Fig:BeamQAbs} Total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a function of
-        initial beam charge (blue), and final momentum (red), after $4\unit{m}$ of plasma and with an initial emittance
+        initial beam charge (blue %PM
+        symbols, lines), and final %PMmomentum
+        energy (red %PM
+        symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
         $\epsilon_{N,0}=2\unit{\mu m}$.}
@@
     \caption{\label{Fig:BeamQEmit} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial emittance (blue), and relative energy spread of the accepted charge (red), after $4\unit{m}$
+        function of initial emittance (blue %PM
+        symbols, lines), and relative energy spread of the accepted charge (red %PM
+        symbols, lines), after $4\unit{m}$
         of plasma.}
@@
 
-The beam loading and blow out properties of the electron beam depends on a large number of parameters, including the
-longitudinal profile, the transverse profile as well as the relative phasing of the proton and the electron beams.
-
+The beam loading and blow out properties of the electron beam depend on a large number of parameters, including %PMthe
+longitudinal profile, %PMthe 
+transverse profile as well as %PMthe 
+relative phasing of the proton and the electron beams.  We present a limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2.
 %~ We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
-For AWAKE Run 2 we desire to maximize the energy gain, minimize the energy spread, maximize the charge to be
-accelerated, and minimize the emittance growth. In addition, the bunch length should be such that it is possible to
-generate and transport by a compact electron injector \cite{adli:2016}. These are contradictory constraints. We
-investigate the interdependence of these parameters in our simulation by varying the electron bunch length, its charge,
+For electron beam to be externally injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated, and minimize the emittance growth \cite{adli:2016}.
+In addition, the bunch length should be such that it is possible to
+generate and transport the bunch using a compact electron injector \cite{adli:2016}. We
+investigate the interdependence of these parameters in simulation by varying the electron bunch length, its charge,
 and initial emittance. The results were quantified in terms of how much of the initial charge retained its initial
 emittance within a $5\%$ margin. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$,
-and let the beams proagate through $4\unit{m}$ of plasma.
+and let the beams propagate through $4\unit{m}$ of plasma.
 %~ We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will
@@
 
-Figures \ref{Fig:BeamQ} and \ref{Fig:BeamQAbs} show the dependence on bunch length and bunch charge for an initial beam
-emittance of $2\unit{\mu m}$. We ran the scan with beam charges from $10\unit{pC}$ to $300\unit{pC}$ and with length
-$\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ}, both the
-$40\unit{\mu m}$ and the $60\unit{\mu m}$ beam has a well defined minimum energy spread with a beam charge
-$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$ respectively. Lower beam charges tend to underload the electric field,
+Figure \ref{Fig:BeamQ}  show the dependence of %PM emittance
+charge and energy spread on bunch length and %PMbunch
+incoming charge.  An initial beam
+emittance of $2\unit{\mu m}$ was used.  %
+%PM
+Therefore, we define the fractional charge as that whose emittance remains smaller than $2.1\unit{\mu m}$. %PM We ran the scan with beam charges from 
+The beam charge range $10\unit{pC}$ to $300\unit{pC}$ and %with length
+the $\sigma_{z}$ range from $40\unit{\mu m}$ to $100\unit{\mu m}$.  As can be seen from figure \ref{Fig:BeamQ} %, red curves
+(red curves), both the
+$40\unit{\mu m}$ and the $60\unit{\mu m}$ beam %PMhas
+have a well defined minimum energy spread with a beam charge
+$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the electric field,
 while higher beam charges tend to overload it. It is also clear that longer beams with respect to the accelerating phase
-of the field, $\approx\lambda_{pe}/4$, will not optimally load the, thus producing a larger spread in energy.
+of the field, $\approx\lambda_{pe}/4$, %PMwill
+does not optimally load the wake, thus producing a larger spread in energy.  The blue curves show the fraction of %PMthe sliced emittance where the
+charge whose initial emittance is preserved (the slice%Md
+  emittance for the base case is shown in figure \ref{Fig:BeamEmitt}).
+As the witness beam charge increases the fraction of slices with preserved emittance increases, as expected from an earlier onset of the bubble formation and also increase in the bubble size \cite{lu:2006-1, lu:2006}.
+%PM SHOULD WE ADD SOMETHING LIKE:
+We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.
+%???
+
+Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on bunch length and bunch charge %PM, in red curves
+(red curves). The blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as function of bunch length and bunch charge.
 
 Figure \ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
-emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
-to growth for high emittance beams; the transverse beam size may increase beyond the size of the bubble, or the beam
-density may be reduced so much that the plasma electrons are no longer fully evacuated from the ion column. Emittance
-values higher than a few micrometres lead to a significant increase in both emittance and energy spread. In these
-simulations the focusing of the beam to the plasma remains matched for each emittance value.
+emittance.  In these simulations %PMthe focusing of the beam to the plasma remains matched for each emittance value.
+we adjusted the witness beam radius to maintain the matching condition at each emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
+to emittance growth for high initial emittance beams; the transverse beam size may increase beyond the size of the bubble, and the beam
+density may be reduced so much that the plasma electrons are no longer fully evacuated from the bubble. Emittance
+values higher than a few micrometers lead to a significant increase in both emittance and energy spread.
+
+% EA: slight rewrite to argue what we want with this section
+The optimal working point will depend on the application and must be studied for each case and is, as illustrated in this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters like the plasma density.
 
@@
 
-We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a quasi-
-linear proton driven wake. When optimally loaded, the electron beam creates its own ion bubble, yielding emittance
-preservation for a large parts of the electron beam.
+%We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a quasi-linear proton driven wake.
+When optimally loaded an electron witness beam has sufficient charge to create a strong blow out forming a %n ion
+%bubble trailing the witness beam.  The focusing forces from the ions ensures emittance preservation for large parts of the %PM 
+%witness beam. %PM, also when the electron beam has some offset with respect to the proton driver.
+%Simulations show that the emittance of a large fraction of the electron beam is preserved even when it enters the plasma with and offset with respect to the proton bunch axis. %
 
-These result indicates that emittance preservation for an on-axis injected electron beam, properly optimized, is
-feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might be accelerated, for bunches of length
-$40-60\unit{\mu m}$. Such an electron bunch may be generated by a standard S-band RF gun.
+%Using AWAKE parameters these result indicates that emittance preservation for an electron beam injected on-axis into a plasma stage, and properly optimized, may be
+%feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might be accelerated, for bunches of length
+%$40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based on a standard RF gun [S. Doebert, private communication].
 
-As this study assumes a wake driven by a single, short proton beam, the studies for interesting cases for AWAKE should
-be repeated by a full simulation of a self-modulated proton beam.
+%This study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single, short proton bunch, and investigates an ideal, uniform plasma profile.
+To fully investigate optimal AWAKE injection, further study should be performed including simulations of realistic plasma profiles combined with a self-modulated proton beam.
+% EA: we could also say "is underway" and cite Lotov et co?
+%PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest - EA patric's verson of conclusions are OK with me
+
+We have devised a method to accelerate an electron witness bunch to high energy with a low relative energy spread while maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
+This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by self-modulation of a long proton bunch.
+This method is in principle applicable to all experiments operating in the quasi-linear regime.
+Low relative energy spread and emittance preservation are achieved by choosing the electron beam parameters to load the wakefields and evacuate the remaining plasma electrons from the accelerating structure.
+
+Parameter studies indicate that up to a few $100\unit{pC}$, up to 70\% of the incoming bunch charge, is accelerated, for bunch of lengths of $40-60\unit{\mu m}$.
+Such electron bunches may be generated by an injector based on a standard RF photo-emission gun [EA: S.
+Doebert, private communication].
+
+In order to use manageable computer time for simulations, this study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single, short proton bunch producing similar wakefields.
+However, the wakefields driven by a train of bunches evolve with the ramp of a real plasma and when entering the plasma.
+Therefore, to be fully applicable to an experiment such as AWAKE, the study will have to be redone with more realistic parameters.
+However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated bunch with low relative energy spread and emittance remains applicable.
 
@@
 
-The simulations for this study have been run using the open source version of QuickPIC released in early 2017 and owned
+% EA: I think owned also by IST.  I will check with Weiming and Warren
+The simulations for this study have been performed using the open source version of QuickPIC released in early 2017 and owned
 by UCLA.
@@
 is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
-University of Oslo, the University of Tromsø and the Norwegian University of Science and Technology. Project code:
+University of Oslo, the University of Troms{\o} and the Norwegian University of Science and Technology. Project code:
 nn9303k. Some of the simulations were also run on the student-maintained computing cluster ``Smaug'' at the University
@@
 
-The authors would also like to thank the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS was used
-extensively for simulations leading to the work presented in this paper.
+% EA: not needed (checked with Jorge)
+%The authors would also like to thank the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS was used
+%extensively for simulations leading to the work presented in this paper.
+% EA: instead I suggest something like (also promised Jorge)
+We gratefully acknowledge helpful discussions with Jorge Vieria from IST Lisbon.
 

### 2017-10-05 Tex/PaperPM.tex
Additional files from Erik and Patric

--- 2017-10-05 Tex/Paper.tex
@@
 properly choosing the electron beam parameters and exploiting two well known effects, beam loading of the wake field and full blow out
-of plasma electrons by the accelerated beam, the electron beam can %PM be accelerated - EA ok
-gain large amounts of energy with a narrow final energy spread (\%-level) and without significant emittance growth.
+of plasma electrons by the accelerated beam, the electron beam can %PM be accelerated
+gained large amounts of energy, have a narrow final energy spread (\%-level) and without significant emittance growth.
 \end{abstract}
@@
 beam travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
-witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. %to a minimum. %PM - EA ok
+witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. %to a minimum. %PM
 The concept
 has been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} [EA: M. Litos et al., Nature 515, 92?95 (2014)].
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} ***add [M. Litos and 23 co-authors, Nature 515, 92?95 (2014)]***.
 
 A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread and
-emittance growth small. %growth to a minimum. PM - EA ok
+emittance small. %growth to a minimum. PM
 In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the
 plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. The beam
-%will %PM - EA ok
+%will PM
 also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has
 been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the
-transverse oscillations of the plasma electrons, %forming PM - EA ok
+transverse oscillations of the plasma electrons, %forming PM
 gathering in a sheet around an evacuated area filled with only ions. The
 ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
-radius. This %produces a  PM - EA ok
-focusing force %that PM - EA ok
+radius. This %produces a  PM
+focusing force %that PM
 preserves emittance \cite{rosenzweig:1991}.
@@
 In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can be ensured, when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}.
-By quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
+By quasi-linear wakefields we mean mean wakefields with only partial blow out of the plasma electrons in the bubble.
 %~ Patric's version is implemented:
 The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low
-relative energy spread%$\Delta E/E$, 
-, and completely blow out the electrons left in the bubble after the beam to reach conditions that preserves emittance.
+relative energy spread
+%$\Delta E/E$, 
+and completely blow out the electrons left in the bubble after the beam to reach conditions that preserves emittance.
 The results have importance for the preparation of AWAKE Run 2 and possibly other applications in the quasi-linear regime.
@@
 international linear collider, is $1.6\unit{kJ}$. Using electron beams 
-as drivers a large number of plasma stages is required to reach %PM - EA ok
+as drivers a large number of plasma stages is required to reach %PM
 an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma accelerators without reducing the
@@
 allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of magnitude longer
-than the plasma wavelengths needed for such applications, and the beam %will PM - EA ok
+than the plasma wavelengths needed for such applications, and the beam %will PM
 does not drive a strong wake \cite{gschwendtner:2016}.  By letting the proton beam undergo
-self-modulation before injecting the witness beam into accelerating structure, %most PM - EA ok
-stronger wakefields are %formed PM - EA ok
+self-modulation before injecting the witness beam into accelerating structure, %most PM
+stronger wakefields are %formed PM
 excited. The self-modulation of the beam is
@@
 defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton
-bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly %produces - EA ok
+bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly %produces
 drives
-wakefields to large %r PM - EA ok 
+wakefields to large %r PM 
 amplitudes.
@@
 size of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave
-number, %PM. - EA ok
-$\lambda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency. %
+number, %PM.
+$\lanmda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency. %
 
@@
 The focus in this study is the beam loading of the wakefields driven by the proton beam.
-Studies of self-modulated proton bunches show that the proton bunch evolve as it propagates through a uniform plasma [EA: K.
+Studies of self-modulated proton bunches show that the proton bunch evolve as it propagates through a uniform plasma [K.
 V.
@@
 Plas.
-18, 024501 (2011], but that small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances [EA: K.
+18, 024501 (2011], but that small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances [K.
 V.
@@
 5, 103101 (2011)].
-To study the witness beam evolution in a stable wake, independent of the dynamics of the self-modulation, %PMwe define here - EA ok
+To study the witness beam evolution in a stable wake, independent of the dynamics of the self-modulation, %PMwe define here
 here we use a single, non-evolving proton bunch as driver.
-The proton bunch parameters are chosen so that key features of the wake - the plasma electron density in the wake and the longitudinal electric field - are the same as %PM - EA ok
-in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}.  Both the proton beam and the witness have Gaussian %PM - EA ok
+The proton bunch parameters are chosen so that key features of the wake - the plasma electron density in the wake and the longitudinal electric field - are the same as %PM
+in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}.  Both the proton beam and the witness have Gaussian %PM
 longitudinal charge distribution and bi-Gaussian transverse charge distributions.
@@
 We have previously studied the beam loading in a proton beam wake using the full PIC code Osiris \cite{fonseca:2002}
-%using PM - EA ok
-and with 2D cylindrical-symmetric simulations.
+%using PM
+and withs 2D cylindrical-symmetric simulations.
 The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to create a stable drive beam structure based on previous self-modulation studies.
@@
 the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
-study emittance preservation.  All simulation results in this paper are %PMcalculated - EA ok
+study emittance preservation.  All simulation results in this paper are %PMcalculated
 obtained using QuickPIC open source.
@@
 
-%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. - EA ok
+%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. 
 The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void of plasma electrons. When
@@
 %PM The beam energy is $400\unit{GeV}$.
-To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam [EA: K.
+To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam [K.
 V.
@@
 %The small size of the accelerating structure produced by the self-modulated beam also
-%puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
-%to prevent large energy spread.  
-%PM not sure what the point of the above sentence is ... - EA ok
+puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
+to prevent large energy spread.  
+%PM not sure what the point of the above sentence is ...
 In order to prevent large amplitude oscillations %PM
@@
 %    \sigma_{x,y}^{2} = c\epsilon_{N}\sqrt{2\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}} \label{EQ:MatchedR}
-%    \sigma_{x,y} =\left(c^2\epsilon_{N}^2m_{e}\varepsilon_{0}n_{pe}e^{2}\gamma \right)^{1/4} \label{EQ:MatchedR} - % PM - EA: not correct
-	\sigma_{x,y}=\left(\frac{2c^{2}\varepsilon_{\mathrm{\mathrm{N}}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}  \label{EQ:MatchedR}  % EA 
+    \sigma_{x,y} =\left(c^2\epsilon_{N}^2m_{e}\varepsilon_{0}n_{pe}e^{2}\gamma}\right)^{1/4} \label{EQ:MatchedR}
 \end{equation}
 
-We %furthermore PM - EA ok
+We %furthermore PM
 assume an initial normalized emittance of $\epsilon_{N} = 2\unit{\mu m}$.
@@
 beam loading studies \cite{berglyd_olsen:2016}.  The charge %PM was
-is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the \emph{base case}.  
-% EA: the key figure, figure 2, was not discussed in the text until very far down!  I therefore added (text could possibly be improved)
-Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base case parameters; the proton bunch in blue, the trailing electron beam in red and the plasma electron density in grey.
+is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the {base case}.
 
@@
 The relatively small size of the witness beam %PM compared to the proton beam put some restrictions on the transverse resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the narrower one (see figure \ref{Fig:PlasmaDenTWake}).
-puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron beam and large number of to resolve the large proton beam and the wakefields. %
-We use %PMd  - EA ok
+puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron beam and large number of to resolve the large proton eam and the wakefields. %
+We use %PMd 
 a transverse grid cell size of $1.17\unit{\mu m}$, and of
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} Top plot%PM plot shows the - EA ok
-: unloaded longitudinal electric field with no witness beam
+    \caption{\label{Fig:BeamLoading} The top%PM plot shows the 
+:unloaded longitudinal electric field with no witness beam
         (dashed blue line) and %PMthe 
@@
 So far we have considered a witness beam injected on the axis of the proton bunch. %
-We now briefly examine the case of injection of a witness beam with an offset with respect to the proton bunch axis. %
+We now briefly examine the case of injection of a witness beam with an offset with respect to the axis of the proton bunch. %
+
 Since the witness beam creates its own plasma bubble, the emittance of the part of the beam inside the
-bubble is not affected by small transverse offsets of the witness beam with respect to the proton beam axis.
-This is illustrated in figure \ref{Fig:BeamEmitt}, right, for an electron beam offset of $1\sigma_{xe}$.
-Emittance preservation for small offsets is an added benefit of this
-accelerating regime, and may ease transverse injection tolerances. 
-The head of the beam experiences a 
-%larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f),
+bubble is not affected by small transverse offsets of the witness beam with respect to the proton beam axis. This is an added benefit of this 
+accelerating regime, and may ease transverse injection tolerances. Also in the offset case the emittance of the head of the beam still stabilizes after some time.
+This is illustrated in figure \ref{Fig:BeamEmitt} for an electron beam offset of $1\sigma_{x}$. In this case there is a
+larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f),
 %PM
 %THERE IS NO EMITTANCE SHOWN OR NOTHING TO COMPARE TO ... WHAT TO DO????
-% EA: one way out, can compare emittance growth using fig 5 instead, as follows (alternatively, a new set of figures must be created)
-larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to \ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
-Figure \ref{Fig:BeamFilament} a-c show the phase space of the head of the electron beam after 0, 1.0 and 2.5 m, while figure \ref{Fig:BeamFilament} d-f show the phase space of the trailing part of the beam.
-The centroid oscillations of the head and the trailing part are shown in figure \ref{Fig:BeamFilament} g.
-This effect of a transverse offset is likely to be greater for larger offsets as the beam oscillates
-around the axis of the drive beam wakefield.% EA: would be good to include a statement of how large the offsets can be before when the electron beam starts to break up / not preserve emittance.
+ but the emittance growth stops after the first
+few meters (figure \ref{Fig:BeamEmitt}). This effect is likely to be greater for larger offsets as the beam oscillates
+around the axis of the drive beam wakefield, as can bee seen %PMfrom 
+in figures \ref{Fig:BeamFilament}%PMg-h.
+g and h.
 
 The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
-equation \ref{EQ:MatchedR} %PM where the plasma density is given by the ion density - EA ok
+equation \ref{EQ:MatchedR}%PM where the plasma density is given by the ion density
 ,i .e., evolves to stay matched. The on-axis density of the electron
@@
 %PM SHOULD WE ADD SOMETHING LIKE:
-We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.
+We note here that operation with 100\unit{pC}$ leads to a significantly larger charge (factor $\sim4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.
 %???
@@
 
-% EA: slight rewrite to argue what we want with this section
-The optimal working point will depend on the application and must be studied for each case and is, as illustrated in this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters like the plasma density.
+The optimal working point will depend on the application and must be studied for each case, based on a trade off between bunch length, bunch charge and emittance preservation, taking into account also other parameters, like the plasma density.
 
@@
 % EA: we could also say "is underway" and cite Lotov et co?
-%PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest - EA patric's verson of conclusions are OK with me
+%PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest
 
@@
 Parameter studies indicate that up to a few $100\unit{pC}$, up to 70\% of the incoming bunch charge, is accelerated, for bunch of lengths of $40-60\unit{\mu m}$.
-Such electron bunches may be generated by an injector based on a standard RF photo-emission gun [EA: S.
+Such electron bunches may be generated by an injector based on a standard RF photo-emission gun [S.
 Doebert, private communication].
@@
 
-% EA: I think owned also by IST.  I will check with Weiming and Warren
 The simulations for this study have been performed using the open source version of QuickPIC released in early 2017 and owned

### 2017-10-05 Tex/comments_to_discuss.tex
Additional files from Erik and Patric

%Patric general comments

%energy labels not consistent between figs 7, 9 and 8
%labels for the fractional charge is too complicated on Figs 7,8,9. it needs to be explained in the caption and/or in the text. "On the left axis we plot the fraction of that charge whose emittance remains .... "

Veronica: to add sufficient graph explanations in the captions

%Add scale for grey color on Fig. 2

Veronica: to add scale for grey color (color bar with p.e. density)

%Fig. 3 has a "v=c" and an arrow that are only on that figure ...

Veronica: to add.

% the same symbol was used for sigma_x proton beam and electron beam.  I added ",proton" to the proton parameters to separate.  Should we also add ",electron" to ebeam?

Veronica: check for consistency of ",proton" , also consider a different way of descriptin the two beams (sigma_x,p and sigma_x,e is ok with me).

%It is not clear to me what the conclusions/outcome of the last section are ....

I still think this section is needed, both to make the paper more relevant for AWAKE and to avoid (valid) criticism that we only study one parameter set, and do not discuss at all the dependence of the result on parameters.  I slightly rewrote the last line in the section to highlight that this section illustrates the parameter dependence in this accelerating regime. n

"The optimal working point will depend on the application and must be studied for each case and is, as illustrated in this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters like the plasma density."

(Veronica: unless better ideas no need to take action, expect review)

%THERE IS NO EMITTANCE SHOWN OR NOTHING TO COMPARE TO ... WHAT TO DO????

I have rewriten the text to use Fig 5 to compare the emittance growth, and not Fig 6.

(Veronica: unless better ideas no need to take action, expect review)

%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?

Good idea, but I did not find an obvious place to state it without rewrite.  When we talk about the SSM bunch train we have not discussed the ebeam parameters.  And when we have discuss ebeam parameters we have made effort to focus on the single bunch proton driver.  So I did not implement this.

(Veronica: unless better ideas no need to take action, expect review)

### 2017-10-05 Tex/Paper.tex
Some source cleanup and fixes. Added citations.

@@
 
-\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress,onecolumn]{revtex4-1}
+\documentclass[aps,prstab,reprint,amsmath,amssymb,groupedaddress]{revtex4-1}
 \bibliographystyle{apsrev4-1}
@@
 We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear
-plasma wakefield driven by a short proton beam. The structure of the studied wakefields are similar to those of a long, modulated
-proton beam, such as the AWAKE proton driver.  We show that by %
-properly choosing the electron beam parameters and exploiting two well known effects, beam loading of the wake field and full blow out
-of plasma electrons by the accelerated beam, the electron beam can %PM be accelerated - EA ok
+plasma wakefield driven by a short proton beam. The structure of the studied wakefields are similar to those of a long,
+modulated proton beam, such as the AWAKE proton driver. We show that by properly choosing the electron beam parameters
+and exploiting two well known effects, beam loading of the wake field and full blow out of plasma electrons by the
+accelerated beam, the electron beam can %PM be accelerated - EA ok
 gain large amounts of energy with a narrow final energy spread (\%-level) and without significant emittance growth.
@@
 
-Beam driven plasma wakefield accelerators \cite{chen:1985} have the potential to offer compact linear accelerators with high energy
-gradients, and have been of interest for several decades. With a relativistic charged particle drive
+Beam driven plasma wakefield accelerators \cite{chen:1985} have the potential to offer compact linear accelerators with
+high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive
 beam travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
 witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. %to a minimum. %PM - EA ok
-The concept
-has been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008} [EA: M. Litos et al., Nature 515, 92?95 (2014)].
+The concept has been demonstrated experimentally in the past using electron drive beams accelerating electron witness
+beams \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
 
-A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread and
-emittance growth small. %growth to a minimum. PM - EA ok
-In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the
-plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. The beam
+A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread
+and emittance growth small. %growth to a minimum. PM - EA ok
+In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the plasma density
+$n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. The beam
 %will %PM - EA ok
@@
 transverse oscillations of the plasma electrons, %forming PM - EA ok
-gathering in a sheet around an evacuated area filled with only ions. The
-ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly with
-radius. This %produces a  PM - EA ok
+gathering in a sheet around an evacuated area filled with only ions. The ions, assumed stationary, form an uniform
+density ion channel creating a focusing force that varies linearly with radius. This %produces a  PM - EA ok
 focusing force %that PM - EA ok
@@
 
-In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can be ensured, when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}.
-By quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
+In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can
+be ensured, when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}. By
+quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
 %~ Patric's version is implemented:
@@
 The energy carried by electron drive bunches used in previous plasma wakefield experiments have been no more than
-$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}.
-For high-energy physics application a higher total beam energy is often desired, for instance, the energy of a high-charge electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be produced by the
-international linear collider, is $1.6\unit{kJ}$.  Using electron beams 
-as drivers a large number of plasma stages is required to reach %PM - EA ok
+$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. For
+high-energy physics application a higher total beam energy is often desired, for instance, the energy of a high-charge
+electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be produced by
+the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers a large number of plasma stages is
+required to reach %PM - EA ok
 an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma accelerators without reducing the
@@
 
-Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS beam \cite{gschwendtner:2016},
-allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of magnitude longer
-than the plasma wavelengths needed for such applications, and the beam %will PM - EA ok
-does not drive a strong wake \cite{gschwendtner:2016}.  By letting the proton beam undergo
-self-modulation before injecting the witness beam into accelerating structure, %most PM - EA ok
+Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS
+beam \cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
+magnitude longer than the plasma wavelengths needed for such applications, and the beam %will PM - EA ok
+does not drive a strong wake \cite{gschwendtner:2016}.  By letting the proton beam undergo self-modulation before
+injecting the witness beam into accelerating structure, %most PM - EA ok
 stronger wakefields are %formed PM - EA ok
-excited. The self-modulation of the beam is
-produced by the transverse fields generated by the beam acting upon itself, causing regions of the beam to rapidly
-defocus \cite{kumar:2010}. The modulation frequency is close to that of the plasma, and produces a train of short proton
-bunches along the beam axis with a surrounding halo of defocused particles. This train of bunches resonantly %produces - EA ok
-drives
-wakefields to large %r PM - EA ok 
+excited. The self-modulation of the beam is produced by the transverse fields generated by the beam acting upon itself,
+causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the
+plasma, and produces a train of short proton bunches along the beam axis with a surrounding halo of defocused particles.
+This train of bunches resonantly %produces - EA ok
+drives wakefields to large %r PM - EA ok 
 amplitudes.
 
-AWAKE at CERN is a proof of concept proton beam driven plasma wakefield
-accelerator experiment \cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton beam delivered by the
-SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$
-\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$ -- matched to the transverse
-size of the SPS proton beam such that $k_{pe}\sigma_{x,y} = 1$, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave
-number, %PM. - EA ok
-$\lambda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency. %
+AWAKE at CERN is a proof of concept proton beam driven plasma wakefield accelerator experiment
+\cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton
+beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of
+$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
+-- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
+$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, %PM. - EA ok
+$\lambda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron
+angular frequency.
 
-The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of
-the second phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented
-here has relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate acceleration of a short electron beam, $\ll\lambda_{pe}$,
-to high energy and with a minimal increase in emittance and absolute energy spread.
+The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of the second
+phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
+relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate
+acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
+absolute energy spread.
 
@@
 The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}. The first
-section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the electron
-beam present. The electron witness beam is then injected into the modulated proton beam before section two, where it
-undergoes acceleration. The self-modulated proton beam does not produce a fully non-linear wakefield, and
+section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
+electron beam present. The electron witness beam is then injected into the modulated proton beam before section two,
+where it undergoes acceleration. The self-modulated proton beam does not produce a fully non-linear wakefield, and
 therefore not all plasma electrons are evacuated from the plasma bubble. The result is that the focusing force does not
-increase linearly with radius %PM
-and the accelerated beam emittance is not preserved.
+increase linearly with radius and the accelerated beam emittance is not preserved.
 
@@
 
-The focus in this study is the beam loading of the wakefields driven by the proton beam.
-Studies of self-modulated proton bunches show that the proton bunch evolve as it propagates through a uniform plasma [EA: K.
-V.
-Lotov, Phys.
-Plas.
-18, 024501 (2011], but that small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances [EA: K.
-V.
-Lotov, Phys.
-Plas.
-18, 024501 (2011), K.
-V.
-Lotov, Phys.
-Plas.
-22, 103110 (2015), A.
-Caldwell and K.
-Lotov, Phys.
-Plas.
-5, 103101 (2011)].
-To study the witness beam evolution in a stable wake, independent of the dynamics of the self-modulation, %PMwe define here - EA ok
-here we use a single, non-evolving proton bunch as driver.
-The proton bunch parameters are chosen so that key features of the wake - the plasma electron density in the wake and the longitudinal electric field - are the same as %PM - EA ok
-in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}.  Both the proton beam and the witness have Gaussian %PM - EA ok
+The focus in this study is the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
+proton bunches show that the proton bunch evolve as it propagates through a uniform plasma \cite{lotov:2011}, but that
+small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances
+\cite{lotov:2011, lotov:2015, caldwell:2011}.  To study the witness beam evolution in a stable wake, independent of the
+dynamics of the self-modulation, %PMwe define here - EA ok
+here we use a single, non-evolving proton bunch as driver. The proton bunch parameters are chosen so that key features of
+the wake -- the plasma electron density in the wake and the longitudinal electric field -- are the same as %PM - EA ok
+in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}. Both the proton
+beam and the witness have Gaussian %PM - EA ok
 longitudinal charge distribution and bi-Gaussian transverse charge distributions.
@@
 %using PM - EA ok
-and with 2D cylindrical-symmetric simulations.
-The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to create a stable drive beam structure based on previous self-modulation studies.
-In order to study the witness beam emittance evolution we adopt the recently released open source version of QuickPIC \cite{huang:2006, an:2013}.
-QuickPIC is a fully relativistic 3D quasi-static PIC code.
-It does not suffer from
-the numerical Cherenkov effect that full PIC codes do \cite{godfrey:1974,lehe:2013}, making it a well suited tool to
-study emittance preservation.  All simulation results in this paper are %PMcalculated - EA ok
+and with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily
+looked at beam loading, energy gain and energy spread, as well as different approaches to create a stable drive beam
+structure based on previous self-modulation studies. In order to study the witness beam emittance evolution we adopt the
+recently released open source version of QuickPIC \cite{huang:2006, an:2013}. QuickPIC is a fully relativistic 3D
+quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC codes do
+\cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation.  All simulation results in
+this paper are %PMcalculated - EA ok
 obtained using QuickPIC open source.
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} %PMThe p
-    Plasma density in grey with the drive beam (blue) and the witness beam (red)
+    \caption{\label{Fig:PlasmaDenTWake} Plasma density in grey with the drive beam (blue) and the witness beam (red)
         superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
-        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.
-        %PM
-        Beams move to the left.}
+        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to the left.}
 \end{figure}
@@
 %PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. - EA ok
-The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void of plasma electrons. When
-the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second plasma stage (figure \ref{Fig:AWAKER2}), the peak
-electric field is expected to be about $500\funit{MV}{m}$. The plasma electron density are only depleted to around $65\%$ of
-nominal plasma density at the point where we inject the electron beam \cite{awake_collaboration:2016}.
-The plasma electron density depletion and the peak field is replicated using a single %PM proton
+The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void
+of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second
+plasma stage (figure \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The plasma
+electron density are only depleted to around $65\%$ of nominal plasma density at the point where we inject the electron
+beam \cite{awake_collaboration:2016}.  The plasma electron density depletion and the peak field is replicated using a
+single %PM proton 
 bunch with $1.46\nexp{10}$ protons (or $2.34\unit{nC}$), a %PM bunch
-length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$), and a transverse size $\sigma_{x,y,proton} = 200\unit{\mu m}$.
-The peak density is $0.83\cdot n_{0}$ results in a quasi-linear wake.
-%PM The beam energy is $400\unit{GeV}$.
-To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam [EA: K.
-V.
-Lotov, Phys.
-Plas.
-18, 024501 (2011), K.
-V.
-Lotov, Phys.
-Plas.
-22, 103110 (2015), A.
-Caldwell and K.
-Lotov, Phys.
-Plas.
-5, 103101 (2011)] we freeze the transverse evolution of the equivalent proton bunch by increasing the particles mass by six orders of magnitude.
+length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$.
+The peak density is $0.83\cdot n_{0}$ results in a quasi-linear wake. %PM The beam energy is $400\unit{GeV}$.
+To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam
+\cite{lotov:2011, lotov:2015, caldwell:2011} we freeze the transverse evolution of the equivalent proton bunch by
+increasing the particles mass by six orders of magnitude.
 
@@
 %PM not sure what the point of the above sentence is ... - EA ok
-In order to prevent large amplitude oscillations %PM
-of the witness beam particles, which may cause additional energy spread as well as emittance growth, we %PMstudy
+In order to prevent large amplitude oscillations of the witness beam particles, which may cause additional energy spread
+as well as emittance growth, we %PMstudy
 consider a witness beam matched to the plasma density.  
@@
 \begin{equation}
-%    \sigma_{x,y}^{2} = c\epsilon_{N}\sqrt{2\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}} \label{EQ:MatchedR}
-%    \sigma_{x,y} =\left(c^2\epsilon_{N}^2m_{e}\varepsilon_{0}n_{pe}e^{2}\gamma \right)^{1/4} \label{EQ:MatchedR} - % PM - EA: not correct
-	\sigma_{x,y}=\left(\frac{2c^{2}\varepsilon_{\mathrm{\mathrm{N}}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}  \label{EQ:MatchedR}  % EA 
+    \sigma_{x,y,eb}=\left(\frac{2c^{2}\epsilon_{\mathrm{N}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}
+    \label{EQ:Matched}
 \end{equation}
@@
 We %furthermore PM - EA ok
-assume an initial normalized emittance of $\epsilon_{N} = 2\unit{\mu m}$.
-This emittance is possible to produce with a standard RF-injector, while at the same time yielding a sufficient narrow beam.
-% EA: comment, perhaps put a ref here [***ref].
+assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$. This emittance is possible to produce
+with a standard RF-injector, while at the same time yielding a sufficient narrow beam. % EA: comment, perhaps put a ref here [***ref].
 
-Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009} %PM
+Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}
 as well as to its dephasing with respect to the wakefields when at low energy.
@@
 
-Eq.
-(\ref{EQ:MatchedR}) yields a transverse size of $\sigma_{x,y}$ of $5.25\unit{\mu m}$, narrow compared to the drive beam $\sigma_{x,y,proton} = 200\unit{\mu m}$.
-The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier %PM
+Eq. (\ref{EQ:Matched}) yields a transverse size of $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, narrow compared to the drive
+beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier
 beam loading studies \cite{berglyd_olsen:2016}. The charge %PM was
-is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the \emph{base case}.  
+is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive
+beam and witness beam parameter set as the \emph{base case}.  
 % EA: the key figure, figure 2, was not discussed in the text until very far down!  I therefore added (text could possibly be improved)
-Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base case parameters; the proton bunch in blue, the trailing electron beam in red and the plasma electron density in grey.
+Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base
+case parameters; the proton bunch in blue, the trailing electron beam in red and the plasma electron density in grey.
 
@@
 The relatively small size of the witness beam %PM compared to the proton beam put some restrictions on the transverse resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the narrower one (see figure \ref{Fig:PlasmaDenTWake}).
-puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron beam and large number of to resolve the large proton beam and the wakefields. %
+puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron
+beam and large number of to resolve the large proton beam and the wakefields.
 We use %PMd  - EA ok
-a transverse grid cell size of $1.17\unit{\mu m}$, and of
-$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
-was simulated with $16.8\nexp{6}$ non-weighted particles.  ***NN*** plasma particles were simulated per grid cell.
+a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal grid cells for the
+simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\nexp{6}$ non-weighted particles.
+%  ***NN*** plasma particles were simulated per grid cell.
 % EA: Veronica to fill in NN above
+% VO: QuickPIC doesn't specify particles per cell. Only in Osiris,
 
@@
     \caption{\label{Fig:BeamLoading} Top plot%PM plot shows the - EA ok
-: unloaded longitudinal electric field with no witness beam
-        (dashed blue line) and %PMthe 
-        loaded field (whole blue line) along the beam axis. The beam density along the axis
-        for both beams are shown in red. %PM The bottom plot compares the 
-        Bottom plot: plasma densities along the beam axis for a drive
-        beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line), and
-        both beams present (whole green line). $\xi = z - tc$ is the position in the simulation box, moving towards the
-        left.}
+    : unloaded longitudinal electric field with no witness beam (dashed blue line) and %PMthe
+        loaded field (whole blue line) along the beam axis. The beam density along the axis for both beams are shown in
+        red. %PM The bottom plot compares the 
+        Bottom plot: plasma densities along the beam axis for a drive beam with no witness beam (dashed green line),
+        witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
+        $\xi = z - tc$ is the position in the simulation box, moving towards the left.}
 \end{figure}
@@
     \caption{\label{Fig:BeamPS} %PMThe p
-    Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness
-        beam after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of
-        $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
+        Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam after $4\unit{m}$ of
+        plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of $87\unit{MeV/c}$ ($5.2\%$) for the
+        full beam.}
 \end{figure}
@@
     \caption{\label{Fig:BeamEmitt} Beam density in blue along the beam axis for an on-axis beam with respect to the
-        drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x} = 5.24\unit{\mu m}$ in the
-        x-plane. At four different positions $z$ in the plasma stage. The red lines show a moving window calculation of
-        transverse normalised emittance. The moving window calculation uses longitudinal slices of
+        drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x,eb} = 5.24\unit{\mu m}$ in
+        the x-plane. At four different positions $z$ in the plasma stage. The red lines show a moving window calculation
+        of transverse normalised emittance. The moving window calculation uses longitudinal slices of
         $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
@@
         \textbf{g} and \textbf{h} represent particles %PM
-        not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots
-        \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent particles %PM
-        in the ion column 
-        with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
+        not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$.
+        Plots \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent
+        particles in the ion column with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
 \end{figure*}
@@
 
-Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step, for the base case parameters. The $E_{z}$-field
-generated by the proton drive beam is seen as the blue line, shown with and without the
+Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step, for the base case
+parameters. The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the
 electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, %PMwe 
-the wakefields are in the quasi-linear regime
-\cite{rosenzweig:2010}. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis
-plasma density has a depletion of $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
-\cite{awake_collaboration:2016}.
+the wakefields are in the quasi-linear regime \cite{rosenzweig:2010}. The dashed green line in the lower part of figure
+\ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of $67\%$, close to what we see in full
+scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
 
@@
 The witness beam generates its own wakefield which %PM partially cancels out 
-loads the $E_{z}$ field generated by the drive beam.
-With an ideally shaped electron beam charge profile it is possible to optimally load the field in such a way that the
-accelerating field is constant along the beam \cite{katsouleas:1987, tzoufras:2009}.  Gaussian beams, as assumed in these studies, cannot
-completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
-tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}.  The bulk of
-the beam, however, sees a relatively flat field.  
+loads the $E_{z}$ field generated by the drive beam. With an ideally shaped electron beam charge profile it is possible
+to optimally load the field in such a way that the accelerating field is constant along the beam
+\cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot completely flatten the
+electric field in the tails of the charge distribution, and our base case beam therefore has a tail in energy both at
+the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}. The bulk of the beam, however, sees a
+relatively flat field.
 % EA: I rewrote this to the sentence after the comments
@@
 The %PM corresponding 
-electron beam density is $n_{eb} \approx 35\times n_{0}$.  This means that the witness beam's own wakefield
-is in the fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting
-in the formation of an ion column %PM 
-(Fig.~\ref{Fig:BeamLoading} bottom). This ion column, as is well known \cite{rosenzweig:1991}, provides a linear focusing
-force on the part the electron beam within the column, and therefore prevents emittance growth for this %PMregion
-part of the
-beam.  This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}.  The focusing field has a gradient of
-$20\unit{kT/m}$ near the beam axis, corresponding to the matched field gradient.
+electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield is in the
+fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting in the
+formation of an ion column %PM 
+(Fig.~\ref{Fig:BeamLoading} bottom). This ion column, as is well known \cite{rosenzweig:1991}, provides a linear
+focusing force on the part the electron beam within the column, and therefore prevents emittance growth for this %PMregion
+part of the beam.  This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
+gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the matched field gradient.
 
@@
  %PMDue to the ion column focusing, 
- Simulation results show that about $70-80\%$ of the electron beam longitudinal slices retain their initial emittance after the propagation in the plasma.
-Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma.
-Emittance growth mainly occurs in first few meters, and no significant emittance growth %PMwas
-is observed after this for propagation lengths up to
-$100\unit{m}$.
-The head of the beam does not benefit from the full ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still stabilizes after some time.
-For the 100 meter simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing,
-as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
+Simulation results show that about $70-80\%$ of the electron beam longitudinal slices retain their initial emittance
+after the propagation in the plasma. Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base
+case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma. Emittance growth mainly occurs in
+first few meters, and no significant emittance growth %PMwas
+is observed after this for propagation lengths up to $100\unit{m}$. The head of the beam does not benefit from the full
+ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still
+stabilizes after some time. For the 100 meter simulation, the drive beam energy was increased to $7\unit{TeV}$
+(LHC energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of
+$400\unit{GeV}$ after about $50\unit{m}$.
 
@@
 %PM
-So far we have considered a witness beam injected on the axis of the proton bunch. %
-We now briefly examine the case of injection of a witness beam with an offset with respect to the proton bunch axis. %
-Since the witness beam creates its own plasma bubble, the emittance of the part of the beam inside the
-bubble is not affected by small transverse offsets of the witness beam with respect to the proton beam axis.
-This is illustrated in figure \ref{Fig:BeamEmitt}, right, for an electron beam offset of $1\sigma_{xe}$.
-Emittance preservation for small offsets is an added benefit of this
-accelerating regime, and may ease transverse injection tolerances. 
-The head of the beam experiences a 
+So far we have considered a witness beam injected on the axis of the proton bunch. We now briefly examine the case of
+injection of a witness beam with an offset with respect to the proton bunch axis. Since the witness beam creates its own
+plasma bubble, the emittance of the part of the beam inside the bubble is not affected by small transverse offsets of
+the witness beam with respect to the proton beam axis. This is illustrated in figure \ref{Fig:BeamEmitt}, right, for an
+electron beam offset of $1\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
+accelerating regime, and may ease transverse injection tolerances.  The head of the beam experiences a 
 %larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f),
@@
 % EA: one way out, can compare emittance growth using fig 5 instead, as follows (alternatively, a new set of figures must be created)
-larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to \ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
-Figure \ref{Fig:BeamFilament} a-c show the phase space of the head of the electron beam after 0, 1.0 and 2.5 m, while figure \ref{Fig:BeamFilament} d-f show the phase space of the trailing part of the beam.
-The centroid oscillations of the head and the trailing part are shown in figure \ref{Fig:BeamFilament} g.
-This effect of a transverse offset is likely to be greater for larger offsets as the beam oscillates
-around the axis of the drive beam wakefield.% EA: would be good to include a statement of how large the offsets can be before when the electron beam starts to break up / not preserve emittance.
+larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to
+\ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
+Figure \ref{Fig:BeamFilament} a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
+$2.5\unit{m}$, while figure \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
+centroid oscillations of the head and the trailing part are shown in figure \ref{Fig:BeamFilament}g. This effect of a
+transverse offset is likely to be greater for larger offsets as the beam oscillates around the axis of the drive beam
+wakefield.
+% EA: would be good to include a statement of how large the offsets can be before when the electron beam starts to break
+%     up / not preserve emittance.
 
 The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
-equation \ref{EQ:MatchedR} %PM where the plasma density is given by the ion density - EA ok
-,i .e., evolves to stay matched. The on-axis density of the electron
-beam, as a result, increases as its gamma factor increases and its transverse size decreases. The effect can be seen in
-figure \ref{Fig:BeamFilament} h. This has the potential to cause overloading of the field. However, for the base case
-no significant overloading %PMwas
+equation \ref{EQ:Matched} %PM where the plasma density is given by the ion density - EA ok
+,i .e., evolves to stay matched. The on-axis density of the electron beam, as a result, increases as its gamma factor
+increases and its transverse size decreases. The effect can be seen in figure \ref{Fig:BeamFilament}h. This has the
+potential to cause overloading of the field. However, for the base case no significant overloading %PMwas
 is observed.
@@
     \caption{\label{Fig:BeamQ} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial beam charge (blue %PM
-        symbols, lines), and relative energy spread of the accepted charge (red %PM
-        symbols, lines), after
-        $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These are shown for four
-        different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam
-        loading section correspond to the square marked lines at $100\unit{pC}$.}
+        function of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red
+        symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These
+        are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
+        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
 \end{figure}
@@
     \caption{\label{Fig:BeamQAbs} Total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a function of
-        initial beam charge (blue %PM
-        symbols, lines), and final %PMmomentum
-        energy (red %PM
-        symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
-        $\epsilon_{N,0}=2\unit{\mu m}$.}
+        initial beam charge (blue symbols, lines), and final %PMmomentum
+        energy (red symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
+        $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
 \end{figure}
@@
     \caption{\label{Fig:BeamQEmit} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial emittance (blue %PM
-        symbols, lines), and relative energy spread of the accepted charge (red %PM
-        symbols, lines), after $4\unit{m}$
-        of plasma.}
+        function of initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red
+        symbols, lines), after $4\unit{m}$ of plasma.}
 \end{figure}
@@
 transverse profile as well as %PMthe 
-relative phasing of the proton and the electron beams.  We present a limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2.
+relative phasing of the proton and the electron beams. We present a limited parameter study aimed at guiding beam
+parameter choices for AWAKE Run 2.
 %~ We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
-For electron beam to be externally injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the energy gain, minimize the energy spread, maximize the charge to be accelerated, and minimize the emittance growth \cite{adli:2016}.
-In addition, the bunch length should be such that it is possible to
-generate and transport the bunch using a compact electron injector \cite{adli:2016}. We
-investigate the interdependence of these parameters in simulation by varying the electron bunch length, its charge,
-and initial emittance. The results were quantified in terms of how much of the initial charge retained its initial
-emittance within a $5\%$ margin. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$,
-and let the beams propagate through $4\unit{m}$ of plasma.
+For electron beam to be externally injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the
+energy gain, minimize the energy spread, maximize the charge to be accelerated, and minimize the emittance growth
+\cite{adli:2016}. In addition, the bunch length should be such that it is possible to generate and transport the bunch
+using a compact electron injector \cite{adli:2016}. We investigate the interdependence of these parameters in simulation
+by varying the electron bunch length, its charge, and initial emittance. The results were quantified in terms of how
+much of the initial charge retained its initial emittance within a $5\%$ margin. For these parameter scans we used a
+transverse grid cell size of $2.34\unit{\mu m}$, and let the beams propagate through $4\unit{m}$ of plasma.
 %~ We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will
@@
 charge and energy spread on bunch length and %PMbunch
-incoming charge.  An initial beam
-emittance of $2\unit{\mu m}$ was used.  %
-%PM
-Therefore, we define the fractional charge as that whose emittance remains smaller than $2.1\unit{\mu m}$. %PM We ran the scan with beam charges from 
+incoming charge.  An initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge as
+that whose emittance remains smaller than $2.1\unit{\mu m}$. %PM We ran the scan with beam charges from 
 The beam charge range $10\unit{pC}$ to $300\unit{pC}$ and %with length
 the $\sigma_{z}$ range from $40\unit{\mu m}$ to $100\unit{\mu m}$.  As can be seen from figure \ref{Fig:BeamQ} %, red curves
-(red curves), both the
-$40\unit{\mu m}$ and the $60\unit{\mu m}$ beam %PMhas
-have a well defined minimum energy spread with a beam charge
-$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the electric field,
-while higher beam charges tend to overload it. It is also clear that longer beams with respect to the accelerating phase
-of the field, $\approx\lambda_{pe}/4$, %PMwill
-does not optimally load the wake, thus producing a larger spread in energy.  The blue curves show the fraction of %PMthe sliced emittance where the
-charge whose initial emittance is preserved (the slice%Md
-  emittance for the base case is shown in figure \ref{Fig:BeamEmitt}).
-As the witness beam charge increases the fraction of slices with preserved emittance increases, as expected from an earlier onset of the bubble formation and also increase in the bubble size \cite{lu:2006-1, lu:2006}.
+(red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam %PMhas
+have a well defined minimum energy spread with a beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$,
+respectively. Lower beam charges tend to under-load the electric field, while higher beam charges tend to overload it.
+It is also clear that longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, %PMwill
+does not optimally load the wake, thus producing a larger spread in energy. The blue curves show the fraction of
+%PMthe sliced emittance where the
+charge whose initial emittance is preserved (the slice emittance for the base case is shown in figure
+\ref{Fig:BeamEmitt}). As the witness beam charge increases the fraction of slices with preserved emittance increases, as
+expected from an earlier onset of the bubble formation and also increase in the bubble size \cite{lu:2006-1, lu:2006}.
 %PM SHOULD WE ADD SOMETHING LIKE:
-We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.
-%???
+We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance
+preserved, at the expense of an increase of relative energy spread by a factor of two. %???
 
 Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on bunch length and bunch charge %PM, in red curves
-(red curves). The blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as function of bunch length and bunch charge.
+(red curves). The blue curves show the amount of charge in the longitudinal slices where the emittance has been
+preserved, as function of bunch length and bunch charge.
 
@@
 emittance. In these simulations %PMthe focusing of the beam to the plasma remains matched for each emittance value.
-we adjusted the witness beam radius to maintain the matching condition at each emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
-to emittance growth for high initial emittance beams; the transverse beam size may increase beyond the size of the bubble, and the beam
-density may be reduced so much that the plasma electrons are no longer fully evacuated from the bubble. Emittance
-values higher than a few micrometers lead to a significant increase in both emittance and energy spread.
+we adjusted the witness beam radius to maintain the matching condition at each emittance. The smaller the initial
+emittance is, the better the emittance is preserved. There are two effects that lead to emittance growth for high
+initial emittance beams; the transverse beam size may increase beyond the size of the bubble, and the beam density may
+be reduced so much that the plasma electrons are no longer fully evacuated from the bubble. Emittance values higher than
+a few micrometers lead to a significant increase in both emittance and energy spread.
 
 % EA: slight rewrite to argue what we want with this section
-The optimal working point will depend on the application and must be studied for each case and is, as illustrated in this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters like the plasma density.
+The optimal working point will depend on the application and must be studied for each case and is, as illustrated in
+this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters
+like the plasma density.
 
@@
 
-We have devised a method to accelerate an electron witness bunch to high energy with a low relative energy spread while maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
-This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by self-modulation of a long proton bunch.
-This method is in principle applicable to all experiments operating in the quasi-linear regime.
-Low relative energy spread and emittance preservation are achieved by choosing the electron beam parameters to load the wakefields and evacuate the remaining plasma electrons from the accelerating structure.
+We have devised a method to accelerate an electron witness bunch to high energy with a low relative energy spread while
+maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
+This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by
+self-modulation of a long proton bunch. This method is in principle applicable to all experiments operating in the
+quasi-linear regime. Low relative energy spread and emittance preservation are achieved by choosing the electron beam
+parameters to load the wakefields and evacuate the remaining plasma electrons from the accelerating structure.
 
-Parameter studies indicate that up to a few $100\unit{pC}$, up to 70\% of the incoming bunch charge, is accelerated, for bunch of lengths of $40-60\unit{\mu m}$.
-Such electron bunches may be generated by an injector based on a standard RF photo-emission gun [EA: S.
-Doebert, private communication].
+Parameter studies indicate that up to a few $100\unit{pC}$, up to $70\%$ of the incoming bunch charge, is accelerated,
+for bunch of lengths of $40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based on a standard
+RF photo-emission gun \cite{doebert:corr}.
 
-In order to use manageable computer time for simulations, this study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single, short proton bunch producing similar wakefields.
+In order to use manageable computer time for simulations, this study assumes a simplified case with respect to a
+self-modulated proton beam, where the wake is driven by a single, short proton bunch producing similar wakefields.
 However, the wakefields driven by a train of bunches evolve with the ramp of a real plasma and when entering the plasma.
-Therefore, to be fully applicable to an experiment such as AWAKE, the study will have to be redone with more realistic parameters.
-However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated bunch with low relative energy spread and emittance remains applicable.
+Therefore, to be fully applicable to an experiment such as AWAKE, the study will have to be redone with more realistic
+parameters. However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated
+bunch with low relative energy spread and emittance remains applicable.
 
@@
 % EA: I think owned also by IST.  I will check with Weiming and Warren
-The simulations for this study have been performed using the open source version of QuickPIC released in early 2017 and owned
-by UCLA.
+The simulations for this study have been performed using the open source version of QuickPIC released in early 2017
+and owned by UCLA.
 
@@
 % EA: instead I suggest something like (also promised Jorge)
-We gratefully acknowledge helpful discussions with Jorge Vieria from IST Lisbon.
+We gratefully acknowledge helpful discussions with Jorge Vieria from IST, Lisbon.
 
 % ******************************************************************************************************************** %
-\bibliography{Bibliography}
+\bibliography{Bibliography,Additional}
 \end{document}

### 2017-10-05 Tex/Paper.tex
More cleanup, reflow, and figure text updates

@@
 
-% Text
-%~ \newcommand{\eq}[1]{Eq. \ref{#1}}
-%~ \newcommand{\fig}[1]{Fig. \ref{#1}}
-%~ \newcommand{\tbl}[1]{Table \ref{#1}}
-
 % Math
@@
 %Patric general comments
-%energy labels not consistent between figs 7, 9 and 8
-%labels for the fractional charge is too complicated on Figs 7,8,9.
-it needs to be explained in the caption and/or in the text.
-"On the left axis we plot the fraction of that charge whose emittance remains ....
-"
-%Add scale for grey color on Fig. 2
-%Fig. 3 has a "v=c" and an arrow that are only on that figure ...
-%It is not clear to me what the conclusions/outcome of the last section are ....
+%  energy labels not consistent between figs 7, 9 and 8
+%  labels for the fractional charge is too complicated on Figs 7,8,9. it needs to be explained in the caption and/or in
+%  the text. "On the left axis we plot the fraction of that charge whose emittance remains .... "
+%  Add scale for grey color on Fig. 2
+%  Fig. 3 has a "v=c" and an arrow that are only on that figure ...
+%  It is not clear to me what the conclusions/outcome of the last section are ....
 
@@
 and exploiting two well known effects, beam loading of the wake field and full blow out of plasma electrons by the
-accelerated beam, the electron beam can %PM be accelerated - EA ok
-gain large amounts of energy with a narrow final energy spread (\%-level) and without significant emittance growth.
+accelerated beam, the electron beam can gain large amounts of energy with a narrow final energy spread (\%-level) and
+without significant emittance growth.
 \end{abstract}
@@
 Beam driven plasma wakefield accelerators \cite{chen:1985} have the potential to offer compact linear accelerators with
-high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive
-beam travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
-witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. %to a minimum. %PM - EA ok
-The concept has been demonstrated experimentally in the past using electron drive beams accelerating electron witness
-beams \cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
+high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive beam
+travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
+witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. The concept has
+been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
+\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
 
 A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread
-and emittance growth small. %growth to a minimum. PM - EA ok
-In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the plasma density
-$n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam. The beam
-%will %PM - EA ok
-also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has
-been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the
-transverse oscillations of the plasma electrons, %forming PM - EA ok
-gathering in a sheet around an evacuated area filled with only ions. The ions, assumed stationary, form an uniform
-density ion channel creating a focusing force that varies linearly with radius. This %produces a  PM - EA ok
-focusing force %that PM - EA ok
-preserves emittance \cite{rosenzweig:1991}.
-% EA: I put Rosenzweig original blow out paper as citation here instead of, \cite{lu:2006-1, lu:2006}.
+and emittance growth small. In the well described linear regime, valid when the beam density $n_{b}$ is much smaller
+than the plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam.
+The beam also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the
+beam has been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
+the transverse oscillations of the plasma electrons, gathering in a sheet around an evacuated area filled with only
+ions. The ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly
+with radius. This focusing force preserves emittance \cite{rosenzweig:1991}.
 
@@
 quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
-%~ Patric's version is implemented:
-The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low
-relative energy spread%$\Delta E/E$, 
-, and completely blow out the electrons left in the bubble after the beam to reach conditions that preserves emittance.
-The results have importance for the preparation of AWAKE Run 2 and possibly other applications in the quasi-linear regime.
+The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low relative
+energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
+preserves emittance. The results have importance for the preparation of AWAKE Run 2 and possibly other applications in
+the quasi-linear regime.
 
@@
 
-The energy carried by electron drive bunches used in previous plasma wakefield experiments have been no more than
-$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}. For
-high-energy physics application a higher total beam energy is often desired, for instance, the energy of a high-charge
-electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be produced by
-the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers a large number of plasma stages is
-required to reach %PM - EA ok
-an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma accelerators without reducing the
-effective gradient and spoiling the beam quality is challenging \cite{steinke:2016,lindstrom:2016}.
-
-Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS
-beam \cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
-magnitude longer than the plasma wavelengths needed for such applications, and the beam %will PM - EA ok
-does not drive a strong wake \cite{gschwendtner:2016}.  By letting the proton beam undergo self-modulation before
-injecting the witness beam into accelerating structure, %most PM - EA ok
-stronger wakefields are %formed PM - EA ok
-excited. The self-modulation of the beam is produced by the transverse fields generated by the beam acting upon itself,
-causing regions of the beam to rapidly defocus \cite{kumar:2010}. The modulation frequency is close to that of the
-plasma, and produces a train of short proton bunches along the beam axis with a surrounding halo of defocused particles.
-This train of bunches resonantly %produces - EA ok
-drives wakefields to large %r PM - EA ok 
-amplitudes.
-
-AWAKE at CERN is a proof of concept proton beam driven plasma wakefield accelerator experiment
-\cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton
-beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of
-$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
--- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
-$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, %PM. - EA ok
-$\lambda_{pe}=2\pi c/\omega_{pe}$ and $\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron
-angular frequency.
-
-The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of the second
-phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
-relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate
-acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
-absolute energy spread.
-
 \begin{figure}[hbt]
@@
 \end{figure}
+
+The energy carried by electron drive bunches used in previous plasma wakefield experiments have been no more than
+$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}.
+% VKBO: Not sure "no more than" is true.
+For high-energy physics application a higher total beam energy is often desired, for instance, the energy of a
+high-charge electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
+produced by the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers a large number of
+plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma
+accelerators without reducing the effective gradient and spoiling the beam quality is challenging
+\cite{steinke:2016,lindstrom:2016}.
+
+Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS
+beam \cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
+magnitude longer than the plasma wavelengths needed for such applications, and the beam does not drive a strong wake
+\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into the % added "the"
+accelerating structure, stronger wakefields are excited. The self-modulation of the beam is produced by the transverse
+fields generated by the beam acting upon itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The
+modulation frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis
+with a surrounding halo of defocused particles. This train of bunches resonantly drives wakefields to large amplitudes.
+
+AWAKE at CERN is a proof of concept proton beam driven plasma wakefield accelerator experiment
+\cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton
+beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of
+$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
+-- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
+$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe}=2\pi c/\omega_{pe}$ and
+$\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency.
+
+The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of the second
+phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
+relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate
+acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
+absolute energy spread.
 
@@
 proton bunches show that the proton bunch evolve as it propagates through a uniform plasma \cite{lotov:2011}, but that
-small variations in the plasma profile the modulation, and thus the wake fields, may be stabilized over long distances
+small variations in the plasma profile the modulation, and thus the wake fields, may be stabilised over long distances
 \cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake, independent of the
-dynamics of the self-modulation, %PMwe define here - EA ok
-here we use a single, non-evolving proton bunch as driver. The proton bunch parameters are chosen so that key features of
-the wake -- the plasma electron density in the wake and the longitudinal electric field -- are the same as %PM - EA ok
-in the wake of a self-modulated proton beam with AWAKE baseline parameters \cite{gschwendtner:2016}. Both the proton
-beam and the witness have Gaussian %PM - EA ok
-longitudinal charge distribution and bi-Gaussian transverse charge distributions.
+dynamics of the self-modulation, here we use a single, non-evolving proton bunch as driver. The proton bunch parameters
+are chosen so that key features of the wake -- the plasma electron density in the wake and the longitudinal electric
+field -- are the same as in the wake of a self-modulated proton beam with AWAKE baseline parameters
+\cite{gschwendtner:2016}. Both the proton beam and the witness have Gaussian longitudinal charge distribution and
+bi-Gaussian transverse charge distributions.
 
 We have previously studied the beam loading in a proton beam wake using the full PIC code Osiris \cite{fonseca:2002}
-%using PM - EA ok
 and with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily
@@
 \cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation.  All simulation results in
-this paper are %PMcalculated - EA ok
-obtained using QuickPIC open source.
+this paper are obtained using QuickPIC open source.
 
@@
 %~ see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}).
+%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble.
 
-%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble. - EA ok
 The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void
@@
 beam \cite{awake_collaboration:2016}.  The plasma electron density depletion and the peak field is replicated using a
-single %PM proton 
-bunch with $1.46\nexp{10}$ protons (or $2.34\unit{nC}$), a %PM bunch
-length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$.
-The peak density is $0.83\cdot n_{0}$ results in a quasi-linear wake. %PM The beam energy is $400\unit{GeV}$.
-To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated proton beam
-\cite{lotov:2011, lotov:2015, caldwell:2011} we freeze the transverse evolution of the equivalent proton bunch by
-increasing the particles mass by six orders of magnitude.
+single bunch with $1.46\nexp{10}$ protons (or $2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$),
+and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The peak density is $0.83\cdot n_{0}$ results in a
+quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation of the
+self-modulated proton beam \cite{lotov:2011, lotov:2015, caldwell:2011} we freeze the transverse evolution of the
+equivalent proton bunch by increasing the particles mass by six orders of magnitude.
 
@@
 
-%The small size of the accelerating structure produced by the self-modulated beam also
-%puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
-%to prevent large energy spread.  
-%PM not sure what the point of the above sentence is ... - EA ok
 In order to prevent large amplitude oscillations of the witness beam particles, which may cause additional energy spread
-as well as emittance growth, we %PMstudy
-consider a witness beam matched to the plasma density.  
-%The beam matching relation is given by
-%\begin{equation}
-%    \beta = \frac{\sigma_{x,y}^{2}\gamma}{\epsilon_{N}}
-%          = \frac{c}{\omega_{pe}}\sqrt{2\gamma}, \label{EQ:MatchedB}
-%    % = c\sqrt{\frac{m_{e}\varepsilon_{0}}{n_{pe}e^{2}}2\gamma}
-%\end{equation}
-%where $\beta$ is the Twiss parameter. It then follows that the transverse profile of the beam must satisfy
-%PM Not sure what the point of the above lines is ....
-The matched beam transverse size is:
+as well as emittance growth, we consider a witness beam matched to the plasma density. The matched beam transverse size
+is:
 \begin{equation}
@@
 
-We %furthermore PM - EA ok
-assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$. This emittance is possible to produce
-with a standard RF-injector, while at the same time yielding a sufficient narrow beam. % EA: comment, perhaps put a ref here [***ref].
+We assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$. This emittance is possible to
+produce with a standard RF-injector, while at the same time yielding a sufficient narrow beam.
+% EA: comment, perhaps put a ref here [***ref].
 
 Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}
-as well as to its dephasing with respect to the wakefields when at low energy.
-%PM A low gamma witness beam can easily drift out of phase with the drive beam wakefield. The drift of the beams is proportional to $\gamma^{-2}$,  
-To eliminate %initial 
-de-phasing of the witness beam, % PM
-the initial beam energy %PMwas
-is set such
-that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.  A lower initial energy is likely to be
-sufficient for AWAKE Run 2 injection. 
-% EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement, no details in \cite{berglyd_olsen:2015}.
+as well as to its de-phasing with respect to the wakefields when at low energy. To eliminate de-phasing of the witness
+beam, the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.
+A lower initial energy is likely to be sufficient for AWAKE Run 2 injection.
+% EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement,
+%     no details in \cite{berglyd_olsen:2015}.
 
 Eq. (\ref{EQ:Matched}) yields a transverse size of $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, narrow compared to the drive
-beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier
-beam loading studies \cite{berglyd_olsen:2016}. The charge %PM was
-is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section. We refer to the defined drive
-beam and witness beam parameter set as the \emph{base case}.  
-% EA: the key figure, figure 2, was not discussed in the text until very far down!  I therefore added (text could possibly be improved)
+beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier beam
+loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam loading, as
+discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
+\emph{base case}.
+% EA: the key figure, figure 2, was not discussed in the text until very far down!
+%     I therefore added (text could possibly be improved)
 Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base
@@
 
-The relatively small size of the witness beam %PM compared to the proton beam put some restrictions on the transverse resolution of the witness beam as we need a simulation box wide enough to contain the larger beam while resolving the narrower one (see figure \ref{Fig:PlasmaDenTWake}).
-puts constraints on the transverse cell size and number in the simulations: small size to resolve the small electron
-beam and large number of to resolve the large proton beam and the wakefields.
-We use %PMd  - EA ok
-a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal grid cells for the
-simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\nexp{6}$ non-weighted particles.
+The relatively small size of the witness beam puts constraints on the transverse cell size and number in the
+simulations: small size to resolve the small electron beam and large number of to resolve the large proton beam and the
+wakefields. % This sounds really bad? Should be improved.
+We use a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal grid cells for
+the simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\nexp{6}$ non-weighted
+particles.
 %  ***NN*** plasma particles were simulated per grid cell.
 % EA: Veronica to fill in NN above
-% VO: QuickPIC doesn't specify particles per cell. Only in Osiris,
+% VO: QuickPIC doesn't specify particles per cell. Only in Osiris, This number has no fixed value, just a range from
+%     zero to whatever is the density at the peak of the Gaussian distribution.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} Top plot%PM plot shows the - EA ok
-    : unloaded longitudinal electric field with no witness beam (dashed blue line) and %PMthe
-        loaded field (whole blue line) along the beam axis. The beam density along the axis for both beams are shown in
-        red. %PM The bottom plot compares the 
-        Bottom plot: plasma densities along the beam axis for a drive beam with no witness beam (dashed green line),
-        witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
+    \caption{\label{Fig:BeamLoading} \textbf{Top plot:} unloaded longitudinal electric field with no witness beam
+        (dashed blue line) and loaded field (whole blue line) along the beam axis. The beam density along the axis for
+        both beams are shown in red.
+        \textbf{Bottom plot:} plasma densities along the beam axis for a drive beam with no witness beam (dashed green
+        line), witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
         $\xi = z - tc$ is the position in the simulation box, moving towards the left.}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} %PMThe p
-        Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam after $4\unit{m}$ of
-        plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of $87\unit{MeV/c}$ ($5.2\%$) for the
-        full beam.}
+    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
+        after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread
+        of $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
 \end{figure}
@@
         \textbf{h} their RMS spread. Plots \textbf{a}, \textbf{b} and \textbf{c}, as well as the blue lines in plots
-        \textbf{g} and \textbf{h} represent particles %PM
-        not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$.
-        Plots \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent
-        particles in the ion column with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
+        \textbf{g} and \textbf{h} represent particles not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with
+        position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots \textbf{d}, \textbf{e} and \textbf{f}, and the red
+        lines in plots \textbf{g} and \textbf{h} represent particles in the ion column with position
+        $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
 \end{figure*}
@@
 parameters. The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the
-electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, %PMwe 
-the wakefields are in the quasi-linear regime \cite{rosenzweig:2010}. The dashed green line in the lower part of figure
-\ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion of $67\%$, close to what we see in full
-scale reference simulations for AWAKE Run 2 \cite{awake_collaboration:2016}.
+electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear regime
+\cite{rosenzweig:2010}. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis
+plasma density has a depletion of $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
+\cite{awake_collaboration:2016}.
 
@@
 
-The witness beam generates its own wakefield which %PM partially cancels out 
-loads the $E_{z}$ field generated by the drive beam. With an ideally shaped electron beam charge profile it is possible
-to optimally load the field in such a way that the accelerating field is constant along the beam
-\cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot completely flatten the
-electric field in the tails of the charge distribution, and our base case beam therefore has a tail in energy both at
-the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}. The bulk of the beam, however, sees a
-relatively flat field.
+The witness beam generates its own wakefield which loads the $E_{z}$ field generated by the drive beam. With an ideally
+shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field
+is constant along the beam \cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot
+completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
+tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}. The bulk of the
+beam, however, sees a relatively flat field.
 % EA: I rewrote this to the sentence after the comments
@@
 
-The %PM corresponding 
-electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield is in the
+The electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield is in the
 fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting in the
-formation of an ion column %PM 
-(Fig.~\ref{Fig:BeamLoading} bottom). This ion column, as is well known \cite{rosenzweig:1991}, provides a linear
-focusing force on the part the electron beam within the column, and therefore prevents emittance growth for this %PMregion
-part of the beam.  This effect is shown for our base case in figure \ref{Fig:PlasmaDenTWake}. The focusing field has a
-gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the matched field gradient.
+formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well known
+\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore
+prevents emittance growth for this part of the beam.  This effect is shown for our base case in figure
+\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the
+matched field gradient.
 
@@
 case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma. Emittance growth mainly occurs in
-first few meters, and no significant emittance growth %PMwas
-is observed after this for propagation lengths up to $100\unit{m}$. The head of the beam does not benefit from the full
-ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still
-stabilizes after some time. For the 100 meter simulation, the drive beam energy was increased to $7\unit{TeV}$
-(LHC energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of
-$400\unit{GeV}$ after about $50\unit{m}$.
+first few meters, and no significant emittance growth is observed after this for propagation lengths up to
+$100\unit{m}$. The head of the beam does not benefit from the full ion column focusing, but since the proton beam
+creates a quasi-linear wake, the emittance of the head of the beam still stabilizes after some time. For the
+$100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
+de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
 
@@
 %~ witness beam wakefield follows the beam itself.
-%PM
 So far we have considered a witness beam injected on the axis of the proton bunch. We now briefly examine the case of
@@
 % EA: one way out, can compare emittance growth using fig 5 instead, as follows (alternatively, a new set of figures must be created)
+% VKBO: How does the phase space plots *NOT* show emittance? 
 larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to
 \ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
-Figure \ref{Fig:BeamFilament} a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
+Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
 $2.5\unit{m}$, while figure \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
@@
 The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
-equation \ref{EQ:Matched} %PM where the plasma density is given by the ion density - EA ok
-,i .e., evolves to stay matched. The on-axis density of the electron beam, as a result, increases as its gamma factor
-increases and its transverse size decreases. The effect can be seen in figure \ref{Fig:BeamFilament}h. This has the
-potential to cause overloading of the field. However, for the base case no significant overloading %PMwas
-is observed.
+equation \ref{EQ:Matched},i .e., evolves to stay matched. The on-axis density of the electron beam, as a result,
+increases as its gamma factor increases and its transverse size decreases. The effect can be seen in figure
+\ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for the base case no
+significant overloading is observed.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \caption{\label{Fig:BeamQ} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red
-        symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{N,0}=2\unit{\mu m}$. These
-        are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
-        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
+    \caption{\label{Fig:BeamQ} Ratio of total beam charge $\widetilde{Q}$ wit h an emittance growth
+        $\Delta\epsilon \leq 5\%$ as a function of initial beam charge (blue symbols, lines), and relative energy spread
+        of the accepted charge (red symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
+        $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$
+        to $100\unit{\mu m}$. The detailed studies presented in beam loading section correspond to the square marked
+        lines at $100\unit{pC}$.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQAbs} Total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a function of
-        initial beam charge (blue symbols, lines), and final %PMmomentum
-        energy (red symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
-        $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+    \caption{\label{Fig:BeamQAbs} Total beam charge $\widetilde{Q}$ with an emittance growth $\Delta\epsilon \leq 5\%${}
+        as a function of initial beam charge (blue symbols, lines), and final energy (red symbols, lines), after
+        $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of total beam charge with an emittance growth $\Delta\epsilon \leq 5\%$ as a
-        function of initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red
-        symbols, lines), after $4\unit{m}$ of plasma.}
+    \caption{\label{Fig:BeamQEmit} Ratio of total beam charge $\widetilde{Q}$ with an emittance growth
+        $\Delta\epsilon \leq 5\%$ as a function of initial emittance (blue symbols, lines), and relative energy spread
+        of the accepted charge (red symbols, lines), after $4\unit{m}$ of plasma.}
 \end{figure}
@@
 
-The beam loading and blow out properties of the electron beam depend on a large number of parameters, including %PMthe
-longitudinal profile, %PMthe 
-transverse profile as well as %PMthe 
-relative phasing of the proton and the electron beams. We present a limited parameter study aimed at guiding beam
-parameter choices for AWAKE Run 2.
-%~ We here study parameter optimization relevant for AWAKE Run 2, in order to understand the ideal injection parameters.
-For electron beam to be externally injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the
-energy gain, minimize the energy spread, maximize the charge to be accelerated, and minimize the emittance growth
-\cite{adli:2016}. In addition, the bunch length should be such that it is possible to generate and transport the bunch
-using a compact electron injector \cite{adli:2016}. We investigate the interdependence of these parameters in simulation
-by varying the electron bunch length, its charge, and initial emittance. The results were quantified in terms of how
-much of the initial charge retained its initial emittance within a $5\%$ margin. For these parameter scans we used a
-transverse grid cell size of $2.34\unit{\mu m}$, and let the beams propagate through $4\unit{m}$ of plasma.
-%~ We quantify the resulting emittance growth, energy spread and and energy gain. The desired injection parameters will
-%~ depend on the application.
+The beam loading and blow out properties of the electron beam depend on a large number of parameters, including
+longitudinal profile, transverse profile as well as relative phasing of the proton and the electron beams. We present a
+limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For electron beam to be externally
+injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the energy gain, minimize the energy
+spread, maximise the charge to be accelerated, and minimise the emittance growth \cite{adli:2016}. In addition, the
+bunch length should be such that it is possible to generate and transport the bunch using a compact electron injector
+\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron bunch
+length, its charge, and initial emittance. The results were quantified in terms of how much of the initial charge
+retained its initial emittance within a $5\%$ margin. For these parameter scans we used a transverse grid cell size of
+$2.34\unit{\mu m}$, and let the beams propagate through $4\unit{m}$ of plasma.
 
-Figure \ref{Fig:BeamQ}  show the dependence of %PM emittance
-charge and energy spread on bunch length and %PMbunch
-incoming charge.  An initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge as
-that whose emittance remains smaller than $2.1\unit{\mu m}$. %PM We ran the scan with beam charges from 
-The beam charge range $10\unit{pC}$ to $300\unit{pC}$ and %with length
-the $\sigma_{z}$ range from $40\unit{\mu m}$ to $100\unit{\mu m}$.  As can be seen from figure \ref{Fig:BeamQ} %, red curves
-(red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beam %PMhas
-have a well defined minimum energy spread with a beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$,
-respectively. Lower beam charges tend to under-load the electric field, while higher beam charges tend to overload it.
-It is also clear that longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, %PMwill
-does not optimally load the wake, thus producing a larger spread in energy. The blue curves show the fraction of
-%PMthe sliced emittance where the
-charge whose initial emittance is preserved (the slice emittance for the base case is shown in figure
-\ref{Fig:BeamEmitt}). As the witness beam charge increases the fraction of slices with preserved emittance increases, as
-expected from an earlier onset of the bubble formation and also increase in the bubble size \cite{lu:2006-1, lu:2006}.
-%PM SHOULD WE ADD SOMETHING LIKE:
-We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance
-preserved, at the expense of an increase of relative energy spread by a factor of two. %???
+Figure \ref{Fig:BeamQ}  show the dependence of charge and energy spread on bunch length and incoming charge. An initial
+beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge as that whose emittance remains
+smaller than $2.1\unit{\mu m}$. The beam charge range $10\unit{pC}$ to $300\unit{pC}$ and the $\sigma_{z}$ ranges from
+$40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red curves), both the
+$40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with a beam charge
+$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the electric
+field, while higher beam charges tend to overload it. It is also clear that longer beams with respect to the
+accelerating phase of the field, $\approx\lambda_{pe}/4$, does not optimally load the wake, thus producing a larger
+spread in energy. The blue curves show the fraction of charge whose initial emittance is preserved (the slice emittance
+for the base case is shown in figure \ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction of slices
+with preserved emittance increases, as expected from an earlier onset of the bubble formation, and also increases in the
+bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a significantly larger
+charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor
+of two.
 
-Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on bunch length and bunch charge %PM, in red curves
-(red curves). The blue curves show the amount of charge in the longitudinal slices where the emittance has been
-preserved, as function of bunch length and bunch charge.
+Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on bunch length and bunch charge (red curves). The
+blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as function of
+bunch length and bunch charge.
 
 Figure \ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
-emittance. In these simulations %PMthe focusing of the beam to the plasma remains matched for each emittance value.
-we adjusted the witness beam radius to maintain the matching condition at each emittance. The smaller the initial
-emittance is, the better the emittance is preserved. There are two effects that lead to emittance growth for high
-initial emittance beams; the transverse beam size may increase beyond the size of the bubble, and the beam density may
-be reduced so much that the plasma electrons are no longer fully evacuated from the bubble. Emittance values higher than
-a few micrometers lead to a significant increase in both emittance and energy spread.
+emittance. In these simulations we adjusted the witness beam radius to maintain the matching condition at each
+emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
+to emittance growth for high initial emittance beams; the transverse beam size may increase beyond the size of the
+bubble, and the beam density may be reduced so much that the plasma electrons are no longer fully evacuated from the
+bubble. Emittance values higher than a few micrometers lead to a significant increase in both emittance and energy
+spread.
 
@@
 
-%We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a quasi-linear proton driven wake.
-When optimally loaded an electron witness beam has sufficient charge to create a strong blow out forming a %n ion
-%bubble trailing the witness beam.  The focusing forces from the ions ensures emittance preservation for large parts of the %PM 
-%witness beam. %PM, also when the electron beam has some offset with respect to the proton driver.
-%Simulations show that the emittance of a large fraction of the electron beam is preserved even when it enters the plasma with and offset with respect to the proton bunch axis. %
+%~ We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a
+%~ quasi-linear proton driven wake. When optimally loaded an electron witness beam has sufficient charge to create a
+%~ strong blow out forming a %n ion 
+%~ bubble trailing the witness beam.  The focusing forces from the ions ensures emittance preservation for large parts of
+%~ the %PM 
+%~ witness beam. %PM, also when the electron beam has some offset with respect to the proton driver.
+%~ Simulations show that the emittance of a large fraction of the electron beam is preserved even when it enters the plasma
+%~ with and offset with respect to the proton bunch axis.
 
-%Using AWAKE parameters these result indicates that emittance preservation for an electron beam injected on-axis into a plasma stage, and properly optimized, may be
-%feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might be accelerated, for bunches of length
-%$40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based on a standard RF gun [S. Doebert, private communication].
+%~ Using AWAKE parameters these result indicates that emittance preservation for an electron beam injected on-axis into a
+%~ plasma stage, and properly optimized, may be feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might
+%~ be accelerated, for bunches of length $40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based
+%~ on a standard RF gun [S. Doebert, private communication].
 
-%This study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single, short proton bunch, and investigates an ideal, uniform plasma profile.
-To fully investigate optimal AWAKE injection, further study should be performed including simulations of realistic plasma profiles combined with a self-modulated proton beam.
+%~ This study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single,
+%~ short proton bunch, and investigates an ideal, uniform plasma profile.  To fully investigate optimal AWAKE injection,
+%~ further study should be performed including simulations of realistic plasma profiles combined with a self-modulated
+%~ proton beam.  
 % EA: we could also say "is underway" and cite Lotov et co?
-%PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest - EA patric's verson of conclusions are OK with me
+% PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest -
+%     EA patric's verson of conclusions are OK with me
 
@@
 
-% EA: not needed (checked with Jorge)
-%The authors would also like to thank the OSIRIS Consortium for providing access to the OSIRIS framework. OSIRIS was used
-%extensively for simulations leading to the work presented in this paper.
-% EA: instead I suggest something like (also promised Jorge)
-We gratefully acknowledge helpful discussions with Jorge Vieria from IST, Lisbon.
+We gratefully acknowledge helpful discussions with Jorge Vieira from IST, Lisbon.
 

### 2017-10-06 Tex/Paper.tex
Edits w/Erik

@@
 high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive beam
-travelling through a plasma, a strong wakefield is excited, that can be loaded by a trailing witness beam. When the
+travelling through a plasma, a strong wakefield is excited that can be loaded by a trailing witness beam. When the
 witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. The concept has
@@
 the transverse oscillations of the plasma electrons, gathering in a sheet around an evacuated area filled with only
-ions. The ions, assumed stationary, form an uniform density ion channel creating a focusing force that varies linearly
+ions. The ions, assumed stationary, form a uniform density ion channel creating a focusing force that varies linearly
 with radius. This focusing force preserves emittance \cite{rosenzweig:1991}.
@@
 In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can
-be ensured, when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}. By
+be ensured when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}. By
 quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
 The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low relative
-energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
+energy spread, and completely blow out the electrons left in the bubble after the beam, to reach conditions that
 preserves emittance. The results have importance for the preparation of AWAKE Run 2 and possibly other applications in
@@
 
-The energy carried by electron drive bunches used in previous plasma wakefield experiments have been no more than
-$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007,caldwell:2009}.
-% VKBO: Not sure "no more than" is true.
+The energy carried by electron drive beams used in previous plasma wakefield experiments have been on the order of
+$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007, caldwell:2009}.
 For high-energy physics application a higher total beam energy is often desired, for instance, the energy of a
-high-charge electron bunch accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
+high-charge electron beam accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
 produced by the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers a large number of
-plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated bunch. However, staging plasma
+plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated beam. However, staging plasma
 accelerators without reducing the effective gradient and spoiling the beam quality is challenging
-\cite{steinke:2016,lindstrom:2016}.
+\cite{steinke:2016, lindstrom:2016}.
 
@@
 beam \cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
-magnitude longer than the plasma wavelengths needed for such applications, and the beam does not drive a strong wake
-\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into the % added "the"
-accelerating structure, stronger wakefields are excited. The self-modulation of the beam is produced by the transverse
-fields generated by the beam acting upon itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The
+magnitude longer than the plasma wavelengths needed for such applications, and it does not drive a strong wake
+\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into the
+accelerating structure, stronger wakefields are excited. The self-modulation is produced by the transverse fields
+generated by the beam acting upon itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The
 modulation frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis
@@
 -- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
-$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe}=2\pi c/\omega_{pe}$ and
-$\omega_{pe}=\left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency.
+$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe} = 2\pi c/\omega_{pe}$, and
+$\omega_{pe} = \left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency.
 
@@
 section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
-electron beam present. The electron witness beam is then injected into the modulated proton beam before section two,
+electron beam present. The electron witness beam is then injected into the modulated proton beam before section two
 where it undergoes acceleration. The self-modulated proton beam does not produce a fully non-linear wakefield, and
@@
 The focus in this study is the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
-proton bunches show that the proton bunch evolve as it propagates through a uniform plasma \cite{lotov:2011}, but that
+proton beams show that the proton beam evolves as it propagates through a uniform plasma \cite{lotov:2011}, but that
 small variations in the plasma profile the modulation, and thus the wake fields, may be stabilised over long distances
 \cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake, independent of the
-dynamics of the self-modulation, here we use a single, non-evolving proton bunch as driver. The proton bunch parameters
+dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver. The proton beam parameters
 are chosen so that key features of the wake -- the plasma electron density in the wake and the longitudinal electric
 field -- are the same as in the wake of a self-modulated proton beam with AWAKE baseline parameters
-\cite{gschwendtner:2016}. Both the proton beam and the witness have Gaussian longitudinal charge distribution and
+\cite{gschwendtner:2016}. Both the proton beam and the witness beam have Gaussian longitudinal charge distribution and
 bi-Gaussian transverse charge distributions.
@@
 and with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily
-looked at beam loading, energy gain and energy spread, as well as different approaches to create a stable drive beam
-structure based on previous self-modulation studies. In order to study the witness beam emittance evolution we adopt the
+looked at beam loading, energy gain and energy spread, as well as different approaches to creating a stable drive beam
+structure based on previous self-modulation studies. In order to study the witness beam emittance evolution we use the
 recently released open source version of QuickPIC \cite{huang:2006, an:2013}. QuickPIC is a fully relativistic 3D
@@
 \cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation. All simulation results in
-this paper are obtained using QuickPIC open source.
+this paper were obtained using QuickPIC open source.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} Plasma density in grey with the drive beam (blue) and the witness beam (red)
-        superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
+    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulations of the initial time step, for the single proton drive beam
+        and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the witness beam
+        (red) superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
         $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to the left.}
@@
 of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second
-plasma stage (figure \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The plasma
-electron density are only depleted to around $65\%$ of nominal plasma density at the point where we inject the electron
-beam \cite{awake_collaboration:2016}.  The plasma electron density depletion and the peak field is replicated using a
-single bunch with $1.46\nexp{10}$ protons (or $2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$),
-and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The peak density is $0.83\cdot n_{0}$ results in a
-quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation of the
-self-modulated proton beam \cite{lotov:2011, lotov:2015, caldwell:2011} we freeze the transverse evolution of the
+plasma section (figure \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
+plasma electron density is only depleted to around $65\%$ of nominal plasma density at the point where we inject the
+electron beam \cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field is replicated
+using a single bunch with $1.46\nexp{10}$ protons ($2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$
+($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The peak density at $0.83\cdot n_{0}$ results
+in a quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation of the
+self-modulated proton beam \cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
 equivalent proton bunch by increasing the particles mass by six orders of magnitude.
@@
 Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}
-as well as to its de-phasing with respect to the wakefields when at low energy. To eliminate de-phasing of the witness
-beam, the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.
-A lower initial energy is likely to be sufficient for AWAKE Run 2 injection.
+as well as to its de-phasing with respect to the wakefields at low energy. To eliminate de-phasing of the witness beam,
+the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$. A
+lower initial energy is likely to be sufficient for AWAKE Run 2 injection.
 % EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement,
@@
 
-Eq. (\ref{EQ:Matched}) yields a transverse size of $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, narrow compared to the drive
-beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z}=60\unit{\mu m}$, based on earlier beam
-loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam loading, as
-discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
-\emph{base case}.
-% EA: the key figure, figure 2, was not discussed in the text until very far down!
-%     I therefore added (text could possibly be improved)
-Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time step, for the base
-case parameters; the proton bunch in blue, the trailing electron beam in red and the plasma electron density in grey.
+Eq. (\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared to the
+drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based on
+earlier beam loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
+loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
+\emph{base case}. Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time
+step, for the base case parameters; the proton beam in blue, the trailing electron beam in red and the plasma electron
+density in grey.
 
@@
 
-The relatively small size of the witness beam puts constraints on the transverse cell size and number in the
-simulations: small size to resolve the small electron beam and large number of to resolve the large proton beam and the
-wakefields. % This sounds really bad? Should be improved.
-We use a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal grid cells for
-the simulations presented in section \ref{S:BL}. The witness beam was simulated with $16.8\nexp{6}$ non-weighted
-particles.
-%  ***NN*** plasma particles were simulated per grid cell.
-% EA: Veronica to fill in NN above
-% VO: QuickPIC doesn't specify particles per cell. Only in Osiris, This number has no fixed value, just a range from
-%     zero to whatever is the density at the peak of the Gaussian distribution.
+The relatively small size of the witness beam puts constraints on the transverse grid cell size and number in the
+simulations. We need a small size to resolve the narrow electron beam, and a large number of grid cells to resolve the
+much wider proton beam and its wakefields. We use a transverse grid cell size of $1.17\unit{\mu m}$, and of
+$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
+was simulated with $16.8\nexp{6}$ non-weighted particles, the drive beam with $2,1\nexp{6}$ non-weighted particles, and
+the plasma electrons with $1024 \times 1024$ weighted particles per transverse slice.
 
@@
 
-The witness beam generates its own wakefield which loads the $E_{z}$ field generated by the drive beam. With an ideally
+The witness beam generates its own wakefield which loads the $E_{z}$-field generated by the drive beam. With an ideally
 shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field
@@
 
-The electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield is in the
-fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting in the
-formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well known
+The initial electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield
+is in the fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting
+in the formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well known
 \cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore
@@
  %PMDue to the ion column focusing,
-Simulation results show that about $70-80\%$ of the electron beam longitudinal slices retain their initial emittance
-after the propagation in the plasma. Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base
-case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma. Emittance growth mainly occurs in
-first few meters, and no significant emittance growth is observed after this for propagation lengths up to
-$100\unit{m}$. The head of the beam does not benefit from the full ion column focusing, but since the proton beam
-creates a quasi-linear wake, the emittance of the head of the beam still stabilizes after some time. For the
-$100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
-de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
+
+Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through
+$0$, $4$, $40$ and $100\unit{m}$ of plasma. We define emittance of a slice as preserved if the growth is less than
+$5\%$, and $\widetilde{Q}$ as the sum charge of the slices for which the emittance is preserved. Simulation results show
+that $\widetilde{Q}/Q = 73\%$ of the electron beam longitudinal slices retain their initial emittance after the
+propagation in the plasma. Emittance growth mainly occurs in the first few meters, and no significant emittance growth
+is observed after this for propagation lengths up to $100\unit{m}$. The head of the beam does not benefit from the full
+ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still
+stabilizes after some time. For the $100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC
+energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$
+after about $50\unit{m}$.
 
@@
 %~ witness beam wakefield follows the beam itself.
-So far we have considered a witness beam injected on the axis of the proton bunch. We now briefly examine the case of
-injection of a witness beam with an offset with respect to the proton bunch axis. Since the witness beam creates its own
+So far we have considered a witness beam injected on the axis of the proton beam. We now briefly examine the case of
+injection of a witness beam with an offset with respect to the proton beam axis. Since the witness beam creates its own
 plasma bubble, the emittance of the part of the beam inside the bubble is not affected by small transverse offsets of
@@
 larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to
-\ref{Fig:BeamEmitt}, right), however, also for the head the emittance growth ends after the first few meters.
-Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
+\ref{Fig:BeamEmitt}, right). However, also for the head of the beam the emittance growth ends after the first few
+metres. Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
 $2.5\unit{m}$, while figure \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
@@
 The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
-equation \ref{EQ:Matched},i .e., evolves to stay matched. The on-axis density of the electron beam, as a result,
-increases as its gamma factor increases and its transverse size decreases. The effect can be seen in figure
+equation \ref{EQ:Matched}, i.e., evolves to stay matched. The on-axis density of the electron beam, as a result,
+increases as its gamma factor increases and its transverse size decreases. This effect can be seen in figure
 \ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for the base case no
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \caption{\label{Fig:BeamQ} Ratio of total beam charge $\widetilde{Q}$ wit h an emittance growth
-        $\Delta\epsilon \leq 5\%$ as a function of initial beam charge (blue symbols, lines), and relative energy spread
-        of the accepted charge (red symbols, lines), after $4\unit{m}$ of plasma and with an initial emittance
+    \caption{\label{Fig:BeamQ} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of initial
+        beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols, lines), after
+        $4\unit{m}$ of plasma and with an initial emittance
         $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQAbs} Total beam charge $\widetilde{Q}$ with an emittance growth $\Delta\epsilon \leq 5\%${}
+    \caption{\label{Fig:BeamQAbs} Beam charge with emittance preserved, $\widetilde{Q}$,
         as a function of initial beam charge (blue symbols, lines), and final energy (red symbols, lines), after
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of total beam charge $\widetilde{Q}$ with an emittance growth
-        $\Delta\epsilon \leq 5\%$ as a function of initial emittance (blue symbols, lines), and relative energy spread
+    \caption{\label{Fig:BeamQEmit} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$,
+        as a function of initial emittance (blue symbols, lines), and relative energy spread
         of the accepted charge (red symbols, lines), after $4\unit{m}$ of plasma.}
@@
 longitudinal profile, transverse profile as well as relative phasing of the proton and the electron beams. We present a
-limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For electron beam to be externally
-injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximize the energy gain, minimize the energy
+limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For an electron beam to be externally
+injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
 spread, maximise the charge to be accelerated, and minimise the emittance growth \cite{adli:2016}. In addition, the
-bunch length should be such that it is possible to generate and transport the bunch using a compact electron injector
-\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron bunch
-length, its charge, and initial emittance. The results were quantified in terms of how much of the initial charge
-retained its initial emittance within a $5\%$ margin. For these parameter scans we used a transverse grid cell size of
-$2.34\unit{\mu m}$, and let the beams propagate through $4\unit{m}$ of plasma.
+beam length should be such that it is possible to generate and transport the beam using a compact electron injector
+\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron beam
+length, its charge, and initial emittance. The results are quantified in terms of how much of the beam retains its
+initial emittance. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$, and let the
+beams propagate through $4\unit{m}$ of plasma.
 
-Figure \ref{Fig:BeamQ}  show the dependence of charge and energy spread on bunch length and incoming charge. An initial
-beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge as that whose emittance remains
-smaller than $2.1\unit{\mu m}$. The beam charge range $10\unit{pC}$ to $300\unit{pC}$ and the $\sigma_{z}$ ranges from
-$40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red curves), both the
-$40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with a beam charge
-$\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the electric
-field, while higher beam charges tend to overload it. It is also clear that longer beams with respect to the
+Figure \ref{Fig:BeamQ} shows the dependence of charge and energy spread on beam length and incoming charge. An initial
+beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the charge
+whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range $10\unit{pC}$ to $300\unit{pC}$, and the
+$\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red curves),
+both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an initial beam
+charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the
+electric field, while higher beam charges tend to overload it. It is also clear that longer beams with respect to the
 accelerating phase of the field, $\approx\lambda_{pe}/4$, does not optimally load the wake, thus producing a larger
@@
 for the base case is shown in figure \ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction of slices
-with preserved emittance increases, as expected from an earlier onset of the bubble formation, and also increases in the
-bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a significantly larger
-charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor
-of two.
+with preserved emittance increases -- as expected from an earlier onset of the bubble formation -- and also increases in
+the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a significantly
+larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a
+factor of two.
 
-Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on bunch length and bunch charge (red curves). The
-blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as function of
-bunch length and bunch charge.
+Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The
+blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function
+of beam length and beam charge.
 
@@
 emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
-to emittance growth for high initial emittance beams; the transverse beam size may increase beyond the size of the
+to emittance growth for high initial emittance beams: the transverse beam size may increase beyond the size of the
 bubble, and the beam density may be reduced so much that the plasma electrons are no longer fully evacuated from the
-bubble. Emittance values higher than a few micrometers lead to a significant increase in both emittance and energy
+bubble. Emittance values higher than a few micrometres lead to a significant increase in both emittance and energy
 spread.
@@
 The optimal working point will depend on the application and must be studied for each case and is, as illustrated in
-this section, a trade off between bunch length, bunch charge and emittance preservation, as well as other parameters
+this section, a trade off between beam length, beam charge and emittance preservation, as well as other parameters
 like the plasma density.
@@
 
-We have devised a method to accelerate an electron witness bunch to high energy with a low relative energy spread while
+We have devised a method to accelerate an electron witness beam to high energy with a low relative energy spread, while
 maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
 This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by
-self-modulation of a long proton bunch. This method is in principle applicable to all experiments operating in the
+self-modulation of a long proton beam. This method is in principle applicable to all experiments operating in the
 quasi-linear regime. Low relative energy spread and emittance preservation are achieved by choosing the electron beam
@@
 
-Parameter studies indicate that up to a few $100\unit{pC}$, up to $70\%$ of the incoming bunch charge, is accelerated,
-for bunch of lengths of $40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based on a standard
+Parameter studies indicate that for up to a few $100\unit{pC}$, about $70\%$ of the incoming beam charge is accelerated
+for beam of lengths of $40-60\unit{\mu m}$. Such electron beams may be generated by an injector based on a standard
 RF photo-emission gun \cite{doebert:corr}.
@@
 parameters. However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated
-bunch with low relative energy spread and emittance remains applicable.
+beam with low relative energy spread and emittance remains applicable.
 
@@
 We gratefully acknowledge helpful discussions with Jorge Vieira from IST, Lisbon.
+\vfill
 

### 2017-10-06 Tex/Paper.tex
Fixed spelling and typos

@@
 We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear
-plasma wakefield driven by a short proton beam. The structure of the studied wakefields are similar to those of a long,
+plasma wakefields driven by a short proton beam. The structure of the studied wakefields are similar to those of a long,
 modulated proton beam, such as the AWAKE proton driver. We show that by properly choosing the electron beam parameters
-and exploiting two well known effects, beam loading of the wake field and full blow out of plasma electrons by the
+and exploiting two well known effects, beam loading of the wakefield and full blow out of plasma electrons by the
 accelerated beam, the electron beam can gain large amounts of energy with a narrow final energy spread (\%-level) and
@@
 The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low relative
-energy spread, and completely blow out the electrons left in the bubble after the beam, to reach conditions that
-preserves emittance. The results have importance for the preparation of AWAKE Run 2 and possibly other applications in
+energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
+preserves emittance. The results have importance for the preparation of AWAKE Run 2, and possibly other applications in
 the quasi-linear regime.
@@
 $100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007, caldwell:2009}.
-For high-energy physics application a higher total beam energy is often desired, for instance, the energy of a
+For high-energy physics application a higher total beam energy is often desired. For instance, the energy of a
 high-charge electron beam accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
-produced by the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers a large number of
+produced by the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers, a large number of
 plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated beam. However, staging plasma
@@
 
-The focus in this study is the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
+The focus in this study is on the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
 proton beams show that the proton beam evolves as it propagates through a uniform plasma \cite{lotov:2011}, but that
-small variations in the plasma profile the modulation, and thus the wake fields, may be stabilised over long distances
+small variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long distances
 \cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake, independent of the
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulations of the initial time step, for the single proton drive beam
+    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulations of the initial time step for the single proton drive beam
         and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the witness beam
@@
 $2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
-was simulated with $16.8\nexp{6}$ non-weighted particles, the drive beam with $2,1\nexp{6}$ non-weighted particles, and
+was simulated with $16.8\nexp{6}$ non-weighted particles, the drive beam with $2.1\nexp{6}$ non-weighted particles, and
 the plasma electrons with $1024 \times 1024$ weighted particles per transverse slice.
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} \textbf{Top plot:} unloaded longitudinal electric field with no witness beam
+    \caption{\label{Fig:BeamLoading} \textbf{Top plot:} Unloaded longitudinal electric field with no witness beam
         (dashed blue line) and loaded field (whole blue line) along the beam axis. The beam density along the axis for
         both beams are shown in red.
-        \textbf{Bottom plot:} plasma densities along the beam axis for a drive beam with no witness beam (dashed green
+        \textbf{Bottom plot:} Plasma densities along the beam axis for a drive beam with no witness beam (dashed green
         line), witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
@@
         drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x,eb} = 5.24\unit{\mu m}$ in
-        the x-plane. At four different positions $z$ in the plasma stage. The red lines show a moving window calculation
-        of transverse normalised emittance. The moving window calculation uses longitudinal slices of
+        the x-plane -- at four different positions $z$ in the plasma stage. The red lines show a moving window
+        calculation of transverse normalised emittance. The moving window calculation uses longitudinal slices of
         $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
@@
 
-Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step, for the base case
+Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step for the base case
 parameters. The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the
@@
 
-The initial electron beam density is $n_{eb} \approx 35\times n_{0}$. This means that the witness beam's own wakefield
-is in the fully non-linear regime, where the space charge force is sufficient to blow-out all plasma electrons resulting
-in the formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well known
-\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore
-prevents emittance growth for this part of the beam. This effect is shown for our base case in figure
+The initial electron beam density is $n_{eb} \approx 35\cdot n_{0}$. This means that the witness beam's own wakefield
+is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons,
+resulting in the formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well
+known \cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
+therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in figure
 \ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the
@@
 that $\widetilde{Q}/Q = 73\%$ of the electron beam longitudinal slices retain their initial emittance after the
-propagation in the plasma. Emittance growth mainly occurs in the first few meters, and no significant emittance growth
+propagation in the plasma. Emittance growth mainly occurs in the first few metres, and no significant emittance growth
 is observed after this for propagation lengths up to $100\unit{m}$. The head of the beam does not benefit from the full
 ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still
-stabilizes after some time. For the $100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC
+stabilises after some time. For the $100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC
 energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$
@@
 electron beam offset of $1\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
-accelerating regime, and may ease transverse injection tolerances. The head of the beam experiences a 
-%larger initial emittance growth (see figure \ref{Fig:BeamFilament}a-f),
-%PM
-%THERE IS NO EMITTANCE SHOWN OR NOTHING TO COMPARE TO ... WHAT TO DO????
-% EA: one way out, can compare emittance growth using fig 5 instead, as follows (alternatively, a new set of figures must be created)
-% VKBO: How does the phase space plots *NOT* show emittance? 
-larger initial emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to
-\ref{Fig:BeamEmitt}, right). However, also for the head of the beam the emittance growth ends after the first few
-metres. Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
+accelerating regime, and may ease transverse injection tolerances. The head of the beam experiences a larger initial
+emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to \ref{Fig:BeamEmitt}, right).
+However, also for the head of the beam the emittance growth ends after the first few metres.
+Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
 $2.5\unit{m}$, while figure \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
@@
 transverse offset is likely to be greater for larger offsets as the beam oscillates around the axis of the drive beam
-wakefield.
-% EA: would be good to include a statement of how large the offsets can be before when the electron beam starts to break
-%     up / not preserve emittance.
+wakefield. [Will add results on how much offset can be tolerated as soon as the simulations are done.]
 
-The transverse beam size within the bubble, where normalized emittance is preserved, follows the evolution given by
-equation \ref{EQ:Matched}, i.e., evolves to stay matched. The on-axis density of the electron beam, as a result,
+The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
+equation \ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
 increases as its gamma factor increases and its transverse size decreases. This effect can be seen in figure
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \caption{\label{Fig:BeamQ} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of initial
-        beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols, lines), after
-        $4\unit{m}$ of plasma and with an initial emittance
-        $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$
-        to $100\unit{\mu m}$. The detailed studies presented in beam loading section correspond to the square marked
-        lines at $100\unit{pC}$.}
+    \caption{\label{Fig:BeamQ} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of
+        initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
+        lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
+        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
+        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQAbs} Beam charge with emittance preserved, $\widetilde{Q}$,
-        as a function of initial beam charge (blue symbols, lines), and final energy (red symbols, lines), after
-        $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+    \caption{\label{Fig:BeamQAbs} Beam charge with emittance preserved, $\widetilde{Q}$, as a function of initial beam
+        charge (blue symbols, lines), and final energy (red symbols, lines), after $4\unit{m}$ of plasma and with an
+        initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$,
-        as a function of initial emittance (blue symbols, lines), and relative energy spread
-        of the accepted charge (red symbols, lines), after $4\unit{m}$ of plasma.}
+    \caption{\label{Fig:BeamQEmit} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of
+        initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red symbols, lines),
+        after $4\unit{m}$ of plasma.}
 \end{figure}
@@
 The beam loading and blow out properties of the electron beam depend on a large number of parameters, including
-longitudinal profile, transverse profile as well as relative phasing of the proton and the electron beams. We present a
+longitudinal profile, transverse profile, as well as relative phasing of the proton and the electron beams. We present a
 limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For an electron beam to be externally
@@
 beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the charge
-whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range $10\unit{pC}$ to $300\unit{pC}$, and the
-$\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red curves),
-both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an initial beam
-charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to under-load the
-electric field, while higher beam charges tend to overload it. It is also clear that longer beams with respect to the
-accelerating phase of the field, $\approx\lambda_{pe}/4$, does not optimally load the wake, thus producing a larger
-spread in energy. The blue curves show the fraction of charge whose initial emittance is preserved (the slice emittance
-for the base case is shown in figure \ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction of slices
-with preserved emittance increases -- as expected from an earlier onset of the bubble formation -- and also increases in
-the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a significantly
-larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a
-factor of two.
+whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range from $10\unit{pC}$ to $300\unit{pC}$, and
+the $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red
+curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an
+initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to
+underload the electric field, while higher beam charges tend to overload it. It is also clear that longer beams with
+respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the wake, thus producing
+a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is preserved (the slice
+emittance for the base case is shown in figure \ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction
+of slices with preserved emittance increases -- as expected from an earlier onset of the bubble formation -- and also
+increases in the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a
+significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy
+spread by a factor of two.
 
-Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The
-blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function
-of beam length and beam charge.
+Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
+curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
+beam length and beam charge.
 
@@
 
-We have devised a method to accelerate an electron witness beam to high energy with a low relative energy spread, while
+We have devised a method to accelerate an electron witness beam to high energy with a low relative energy spread while
 maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
@@
 
-These numerical simulations have been made possible through access to the Abel computing cluster in Oslo, Norway. Abel
-is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
+These numerical simulations have been made possible through access to the \emph{Abel} computing cluster in Oslo, Norway.
+Abel is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
 University of Oslo, the University of Troms{\o} and the Norwegian University of Science and Technology. Project code:
-nn9303k. Some of the simulations were also run on the student-maintained computing cluster ``Smaug'' at the University
-of Oslo, Department of Physics.
+nn9303k. Some of the simulations were also run on the student-maintained computing cluster \emph{Smaug} at the
+University of Oslo, Department of Physics.
 

### 2017-10-07 Tex/Paper.tex
Implemented some changes from Carl, and a suggestion from Weiming

@@
 beam has been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
-the transverse oscillations of the plasma electrons, gathering in a sheet around an evacuated area filled with only
+the transverse oscillations of the plasma electrons, gathering in a sheath around an evacuated area filled with only
 ions. The ions, assumed stationary, form a uniform density ion channel creating a focusing force that varies linearly
@@
 energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
-preserves emittance. The results have importance for the preparation of AWAKE Run 2, and possibly other applications in
-the quasi-linear regime.
+preserves emittance. The results have importance for the preparation of AWAKE Run 2 \cite{adli:2016}, and possibly other
+applications in the quasi-linear regime.
 
@@
         accelerating structure, and undergoes acceleration in the second plasma section
-        \cite{berglyd_olsen:2015, adli:2016}.}
+        \cite{berglyd_olsen:2015, adli:2016}}.
 \end{figure}
@@
 high-charge electron beam accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
-produced by the international linear collider, is $1.6\unit{kJ}$. Using electron beams as drivers, a large number of
+produced by the International Linear Collider, is $1.6\unit{kJ}$. Using electron beams as drivers, a large number of
 plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated beam. However, staging plasma
@@
 phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
-relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shut down 2, and aims to demonstrate
+relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
 acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
@@
 
-The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in figure \ref{Fig:AWAKER2}. The first
+The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in Fig. \ref{Fig:AWAKER2}. The first
 section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
@@
 
-We have previously studied the beam loading in a proton beam wake using the full PIC code Osiris \cite{fonseca:2002}
-and with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily
-looked at beam loading, energy gain and energy spread, as well as different approaches to creating a stable drive beam
-structure based on previous self-modulation studies. In order to study the witness beam emittance evolution we use the
-recently released open source version of QuickPIC \cite{huang:2006, an:2013}. QuickPIC is a fully relativistic 3D
-quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC codes do
+We have previously studied the beam loading in a proton beam wake using the full particle-in-cell (PIC) code OSIRIS
+\cite{fonseca:2002} with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016}
+primarily looked at beam loading, energy gain and energy spread, as well as different approaches to creating a stable
+drive beam structure based on previous self-modulation studies. In order to study the witness beam emittance evolution
+we use the recently released open-source version of QuickPIC \cite{huang:2006, an:2013}. QuickPIC is a fully
+relativistic 3D quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC codes do
 \cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation. All simulation results in
-this paper were obtained using QuickPIC open source.
+this paper were obtained using QuickPIC open-source \cite{quickpic:web}.
 
@@
 of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second
-plasma section (figure \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
+plasma section (Fig. \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
 plasma electron density is only depleted to around $65\%$ of nominal plasma density at the point where we inject the
@@
 We assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$. This emittance is possible to
-produce with a standard RF-injector, while at the same time yielding a sufficient narrow beam.
+produce with a standard RF-injector, while at the same time yielding a sufficiently narrow beam.
 % EA: comment, perhaps put a ref here [***ref].
@@
 
-Eq. (\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared to the
-drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based on
-earlier beam loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
+Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared
+to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based
+on earlier beam loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
 loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
-\emph{base case}. Figure \ref{Fig:PlasmaDenTWake} shows the two beams from QuickPIC simulations of the initial time
-step, for the base case parameters; the proton beam in blue, the trailing electron beam in red and the plasma electron
+\emph{base case}. Figure \ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
+step, for the base case parameters; the proton beam in blue, the trailing electron beam in red, and the plasma electron
 density in grey.
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} Phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam
-        after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread
+    \caption{\label{Fig:BeamPS} Longitudinal phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long
+        witness beam after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread
         of $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
@@
 electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear regime
-\cite{rosenzweig:2010}. The dashed green line in the lower part of figure \ref{Fig:BeamLoading} shows that the on-axis
-plasma density has a depletion of $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
+\cite{rosenzweig:2010}. The dashed green line in the lower part of Fig. \ref{Fig:BeamLoading} shows that the on-axis
+plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
 \cite{awake_collaboration:2016}.
@@
 completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
-tail in energy both at the front and the back of the beam, as illustrated in figure \ref{Fig:BeamPS}. The bulk of the
+tail in energy both at the front and the back of the beam, as illustrated in Fig. \ref{Fig:BeamPS}. The bulk of the
 beam, however, sees a relatively flat field.
@@
 is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons,
-resulting in the formation of an ion column (see figure \ref{Fig:BeamLoading}, bottom). This ion column, as is well
+resulting in the formation of an ion column (see Fig. \ref{Fig:BeamLoading}, bottom). This ion column, as is well
 known \cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
-therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in figure
+therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in Fig.
 \ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the
@@
 plasma bubble, the emittance of the part of the beam inside the bubble is not affected by small transverse offsets of
-the witness beam with respect to the proton beam axis. This is illustrated in figure \ref{Fig:BeamEmitt}, right, for an
+the witness beam with respect to the proton beam axis. This is illustrated in Fig. \ref{Fig:BeamEmitt}, right, for an
 electron beam offset of $1\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
 accelerating regime, and may ease transverse injection tolerances. The head of the beam experiences a larger initial
-emittance growth than for the on-axis case (compare figure \ref{Fig:BeamEmitt}, left, to \ref{Fig:BeamEmitt}, right).
+emittance growth than for the on-axis case (compare Fig. \ref{Fig:BeamEmitt}, left, to Fig. \ref{Fig:BeamEmitt}, right).
 However, also for the head of the beam the emittance growth ends after the first few metres.
 Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
-$2.5\unit{m}$, while figure \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
-centroid oscillations of the head and the trailing part are shown in figure \ref{Fig:BeamFilament}g. This effect of a
+$2.5\unit{m}$, while Fig. \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
+centroid oscillations of the head and the trailing part are shown in Fig. \ref{Fig:BeamFilament}g. This effect of a
 transverse offset is likely to be greater for larger offsets as the beam oscillates around the axis of the drive beam
@@
 The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
-equation \ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
-increases as its gamma factor increases and its transverse size decreases. This effect can be seen in figure
+Eq. \ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
+increases as its gamma factor increases and its transverse size decreases. This effect can be seen in Fig.
 \ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for the base case no
 significant overloading is observed.
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \caption{\label{Fig:BeamQ} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of
-        initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
-        lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
-        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
-        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
-\end{figure}
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQAbs} Beam charge with emittance preserved, $\widetilde{Q}$, as a function of initial beam
-        charge (blue symbols, lines), and final energy (red symbols, lines), after $4\unit{m}$ of plasma and with an
-        initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
-\end{figure}
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function of
-        initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red symbols, lines),
-        after $4\unit{m}$ of plasma.}
-\end{figure}
 
@@
 limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For an electron beam to be externally
-injected in AWAKE Run 2 (see figure \ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
+injected in AWAKE Run 2 (see Fig. \ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
 spread, maximise the charge to be accelerated, and minimise the emittance growth \cite{adli:2016}. In addition, the
@@
 
-Figure \ref{Fig:BeamQ} shows the dependence of charge and energy spread on beam length and incoming charge. An initial
-beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the charge
-whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range from $10\unit{pC}$ to $300\unit{pC}$, and
-the $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from figure \ref{Fig:BeamQ} (red
-curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an
-initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam charges tend to
-underload the electric field, while higher beam charges tend to overload it. It is also clear that longer beams with
-respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the wake, thus producing
-a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is preserved (the slice
-emittance for the base case is shown in figure \ref{Fig:BeamEmitt}). As the witness beam charge increases, the fraction
-of slices with preserved emittance increases -- as expected from an earlier onset of the bubble formation -- and also
-increases in the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with $100\unit{pC}$ leads to a
-significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy
-spread by a factor of two.
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
+    \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
+        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
+        lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
+        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
+        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
+\end{figure}
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
+    \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
+        initial beam charge (blue symbols, lines), and final energy (red symbols, lines), after $4\unit{m}$ of plasma
+        and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+\end{figure}
+
+Figure \ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An
+initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the
+charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range from $10\unit{pC}$ to
+$300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from Fig.
+\ref{Fig:BeamQ} (red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum
+energy spread with an initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam
+charges tend to underload the electric field, while higher beam charges tend to overload it. It is also clear that
+longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the
+wake, thus producing a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is
+preserved (the slice emittance for the base case is shown in Fig. \ref{Fig:BeamEmitt}). As the witness beam charge
+increases, the fraction of slices with preserved emittance increases -- as expected from an earlier onset of the bubble
+formation -- and also increases in the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with
+$100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an
+increase of relative energy spread by a factor of two.
 
@@
 beam length and beam charge.
+
+\begin{figure}[hbt]
+    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
+    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a
+        function of initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red
+        symbols, lines), after $4\unit{m}$ of plasma.}
+\end{figure}
 

### 2017-10-08 Tex/Paper.tex
Implemented changes from Kyrre

@@
 
-Beam driven plasma wakefield accelerators \cite{chen:1985} have the potential to offer compact linear accelerators with
+Beam driven plasma wakefield accelerators~\cite{chen:1985} have the potential to offer compact linear accelerators with
 high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive beam
@@
 witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. The concept has
-been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams
-\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
+been demonstrated experimentally in the past using electron drive beams accelerating electron witness
+beams~\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
 
@@
 The beam also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the
-beam has been accelerated \cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
+beam has been accelerated~\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
 the transverse oscillations of the plasma electrons, gathering in a sheath around an evacuated area filled with only
 ions. The ions, assumed stationary, form a uniform density ion channel creating a focusing force that varies linearly
-with radius. This focusing force preserves emittance \cite{rosenzweig:1991}.
+with radius. This focusing force preserves emittance~\cite{rosenzweig:1991}.
 
 In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can
-be ensured when accelerated by a proton drive beam producing quasi-linear wakefields \cite{rosenzweig:2010}. By
+be ensured when accelerated by a proton drive beam producing quasi-linear wakefields~\cite{rosenzweig:2010}. By
 quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
@@
 energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
-preserves emittance. The results have importance for the preparation of AWAKE Run 2 \cite{adli:2016}, and possibly other
+preserves emittance. The results have importance for the preparation of AWAKE Run 2~\cite{adli:2016}, and possibly other
 applications in the quasi-linear regime.
@@
 %plasma wavelength $\lambda_{pe} = 2\pi c/\omega_{pe}$ and the plasma frequency $\omega_{pe} = (n_{0} e^{2} / m_{e}
-%\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch \cite{chen:1985}. A tailing witness
+%\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch~\cite{chen:1985}. A tailing witness
 %beam loading the peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches
 %when they are properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two
-%electron drive beams has been demonstrated at Brookhaven National Laboratory \cite{muggli:2011}.
+%electron drive beams has been demonstrated at Brookhaven National Laboratory~\cite{muggli:2011}.
 
@@
         beam undergoes self-modulation in the first plasma section. The electron witness beam is injected into the
-        accelerating structure, and undergoes acceleration in the second plasma section
-        \cite{berglyd_olsen:2015, adli:2016}}.
+        accelerating structure, and undergoes acceleration in the second plasma
+        section~\cite{berglyd_olsen:2015, adli:2016}}.
 \end{figure}
@@
 The energy carried by electron drive beams used in previous plasma wakefield experiments have been on the order of
-$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$ \cite{blumenfeld:2007, caldwell:2009}.
+$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$~\cite{blumenfeld:2007, caldwell:2009}.
 For high-energy physics application a higher total beam energy is often desired. For instance, the energy of a
@@
 Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS
-beam \cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
-magnitude longer than the plasma wavelengths needed for such applications, and it does not drive a strong wake
-\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into the
-accelerating structure, stronger wakefields are excited. The self-modulation is produced by the transverse fields
-generated by the beam acting upon itself, causing regions of the beam to rapidly defocus \cite{kumar:2010}. The
+beam~\cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
+magnitude longer than the plasma wavelengths needed for such applications, and it does not drive a strong
+wake~\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into
+the accelerating structure, stronger wakefields are excited. The self-modulation is produced by the transverse fields
+generated by the beam acting upon itself, causing regions of the beam to rapidly defocus~\cite{kumar:2010}. The
 modulation frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis
@@
 beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of
-$7\nexp{14}\unit{cm}^{-3}$ \cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
+$7\nexp{14}\unit{cm}^{-3}$~\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
 -- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
@@
 phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
-relevance for Run 2 \cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
+relevance for Run 2~\cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
 acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
@@
 
-The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in Fig. \ref{Fig:AWAKER2}. The first
+The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in Fig.~\ref{Fig:AWAKER2}. The first
 section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
@@
 The focus in this study is on the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
-proton beams show that the proton beam evolves as it propagates through a uniform plasma \cite{lotov:2011}, but that
-small variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long distances
-\cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake, independent of the
-dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver. The proton beam parameters
-are chosen so that key features of the wake -- the plasma electron density in the wake and the longitudinal electric
-field -- are the same as in the wake of a self-modulated proton beam with AWAKE baseline parameters
-\cite{gschwendtner:2016}. Both the proton beam and the witness beam have Gaussian longitudinal charge distribution and
-bi-Gaussian transverse charge distributions.
+proton beams show that the proton beam evolves as it propagates through a uniform plasma~\cite{lotov:2011}, but that
+small variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long
+distances~\cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake,
+independent of the dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver. The proton
+beam parameters are chosen so that key features of the wake -- the plasma electron density in the wake and the
+longitudinal electric field -- are the same as in the wake of a self-modulated proton beam with AWAKE baseline
+parameters~\cite{gschwendtner:2016}. Both the proton beam and the witness beam have Gaussian longitudinal charge
+distribution and bi-Gaussian transverse charge distributions.
 
-We have previously studied the beam loading in a proton beam wake using the full particle-in-cell (PIC) code OSIRIS
-\cite{fonseca:2002} with 2D cylindrical-symmetric simulations. The studies \cite{berglyd_olsen:2015, berglyd_olsen:2016}
-primarily looked at beam loading, energy gain and energy spread, as well as different approaches to creating a stable
-drive beam structure based on previous self-modulation studies. In order to study the witness beam emittance evolution
-we use the recently released open-source version of QuickPIC \cite{huang:2006, an:2013}. QuickPIC is a fully
-relativistic 3D quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC codes do
-\cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation. All simulation results in
-this paper were obtained using QuickPIC open-source \cite{quickpic:web}.
+We have previously studied the beam loading in a proton beam wake using the full particle-in-cell (PIC) code
+OSIRIS~\cite{fonseca:2002} with 2D cylindrical-symmetric simulations. The studies~\cite{berglyd_olsen:2015,
+berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to
+creating a stable drive beam structure based on previous self-modulation studies. In order to study the witness beam
+emittance evolution we use the recently released open-source version of QuickPIC~\cite{huang:2006, an:2013}. QuickPIC is
+a fully relativistic 3D quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC
+codes do~\cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation. All simulation
+results in this paper were obtained using QuickPIC open-source~\cite{quickpic:web}.
 
@@
         and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the witness beam
-        (red) superimposed. The line plot indicates the transverse wakefield gradient $dW_{x}/dx$ where
-        $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to the left.}
+        (red) superimposed. The line plot indicates the transverse wakefield gradient $\textrm{d}W_{x}/\textrm{d}x$
+        where $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to the left.}
 \end{figure}
@@
 The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void
-of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons \cite{gschwendtner:2016}, enters the second
-plasma section (Fig. \ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
+of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons~\cite{gschwendtner:2016}, enters the second
+plasma section (Fig.~\ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
 plasma electron density is only depleted to around $65\%$ of nominal plasma density at the point where we inject the
-electron beam \cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field is replicated
+electron beam~\cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field is replicated
 using a single bunch with $1.46\nexp{10}$ protons ($2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$
@@
 in a quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation of the
-self-modulated proton beam \cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
+self-modulated proton beam~\cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
 equivalent proton bunch by increasing the particles mass by six orders of magnitude.
@@
 In order to prevent large amplitude oscillations of the witness beam particles, which may cause additional energy spread
-as well as emittance growth, we consider a witness beam matched to the plasma density. The matched beam transverse size
-is:
+as well as emittance growth, we consider a witness beam matched to the plasma density. The matched beam transverse
+size~\cite{esarey:1996} is:
 \begin{equation}
@@
 
-Beam loading of a short witness beam is sensitive to its position relative to the electric field \cite{tzoufras:2009}
+Beam loading of a short witness beam is sensitive to its position relative to the electric field~\cite{tzoufras:2009}
 as well as to its de-phasing with respect to the wakefields at low energy. To eliminate de-phasing of the witness beam,
@@
 to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based
-on earlier beam loading studies \cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
+on earlier beam loading studies~\cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
 loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
-\emph{base case}. Figure \ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
+\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
 step, for the base case parameters; the proton beam in blue, the trailing electron beam in red, and the plasma electron
@@
 much wider proton beam and its wakefields. We use a transverse grid cell size of $1.17\unit{\mu m}$, and of
-$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section \ref{S:BL}. The witness beam
+$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section~\ref{S:BL}. The witness beam
 was simulated with $16.8\nexp{6}$ non-weighted particles, the drive beam with $2.1\nexp{6}$ non-weighted particles, and
@@
         line), witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
-        $\xi = z - tc$ is the position in the simulation box, moving towards the left.}
+        $\xi = z - tc$ is the position in the simulation box, moving towards the left. The plots show the initial time
+        step.}
 \end{figure}
@@
         calculation of transverse normalised emittance. The moving window calculation uses longitudinal slices of
-        $l = 4\times\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
+        $l = 4\cdot\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
         particles have been included. The plasma density profile is included in green, and scaled up by a factor of
@@
 
-Figure \ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step for the base case
+Figure~\ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step for the base case
 parameters. The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the
-electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear regime
-\cite{rosenzweig:2010}. The dashed green line in the lower part of Fig. \ref{Fig:BeamLoading} shows that the on-axis
-plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE Run 2
-\cite{awake_collaboration:2016}.
+electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear
+regime~\cite{rosenzweig:2010}. The dashed green line in the lower part of Fig.~\ref{Fig:BeamLoading} shows that the
+on-axis plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE
+Run 2~\cite{awake_collaboration:2016}.
 
@@
 shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field
-is constant along the beam \cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot
+is constant along the beam~\cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot
 completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
-tail in energy both at the front and the back of the beam, as illustrated in Fig. \ref{Fig:BeamPS}. The bulk of the
+tail in energy both at the front and the back of the beam, as illustrated in Fig.~\ref{Fig:BeamPS}. The bulk of the
 beam, however, sees a relatively flat field.
@@
 is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons,
-resulting in the formation of an ion column (see Fig. \ref{Fig:BeamLoading}, bottom). This ion column, as is well
-known \cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
-therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in Fig.
-\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the
-matched field gradient.
+resulting in the formation of an ion column (see Fig.~\ref{Fig:BeamLoading}, bottom). This ion column, as is well
+known~\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
+therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in
+Fig.~\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to
+the matched field gradient.
 
@@
 
-Figure \ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through
+Figure~\ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through
 $0$, $4$, $40$ and $100\unit{m}$ of plasma. We define emittance of a slice as preserved if the growth is less than
@@
 plasma bubble, the emittance of the part of the beam inside the bubble is not affected by small transverse offsets of
-the witness beam with respect to the proton beam axis. This is illustrated in Fig. \ref{Fig:BeamEmitt}, right, for an
-electron beam offset of $1\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
+the witness beam with respect to the proton beam axis. This is illustrated in Fig.~\ref{Fig:BeamEmitt}, right, for an
+electron beam offset of one $\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
 accelerating regime, and may ease transverse injection tolerances. The head of the beam experiences a larger initial
-emittance growth than for the on-axis case (compare Fig. \ref{Fig:BeamEmitt}, left, to Fig. \ref{Fig:BeamEmitt}, right).
+emittance growth than for the on-axis case (compare Fig.~\ref{Fig:BeamEmitt}, left, to Fig.~\ref{Fig:BeamEmitt}, right).
 However, also for the head of the beam the emittance growth ends after the first few metres.
-Figure \ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
-$2.5\unit{m}$, while Fig. \ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
-centroid oscillations of the head and the trailing part are shown in Fig. \ref{Fig:BeamFilament}g. This effect of a
+Figure~\ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
+$2.5\unit{m}$, while Fig.~\ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
+centroid oscillations of the head and the trailing part are shown in Fig.~\ref{Fig:BeamFilament}g. This effect of a
 transverse offset is likely to be greater for larger offsets as the beam oscillates around the axis of the drive beam
@@
 The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
-Eq. \ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
+Eq.~\ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
 increases as its gamma factor increases and its transverse size decreases. This effect can be seen in Fig.
@@
 limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For an electron beam to be externally
-injected in AWAKE Run 2 (see Fig. \ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
-spread, maximise the charge to be accelerated, and minimise the emittance growth \cite{adli:2016}. In addition, the
-beam length should be such that it is possible to generate and transport the beam using a compact electron injector
-\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron beam
-length, its charge, and initial emittance. The results are quantified in terms of how much of the beam retains its
+injected in AWAKE Run 2 (see Fig.~\ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
+spread, maximise the charge to be accelerated, and minimise the emittance growth~\cite{adli:2016}. In addition, the
+beam length should be such that it is possible to generate and transport the beam using a compact electron
+injector~\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron
+beam length, its charge, and initial emittance. The results are quantified in terms of how much of the beam retains its
 initial emittance. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$, and let the
@@
 
-Figure \ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An
+Figure~\ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An
 initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the
@@
 wake, thus producing a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is
-preserved (the slice emittance for the base case is shown in Fig. \ref{Fig:BeamEmitt}). As the witness beam charge
+preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}). As the witness beam charge
 increases, the fraction of slices with preserved emittance increases -- as expected from an earlier onset of the bubble
-formation -- and also increases in the bubble size \cite{lu:2006-1, lu:2006}. We note here that operation with
+formation -- and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that operation with
 $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an
@@
 
-Figure \ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
+Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
 curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
@@
 
-Figure \ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
+Figure~\ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
 emittance. In these simulations we adjusted the witness beam radius to maintain the matching condition at each
@@
 for beam of lengths of $40-60\unit{\mu m}$. Such electron beams may be generated by an injector based on a standard
-RF photo-emission gun \cite{doebert:corr}.
+RF photo-emission gun~\cite{doebert:corr}.
 

### 2017-10-09 Tex/Paper.tex
Plot updates

@@
 $7\nexp{14}\unit{cm}^{-3}$~\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
--- matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$, where
+and is matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$~\cite{lu:2005}, where
 $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe} = 2\pi c/\omega_{pe}$, and
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} \textbf{Top plot:} Unloaded longitudinal electric field with no witness beam
+    \caption{\label{Fig:BeamLoading} Top plot: Unloaded longitudinal electric field with no witness beam
         (dashed blue line) and loaded field (whole blue line) along the beam axis. The beam density along the axis for
         both beams are shown in red.
-        \textbf{Bottom plot:} Plasma densities along the beam axis for a drive beam with no witness beam (dashed green
-        line), witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
+        Bottom plot: Plasma densities along the beam axis for a drive beam with no witness beam (dashed green line),
+        witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
         $\xi = z - tc$ is the position in the simulation box, moving towards the left. The plots show the initial time
@@
         of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
-        lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
+        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
         These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
@@
     \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
-        initial beam charge (blue symbols, lines), and final energy (red symbols, lines), after $4\unit{m}$ of plasma
-        and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
+        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
 \end{figure}
@@
     \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a
-        function of initial emittance (blue symbols, lines), and relative energy spread of the accepted charge (red
-        symbols, lines), after $4\unit{m}$ of plasma.}
+        function of initial emittance (blue symbols, line), and relative energy spread of the accepted charge (red
+        symbols, dashed line), after $4\unit{m}$ of plasma.}
 \end{figure}

### 2017-10-09 Tex/Paper.tex
Added beam offset plot

@@
 
+\begin{figure*}[hbt]
+    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
+    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
+    \caption{\label{Fig:BeamQ} Left: Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
+        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
+        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
+        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
+        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.
+        Right: Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
+        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
+        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+\end{figure*}
+
 Figure~\ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through
@@
 
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
-        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
-        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
-        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
-        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
-\end{figure}
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
-        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
-        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
-\end{figure}
+\begin{figure*}[hbt]
+    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityOffset}
+    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
+    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$
+        (blue symbols, line), as a function of beam offset (left) and initial emittance (right), with relative energy
+        spread of the accepted charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
+\end{figure*}
 
@@
 
-Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
+Figure~\ref{Fig:BeamQ} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
 curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
 beam length and beam charge.
-
-\begin{figure}[hbt]
-    \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a
-        function of initial emittance (blue symbols, line), and relative energy spread of the accepted charge (red
-        symbols, dashed line), after $4\unit{m}$ of plasma.}
-\end{figure}
 

### 2017-10-09 Tex/Paper.tex
Updates

@@
 independent of the dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver. The proton
-beam parameters are chosen so that key features of the wake -- the plasma electron density in the wake and the
-longitudinal electric field -- are the same as in the wake of a self-modulated proton beam with AWAKE baseline
+beam parameters are chosen so that key features of the wake \textendash the plasma electron density in the wake and the
+longitudinal electric field \textendash are the same as in the wake of a self-modulated proton beam with AWAKE baseline
 parameters~\cite{gschwendtner:2016}. Both the proton beam and the witness beam have Gaussian longitudinal charge
@@
         drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x,eb} = 5.24\unit{\mu m}$ in
-        the x-plane -- at four different positions $z$ in the plasma stage. The red lines show a moving window
+        the x-plane \textendash at four different positions $z$ in the plasma stage. The red lines show a moving window
         calculation of transverse normalised emittance. The moving window calculation uses longitudinal slices of
@@
 \begin{figure*}[hbt]
-    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-    \caption{\label{Fig:BeamQ} Left: Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$, as a function
-        of initial beam charge (blue symbols, lines), and relative energy spread of the accepted charge (red symbols,
-        dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
-        These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies
-        presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.
-        Right: Witness beam charge with emittance preserved, $\widetilde{Q}$, as a function of
-        initial beam charge (blue symbols, lines), and final energy (red symbols, dashed lines), after $4\unit{m}$ of
-        plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+    \begin{minipage}[t]{.48\textwidth}
+        \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
+        \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
+            symbols, lines), as a function of initial beam charge, and relative energy spread of the accepted charge
+            (red symbols, dashed lines), after $4\unit{m}$ of plasma and with an initial emittance
+            $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from
+            $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam loading section correspond to
+            the square marked lines at $100\unit{pC}$.}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{.48\textwidth}
+        \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
+        \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$ (blue symbols,
+            lines), as a function of initial beam charge, and final energy (red symbols, dashed lines), after
+            $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+    \end{minipage}
 \end{figure*}
@@
 preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}). As the witness beam charge
-increases, the fraction of slices with preserved emittance increases -- as expected from an earlier onset of the bubble
-formation -- and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that operation with
-$100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an
-increase of relative energy spread by a factor of two.
+increases, the fraction of slices with preserved emittance increases \textendash as expected from an earlier onset of
+the bubble formation \textendash and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that
+operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the
+expense of an increase of relative energy spread by a factor of two.
 
-Figure~\ref{Fig:BeamQ} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
+Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
 curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of

### 2017-10-10 Tex/Paper.tex
Updated figures 9 and 10

@@
 that $\widetilde{Q}/Q = 73\%$ of the electron beam longitudinal slices retain their initial emittance after the
-propagation in the plasma. Emittance growth mainly occurs in the first few metres, and no significant emittance growth
-is observed after this for propagation lengths up to $100\unit{m}$. The head of the beam does not benefit from the full
-ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still
-stabilises after some time. For the $100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC
-energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$
-after about $50\unit{m}$.
+propagation in the plasma. The total (projected) emittance of these slices combined is also preserved. Emittance growth
+mainly occurs in the first few metres, and no significant emittance growth is observed after this for propagation
+lengths up to $100\unit{m}$. The head of the beam does not benefit from the full ion column focusing, but since the
+proton beam creates a quasi-linear wake, the emittance of the head of the beam still stabilises after some time. For the
+$100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
+de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
 
@@
 centroid oscillations of the head and the trailing part are shown in Fig.~\ref{Fig:BeamFilament}g. This effect of a
-transverse offset is likely to be greater for larger offsets as the beam oscillates around the axis of the drive beam
-wakefield. [Will add results on how much offset can be tolerated as soon as the simulations are done.]
+transverse offset is greater for larger offsets as the beam oscillates around the axis of the drive beam wakefield.
 
@@
 \begin{figure*}[hbt]
-    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityOffset}
-    \includegraphics[width=0.49\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-    \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$
-        (blue symbols, line), as a function of beam offset (left) and initial emittance (right), with relative energy
-        spread of the accepted charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
+    \begin{minipage}[t]{.48\textwidth}
+        \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
+        \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
+            symbols, line), as a function of beam initial emittance (right), with relative energy spread of the accepted
+            charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
+    \end{minipage}\hfill
+    \begin{minipage}[t]{.48\textwidth}
+        \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityOffset}
+        \caption{\label{Fig:BeamQOffset} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
+            symbols, line), as a function of beam offset, with relative energy spread of the accepted charge (red
+            symbols, dashed line), after $4\unit{m}$ of plasma.}
+    \end{minipage}
 \end{figure*}
@@
 spread.
+
+Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x}$, but
+with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
+correlation between this ratio for a range of offsets up to $4\cdot\sigma_{x}$. The effect on the head of the beam shown
+in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament} increase with larger offsets causing the section of the beam
+being defocused to extend backwards to the point where the witness beam wakefields are no longer non-linear as the
+offset approaches $4\cdot\sigma_{x}$.
 

### 2017-10-11 Tex/Paper.tex
Some text changes to offset paragraph

@@
 Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared
-to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$, based
+to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$ based
 on earlier beam loading studies~\cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
@@
 with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
-correlation between this ratio for a range of offsets up to $4\cdot\sigma_{x}$. The effect on the head of the beam shown
-in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament} increase with larger offsets causing the section of the beam
-being defocused to extend backwards to the point where the witness beam wakefields are no longer non-linear as the
-offset approaches $4\cdot\sigma_{x}$.
+correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x}$. The effect on the head of the beam,
+shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section of the
+beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the blow-out
+regime. At around $3\cdot\sigma_{x}$ emittance is no longer preserved at all.
 

### 2017-10-12 Tex/Paper.tex
Corrections from Erik

@@
 
-Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x}$, but
-with a cost in the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows the
-correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x}$. The effect on the head of the beam,
-shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section of the
-beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the blow-out
-regime. At around $3\cdot\sigma_{x}$ emittance is no longer preserved at all.
+Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x,eb}$,
+but with a reduction of the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows
+the correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x,eb}$. The effect on the head of the
+beam, shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section
+of the beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the
+blow-out regime. At around $3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
 

### 2017-10-12 Tex/Paper.tex
Patric's final changes, and some cleanup

@@
 be ensured when accelerated by a proton drive beam producing quasi-linear wakefields~\cite{rosenzweig:2010}. By
-quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the bubble.
-The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low relative
-energy spread, and completely blow out the electrons left in the bubble after the beam to reach conditions that
-preserves emittance. The results have importance for the preparation of AWAKE Run 2~\cite{adli:2016}, and possibly other
-applications in the quasi-linear regime.
+quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the accelerating
+structure (bubble). The key idea is to have enough charge in the witness beam to at the same time load the wakefield to
+produce low relative energy spread, and completely blow out the electrons left in the accelerating structure after the
+beam to reach conditions that preserves emittance. The results have importance for the preparation of AWAKE
+Run~2~\cite{adli:2016}, and possibly other applications in the quasi-linear regime.
 
@@
 generated by the beam acting upon itself, causing regions of the beam to rapidly defocus~\cite{kumar:2010}. The
-modulation frequency is close to that of the plasma, and produces a train of short proton bunches along the beam axis
-with a surrounding halo of defocused particles. This train of bunches resonantly drives wakefields to large amplitudes.
+modulation frequency is close to that of the plasma electrons, and produces a train of short proton bunches along the
+beam axis with a surrounding halo of defocused particles. This train of bunches resonantly drives wakefields to large
+amplitudes.
 
@@
 $7\nexp{14}\unit{cm}^{-3}$~\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
-and is matched to the transverse size of the SPS proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$~\cite{lu:2005}, where
+and is matched to the transverse size of the proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$~\cite{lu:2005}, where
 $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe} = 2\pi c/\omega_{pe}$, and
@@
 The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of the second
-phase, in 2018, is to sample the wakefield with a long electron beam $\simeq\lambda_{pe}$. The study presented here has
-relevance for Run 2~\cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
-acceleration of a short electron beam, $\ll\lambda_{pe}$, to high energy and with a minimal increase in emittance and
+phase, in 2018, is to sample the wakefield with a long electron beam ($\simeq\lambda_{pe}$). The study presented here
+has relevance for Run~2~\cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
+acceleration of a short electron beam ($\ll\lambda_{pe}$) to high energy and with a minimal increase in emittance and
 absolute energy spread.
 
-The plans for AWAKE Run 2 proposes to use two plasma sections, illustrated in Fig.~\ref{Fig:AWAKER2}. The first
+The plans for AWAKE Run~2 propose to use two plasma sections, as illustrated in Fig.~\ref{Fig:AWAKER2}. The first
 section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
@@
 The focus in this study is on the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
-proton beams show that the proton beam evolves as it propagates through a uniform plasma~\cite{lotov:2011}, but that
-small variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long
+proton beams show that the beam evolves as it propagates through a uniform plasma~\cite{lotov:2011}, but small
+variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long
 distances~\cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake,
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulations of the initial time step for the single proton drive beam
-        and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the witness beam
-        (red) superimposed. The line plot indicates the transverse wakefield gradient $\textrm{d}W_{x}/\textrm{d}x$
-        where $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to the left.}
+    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulation results showing the initial time step for the single proton
+        drive beam and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the
+        witness beam (red) superimposed. The line plot indicates the transverse wakefield gradient
+        $\textrm{d}W_{x}/\textrm{d}x$ where $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to
+        the left.}
 \end{figure}
@@
 plasma section (Fig.~\ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
-plasma electron density is only depleted to around $65\%$ of nominal plasma density at the point where we inject the
-electron beam~\cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field is replicated
+plasma electron density is only depleted to around $65\%$ of nominal value at the point where we inject the
+electron beam~\cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field are replicated
 using a single bunch with $1.46\nexp{10}$ protons ($2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$
-($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The peak density at $0.83\cdot n_{0}$ results
-in a quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation of the
-self-modulated proton beam~\cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
+($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The beam peak density is $0.83\cdot n_{0}$
+and results in a quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation
+of the self-modulated beam~\cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
 equivalent proton bunch by increasing the particles mass by six orders of magnitude.
@@
 \begin{equation}
-    \sigma_{x,y,eb}=\left(\frac{2c^{2}\epsilon_{\mathrm{N}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}
+    \sigma_{x,y,eb}=\left(\frac{2c^{2}\epsilon_{\mathrm{N}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}.
     \label{EQ:Matched}
@@
 
-Beam loading of a short witness beam is sensitive to its position relative to the electric field~\cite{tzoufras:2009}
-as well as to its de-phasing with respect to the wakefields at low energy. To eliminate de-phasing of the witness beam,
-the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$. A
-lower initial energy is likely to be sufficient for AWAKE Run 2 injection.
+Beam loading by a short witness beam is sensitive to its position relative to the electric field~\cite{tzoufras:2009}
+as well as, at low energy, to its de-phasing with respect to the wakefields. To eliminate de-phasing of the witness
+beam, the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.
+A lower initial energy is likely to be sufficient for AWAKE Run~2 injection.
 % EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement,
@@
 loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
-\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams from a QuickPIC simulation of the initial time
-step, for the base case parameters; the proton beam in blue, the trailing electron beam in red, and the plasma electron
-density in grey.
+\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams \textendash the proton beam in blue, the trailing
+electron beam in red, and the plasma electron density in grey \textendash from a QuickPIC simulation of the initial time
+step, for the base case parameters.
 
@@
 $2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section~\ref{S:BL}. The witness beam
-was simulated with $16.8\nexp{6}$ non-weighted particles, the drive beam with $2.1\nexp{6}$ non-weighted particles, and
-the plasma electrons with $1024 \times 1024$ weighted particles per transverse slice.
+was simulated with $16.8\nexp{6}$ and the drive beam with $2.1\nexp{6}$ non-weighted particles, and the plasma electrons
+with $1024 \times 1024$ weighted particles per transverse slice.
 
@@
         Bottom plot: Plasma densities along the beam axis for a drive beam with no witness beam (dashed green line),
-        witness beam with no drive beam (dash-dotted green line), and both beams present (whole green line).
-        $\xi = z - tc$ is the position in the simulation box, moving towards the left. The plots show the initial time
+        witness beam with no drive beam (dash-dotted green line), and both beams present (continuous green line).
+        The position in the simulation box $\xi = z - tc$, moving towards the left. The plots show the initial time
         step.}
@@
 on-axis plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE
-Run 2~\cite{awake_collaboration:2016}.
+Run~2~\cite{awake_collaboration:2016}.
 
@@
 
-The witness beam generates its own wakefield which loads the $E_{z}$-field generated by the drive beam. With an ideally
+The witness beam generates its own wakefield that loads the $E_{z}$-field generated by the drive beam. With an ideally
 shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field
@@
 is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons,
-resulting in the formation of an ion column (see Fig.~\ref{Fig:BeamLoading}, bottom). This ion column, as is well
+resulting in the formation of a pure ion column (see Fig.~\ref{Fig:BeamLoading}, bottom). This ion column, as is well
 known~\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
-therefore prevents emittance growth for this part of the beam. This effect is shown for our base case in
-Fig.~\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to
-the matched field gradient.
+therefore prevents emittance growth for this part of the beam. This bubble and the focusing force is shown for our base
+case in Fig.~\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis,
+corresponding to the matched field gradient.
 
@@
 injection of a witness beam with an offset with respect to the proton beam axis. Since the witness beam creates its own
-plasma bubble, the emittance of the part of the beam inside the bubble is not affected by small transverse offsets of
+plasma bubble, the emittance of the part of the beam inside that bubble is not affected by small transverse offsets of
 the witness beam with respect to the proton beam axis. This is illustrated in Fig.~\ref{Fig:BeamEmitt}, right, for an
@@
 \ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for the base case no
-significant overloading is observed.
+significant overloading is observed. Parameters can also be chosen in order to minimise this effect by slightly
+underloading the wakefield at first, and let the high energy beam overload the wakefield at the end.
 
@@
 longitudinal profile, transverse profile, as well as relative phasing of the proton and the electron beams. We present a
-limited parameter study aimed at guiding beam parameter choices for AWAKE Run 2. For an electron beam to be externally
-injected in AWAKE Run 2 (see Fig.~\ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
+limited parameter study aimed to guide beam parameter choices for AWAKE Run~2. For an electron beam to be externally
+injected in AWAKE Run~2 (see Fig.~\ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
 spread, maximise the charge to be accelerated, and minimise the emittance growth~\cite{adli:2016}. In addition, the
@@
 initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the
-charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charges range from $10\unit{pC}$ to
+charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charge ranges from $10\unit{pC}$ to
 $300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from Fig.
@@
 curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
-beam length and beam charge.
+beam length and beam charge. The results are weakly dependent on the electron beam length. As expected, a larger value
+of $\widetilde{Q}$ corresponds to a lesser energy gain.
 
@@
 but with a reduction of the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows
-the correlation between this ratio for a range of offsets up to $3.2\cdot\sigma_{x,eb}$. The effect on the head of the
-beam, shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the section
-of the beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the
-blow-out regime. At around $3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
+the correlation between this ratio for a range of offsets up to $16\unit{\mu m}$, corresponding to
+$3.2\cdot\sigma_{x,eb}$. The effect on the head of the beam, shown in Figs.~\ref{Fig:BeamEmitt}
+and~\ref{Fig:BeamFilament}, increases with larger offsets causing the part of the beam being defocused to extend
+backwards to the point where the witness beam wakefields are no longer in the blow-out regime. At around
+$3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
 

### 2017-10-13 Tex/Paper.tex
Last edit by Patric
Removed all comments in source
Removed redundant figures and fixed an error

@@
 % ******************************************************************************************************************** %
-
-%Patric general comments
-%  energy labels not consistent between figs 7, 9 and 8
-%  labels for the fractional charge is too complicated on Figs 7,8,9. it needs to be explained in the caption and/or in
-%  the text. "On the left axis we plot the fraction of that charge whose emittance remains .... "
-%  Add scale for grey color on Fig. 2
-%  Fig. 3 has a "v=c" and an arrow that are only on that figure ...
-%  It is not clear to me what the conclusions/outcome of the last section are ....
-
-%~ Eric's Comments
-%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
-%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
-%~   unloaded wake)
-%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
-%~   flatten and energy spread reduced [well known result, Tzoufras] 
-%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
-%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
-%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
-%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
-%~   electron densities etc. )
-%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
-%~   longitudinal phase spaces, space long simulation)
-%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
-%~   show: transverse and longitudinal phase spaces, long offset simulation)
-%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
-%~ beam, and preferably some scalings]
-%~ - how to select electron beam parameters:
-%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
-%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
-%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
-%~ (- plasma density?)
-
-%~ Patric's Comments
-%~ - Self-modulation as a driver
-%~ - SM does not reach blow out
-%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
-%~   not desirable
-%~ - Beam loading for narrow energy spread
-%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
-%~   (Tzoufras) well know
-%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
-%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
-%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
-%~   bunch and the SM
-%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
-%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
-%~ As for N+2, I am a firm supporter of on-axis injection ... and most of the issue with that has to do with the plasma
-%~ ramp, otherwise it would be a non-issue (assuming of course that one can split the plasma in two sections). It is in
-%~ itself a topic of research, so I think we can only state a few things ...
 
@@
 \section{Introduction}\label{S:I}
-% interested from SMI/AWAKE
-% requirements for AWAKE Run 2
 % ******************************************************************************************************************** %
@@
 Run~2~\cite{adli:2016}, and possibly other applications in the quasi-linear regime.
-
-% ******************************************************************************************************************** %
-%\subsection[\label{S:I:SMI}]{Self-modulation as a Driver}
-%~ Patric's Comments
-%~ - Self-modulation as a driver
-%~ - SM does not reach blow out
-%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
-%~   not desirable
-% ******************************************************************************************************************** %
-
-% 	EA comment: is this part relevant?  Feels out of place.  We repeat this physics below when discussing proton beam SMI.  
-%A train of electron drive bunches with a separation $\lambda_{pe}$ and a length $l_{b} \ll \lambda_{pe}$, where the
-%plasma wavelength $\lambda_{pe} = 2\pi c/\omega_{pe}$ and the plasma frequency $\omega_{pe} = (n_{0} e^{2} / m_{e}
-%\epsilon_{0})^{1/2}$, produces a field $E_{z}$ that increases for each drive bunch~\cite{chen:1985}. A tailing witness
-%beam loading the peak accelerating phase of this field will gain energy from the wakefield from all of the drive bunches
-%when they are properly phased with respect to the wakefields. Acceleration of an electron witness beam driven by two
-%electron drive beams has been demonstrated at Brookhaven National Laboratory~\cite{muggli:2011}.
 
@@
 
-%   EA: Moved to "witness beam"
-%The small size of the accelerating structure produced by the self-modulated beam also
-%puts constraints on the size of the electron witness beam, and thus its charge and current, if at the same time we wish
-%to prevent large energy spread. By matching the transverse size of the beam at a given emittance to the plasma density,
-%we prevent large amplitude oscillations which may cause additional energy spread as well as emittance growth.
-
-%    EA: I kept Patric's version, but moved it to the end of the introduction
-%~ Eric's version:
-%~ The key idea in this paper is that while the proton beam wake is not fully blown-out, and thus leading to non-linear
-%~ focusing forces, the electron beam, if intense enough, may load the field and at the same time create its own ion
-%~ bubble. As will be shown, exploiting these two well known effects, the electron beam can be accelerated for long
-%~ distances without significant emittance growth.
-
 % ******************************************************************************************************************** %
 \section[\label{S:M}]{Method}
-%- explain analogy of short-bunch, SMI case, by referring to earlier Veronica-papers
-%- simulation setup PIC/quickpic OS
 % ******************************************************************************************************************** %
@@
 
-%~ In order to evaluate the quality of the accelerated bunch it was also necessary to study emittance evolution. However,
-%~ full PIC codes are vulnerable to numerical growth of emittance caused by the ``numerical Cherenkov effect''
-%~ \cite{godfrey:1974}. This is a know issue with the Yee EMF solver which causes the phase velocity of electromagnetic
-%~ fields to be lower than $c$ while the beam moves very close to $c$. The effect can be mitigated somewhat by replacing
-%~ the Yee solver with a solver designed by Lehe \cite{lehe:2013}. Our simulations showed that this numerical effect is
-%~ still prominent in the high density regions of our very compact electron bunch, making it difficult to distinguish
-%~ emittance growth from the physics from that originating from numerical error.
-
 \begin{figure}[hbt]
@@
 \subsection{Drive Beam Parameters}\label{S:M:Setup}
-%~ Patric's Comments
-%~ - Self-modulation as a driver
-%~ - SM does not reach blow out
-%~ - SM does not preserve emittance and produces large energy spread and parameters may evolve along the accelerator,
-%~   not desirable
 % ******************************************************************************************************************** %
-
-%~ In these simulations we use a single proton drive beam that sets up a wakefield comparable to that which we expect to
-%~ see from the self-modulated SPS beam in the second plasma cell of AWAKE Run 2 (Figure \ref{Fig:AWAKER2}).
-%PM The baseline AWAKE drive beam current is insufficient to reach the non-linear regime and produce a plasma bubble.
 
@@
 produce with a standard RF-injector, while at the same time yielding a sufficiently narrow beam.
-% EA: comment, perhaps put a ref here [***ref].
 
@@
 A lower initial energy is likely to be sufficient for AWAKE Run~2 injection.
-% EA: we have studied this to some extent, but unfortunately we do not have a good refence for the last statement,
-%     no details in \cite{berglyd_olsen:2015}.
 
@@
 step, for the base case parameters.
-
-%   EA: the discussing of charge could better be discussed in the "beam loading chapter" - the information has been moved to there
-% the charge required to load the field is 
-% density of the electron beam reaches that of the plasma density for a bunch charge of a few $\unit{pC}$.   
-% but reaches optimal beam loading at around $100-200\unit{pC}$. 
-%The implication here being that the witness beam produces its own non-linear
-%wakefield already at the head of the beam. The majority of the electrons within it will therefore see a linear focusing
-%force preventing the bulk of the beam from undergoing emittance growth.
 
@@
 \section{Beam Loading}\label{S:BL}
-%~ Eric's Comments
-%~ Sec N: Beam loading [in this section we describe the interesting physics, based on a single parameters set]
-%~ - describe proton beam wake structure [similar to that of a modulated proton beam] (simulation results to show:
-%~   unloaded wake)
-%~ - by varying the current of the electron beam, the electron beam may load the wake and the longitudinal field can be
-%~   flatten and energy spread reduced [well known result, Tzoufras]
-%~ - the electron beam blows out the remaining plasma electrons. The transverse fields are dominated by the linear
-%~   focusing fields originating from the ion background, leading to emittance preservation of the part of the electron
-%~   beam inside the bubble [loading of a quasi-linear wake, and still get emittance preservation: this is new]
-%~   (simulation results to show: loaded wake, with bubble - many different aspects of this, trans., long. field,
-%~   electron densities etc. )
-%~ - the acceleration and the transverse emittance stable on long timescales (simulation results to show: transverse and
-%~   longitudinal phase spaces, space long simulation)
-%~ - in this regime, emittance preservation is robustness to drive-witness offset [this is new] (simulation results to
-%~   show: transverse and longitudinal phase spaces, long offset simulation)
-%~
-%~ Patric's Comments
-%~ - Beam loading for narrow energy spread
-%~ - Beam loading in linear regime (old papers from SLAC in the 80's, then Katsouleas for PWFA) and nonlinear regime
-%~   (Tzoufras) well know
-%~ - Propose "new regime" in the SM case, beam loading and blowout to get emittance preservation
-%~ - Limitation as for PWFA driver, must use some of the W bunch to reach the blowout, it is kind of like the early SLAC
-%~   experiments (84GeV) where the W-bunch is like the D-bunch in these experiments, but in a plasma prepared by the p+
-%~   bunch and the SM
-%~ - maybe also something about the fact that 200pC in a 60µm bunch corresponds to a 1kA current, much larger than the
-%~   p+ bunch current, because of the fact that the wakefields are driven my multiple bunches?
 % ******************************************************************************************************************** %
-
-%  EA: the below has already been clearly spelled out in methods
-%The single drive beam setup is designed to produce similar initial conditions for the witness beam as the self-modulated
-%case. However, since the drive beam is prevented from significant transverse evolution, we are presented with an
-%idealised case where the electron witness beam sees consistent wakefields throughout the plasma stage.
 
@@
 
-%~ The witness beam generates its own wakefield, which in the accelerating phase partially cancels out the $E_{z}$ field
-%~ generated by the drive beam. For a finite length beam this causes the particles in the tail of the witness beam to be
-%~ accelerated less than those at the front resulting in higher energy spread in exchange for higher energy transfer
-%~ \cite{van_der_meer:1985}. A beam profile $\rho_{b}(\xi)$ that perfectly flattens the
-%~ accelerating field within the witness beam will reduces energy spread to zero. The ideal shape is triangular or
-%~ trapezoidal with the peak density in the direction of the beam velocity \cite{katsouleas:1987, tzoufras:2009}.
-
 The witness beam generates its own wakefield that loads the $E_{z}$-field generated by the drive beam. With an ideally
@@
 beam, however, sees a relatively flat field.
-% EA: I rewrote this to the sentence after the comments
-%we can acceleratoreHowever, with such a narrow beam when matched beam to the plasma density (equation
-%\ref{EQ:MatchedB}), we are limited on how much total charge we can accelerate without reaching charge densities that
-%will overload the field.
-%  EA: shall we say the below?  The sentence asks for more detailed studies of the dependence of the loading of the transverse fields.
-%The amounts of charge required to load the field depends both on the witness bunch length as well as the transverse size.
 
@@
 corresponding to the matched field gradient.
-
-%~ Due to the high charge density resulting from a very narrow beam, the witness beam's own wakefield reaches the full
-%~ non-linear regime with $n_{eb} \approx 35\times n_{0}$. This second wakefield is driven by the beam's own front. The
-%~ space charge rapidly becomes high enough to start expel plasma electrons from the beam axis and form the characteristic
-%~ electrons sheet that defines the blowout regime. As a result the plasma region reaches full depletion close to the peak
-%~ of the electron beam, which in turn generates strong focusing fields, with gradients of $20\unit{kT/m}$ near the beam
-%~ axis (see figure \ref{Fig:PlasmaDenTWake}).
-
-%~ The witness beam's self-generated bubble prevents the tailing end of the beam to see any significant emittance growth.
-% EA: I cut the line below, we are still discussing the base case
-%For the majority of the cases we studied, that maintained a stable accelerating structure, 
- %PMDue to the ion column focusing,
 
@@
 
-%~ Our configuration also shows some robustness to small electron beam transverse offsets as the bubble generated by the
-%~ witness beam wakefield follows the beam itself.
 So far we have considered a witness beam injected on the axis of the proton beam. We now briefly examine the case of
@@
 \section{Parameter Optimisation}\label{S:PO}
-%~ Sec N+1: Parameter optimization, or, parameter scaling [in this section we describe how to optimize the electron
-%~ beam, and preferably some scalings]
-%~ - how to select electron beam parameters:
-%~ - longitudinal parameters bunch length and current (simulations results to show: overloaded/underloaded cases)
-%~ - transverse parameters of electron emittance / matching [too large, outside bubble.  Do we see increased head
-%~   erosion -> faster decay]?  (simulations results to show: evolution of high emittance vs low emittance cases)
-%~ (- plasma density?)
 % ******************************************************************************************************************** %
@@
 beam length and beam charge. The results are weakly dependent on the electron beam length. As expected, a larger value
-of $\widetilde{Q}$ corresponds to a lesser energy gain.
+of $\widetilde{Q}$ corresponds to a lesser energy gain. No optimum is observed.
 
@@
 but with a reduction of the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows
-the correlation between this ratio for a range of offsets up to $16\unit{\mu m}$, corresponding to
+the correlation between this ratio for a range of offsets up to $16.8\unit{\mu m}$, corresponding to
 $3.2\cdot\sigma_{x,eb}$. The effect on the head of the beam, shown in Figs.~\ref{Fig:BeamEmitt}
@@
 % ******************************************************************************************************************** %
-
-%~ We have studied a new plasma wakefield acceleration regime; acceleration of a strongly loaded electron beam in a
-%~ quasi-linear proton driven wake. When optimally loaded an electron witness beam has sufficient charge to create a
-%~ strong blow out forming a %n ion 
-%~ bubble trailing the witness beam.  The focusing forces from the ions ensures emittance preservation for large parts of
-%~ the %PM 
-%~ witness beam. %PM, also when the electron beam has some offset with respect to the proton driver.
-%~ Simulations show that the emittance of a large fraction of the electron beam is preserved even when it enters the plasma
-%~ with and offset with respect to the proton bunch axis.
-
-%~ Using AWAKE parameters these result indicates that emittance preservation for an electron beam injected on-axis into a
-%~ plasma stage, and properly optimized, may be feasible. Parameter studies indicate that up to a few $100\unit{pC}$ might
-%~ be accelerated, for bunches of length $40-60\unit{\mu m}$. Such electron bunches may be generated by an injector based
-%~ on a standard RF gun [S. Doebert, private communication].
-
-%~ This study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single,
-%~ short proton bunch, and investigates an ideal, uniform plasma profile.  To fully investigate optimal AWAKE injection,
-%~ further study should be performed including simulations of realistic plasma profiles combined with a self-modulated
-%~ proton beam.  
-% EA: we could also say "is underway" and cite Lotov et co?
-% PM: NOT SURE WHAT PLASMA PROFILE WEA RE TALKING ABOUT ... I would suggest -
-%     EA patric's verson of conclusions are OK with me
 
@@
 
-% EA: I think owned also by IST.  I will check with Weiming and Warren
 The simulations for this study have been performed using the open source version of QuickPIC released in early 2017

### 2017-12-04 Tex/Paper.tex
Reflow

@@
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \begin{document}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
@@
 \begin{abstract}
-We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear
-plasma wakefields driven by a short proton beam. The structure of the studied wakefields are similar to those of a long,
-modulated proton beam, such as the AWAKE proton driver. We show that by properly choosing the electron beam parameters
-and exploiting two well known effects, beam loading of the wakefield and full blow out of plasma electrons by the
-accelerated beam, the electron beam can gain large amounts of energy with a narrow final energy spread (\%-level) and
-without significant emittance growth.
+We investigate beam loading and emittance preservation for a high-charge electron beam being accelerated in quasi-linear plasma wakefields driven by a short proton beam.
+The structure of the studied wakefields are similar to those of a long, modulated proton beam, such as the AWAKE proton driver.
+We show that by properly choosing the electron beam parameters and exploiting two well known effects, beam loading of the wakefield and full blow out of plasma electrons by the accelerated beam, the electron beam can gain large amounts of energy with a narrow final energy spread (\%-level) and without significant emittance growth.
 \end{abstract}
@@
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \section{Introduction}\label{S:I}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-Beam driven plasma wakefield accelerators~\cite{chen:1985} have the potential to offer compact linear accelerators with
-high energy gradients, and have been of interest for several decades. With a relativistic charged particle drive beam
-travelling through a plasma, a strong wakefield is excited that can be loaded by a trailing witness beam. When the
-witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small. The concept has
-been demonstrated experimentally in the past using electron drive beams accelerating electron witness
-beams~\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
+Beam driven plasma wakefield accelerators~\cite{chen:1985} have the potential to offer compact linear accelerators with high energy gradients, and have been of interest for several decades.
+With a relativistic charged particle drive beam travelling through a plasma, a strong wakefield is excited that can be loaded by a trailing witness beam.
+When the witness beam optimally loads the wakefield, an increase in absolute energy spread can be kept small.
+The concept has been demonstrated experimentally in the past using electron drive beams accelerating electron witness beams~\cite{rosenzweig:1988, blumenfeld:2007, kallos:2008, litos:2014}.
 
-A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread
-and emittance growth small. In the well described linear regime, valid when the beam density $n_{b}$ is much smaller
-than the plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam.
-The beam also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the
-beam has been accelerated~\cite{katsouleas:1987}. In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by
-the transverse oscillations of the plasma electrons, gathering in a sheath around an evacuated area filled with only
-ions. The ions, assumed stationary, form a uniform density ion channel creating a focusing force that varies linearly
-with radius. This focusing force preserves emittance~\cite{rosenzweig:1991}.
+A major challenge with plasma wakefield accelerators is, however, to accelerate a beam while keeping both energy spread and emittance growth small.
+In the well described linear regime, valid when the beam density $n_{b}$ is much smaller than the plasma density $n_{0}$, a non-linear transverse focusing force causes emittance growth of the witness beam.
+The beam also sees a transversely and longitudinally varying accelerating field causing a spread in energy after the beam has been accelerated~\cite{katsouleas:1987}.
+In the non-linear regime, where $n_{b} > n_{0}$, a bubble is formed by the transverse oscillations of the plasma electrons, gathering in a sheath around an evacuated area filled with only ions.
+The ions, assumed stationary, form a uniform density ion channel creating a focusing force that varies linearly with radius.
+This focusing force preserves emittance~\cite{rosenzweig:1991}.
 
-In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can
-be ensured when accelerated by a proton drive beam producing quasi-linear wakefields~\cite{rosenzweig:2010}. By
-quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the accelerating
-structure (bubble). The key idea is to have enough charge in the witness beam to at the same time load the wakefield to
-produce low relative energy spread, and completely blow out the electrons left in the accelerating structure after the
-beam to reach conditions that preserves emittance. The results have importance for the preparation of AWAKE
-Run~2~\cite{adli:2016}, and possibly other applications in the quasi-linear regime.
+In this paper we present simulation results showing how emittance preservation of a high charge density witness beam can be ensured when accelerated by a proton drive beam producing quasi-linear wakefields~\cite{rosenzweig:2010}.
+By quasi-linear wakefields we here mean wakefields with only partial blow out of the plasma electrons in the accelerating structure (bubble).
+The key idea is to have enough charge in the witness beam to at the same time load the wakefield to produce low relative energy spread, and completely blow out the electrons left in the accelerating structure after the beam to reach conditions that preserves emittance.
+The results have importance for the preparation of AWAKE Run~2~\cite{adli:2016}, and possibly other applications in the quasi-linear regime.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \subsection{AWAKE Run 2}\label{S:I:AWAKE}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
@@
     \includegraphics[width=0.99\linewidth,trim={1mm 2mm 1mm 2mm},clip]{figures/figAWAKE}
-    \caption{\label{Fig:AWAKER2} A simplified illustration of the experimental setup for AWAKE Run 2. The SPS proton
-        beam undergoes self-modulation in the first plasma section. The electron witness beam is injected into the
-        accelerating structure, and undergoes acceleration in the second plasma
-        section~\cite{berglyd_olsen:2015, adli:2016}}.
+    \caption{\label{Fig:AWAKER2} A simplified illustration of the experimental setup for AWAKE Run 2.
+The SPS proton beam undergoes self-modulation in the first plasma section.
+The electron witness beam is injected into the accelerating structure, and undergoes acceleration in the second plasma section~\cite{berglyd_olsen:2015, adli:2016}}.
 \end{figure}
 
-The energy carried by electron drive beams used in previous plasma wakefield experiments have been on the order of
-$100\unit{J}$ and the propagation length typically no more than $1\unit{m}$~\cite{blumenfeld:2007, caldwell:2009}.
-For high-energy physics application a higher total beam energy is often desired. For instance, the energy of a
-high-charge electron beam accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be
-produced by the International Linear Collider, is $1.6\unit{kJ}$. Using electron beams as drivers, a large number of
-plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated beam. However, staging plasma
-accelerators without reducing the effective gradient and spoiling the beam quality is challenging
-\cite{steinke:2016, lindstrom:2016}.
+The energy carried by electron drive beams used in previous plasma wakefield experiments have been on the order of $100\unit{J}$ and the propagation length typically no more than $1\unit{m}$~\cite{blumenfeld:2007, caldwell:2009}.
+For high-energy physics application a higher total beam energy is often desired.
+For instance, the energy of a high-charge electron beam accelerated to $1\unit{TeV}$ with $1\nexp{10}$ electrons, similar to the beam that could be produced by the International Linear Collider, is $1.6\unit{kJ}$.
+Using electron beams as drivers, a large number of plasma stages is required to reach an energy of a $\unit{kJ}$ for the accelerated beam.
+However, staging plasma accelerators without reducing the effective gradient and spoiling the beam quality is challenging \cite{steinke:2016, lindstrom:2016}.
 
-Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS
-beam~\cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages. The SPS beam is orders of
-magnitude longer than the plasma wavelengths needed for such applications, and it does not drive a strong
-wake~\cite{gschwendtner:2016}. By letting the proton beam undergo self-modulation before injecting the witness beam into
-the accelerating structure, stronger wakefields are excited. The self-modulation is produced by the transverse fields
-generated by the beam acting upon itself, causing regions of the beam to rapidly defocus~\cite{kumar:2010}. The
-modulation frequency is close to that of the plasma electrons, and produces a train of short proton bunches along the
-beam axis with a surrounding halo of defocused particles. This train of bunches resonantly drives wakefields to large
-amplitudes.
+Proton beams available at CERN carry significantly more energy than available electron beams, $19\unit{kJ}$ for the SPS beam~\cite{gschwendtner:2016}, allowing for much longer plasma wakefield accelerator stages.
+The SPS beam is orders of magnitude longer than the plasma wavelengths needed for such applications, and it does not drive a strong wake~\cite{gschwendtner:2016}.
+By letting the proton beam undergo self-modulation before injecting the witness beam into the accelerating structure, stronger wakefields are excited.
+The self-modulation is produced by the transverse fields generated by the beam acting upon itself, causing regions of the beam to rapidly defocus~\cite{kumar:2010}.
+The modulation frequency is close to that of the plasma electrons, and produces a train of short proton bunches along the beam axis with a surrounding halo of defocused particles.
+This train of bunches resonantly drives wakefields to large amplitudes.
 
-AWAKE at CERN is a proof of concept proton beam driven plasma wakefield accelerator experiment
-\cite{awake_collaboration:2014}, currently in its first phase of operation. The experiment uses a $400\unit{GeV}$ proton
-beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of
-$7\nexp{14}\unit{cm}^{-3}$~\cite{gschwendtner:2016}. This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$
-and is matched to the transverse size of the proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$~\cite{lu:2005}, where
-$k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe} = 2\pi c/\omega_{pe}$, and
-$\omega_{pe} = \left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency.
+AWAKE at CERN is a proof of concept proton beam driven plasma wakefield accelerator experiment \cite{awake_collaboration:2014}, currently in its first phase of operation.
+The experiment uses a $400\unit{GeV}$ proton beam delivered by the SPS as its driver, and a single $10\unit{m}$ plasma stage with a nominal plasma density of $7\nexp{14}\unit{cm}^{-3}$~\cite{gschwendtner:2016}.
+This plasma density corresponds to $\lambda_{pe} = 1.26\unit{mm}$ and is matched to the transverse size of the proton beam such that $k_{pe}\sigma_{x,y,pb} = 1$~\cite{lu:2005}, where $k_{pe} = 2\pi/\lambda_{pe}$ is the plasma wave number, $\lambda_{pe} = 2\pi c/\omega_{pe}$, and $\omega_{pe} = \left(n_0e^2/m_e\epsilon_0\right)^{1/2}$ is the plasma electron angular frequency.
 
-The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam. The aim of the second
-phase, in 2018, is to sample the wakefield with a long electron beam ($\simeq\lambda_{pe}$). The study presented here
-has relevance for Run~2~\cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate
-acceleration of a short electron beam ($\ll\lambda_{pe}$) to high energy and with a minimal increase in emittance and
-absolute energy spread.
+The aim of the first phase of the experiment is to demonstrate self-modulation of the proton beam.
+The aim of the second phase, in 2018, is to sample the wakefield with a long electron beam ($\simeq\lambda_{pe}$).
+The study presented here has relevance for Run~2~\cite{adli:2016}, starting in 2021 after the LHC long shutdown 2, and aims to demonstrate acceleration of a short electron beam ($\ll\lambda_{pe}$) to high energy and with a minimal increase in emittance and absolute energy spread.
 
-The plans for AWAKE Run~2 propose to use two plasma sections, as illustrated in Fig.~\ref{Fig:AWAKER2}. The first
-section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the
-electron beam present. The electron witness beam is then injected into the modulated proton beam before section two
-where it undergoes acceleration. The self-modulated proton beam does not produce a fully non-linear wakefield, and
-therefore not all plasma electrons are evacuated from the plasma bubble. The result is that the focusing force does not
-increase linearly with radius and the accelerated beam emittance is not preserved.
+The plans for AWAKE Run~2 propose to use two plasma sections, as illustrated in Fig.~\ref{Fig:AWAKER2}.
+The first section of about $4\unit{m}$ is the self-modulation stage where the proton beam undergoes self-modulation without the electron beam present.
+The electron witness beam is then injected into the modulated proton beam before section two where it undergoes acceleration.
+The self-modulated proton beam does not produce a fully non-linear wakefield, and therefore not all plasma electrons are evacuated from the plasma bubble.
+The result is that the focusing force does not increase linearly with radius and the accelerated beam emittance is not preserved.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \section[\label{S:M}]{Method}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-The focus in this study is on the beam loading of the wakefields driven by the proton beam. Studies of self-modulated
-proton beams show that the beam evolves as it propagates through a uniform plasma~\cite{lotov:2011}, but small
-variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long
-distances~\cite{lotov:2011, lotov:2015, caldwell:2011}. To study the witness beam evolution in a stable wake,
-independent of the dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver. The proton
-beam parameters are chosen so that key features of the wake \textendash the plasma electron density in the wake and the
-longitudinal electric field \textendash are the same as in the wake of a self-modulated proton beam with AWAKE baseline
-parameters~\cite{gschwendtner:2016}. Both the proton beam and the witness beam have Gaussian longitudinal charge
-distribution and bi-Gaussian transverse charge distributions.
+The focus in this study is on the beam loading of the wakefields driven by the proton beam.
+Studies of self-modulated proton beams show that the beam evolves as it propagates through a uniform plasma~\cite{lotov:2011}, but small variations in the plasma profile the modulation, and thus the wakefields, may be stabilised over long distances~\cite{lotov:2011, lotov:2015, caldwell:2011}.
+To study the witness beam evolution in a stable wake, independent of the dynamics of the self-modulation, we use a single, non-evolving proton bunch as driver.
+The proton beam parameters are chosen so that key features of the wake \textendash the plasma electron density in the wake and the longitudinal electric field \textendash are the same as in the wake of a self-modulated proton beam with AWAKE baseline parameters~\cite{gschwendtner:2016}.
+Both the proton beam and the witness beam have Gaussian longitudinal charge distribution and bi-Gaussian transverse charge distributions.
 
-We have previously studied the beam loading in a proton beam wake using the full particle-in-cell (PIC) code
-OSIRIS~\cite{fonseca:2002} with 2D cylindrical-symmetric simulations. The studies~\cite{berglyd_olsen:2015,
-berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to
-creating a stable drive beam structure based on previous self-modulation studies. In order to study the witness beam
-emittance evolution we use the recently released open-source version of QuickPIC~\cite{huang:2006, an:2013}. QuickPIC is
-a fully relativistic 3D quasi-static PIC code. It does not suffer from the numerical Cherenkov effect that full PIC
-codes do~\cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation. All simulation
-results in this paper were obtained using QuickPIC open-source~\cite{quickpic:web}.
+We have previously studied the beam loading in a proton beam wake using the full particle-in-cell (PIC) code OSIRIS~\cite{fonseca:2002} with 2D cylindrical-symmetric simulations.
+The studies~\cite{berglyd_olsen:2015, berglyd_olsen:2016} primarily looked at beam loading, energy gain and energy spread, as well as different approaches to creating a stable drive beam structure based on previous self-modulation studies.
+In order to study the witness beam emittance evolution we use the recently released open-source version of QuickPIC~\cite{huang:2006, an:2013}.
+QuickPIC is a fully relativistic 3D quasi-static PIC code.
+It does not suffer from the numerical Cherenkov effect that full PIC codes do~\cite{godfrey:1974,lehe:2013}, making it a well suited tool to study emittance preservation.
+All simulation results in this paper were obtained using QuickPIC open-source~\cite{quickpic:web}.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/plasmaDenTWake}
-    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulation results showing the initial time step for the single proton
-        drive beam and witness beam setup. Plasma electron density is shown in grey with the drive beam (blue) and the
-        witness beam (red) superimposed. The line plot indicates the transverse wakefield gradient
-        $\textrm{d}W_{x}/\textrm{d}x$ where $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis. Beams move to
-        the left.}
+    \caption{\label{Fig:PlasmaDenTWake} QuickPIC simulation results showing the initial time step for the single proton drive beam and witness beam setup.
+Plasma electron density is shown in grey with the drive beam (blue) and the witness beam (red) superimposed.
+The line plot indicates the transverse wakefield gradient $\textrm{d}W_{x}/\textrm{d}x$ where $W_{x} = E_{x} - v_{b} B_{y}$, evaluated along the beam axis.
+Beams move to the left.}
 \end{figure}
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \subsection{Drive Beam Parameters}\label{S:M:Setup}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void
-of plasma electrons. When the SPS beam, containing $3\nexp{11}$ protons~\cite{gschwendtner:2016}, enters the second
-plasma section (Fig.~\ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$. The
-plasma electron density is only depleted to around $65\%$ of nominal value at the point where we inject the
-electron beam~\cite{awake_collaboration:2016}. The plasma electron density depletion and the peak field are replicated
-using a single bunch with $1.46\nexp{10}$ protons ($2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$
-($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$. The beam peak density is $0.83\cdot n_{0}$
-and results in a quasi-linear wake. To avoid transverse evolution of the proton driver, emulating the stable propagation
-of the self-modulated beam~\cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the
-equivalent proton bunch by increasing the particles mass by six orders of magnitude.
+The modulation process used in AWAKE does not reach the fully non-linear regime and thus does not produce a bubble void of plasma electrons.
+When the SPS beam, containing $3\nexp{11}$ protons~\cite{gschwendtner:2016}, enters the second plasma section (Fig.~\ref{Fig:AWAKER2}), the peak electric field is expected to be about $500\funit{MV}{m}$.
+The plasma electron density is only depleted to around $65\%$ of nominal value at the point where we inject the electron beam~\cite{awake_collaboration:2016}.
+The plasma electron density depletion and the peak field are replicated using a single bunch with $1.46\nexp{10}$ protons ($2.34\unit{nC}$), a length $\sigma_{z} = 40\unit{\mu m}$ ($7\unit{kA}$), and a transverse size $\sigma_{x,y,pb} = 200\unit{\mu m}$.
+The beam peak density is $0.83\cdot n_{0}$ and results in a quasi-linear wake.
+To avoid transverse evolution of the proton driver, emulating the stable propagation of the self-modulated beam~\cite{lotov:2011, lotov:2015, caldwell:2011}, we freeze the transverse evolution of the equivalent proton bunch by increasing the particles mass by six orders of magnitude.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \subsection{Witness Beam Parameters}\label{S:M:Setup}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-In order to prevent large amplitude oscillations of the witness beam particles, which may cause additional energy spread
-as well as emittance growth, we consider a witness beam matched to the plasma density. The matched beam transverse
-size~\cite{esarey:1996} is:
+In order to prevent large amplitude oscillations of the witness beam particles, which may cause additional energy spread as well as emittance growth, we consider a witness beam matched to the plasma density.
+The matched beam transverse size~\cite{esarey:1996} is:
 \begin{equation}
-    \sigma_{x,y,eb}=\left(\frac{2c^{2}\epsilon_{\mathrm{N}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}.
-    \label{EQ:Matched}
+    \sigma_{x,y,eb}=\left(\frac{2c^{2}\epsilon_{\mathrm{N}}^{2}m_{e}\varepsilon_{0}}{n_{pe}e^{2}\gamma}\right)^{1/4}. \label{EQ:Matched}
 \end{equation}
 
-We assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$. This emittance is possible to
-produce with a standard RF-injector, while at the same time yielding a sufficiently narrow beam.
+We assume an initial normalized emittance of $\epsilon_{\mathrm{N}} = 2\unit{\mu m}$.
+This emittance is possible to produce with a standard RF-injector, while at the same time yielding a sufficiently narrow beam.
 
-Beam loading by a short witness beam is sensitive to its position relative to the electric field~\cite{tzoufras:2009}
-as well as, at low energy, to its de-phasing with respect to the wakefields. To eliminate de-phasing of the witness
-beam, the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.
+Beam loading by a short witness beam is sensitive to its position relative to the electric field~\cite{tzoufras:2009} as well as, at low energy, to its de-phasing with respect to the wakefields.
+To eliminate de-phasing of the witness beam, the initial beam energy is set such that $\gamma_{eb} = \gamma_{pb} = 426.3$, giving an energy of $217\unit{MeV}$.
 A lower initial energy is likely to be sufficient for AWAKE Run~2 injection.
 
-Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared
-to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$. The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$ based
-on earlier beam loading studies~\cite{berglyd_olsen:2016}. The charge is adjusted to $100\unit{pC}$ for optimal beam
-loading, as discussed in the next section. We refer to the defined drive beam and witness beam parameter set as the
-\emph{base case}. Figure~\ref{Fig:PlasmaDenTWake} shows the two beams \textendash the proton beam in blue, the trailing
-electron beam in red, and the plasma electron density in grey \textendash from a QuickPIC simulation of the initial time
-step, for the base case parameters.
+Equation~(\ref{EQ:Matched}) yields a transverse size $\sigma_{x,y,eb}$ of $5.25\unit{\mu m}$, which is narrow compared to the drive beam $\sigma_{x,y,pb} = 200\unit{\mu m}$.
+The bunch length was set to $\sigma_{z} = 60\unit{\mu m}$ based on earlier beam loading studies~\cite{berglyd_olsen:2016}.
+The charge is adjusted to $100\unit{pC}$ for optimal beam loading, as discussed in the next section.
+We refer to the defined drive beam and witness beam parameter set as the \emph{base case}.
+Figure~\ref{Fig:PlasmaDenTWake} shows the two beams \textendash the proton beam in blue, the trailing electron beam in red, and the plasma electron density in grey \textendash from a QuickPIC simulation of the initial time step, for the base case parameters.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \subsection{Simulation parameters}\label{SIM}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-The relatively small size of the witness beam puts constraints on the transverse grid cell size and number in the
-simulations. We need a small size to resolve the narrow electron beam, and a large number of grid cells to resolve the
-much wider proton beam and its wakefields. We use a transverse grid cell size of $1.17\unit{\mu m}$, and of
-$2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section~\ref{S:BL}. The witness beam
-was simulated with $16.8\nexp{6}$ and the drive beam with $2.1\nexp{6}$ non-weighted particles, and the plasma electrons
-with $1024 \times 1024$ weighted particles per transverse slice.
+The relatively small size of the witness beam puts constraints on the transverse grid cell size and number in the simulations.
+We need a small size to resolve the narrow electron beam, and a large number of grid cells to resolve the much wider proton beam and its wakefields.
+We use a transverse grid cell size of $1.17\unit{\mu m}$, and of $2.34\unit{\mu m}$ for the longitudinal grid cells for the simulations presented in section~\ref{S:BL}.
+The witness beam was simulated with $16.8\nexp{6}$ and the drive beam with $2.1\nexp{6}$ non-weighted particles, and the plasma electrons with $1024 \times 1024$ weighted particles per transverse slice.
 
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamLoading}
-    \caption{\label{Fig:BeamLoading} Top plot: Unloaded longitudinal electric field with no witness beam
-        (dashed blue line) and loaded field (whole blue line) along the beam axis. The beam density along the axis for
-        both beams are shown in red.
-        Bottom plot: Plasma densities along the beam axis for a drive beam with no witness beam (dashed green line),
-        witness beam with no drive beam (dash-dotted green line), and both beams present (continuous green line).
-        The position in the simulation box $\xi = z - tc$, moving towards the left. The plots show the initial time
-        step.}
+    \caption{\label{Fig:BeamLoading} Top plot: Unloaded longitudinal electric field with no witness beam (dashed blue line) and loaded field (whole blue line) along the beam axis.
+The beam density along the axis for both beams are shown in red.
+Bottom plot: Plasma densities along the beam axis for a drive beam with no witness beam (dashed green line), witness beam with no drive beam (dash-dotted green line), and both beams present (continuous green line).
+The position in the simulation box $\xi = z - tc$, moving towards the left.
+The plots show the initial time step.}
 \end{figure}
@@
     \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamPhaseSpace}
-    \caption{\label{Fig:BeamPS} Longitudinal phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long
-        witness beam after $4\unit{m}$ of plasma. The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread
-        of $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
+    \caption{\label{Fig:BeamPS} Longitudinal phase space charge distribution of a $100\unit{pC}$, $60\unit{\mu m}$ long witness beam after $4\unit{m}$ of plasma.
+The mean momentum is $1.67\unit{GeV/c}$ with an RMS energy spread of $87\unit{MeV/c}$ ($5.2\%$) for the full beam.}
 \end{figure}
@@
     \includegraphics[width=0.495\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamEmittanceOffset}
-    \caption{\label{Fig:BeamEmitt} Beam density in blue along the beam axis for an on-axis beam with respect to the
-        drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x,eb} = 5.24\unit{\mu m}$ in
-        the x-plane \textendash at four different positions $z$ in the plasma stage. The red lines show a moving window
-        calculation of transverse normalised emittance. The moving window calculation uses longitudinal slices of
-        $l = 4\cdot\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$. Only slices with more than $100$ macro
-        particles have been included. The plasma density profile is included in green, and scaled up by a factor of
-        $100$ to be visible. These simulations were run with an LHC energy drive beam of $7\unit{TeV}$}
+    \caption{\label{Fig:BeamEmitt} Beam density in blue along the beam axis for an on-axis beam with respect to the drive beam axis (left), and an offset beam (right) with an offset of one $\sigma_{x,eb} = 5.24\unit{\mu m}$ in the x-plane \textendash at four different positions $z$ in the plasma stage.
+The red lines show a moving window calculation of transverse normalised emittance.
+The moving window calculation uses longitudinal slices of $l = 4\cdot\Delta\xi = 9.38\unit{\mu m}$ with a step of $\Delta\xi$.
+Only slices with more than $100$ macro particles have been included.
+The plasma density profile is included in green, and scaled up by a factor of $100$ to be visible.
+These simulations were run with an LHC energy drive beam of $7\unit{TeV}$}
 \end{figure*}
@@
     \includegraphics[width=\linewidth,trim={0mm 0mm 0mm 0mm},clip]{figures/beamFilamentationAll}
-    \caption{\label{Fig:BeamFilament} Plots \textbf{a} to \textbf{f} show the transverse phase space of the offset
-        electron beam at different plasma positions. Plot \textbf{g} shows the macro particle mean position, and plot
-        \textbf{h} their RMS spread. Plots \textbf{a}, \textbf{b} and \textbf{c}, as well as the blue lines in plots
-        \textbf{g} and \textbf{h} represent particles not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with
-        position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$. Plots \textbf{d}, \textbf{e} and \textbf{f}, and the red
-        lines in plots \textbf{g} and \textbf{h} represent particles in the ion column with position
-        $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
+    \caption{\label{Fig:BeamFilament} Plots \textbf{a} to \textbf{f} show the transverse phase space of the offset electron beam at different plasma positions.
+Plot \textbf{g} shows the macro particle mean position, and plot \textbf{h} their RMS spread.
+Plots \textbf{a}, \textbf{b} and \textbf{c}, as well as the blue lines in plots \textbf{g} and \textbf{h} represent particles not in the ion column (see Fig.~\ref{Fig:BeamEmitt}), with position $1.40\unit{\mu m} < \xi < 1.42\unit{\mu m}$.
+Plots \textbf{d}, \textbf{e} and \textbf{f}, and the red lines in plots \textbf{g} and \textbf{h} represent particles in the ion column with position $1.55\unit{\mu m} < \xi < 1.57\unit{\mu m}$.}
 \end{figure*}
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \section{Beam Loading}\label{S:BL}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-Figure~\ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step for the base case
-parameters. The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the
-electron beam present. With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear
-regime~\cite{rosenzweig:2010}. The dashed green line in the lower part of Fig.~\ref{Fig:BeamLoading} shows that the
-on-axis plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE
-Run~2~\cite{awake_collaboration:2016}.
+Figure~\ref{Fig:BeamLoading} shows the results of QuickPIC simulations of the initial time step for the base case parameters.
+The $E_{z}$-field generated by the proton drive beam is seen as the blue line, shown with and without the electron beam present.
+With a proton beam density $n_{pb} \simeq n_{0}$, the wakefields are in the quasi-linear regime~\cite{rosenzweig:2010}.
+The dashed green line in the lower part of Fig.~\ref{Fig:BeamLoading} shows that the on-axis plasma density has a depletion to $67\%$, close to what we see in full scale reference simulations for AWAKE Run~2~\cite{awake_collaboration:2016}.
 
-The witness beam generates its own wakefield that loads the $E_{z}$-field generated by the drive beam. With an ideally
-shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field
-is constant along the beam~\cite{katsouleas:1987, tzoufras:2009}. Gaussian beams, as assumed in these studies, cannot
-completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a
-tail in energy both at the front and the back of the beam, as illustrated in Fig.~\ref{Fig:BeamPS}. The bulk of the
-beam, however, sees a relatively flat field.
+The witness beam generates its own wakefield that loads the $E_{z}$-field generated by the drive beam.
+With an ideally shaped electron beam charge profile it is possible to optimally load the field in such a way that the accelerating field is constant along the beam~\cite{katsouleas:1987, tzoufras:2009}.
+Gaussian beams, as assumed in these studies, cannot completely flatten the electric field in the tails of the charge distribution, and our base case beam therefore has a tail in energy both at the front and the back of the beam, as illustrated in Fig.~\ref{Fig:BeamPS}.
+The bulk of the beam, however, sees a relatively flat field.
 
-The initial electron beam density is $n_{eb} \approx 35\cdot n_{0}$. This means that the witness beam's own wakefield
-is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons,
-resulting in the formation of a pure ion column (see Fig.~\ref{Fig:BeamLoading}, bottom). This ion column, as is well
-known~\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and
-therefore prevents emittance growth for this part of the beam. This bubble and the focusing force is shown for our base
-case in Fig.~\ref{Fig:PlasmaDenTWake}. The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis,
-corresponding to the matched field gradient.
+The initial electron beam density is $n_{eb} \approx 35\cdot n_{0}$.
+This means that the witness beam's own wakefield is in the fully non-linear regime, where the space charge force is sufficient to blow out all plasma electrons, resulting in the formation of a pure ion column (see Fig.~\ref{Fig:BeamLoading}, bottom).
+This ion column, as is well known~\cite{rosenzweig:1991}, provides a linear focusing force on the part the electron beam within the column, and therefore prevents emittance growth for this part of the beam.
+This bubble and the focusing force is shown for our base case in Fig.~\ref{Fig:PlasmaDenTWake}.
+The focusing field has a gradient of $20\unit{kT/m}$ near the beam axis, corresponding to the matched field gradient.
 
@@
         \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQuality}
-        \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
-            symbols, lines), as a function of initial beam charge, and relative energy spread of the accepted charge
-            (red symbols, dashed lines), after $4\unit{m}$ of plasma and with an initial emittance
-            $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$. These are shown for four different $\sigma_{z}$ from
-            $40\unit{\mu m}$ to $100\unit{\mu m}$. The detailed studies presented in beam loading section correspond to
-            the square marked lines at $100\unit{pC}$.}
+        \caption{\label{Fig:BeamQ} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue symbols, lines), as a function of initial beam charge, and relative energy spread of the accepted charge (red symbols, dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.
+These are shown for four different $\sigma_{z}$ from $40\unit{\mu m}$ to $100\unit{\mu m}$.
+The detailed studies presented in beam loading section correspond to the square marked lines at $100\unit{pC}$.}
     \end{minipage}\hfill
@@
         \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityAbs}
-        \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$ (blue symbols,
-            lines), as a function of initial beam charge, and final energy (red symbols, dashed lines), after
-            $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
+        \caption{\label{Fig:BeamQAbs} Witness beam charge with emittance preserved, $\widetilde{Q}$ (blue symbols, lines), as a function of initial beam charge, and final energy (red symbols, dashed lines), after $4\unit{m}$ of plasma and with an initial emittance $\epsilon_{\mathrm{N},0}=2\unit{\mu m}$.}
     \end{minipage}
@@
 
-Figure~\ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through
-$0$, $4$, $40$ and $100\unit{m}$ of plasma. We define emittance of a slice as preserved if the growth is less than
-$5\%$, and $\widetilde{Q}$ as the sum charge of the slices for which the emittance is preserved. Simulation results show
-that $\widetilde{Q}/Q = 73\%$ of the electron beam longitudinal slices retain their initial emittance after the
-propagation in the plasma. The total (projected) emittance of these slices combined is also preserved. Emittance growth
-mainly occurs in the first few metres, and no significant emittance growth is observed after this for propagation
-lengths up to $100\unit{m}$. The head of the beam does not benefit from the full ion column focusing, but since the
-proton beam creates a quasi-linear wake, the emittance of the head of the beam still stabilises after some time. For the
-$100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as
-de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
+Figure~\ref{Fig:BeamEmitt} shows the slice emittance along the beam for the base case, sampled after propagating through $0$, $4$, $40$ and $100\unit{m}$ of plasma.
+We define emittance of a slice as preserved if the growth is less than $5\%$, and $\widetilde{Q}$ as the sum charge of the slices for which the emittance is preserved.
+Simulation results show that $\widetilde{Q}/Q = 73\%$ of the electron beam longitudinal slices retain their initial emittance after the propagation in the plasma.
+The total (projected) emittance of these slices combined is also preserved.
+Emittance growth mainly occurs in the first few metres, and no significant emittance growth is observed after this for propagation lengths up to $100\unit{m}$.
+The head of the beam does not benefit from the full ion column focusing, but since the proton beam creates a quasi-linear wake, the emittance of the head of the beam still stabilises after some time.
+For the $100\unit{m}$ simulation, the drive beam energy was increased to $7\unit{TeV}$ (LHC energy) to prevent de-phasing, as de-phasing starts to become a significant effect for the SPS beam of $400\unit{GeV}$ after about $50\unit{m}$.
 
-So far we have considered a witness beam injected on the axis of the proton beam. We now briefly examine the case of
-injection of a witness beam with an offset with respect to the proton beam axis. Since the witness beam creates its own
-plasma bubble, the emittance of the part of the beam inside that bubble is not affected by small transverse offsets of
-the witness beam with respect to the proton beam axis. This is illustrated in Fig.~\ref{Fig:BeamEmitt}, right, for an
-electron beam offset of one $\sigma_{x,eb}$. Emittance preservation for small offsets is an added benefit of this
-accelerating regime, and may ease transverse injection tolerances. The head of the beam experiences a larger initial
-emittance growth than for the on-axis case (compare Fig.~\ref{Fig:BeamEmitt}, left, to Fig.~\ref{Fig:BeamEmitt}, right).
+So far we have considered a witness beam injected on the axis of the proton beam.
+We now briefly examine the case of injection of a witness beam with an offset with respect to the proton beam axis.
+Since the witness beam creates its own plasma bubble, the emittance of the part of the beam inside that bubble is not affected by small transverse offsets of the witness beam with respect to the proton beam axis.
+This is illustrated in Fig.~\ref{Fig:BeamEmitt}, right, for an electron beam offset of one $\sigma_{x,eb}$.
+Emittance preservation for small offsets is an added benefit of this accelerating regime, and may ease transverse injection tolerances.
+The head of the beam experiences a larger initial emittance growth than for the on-axis case (compare Fig.~\ref{Fig:BeamEmitt}, left, to Fig.~\ref{Fig:BeamEmitt}, right).
 However, also for the head of the beam the emittance growth ends after the first few metres.
-Figure~\ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and
-$2.5\unit{m}$, while Fig.~\ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam. The
-centroid oscillations of the head and the trailing part are shown in Fig.~\ref{Fig:BeamFilament}g. This effect of a
-transverse offset is greater for larger offsets as the beam oscillates around the axis of the drive beam wakefield.
+Figure~\ref{Fig:BeamFilament}a-c show the phase space of the head of the electron beam after $0$, $1.0$ and $2.5\unit{m}$, while Fig.~\ref{Fig:BeamFilament}d-f show the phase space of the trailing part of the beam.
+The centroid oscillations of the head and the trailing part are shown in Fig.~\ref{Fig:BeamFilament}g.
+This effect of a transverse offset is greater for larger offsets as the beam oscillates around the axis of the drive beam wakefield.
 
-The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by
-Eq.~\ref{EQ:Matched}; that is, evolves to stay matched. The on-axis density of the electron beam, as a result,
-increases as its gamma factor increases and its transverse size decreases. This effect can be seen in Fig.
-\ref{Fig:BeamFilament}h. This has the potential to cause overloading of the field. However, for the base case no
-significant overloading is observed. Parameters can also be chosen in order to minimise this effect by slightly
-underloading the wakefield at first, and let the high energy beam overload the wakefield at the end.
+The transverse beam size within the bubble, where normalised emittance is preserved, follows the evolution given by Eq.~\ref{EQ:Matched}; that is, evolves to stay matched.
+The on-axis density of the electron beam, as a result, increases as its gamma factor increases and its transverse size decreases.
+This effect can be seen in Fig.
+\ref{Fig:BeamFilament}h.
+This has the potential to cause overloading of the field.
+However, for the base case no significant overloading is observed.
+Parameters can also be chosen in order to minimise this effect by slightly underloading the wakefield at first, and let the high energy beam overload the wakefield at the end.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \section{Parameter Optimisation}\label{S:PO}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-The beam loading and blow out properties of the electron beam depend on a large number of parameters, including
-longitudinal profile, transverse profile, as well as relative phasing of the proton and the electron beams. We present a
-limited parameter study aimed to guide beam parameter choices for AWAKE Run~2. For an electron beam to be externally
-injected in AWAKE Run~2 (see Fig.~\ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy
-spread, maximise the charge to be accelerated, and minimise the emittance growth~\cite{adli:2016}. In addition, the
-beam length should be such that it is possible to generate and transport the beam using a compact electron
-injector~\cite{adli:2016}. We investigate the interdependence of these parameters in simulation by varying the electron
-beam length, its charge, and initial emittance. The results are quantified in terms of how much of the beam retains its
-initial emittance. For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$, and let the
-beams propagate through $4\unit{m}$ of plasma.
+The beam loading and blow out properties of the electron beam depend on a large number of parameters, including longitudinal profile, transverse profile, as well as relative phasing of the proton and the electron beams.
+We present a limited parameter study aimed to guide beam parameter choices for AWAKE Run~2.
+For an electron beam to be externally injected in AWAKE Run~2 (see Fig.~\ref{Fig:AWAKER2}) it is desired to maximise the energy gain, minimise the energy spread, maximise the charge to be accelerated, and minimise the emittance growth~\cite{adli:2016}.
+In addition, the beam length should be such that it is possible to generate and transport the beam using a compact electron injector~\cite{adli:2016}.
+We investigate the interdependence of these parameters in simulation by varying the electron beam length, its charge, and initial emittance.
+The results are quantified in terms of how much of the beam retains its initial emittance.
+For these parameter scans we used a transverse grid cell size of $2.34\unit{\mu m}$, and let the beams propagate through $4\unit{m}$ of plasma.
 
@@
         \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityEmittance}
-        \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
-            symbols, line), as a function of beam initial emittance (right), with relative energy spread of the accepted
-            charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
+        \caption{\label{Fig:BeamQEmit} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue symbols, line), as a function of beam initial emittance (right), with relative energy spread of the accepted charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
     \end{minipage}\hfill
@@
         \includegraphics[width=\linewidth,trim={2mm 0mm 2mm 0mm},clip]{figures/beamQualityOffset}
-        \caption{\label{Fig:BeamQOffset} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue
-            symbols, line), as a function of beam offset, with relative energy spread of the accepted charge (red
-            symbols, dashed line), after $4\unit{m}$ of plasma.}
+        \caption{\label{Fig:BeamQOffset} Ratio of witness beam charge with emittance preserved, $\widetilde{Q}/Q$ (blue symbols, line), as a function of beam offset, with relative energy spread of the accepted charge (red symbols, dashed line), after $4\unit{m}$ of plasma.}
     \end{minipage}
@@
 
-Figure~\ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge. An
-initial beam emittance of $2\unit{\mu m}$ was used. Therefore, we define the fractional charge $\widetilde{Q}$ as the
-charge whose emittance remains smaller than $2.1\unit{\mu m}$. The beam charge ranges from $10\unit{pC}$ to
-$300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$. As can be seen from Fig.
-\ref{Fig:BeamQ} (red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum
-energy spread with an initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively. Lower beam
-charges tend to underload the electric field, while higher beam charges tend to overload it. It is also clear that
-longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the
-wake, thus producing a larger spread in energy. The blue curves show the fraction of charge whose initial emittance is
-preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}). As the witness beam charge
-increases, the fraction of slices with preserved emittance increases \textendash as expected from an earlier onset of
-the bubble formation \textendash and also increases in the bubble size~\cite{lu:2006-1, lu:2006}. We note here that
-operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the
-expense of an increase of relative energy spread by a factor of two.
+Figure~\ref{Fig:BeamQ} shows the dependence of charge and energy spread on witness beam length and incoming charge.
+An initial beam emittance of $2\unit{\mu m}$ was used.
+Therefore, we define the fractional charge $\widetilde{Q}$ as the charge whose emittance remains smaller than $2.1\unit{\mu m}$.
+The beam charge ranges from $10\unit{pC}$ to $300\unit{pC}$, and $\sigma_{z}$ ranges from $40\unit{\mu m}$ to $100\unit{\mu m}$.
+As can be seen from Fig.~\ref{Fig:BeamQ} (red curves), both the $40\unit{\mu m}$ and the $60\unit{\mu m}$ beams have a well defined minimum energy spread with an initial beam charge $\approx 50\unit{pC}$ and $\approx 100\unit{pC}$, respectively.
+Lower beam charges tend to underload the electric field, while higher beam charges tend to overload it.
+It is also clear that longer beams with respect to the accelerating phase of the field, $\approx\lambda_{pe}/4$, do not optimally load the wake, thus producing a larger spread in energy.
+The blue curves show the fraction of charge whose initial emittance is preserved (the slice emittance for the base case is shown in Fig.~\ref{Fig:BeamEmitt}).
+As the witness beam charge increases, the fraction of slices with preserved emittance increases \textendash as expected from an earlier onset of the bubble formation \textendash and also increases in the bubble size~\cite{lu:2006-1, lu:2006}.
+We note here that operation with $100\unit{pC}$ leads to a significantly larger charge (factor $\sim 4$) with emittance preserved, at the expense of an increase of relative energy spread by a factor of two.
 
-Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves). The blue
-curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of
-beam length and beam charge. The results are weakly dependent on the electron beam length. As expected, a larger value
-of $\widetilde{Q}$ corresponds to a lesser energy gain. No optimum is observed.
+Figure~\ref{Fig:BeamQAbs} shows the dependence of mean energy gain on beam length and beam charge (red curves).
+The blue curves show the amount of charge in the longitudinal slices where the emittance has been preserved, as a function of beam length and beam charge.
+The results are weakly dependent on the electron beam length.
+As expected, a larger value of $\widetilde{Q}$ corresponds to a lesser energy gain.
+No optimum is observed.
 
-Figure~\ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam
-emittance. In these simulations we adjusted the witness beam radius to maintain the matching condition at each
-emittance. The smaller the initial emittance is, the better the emittance is preserved. There are two effects that lead
-to emittance growth for high initial emittance beams: the transverse beam size may increase beyond the size of the
-bubble, and the beam density may be reduced so much that the plasma electrons are no longer fully evacuated from the
-bubble. Emittance values higher than a few micrometres lead to a significant increase in both emittance and energy
-spread.
+Figure~\ref{Fig:BeamQEmit} shows how the growth in emittance and energy spread varies with initial electron beam emittance.
+In these simulations we adjusted the witness beam radius to maintain the matching condition at each emittance.
+The smaller the initial emittance is, the better the emittance is preserved.
+There are two effects that lead to emittance growth for high initial emittance beams: the transverse beam size may increase beyond the size of the bubble, and the beam density may be reduced so much that the plasma electrons are no longer fully evacuated from the bubble.
+Emittance values higher than a few micrometres lead to a significant increase in both emittance and energy spread.
 
-Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x,eb}$,
-but with a reduction of the fraction of the beam which retains its initial emittance. Figure~\ref{Fig:BeamQOffset} shows
-the correlation between this ratio for a range of offsets up to $16.8\unit{\mu m}$, corresponding to
-$3.2\cdot\sigma_{x,eb}$. The effect on the head of the beam, shown in Figs.~\ref{Fig:BeamEmitt}
-and~\ref{Fig:BeamFilament}, increases with larger offsets causing the part of the beam being defocused to extend
-backwards to the point where the witness beam wakefields are no longer in the blow-out regime. At around
-$3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
+Our base case showed some robustness to a small offset from the proton beam axis on the order of one $\sigma_{x,eb}$, but with a reduction of the fraction of the beam which retains its initial emittance.
+Figure~\ref{Fig:BeamQOffset} shows the correlation between this ratio for a range of offsets up to $16.8\unit{\mu m}$, corresponding to $3.2\cdot\sigma_{x,eb}$.
+The effect on the head of the beam, shown in Figs.~\ref{Fig:BeamEmitt} and~\ref{Fig:BeamFilament}, increases with larger offsets causing the part of the beam being defocused to extend backwards to the point where the witness beam wakefields are no longer in the blow-out regime.
+At around $3\cdot\sigma_{x,eb}$ emittance is no longer preserved at all.
 
 % EA: slight rewrite to argue what we want with this section
-The optimal working point will depend on the application and must be studied for each case and is, as illustrated in
-this section, a trade off between beam length, beam charge and emittance preservation, as well as other parameters
-like the plasma density.
+The optimal working point will depend on the application and must be studied for each case and is, as illustrated in this section, a trade off between beam length, beam charge and emittance preservation, as well as other parameters like the plasma density.
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \section{Conclusion}\label{S:C}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-We have devised a method to accelerate an electron witness beam to high energy with a low relative energy spread while
-maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
-This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by
-self-modulation of a long proton beam. This method is in principle applicable to all experiments operating in the
-quasi-linear regime. Low relative energy spread and emittance preservation are achieved by choosing the electron beam
-parameters to load the wakefields and evacuate the remaining plasma electrons from the accelerating structure.
+We have devised a method to accelerate an electron witness beam to high energy with a low relative energy spread while maintaining its incoming emittance in wakefields such that the accelerating structure is not void of plasma electrons.
+This is the case for the AWAKE experiment in which the wakefields are driven by a train of proton bunches produce by self-modulation of a long proton beam.
+This method is in principle applicable to all experiments operating in the quasi-linear regime.
+Low relative energy spread and emittance preservation are achieved by choosing the electron beam parameters to load the wakefields and evacuate the remaining plasma electrons from the accelerating structure.
 
-Parameter studies indicate that for up to a few $100\unit{pC}$, about $70\%$ of the incoming beam charge is accelerated
-for beam of lengths of $40-60\unit{\mu m}$. Such electron beams may be generated by an injector based on a standard
-RF photo-emission gun~\cite{doebert:corr}.
+Parameter studies indicate that for up to a few $100\unit{pC}$, about $70\%$ of the incoming beam charge is accelerated for beam of lengths of $40-60\unit{\mu m}$.
+Such electron beams may be generated by an injector based on a standard RF photo-emission gun~\cite{doebert:corr}.
 
-In order to use manageable computer time for simulations, this study assumes a simplified case with respect to a
-self-modulated proton beam, where the wake is driven by a single, short proton bunch producing similar wakefields.
+In order to use manageable computer time for simulations, this study assumes a simplified case with respect to a self-modulated proton beam, where the wake is driven by a single, short proton bunch producing similar wakefields.
 However, the wakefields driven by a train of bunches evolve with the ramp of a real plasma and when entering the plasma.
-Therefore, to be fully applicable to an experiment such as AWAKE, the study will have to be redone with more realistic
-parameters. However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated
-beam with low relative energy spread and emittance remains applicable.
+Therefore, to be fully applicable to an experiment such as AWAKE, the study will have to be redone with more realistic parameters.
+However, using loading of the wakefields and the pure plasma ion column fields to produce an accelerated beam with low relative energy spread and emittance remains applicable.
 
+% ************************************************************************************************ %
 \section{Acknowledgements}\label{Ack}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 
-The simulations for this study have been performed using the open source version of QuickPIC released in early 2017
-and owned by UCLA.
+The simulations for this study have been performed using the open source version of QuickPIC released in early 2017 and owned by UCLA.
 
 These numerical simulations have been made possible through access to the \emph{Abel} computing cluster in Oslo, Norway.
-Abel is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the
-University of Oslo, the University of Troms{\o} and the Norwegian University of Science and Technology. Project code:
-nn9303k. Some of the simulations were also run on the student-maintained computing cluster \emph{Smaug} at the
-University of Oslo, Department of Physics.
+Abel is maintained by UNINETT Sigma2 AS and financed by the Research Council of Norway, the University of Bergen, the University of Oslo, the University of Troms{\o} and the Norwegian University of Science and Technology.
+Project code: nn9303k.
+Some of the simulations were also run on the student-maintained computing cluster \emph{Smaug} at the University of Oslo, Department of Physics.
 
@@
 
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
 \bibliography{Bibliography,Additional}
 \end{document}
-% ******************************************************************************************************************** %
+% ************************************************************************************************ %
